### 2018-09-16 tex/exemplo.tex
Multiple improvements.

\documentclass[sigconf]{acmart}
\settopmatter{printacmref=false} % Removes citation information below abstract
\renewcommand\footnotetextcopyrightpermission[1]{} % removes footnote with conference information in first column
\pagestyle{plain} % removes running headers
\setcopyright{none}

\usepackage{booktabs} % For formal tables
\usepackage[ruled]{algorithm2e} % For algorithms
\renewcommand{\algorithmcfname}{ALGORITHM}
\SetAlFnt{\small}
\SetAlCapFnt{\small}
\SetAlCapNameFnt{\small}
\SetAlCapHSkip{0pt}
\IncMargin{-\parindent}

\usepackage[latin1]{inputenc}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amsfonts}

\DeclareMathOperator*{\argmax}{argmax}

\begin{document}

\title{Named Entity Recognition on HTML as an information extraction subtask}

\author{João Mateus de Freitas Veneroso}
\affiliation{%
  \institution{Universidade Federal de Minas Gerais}
  \streetaddress{Av. Pres. Antônio Carlos, 6627 - Pampulha}
  \city{Belo Horizonte}
  \state{MG}
  \postcode{31270-901}
  \country{Brazil}}
\email{jmfveneroso@gmail.com}

\author{Berthier Ribeiro-Neto}
\affiliation{%
  \institution{Universidade Federal de Minas Gerais}
  \streetaddress{Av. Pres. Antônio Carlos, 6627 - Pampulha}
  \city{Belo Horizonte}
  \state{MG}
  \postcode{31270-901}
  \country{Brazil}}
\email{berthier.dcc.ufmg@gmail.com}

\begin{abstract}

Reliable researcher affiliation data is necessary to allow enquiring
about international research group productivity and publication patterns.
Public bibliographic databases such as DBLP and Google Scholar hold
invaluable data about the academic environment. However, the researcher
affiliation information is frequently missing or outdated.
We propose a statistical data extraction method to acquire affiliation 
information directly from university websites and solve the name extraction
task in general.
Previous approaches to web data extraction either lack in flexibility,
because wrappers do not generalize well on cross website tasks, or 
they lack in precision, because domain agnostic methods neglect 
useful properties of this particular application domain.
Our statistical approach solves the name extraction task with 
a framework that incorporates both textual and structural features to
yield an outstanding tradeoff between generality and precision. 
We conducted experiments over a collection of 152 faculty 
web pages in multiple languages from universities in 49 countries
and obtained 94.40\% precision, 97.61\% recall and 0.9597 F-measure at
the extraction task.

\end{abstract}

% \keywords{Named entity recognition, information extraction, web data extraction}

\maketitle

% ==========================================
% Beginning of text.                       |
% ==========================================

\section{Introduction}

Web information extraction is the task of automatically extracting structured information
from unstructured or semi-structured web documents. The input usually consists of
web documents containing a number of predetermined entities organized in a similar 
manner and the information extraction task consists of identifying these entities
and organizing them according to a template. In this context, named entity recognition
(NER) is a subtask that aims to detect named entities in the text and classify them into 
predetermined categories such as person names, locations or organizations. Once we are able
to reliably detect the relevant entities, we may employ an information extraction 
algorithm to extract structured data. In this paper, we investigate different NER 
approaches from the perspective of web information extraction.

HTML documents most often lie in between the structured / unstructured data paradigm, 
which means that authors take quite a casual approach regarding formal structure. 
However, DOM hierarchy, element disposition, class names, and other features related to 
the document structure and indirectly associated with the data itself can be valuable 
information in the task of identifying entities and determining relationships. Yet we 
cannot expect these features to be completely constrained by an underlying pattern. 
Organization patterns tend to follow some guidelines but are in no way subject to 
strict rules. That is why classical information extraction systems such as automatic
wrapper generators usually do not translate well across different websites. Contrastingly, 
statistical based approaches can be much more flexible.

NER systems are frequently trained and tested on news corpora such as the 
dataset introduced at the Language-Independent Named Entity Recognition Shared Task
at CONLL-2003 \cite{Sang2003}. State-of-the-art approaches have recently achieved 
F1-scores of 90.10 \cite{Huang2015}, 90.94 \cite{Lample2016}, and 91.21 \cite{Ma2016} 
in this task using different combinations of bidirectional LSTM layers, word and 
character representations.

NER on HTML poses a different type of challenge, because web pages are often
very different from the plain text found in news corpora. Named entities may be present 
inside tables, lists, graphs or other types of visual elements that provide
little to no contextual information that could give hints about the semantic category of 
a word. Systems trained on news or similar corpora do not translate well to the web
NER task without requiring some sort of retraining, since in this task we cannot profit
as much from contextual hints or transfer learning approaches such as word embeddings.
Besides, deep learning approaches can require a lot of data to reach peak performance. 
Therefore, in cases where there is little labeled data, we find that generative approaches 
may work better.

To test different NER approaches from the perspective of web information extraction,
we will explore the task of person names extraction from university faculty websites.
Researcher affiliation is often missing from many entries in public databases such as DBLP  
\footnote{
  http://dblp.uni-trier.de/
} and the display of information varies significantly between different university 
websites, so this task can provide a good measure of the expected performance and
data need for other web information extraction tasks. Also, with the lack of a large amount
of training data, we show that feature engineering and resources such as a gazetteer 
may be invaluable.

% \begin{figure}
%   \centering
%   \includegraphics[width=0.5\textwidth]{pics/jap_osaka_lab}
%   \caption{Example of a faculty directory}
%   \label{fig:faculty_directory}
% \end{figure}
% 
% To acknowledge the complexity of this extraction task, take for example a snippet of 
% the staff page for the intelligent robotics laboratory from Osaka University shown in figure 
% \ref{fig:faculty_directory}. There is some structure to the way member profiles are arranged, 
% but the organization is rather flexible, also note that there is little text to contextualize
% each named entity.

\section{Related Work}

In the last 20 years, the astonishing growth of public information in the web has 
led to the development of a number of different approaches to the problem of web 
information extraction. Traditionally, the task was solved by designing special purpose
programs called wrappers to recognize relevant data and store records in a structured
format. These early tools varied wildly relative to their degree of automation.

It was readily perceived that manual wrapper generation was a rather tedious and
error prone process, unsuited for large scale operations. Wrappers tend to
break frequently because they rely heavily on web page features that can change 
often. So, in the late nineties, several authors advocated for wrapper induction, a technique 
that consists of automatically constructing wrappers from a small set of examples by 
identifying delimiters or context tokens that single out the desired attributes. 
Some remarkable wrapper induction methods are WIEN \cite{Kushmerick2000}, Soft 
Mealy \cite{Hsu1998} and STALKER \cite{Muslea1999}.

Despite being better than constructing wrappers manually, wrapper induction methods 
still suffered from a lack of expressive power and flexibility. These methods had 
trouble handling records with missing attributes or unusual structures because
patterns could only be identified if they happened at least once in the examples.

Other approaches such as NoDoSE (\cite{Adelberg1998}) and Debye (\cite{Laender2002a}) 
brought greater flexibility to wrapper induction methods by requiring a greater level 
of human interaction through graphical user interfaces. Web data extraction techniques often 
require some sort of assistance from human experts to boost accuracy. One of the main challenges 
in the field lies in determining an adequate tradeoff between the degree of automation and 
the precision and recall of the data extraction tool.

To automate the task of web data extraction completely some approaches,
such as Road Runner \cite{Crescenzi2001}, removed entirely the need for data examples.
Road Runner parses documents belonging to a same class (e.g. books on Amazon) and 
generates wrappers based on their similarities and differences, yielding comparable results 
to those obtained by wrapper induction methods. However like previous approaches, it was 
unsuited for cross site extraction tasks because the learned rules were not general enough.

NLP based approaches aimed at extracting more general rules that could possibly
be employed over multiple websites. RAPIER \cite{Califf1999} is a method of rule
extraction that uses information such as part-of-speech tags and semantic classes from
a lexicon to derive patterns from a set of training examples. This approach is more
flexible than the wrapper induction methods, however it achieves much lower rates of 
recall and precision.

In 2002, a survey by Laender et al. \cite{Laender2002} made a thorough classification of the
early approaches with a taxonomy based on their main technology, being them: languages for
wrapper development, HTML-aware tools, NLP-based tools, Wrapper Induction Tools,
Modeling-based tools and Ontology-based tools. Some noteworthy examples from this era
are:

\begin{itemize}
\item TSIMMIS \cite{Hammer1997} and WebOQL \cite{Arocena1999}, which are special purpose 
languages for building wrappers.

\item Road Runner \cite{Crescenzi2001}, XWRAP \cite{Liu2000} and W4F \cite{Sahuguet1999}, 
which are HTML-aware tools that infer meaningful patterns from the HTML structure.

\item RAPIER \cite{Califf1999}, SRV \cite{Freitag1998}, WHISK \cite{Soderland1999}, which 
are NLP-based tools.

\item WIEN \cite{Kushmerick2000}, Soft Mealy \cite{Hsu1998} and STALKER \cite{Muslea1999} which 
are wrapper induction methods.

\item NoDoSE \cite{Adelberg1998} and Debye \cite{Laender2002a}, which are semi supervised modeling
based tools that require some interaction with the user by means of a graphical
user interface.
\end{itemize}

In 2006, Chang et al. \cite{Chang2006} complemented the previous surveys with semisupervised 
technologies such as Thresher \cite{Hogue2005}, IEPAD \cite{Chang2001} and 
OLERA \cite{Chang2004}. They differed from supervised 
and unsupervised methods because they either needed only a rough description of
data from users for extraction rule generation or some level of post processing
that needed user attention. The survey also mentioned newer unsupervised methods
such as DeLa \cite{Wang2003}, Exalg \cite{Arasu2003} and Depta \cite{Zhai2005}.

Most of the early information extraction systems were rule-based with either 
manual rule description or automatic rule learning from examples, thus they
suffered from a lack of flexibility when dealing with noisy and unstructured data.
Huge progress in the field of statistical learning led to the development of
statistical models that tried to solve this problem.

In 2008, Sarawagi \cite{Sarawagi2008} produced a survey that classified wrappers in
rule-based methods, statistical methods and hybrid models, bringing together 
the fields of named entity recognition, relationship 
extraction and information extraction. The rule based methods encompass most of the 
previous models. The statistical methods convert the extraction task into a token labeling 
task, identifying the target entities through the assignment of labels as in a typical 
Named Entity Recognition task. Traditionally, Hidden Markov Models, Linear Chain Conditional 
Random Fields \cite{Lafferty2001}, and Maximum Entropy Taggers have been the usual choice 
for linear sequence tagging models.

More recently, with the advancement in Natural Language Processing and Deep Learning, 
neural models outperformed previous NER methods. Using a bidirectional Long Short-Term
Memory (LSTM) model with a Conditional Random Field (CRF) output layer, \cite{Huang2015} 
obtained 90.10 F1 score on the CoNLL 2003 corpus for named entity recognition. A similar model
by \cite{Lample2016} incorporates a Convolutional Neural Network over character embeddings
as an input to the bidirectional LSTM reaching an F-score of 90.94 at the same task. Finally, 
\cite{Ma2016} constructed word representations with the hidden layer of a bidirectional 
LSTM obtaining an F-score of 91.21. The latter two models make use of orthographic and 
morphological evidence to detect named entities, making the models less reliant on feature
engineering and surrounding words. Up to our knowledge, these models still have not been
employed at the web information extraction task.

Surveys by Ferrara et al. \cite{Ferrara2014} and Schulz et al. \cite{Schulz2016} 
updated the previous surveys on information extraction methods with some interesting innovations. 
Some examples are: the Visual Box Model \cite{Krupl2005}, a data extraction system that produces 
a visualization of the web page to exploit visual cues to identify data presented in a tabular form;
automatic wrapper adaptation \cite{Ferrara2011}, a technique that tries to reduce the cost of 
wrapper maintenance by measuring the similarity of HTML trees and adapting
wrappers to the new page structure; AutoRM \cite{Shi2015}, a method to mine
records from a single web page by identifying similar data regions through DOM
tree analysis; and Knowledge Vault \cite{Dong2014}, a method that combines different 
extraction approaches to feed a probabilistic knowledge base.

In 2016, Varlamov et al. \cite{Varlamov2016} argued that the degree of automation can no
longer be the main classification criterion for the data extraction systems
because unsupervised methods which were widely considered to be the state 
of the art when dealing with individual websites performed poorly or were
innapropriate on cross site extraction tasks. The authors proposed a 
classification of methods by the extent of their application. 
The competing approaches were separated into two groups: methods for individual 
websites and methods that are applicable to whole application domains.

The first group contains most of the earlier approaches, including the supervised
approaches: SRV \cite{Freitag1998}, RAPIER \cite{Califf1999}, WHISK \cite{Soderland1999}, 
WIEN \cite{Kushmerick2000} SoftMealy \cite{Hsu1998} and STALKER \cite{Muslea1999}; and
the unsupervised approaches: RoadRunner \cite{Crescenzi2001} and EXALG \cite{Arasu2003}.

The second group is divided between domain specific methods and domain agnostic methods.
Domain specific methods are designed for extracting data about a particular 
application domain across multiple websites.
Domain specific methods integrate information about the particular application domain in the 
course of its development and thus are able to achieve superior performance in
comparison to domain agnostic methods. One example is the method of comment extraction 
from blog posts described by Kao et al. \cite{Kao2010}.

Domain agnostic methods are the most general extraction methods. They can extract
information from any application domain from multiple websites. They pose the hardest
challenge because the tool must infer data relevance without any prior training in
that particular application domain. Some examples are: ODE (\cite{Su2009}), ObjectRunner 
(\cite{Abdessalem2010}), and AMBER (\cite{Furche2012}). These approaches are more flexible but 
yield worse results than domain specific methods.

In this paper, we are exploring NLP based approaches to solve a domain specific problem.

\section{NER Models}

We explored multiple approaches to the Named Entity Recognition problem in the context 
of a web information extraction task.

\subsection{Hidden Markov Model}

A Markov Model is a stochastic model that computes the most probable
sequence of states given a set of observable states $ \S = \{s_1, s_2, ..., s_n \} $.
The Hidden Markov Model (HMM) differs from the Markov Model in that it
does not observe the states directly, but rather a probabilistic function of those 
states. For example in NER, the words are observed, however the Named Entity labels
associated with these words are not. Formally, we want to compute the most probable
sequence of labels $ Y = {y_1, y_2, ..., y_n} $ for a sequence of observed tokens
$ X = {x_1, x_2, ..., x_n} $.

\[

Y = argmax P(Y|X)

\]

Using Bayes theorem:

\[

P(Y|X) = \frac{P(X|Y) P(Y)}{P(X)}

\]

Since $ P(X) $ is the same for all labels sequences, we can simply maximize:

\[

Y = P(X|Y) P(Y)

\]

A Hidden Markov tagger makes two assumptions. First, the 
probability of being in a given state depends only on a fixed number of previous states.
That is $ P(y_i|y_{i-1}x_{i-1}, y_{i-2}x_{i-2}, ..., y_1x_1) = P(y_i|y_{i-1}, y_{i-2},..., y_{i-k}) $. In fact, 
we can get much better results at the NER on HTML task by looking at trigrams
or quadrigrams instead of bigrams as in a regular Markov Model. Some 
label assignments are highly improbable, such as single token named entities separated 
by an Other label, and these kinds of patterns can be caught by a higher order Hidden
Markov Model. Second, the probability of a word depends only on its assigned label 
$ P(x_i|y_{i-1}x_{i-1}, ..., y_1x_1) = P(x_i|y_i) $. Finally, the probability 
$ P(Y|X) $ can be computed with the expression:

\[

P(Y|X) = \prod P(y_i|y_{i-1}, y_{i-2}, ..., y_{i-k}) P(x_i|y_i)

\]

The probabilities can be calculated via maximum likelihood estimation from the relative
frequency of labels and words in the corpus. The best sequence of labels can be computed 
with the Viterbi algorithm. However,
as we increase the order of the Markov Model ($k$ in Equation 1) this computation becomes 
exponentially more expensive. The beam-search strategy may be employed for a faster search,
but we found that for $ k \leq 3 $, the Viterbi algorithm is still viable.

Hidden Markov Models taggers have been succesfully apllied in many NLP tasks and they are 
incredibly fast to train, making them a good choice for a first approximation. However, these
models are highly dependent on the right selections of features, what may outweigh the 
benefit of a small training cost.

\subsubsection{Self training}

\subsection{Linear Chain Conditional Random Fields}

A Linear Chain Conditional Random Field (CRF) is the discriminative analog to the HMM.
It is a distribution $ P(Y|X) $ that takes the form:

\[

P(Y|X) = \frac{1}{Z(x)}\prod exp \left{ \sum_{k=1}^{K} \theta_k f_k(y_{t-1}, y_t, x_t) \right}

\]

where $ \theta $ is the parameter vector that we are going to learn, $ f_k(y_{t-1}, y_{t}, x_t) $ 
is a feature function over the current and previous timesteps and the current word $ x_t $, and
$ Z(x) $ is a partition function that depends on the input. Linear chain conditional random fields
are more general than Hidden Markov Models because the transition from $ y_{t-1} $ to $ y_{t} $ can
depend on the current observation $ x_t $. In fact, linear chain CRFs do not assume independence 
between the input variables $ x $.

Linear Chain CRFs are a natural fit to Named Entity Recognition problems because of the
high label dependency. Therefore, sequence taggers that do not take this output dependency into
account tend to perform poorly. More recently, CRFs have been employed as the output layer
in neural models to account for the label dependency, producing significant improvement over
models that output labels independently.

Label sequences can be decoded with the Viterbi algorithm like HMMs.

\subsection{Neural Models}

Recurrent neural networks (RNN) have been succesfully employed on numerous NLP tasks such as
language modelling, POS tagging, speech recognition and NER. Different
from feedforward neural networks, RNNs can retain information in their internal state,
making them more suitable for processing sequences, and consequently for solving text related
tasks. In NER, the network outputs one label for each input vector. Although RNNs are theoretically 
capable of learning long term dependencies, in practice 
it might be difficult, as shown by \cite{Hochreiter1991}. Long short term memory networks
(LSTM) were introduced \cite{Hochreiter1997} with this problem in mind and have been popularized
since them. The LSTM cell has has the following definition:

\[
\Gamma_f = \sigma(W_f[a])
\]

\[
\]

In NER related tasks, both past and future input features are important when deciding the
label at time $ t $, thus we may employ a bidirectional LSTM (Graves et al., 2013). to 
account for this fact. Bidirectional LSTMs are simply two separate LSTM networks where
the first one receives the backward states and the second is fed in reverse order 
with the forward states XXXX. The hidden layers of both networks are combined and fed to 
the output layer.

\cite{Huang2015} proposed a bidirectional LSTM with a CRF layer (LSTM-CRF) on the output to tackle
the sequence tagging problem. The CRF layer jointly decodes labels for the whole sentence instead
of predicting each label individually. This architecture achieved an F1 score of 90.10 in the 
ConL2003 dataset, in contrast to 85.17 for a bidirectional LSTM without the CRF layer. 
In our experiments, the LSTM-CRF architecture used a bidirectional LSTM with 100 
hidden states, no peepholes and an input and output dropout layers with a dropout
rate of 0.5. The dropout layers have proved to be very important to prevent overfitting 
and allow better generalization.

Ma and Hovy \cite{Ma2016} proposed adding a convolutional neural networks (CNN) layer 
on top of a bidirectional LSTM-CRF to encode character-level information in its 
character-level representation. Those character
representations are combined with word level representations and then fed to the
Bidirectional LSTM. This architecture possesses the capacity to learn morphological
token features that are extremely useful on the NER task, since similar named entities 
often present morphological similarities. This improvement obtained an F1 score of 
91.21 at the ConLL2003 dataset. In our experiments, the LSTM-CRF architecture with
CNN character representations used a one dimensional convolutional neural network with 30 
filters and a window size of three characters on top of the LSTM-CRF architecture,
the character embeddings fed to the CNN had 30 dimensions and were randomly initialized.

\cite{Lample2016} suggested using an a bidirectional LSTM to model character-level 
representations on a bidirectional LSTM-CRF. Combining both the forward and backward 
LSTM representations forming the complete character representation that is also combined 
with a word
representation as in the previous model. The forward LSTM is expected to be a better
representation of the suffix of a token, and the backward LSTM is expected to be a
better representation of the prefix of a token. This differentiates this architecture
from the CNN based approach, because CNN filters discover positional invariant
features while LSTMs can better represent suffixes and prefixes. In our experiments, 
the LSTM-CRF architecture with LSTM character embeddings used a bidirectional LSTM
with 25 hidden states, thus producing character representations with 50 dimensions.

All neural models used GloVe 100-dimensional word embeddings \cite{Pennington2014}
that were fine tuned during training. The models were trained with Stochastic Gradient 
Descent over 50 epochs using a learning rate of 0.01 and momentum 0.9.

Early stopping like cite.

Word embeddings are like a gazetteer.

\\\\\\ Make graphical explanation of model differences. \\\\\\\\\\\\\

\section{Dataset}

We constructed a novel dataset to evaluate the performance of multiple NER models
at the web information extraction task. The task consists of finding researcher
names in faculty directory web pages. This would be the 
first step in linking researcher profiles from university websites to their entries
in public databases such as DBLP \footnote{http://dblp.uni-trier.de/}. Unlike many
information extraction tasks, each web page in the dataset comes from a different 
university, and therefore has a different format, what makes many information
extraction systems impractical. The idea is to construct a system that is general 
enough to allow efficient name extraction from many different sources without requiring
any supervision between different websites. This task would be similar to the task of 
extracting comments from different news sources, in which we must recognize author 
names in different formattings before infering structure and extracting the structured 
tuple author, timestamp, comment, likes. Another similar example would be acquiring 
author information from different publishing platforms before extracting structured 
information in the format author, article, timestamp. Of course, similar systems
could be used to recognize different named entities in other contexts.

We collected 145 computer science faculty directory HTML pages from 42 different countries in 
multiple languages, although the English version was prefered when it was available. 
We tried to gathering web pages from each country in proportion to their number 
of universities relative to the total number of universities worldwide as in 
\footnote{https://univ.cc/world.php}. Each HTML page was preprocessed and converted to 
to the CONLL 2003 data format, that is one word per line with empty lines representing
sentence boundaries. Sentence were determined by the enclosing HTML tag, that is,
except for span, em, td, a, strong, b, font and sup, all other HTML tag closings were
considered to be sentence boundaries. This aimed to preserve the natural flow of reading
in HTML documents. 
CSS classes can be used to style those elements in very unexpected ways,
however this complexity was not encoded in the database. A proper HTML chunker poses many
challenges by itself. 
Take note that by the nature of these documents, many sentences contained
only one or two tokens.

Finally, all tokens were tagged with the IOB scheme put forward by
\cite{Ramshaw and Marcus (1995)} with a modification. O stands for Outside, 
B-PER is the beginning of a person name, I-PER inside a person name and PUNCT is any 
punctuation sign other than ".". Many name representations contain punctuation signs 
and the PUNCT label helps predicting label transitions properly, especially when using 
simpler algorithms like HMMs. A name for example never ends with a punctuation sign.
Also, 12 categorical features are present in the dataset, they are presented in table X.

Finally the dataset was divided in a training, development and test set.

Table 1 contains
a description of the data files.

\begin{table}[h]
  \small
  \begin{center}
    \begin{tabular}{ |l|l|l|l|l| }
      \hline
      Data file & Documents & Sentences & Tokens & Names \\
      \hline
      Training    & 92 & 28958 & 124984 & 6382 \\
      Development & 28 & 9117  & 39748  & 2258 \\
      Test        & 25 & 5790  & 26995  & 1949 \\
      \hline
    \end{tabular}
  \end{center}
  \caption{Number of HTML pages, sentences and tokens in each data file}
  \label{tab:dataset}
\end{table}

\begin{table}[h]
  \small
  \begin{center}
    \begin{tabular}{ |l|l| }
      \hline
      Data file & Documents & Sentences & Tokens & Names \\
      \hline
      Training    & unaccented token \\
      Training    & exact gazetteer match \\
      Training    & partial gazetteer match \\
      Development & is email \\
      Development & is number \\
      Development & is title \\
      Development & is URL \\
      Development & is capitalized \\
      Development & log name gazetteer count\\
      Development & log word gazetteer count\\
      Development & HTML tag parent + second parent \\
      Development & CSS class \\
      \hline
    \end{tabular}
  \end{center}
  \caption{Features present in the bla dataset}
  \label{tab:features}
\end{table}

\subsection{Features}

\subsection{Gazetteer}

\subsection{Evaluation}

Performance was measured based on the F1 score (Van Rijsbergen, 1975)
obtained in the test set. As in the ConLL dataset a named entity was
only considered correct when it was an exact match of the corresponding 
entity in the data file.

\section{Results}

Table X presents the results for X models in the NER-HTML dataset. Results
for each model are presented when incorporating all features and no features.

Deep learning models are better blabla.

HMMs are competitive but demand feature engineering blabla.

Token morphology is necessary.

Label dependency is necessary.

\section{Conclusion}

Our name extraction method achieved 94.40\% precision, 97.61\% recall 
and 0.9597 F-measure on a corpus of 152 faculty directory web pages from
49 different countries with 11782 researcher names. 
The model is tuned for the particular problem of name extraction, 
but we believe this result can be generalized to solve other data extraction 
problems. The algorithm is general enough to handle other types of information
extraction tasks without the need for too much tinkering.
The secondary estimates strategy was very successful in further improving the
base model. It can also be remodeled to fit other statistical classifiers since
it does not rely on any particular implementation details of our strategy.

% ==========================================
% End of text.                             |
% ==========================================

% \nocite{*}
\bibliographystyle{unsrt}
\bibliography{bibfile}

\end{document}

### 2018-09-16 bi_lstm.py

@@ -1,195 +1,0 @@
-import sys
-import math
-import numpy as np
-
-states = np.array(['H', 'C'])
-features = np.array(['1', '2', '3'])
-
-labels       = np.array([1, 1, 1, 1, 1, 1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 1, 1])
-observations = np.array([1, 1, 1, 1, 1, 1, 1, 2, 2, 2, 2, 2, 2, 2, 3, 3, 3, 3, 1, 1, 1])
-
-def one_hot(target, num_classes):
-  v = np.zeros(num_classes)
-  v[target] = 1
-  return v
-
-def softmax(x):
-  # Numerically stable.
-  shift_x = x - np.max(x)
-  exps = np.exp(shift_x)
-  res = exps / np.sum(exps, axis=0)
-  return res
-
-def create_dataset():
-  X = np.zeros((3, len(observations)))
-  Y = np.zeros((2, len(observations)))
-  for i in range(len(observations)):
-    X[:,i] = one_hot(observations[i] - 1, 3)
-    Y[:,i] = one_hot(labels[i], 2)
-  return X, Y
-
-class LSTM():
-  def __init__(self, n_x, n_y, n_a, t):
-    self.n_x = n_x
-    self.n_y = n_y
-    self.n_a = n_a
-    self.t   = t
-
-    np.random.seed(1)
-    self.Wf = np.random.randn(n_a, n_a + n_x)
-    self.Wu = np.random.randn(n_a, n_a + n_x)
-    self.Wc = np.random.randn(n_a, n_a + n_x)
-    self.Wo = np.random.randn(n_a, n_a + n_x)
-    self.Wy = np.random.randn(n_y, n_a)
-    self.bf  = np.random.randn(n_a, 1  )
-    self.bu  = np.random.randn(n_a, 1  )
-    self.bc  = np.random.randn(n_a, 1  )
-    self.bo  = np.random.randn(n_a, 1  )
-    self.by  = np.random.randn(n_y, 1  )
-    self.caches = []
-
-  def lstm_cell_forward(self, xt, a_prev, c_prev):
-    concat = np.zeros((self.n_a + self.n_x, 1))
-    concat[:self.n_a,] = a_prev
-    concat[self.n_a:,] = xt
-  
-    ft      = softmax(np.dot(self.Wf, concat) + self.bf)
[…]

### 2018-09-16 bi_rnn.py

@@ -1,232 +1,0 @@
-import sys
-import math
-import numpy as np
-
-labels       = np.array([1, 1, 1, 1, 1, 1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 1, 1])
-observations = np.array([1, 1, 1, 1, 1, 1, 1, 2, 2, 2, 2, 2, 2, 2, 3, 3, 3, 3, 1, 1, 1])
-t = len(observations)
-
-def one_hot(target, num_classes):
-  v = np.zeros(num_classes)
-  v[target] = 1
-  return v
-
-def softmax(x):
-  # Numerically stable.
-  shift_x = x - np.max(x)
-  exps = np.exp(shift_x)
-  res = exps / np.sum(exps, axis=0)
-  return res
-
-def create_dataset():
-  X = np.zeros((3, t))
-  Y = np.zeros((2, t))
-  for i in range(t):
-    X[:,i] = one_hot(observations[i] - 1, 3)
-    Y[:,i] = one_hot(labels[i], 2)
-  return X, Y
-
-class RNN():
-  def __init__(self, n_x, n_y, n_a, t):
-    self.n_x = n_x
-    self.n_y = n_y
-    self.n_a = n_a
-    self.t   = t
-
-    np.random.seed(6)
-    self.Waa = np.random.randn(n_a, n_a)
-    self.Wax = np.random.randn(n_a, n_x)
-    self.ba  = np.random.randn(n_a, 1  )
-
-  def rnn_cell_forward(self, xt, a_prev):
-    a_next = np.tanh(np.dot(self.Wax, xt) + np.dot(self.Waa, a_prev) + self.ba)
-  
-    cache = (a_prev, a_next, xt) # For backpropagation.
-    return a_next, cache
-
-  def rnn_forward(self, x):
-    a_next = np.zeros((self.n_a, 1))
-    a = np.zeros((self.n_a, self.t))
-    caches = []
-  
-    for i in range(self.t):
-      xt = x[:,i,np.newaxis]
-      a_next, cache = self.rnn_cell_forward(xt, a_next)
-      a[:,i] = np.ravel(a_next)
-      caches.append(cache)
-  
-    # return a, y_pred, caches
-    return a, caches
-
-  def rnn_cell_backward(self, da_next, cache):
-    a_prev, a_next, xt = cache
-  
-    dtanh    = da_next * (1 - a_next**2)
-    dbat     = dtanh
-    dWaxt    = np.dot(dtanh, xt.T)
[…]

### 2018-09-16 chunker.py

@@ -1,112 +1,0 @@
-import pickle
-import string
-from collections import Iterable
-from nltk.tag import ClassifierBasedTagger, CRFTagger
-from nltk.chunk import ChunkParserI
-from nltk.chunk import conlltags2tree, tree2conlltags
-from nltk.stem.snowball import SnowballStemmer
- 
-# def features(tokens, index, history):
-def features(tokens, index):
-  """
-  `tokens`  = a POS-tagged sentence [(w1, t1), ...]
-  `index`   = the index of the token we want to extract features for
-  `history` = the previous predicted IOB tags
-  """
- 
-  # init the stemmer
-  stemmer = SnowballStemmer('english')
- 
-  # Pad the sequence with placeholders
-  tokens = [('[START2]', '[START2]'), ('[START1]', '[START1]')] + list(tokens) + [('[END1]', '[END1]'), ('[END2]', '[END2]')]
-  # history = ['[START2]', '[START1]'] + list(history)
- 
-  # shift the index with 2, to accommodate the padding
-  index += 2
- 
-  word, pos = tokens[index]
-  prevword, prevpos = tokens[index - 1]
-  prevprevword, prevprevpos = tokens[index - 2]
-  nextword, nextpos = tokens[index + 1]
-  nextnextword, nextnextpos = tokens[index + 2]
-  # previob = history[index - 1]
-  previob = ''
-  contains_dash = '-' in word
-  contains_dot = '.' in word
-  allascii = all([True for c in word if c in string.ascii_lowercase])
- 
-  allcaps = word == word.capitalize()
-  capitalized = word[0] in string.ascii_uppercase
- 
-  prevallcaps = prevword == prevword.capitalize()
-  prevcapitalized = prevword[0] in string.ascii_uppercase
- 
-  nextallcaps = prevword == prevword.capitalize()
-  nextcapitalized = prevword[0] in string.ascii_uppercase
- 
-  return {
-    'word': word,
-    'lemma': stemmer.stem(word),
-    'pos': pos,
-    'all-ascii': allascii,
- 
-    'next-word': nextword,
-    'next-lemma': stemmer.stem(nextword),
-    'next-pos': nextpos,
- 
-    'next-next-word': nextnextword,
-    'nextnextpos': nextnextpos,
- 
-    'prev-word': prevword,
-    'prev-lemma': stemmer.stem(prevword),
-    'prev-pos': prevpos,
- 
[…]

### 2018-09-16 collect_results.sh

@@ -1,0 +1,37 @@
+arr=(
+  nb
+  hmm-1
+  hmm-2
+  hmm-3
+  maxent
+  crf
+  lstm-crf
+  lstm-crf-cnn
+  lstm-crf-lstm
+)
+
+arr2=(
+  nb
+  hmm-1
+  hmm-2
+  hmm-3
+)
+
+# # Gazetteer matching.
+# python train_model.py partial_match
+# python train_model.py exact_match
+
+for i in "${arr[@]}"
+do
+  python train_model.py $i -d $1
+done
+
+for i in "${arr[@]}"
+do
+  python train_model.py $i -f -d $1
+done
+
+for i in "${arr2[@]}"
+do
+  python train_model.py $i -f -s -d $1
+done

### 2018-09-16 convert_dataset.py

@@ -1,0 +1,26 @@
+import sys
+
+with open(sys.argv[1]) as f:
+  prev, pprev = '', ''
+  for line in f:
+    tkns = line.strip().split(' ')
+    if len(tkns) < 2:
+      print(line.strip())
+    elif line.startswith('-DOCSTART-'):
+      print(line.strip())
+    else:
+      current = tkns[1]
+      if current == 'I-PER':
+        if prev == 'PUNCT' and pprev == 'I-PER':
+          pass
+        elif prev == 'I-PER':
+          pass
+        else:
+          tkns[1] = 'B-PER'
+
+      if len(tkns) < 14:
+        tkns += ['none'] * (14 - len(tkns))
+      print(' '.join(tkns))
+
+      pprev = prev
+      prev = current

### 2018-09-16 crf.py

@@ -1,176 +1,0 @@
-import sys
-import math
-import numpy as np
-
-states = np.array(['H', 'C'])
-features = np.array(['1', '2', '3'])
-
-# labels       = np.array([1, 1, 1, 1, 1, 1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 1, 1])
-# observations = np.array([1, 1, 1, 1, 1, 1, 1, 2, 2, 2, 2, 2, 2, 2, 3, 3, 3, 3, 1, 1, 1])
-labels       = np.array([1, 0, 0])
-observations = np.array([1, 2, 3])
-
-t = len(observations)
-
-def one_hot(target, num_classes):
-  v = np.zeros(num_classes)
-  v[target] = 1
-  return v
-
-def create_dataset():
-  X = np.zeros((3, t))
-  Y = np.zeros((2, t))
-  for i in range(t):
-    X[:,i] = one_hot(observations[i] - 1, 3)
-    Y[:,i] = one_hot(labels[i], 2)
-  return X, Y
-
-class InputLayer():
-  def __init__(self, n_x, n_y, t):
-    self.n_x = n_x
-    self.n_y = n_y
-    self.t = t
-    self.X = None
-
-    np.random.seed(1)
-    self.Wx  = np.random.randn(n_y, n_x)
-
-  def set_input(self, X):
-    self.X = X
-
-  def propagate(self):
-    return np.dot(self.Wx, self.X)
-
-  def backpropagate(self, dxt, learning_rate=0.01):
-    dx = np.dot(dxt, self.X.T)
-    self.Wx -= learning_rate * np.clip(dx , -5.0, 5.0, dx)
-
-class Crf():
-  def __init__(self, n_y, t, input_layer):
-    self.n_y = n_y
-    self.t = t
-
-    self.input_layer = input_layer
-
-    np.random.seed(2)
-    # self.Wyy = np.random.randn(n_y, n_y)
-    self.Wyy = np.ones((n_y, n_y))
-
-  def score(self, xt):
-    return np.exp(self.Wyy + xt.T)
-
-  def neg_log_likelihood(self, X, Y, partition_value):
-    value = 0
-    prev_y = np.zeros((self.n_y, 1))
-    for i in range(self.t):
-      xt = X[:,i,np.newaxis]
-      yt = Y[:,i,np.newaxis]
-      score = self.Wyy + xt.T
[…]

### 2018-09-16 crf_rnn.py

@@ -1,40 +1,0 @@
-import sys
-import math
-import numpy as np
-from crf import Crf, InputLayer
-from bi_rnn import SingleRNN, BiRNN
-
-labels       = np.array([1, 1, 1, 1, 1, 1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 1, 1])
-observations = np.array([1, 1, 1, 1, 1, 1, 1, 2, 2, 2, 2, 2, 2, 2, 3, 3, 3, 3, 1, 1, 1])
-# labels       = np.array([0, 1, 0, 0])
-# observations = np.array([2, 1, 2, 3])
-t = len(observations)
-n_x = 3
-n_y = 2
-n_a = 20
-
-def one_hot(target, num_classes):
-  v = np.zeros(num_classes)
-  v[target] = 1
-  return v
-
-def create_dataset():
-  X = np.zeros((3, t))
-  Y = np.zeros((2, t))
-  for i in range(t):
-    X[:,i] = one_hot(observations[i] - 1, 3)
-    Y[:,i] = one_hot(labels[i], 2)
-  return X, Y
-
-X, Y = create_dataset()
-
-rnn = BiRNN(n_x, n_y, n_a, t)
-rnn.set_input(X)
-crf = Crf(n_y, t, rnn)
-crf.fit(Y, 0.01, 2000)
-print labels.tolist()
-print crf.viterbi(X)
-
-# y_pred = rnn.fit(X, Y)
-# print np.argmax(y_pred, axis=0)
-# print labels

### 2018-09-16 hidden_markov.py

@@ -1,123 +1,0 @@
-import sys
-import numpy as np
-
-states = np.array(['H', 'C'])
-features = np.array(['1', '2', '3'])
-
-start = [.5, .5]
-end   = [1, 1]
-
-transition_mat = np.array([
-  [.6, .4],
-  [.4, .6]
-])
-
-emission_mat = np.array([
-  [.2, .5],
-  [.4, .4],
-  [.4, .1]
-])
-
-observations = np.array([1, 1, 1, 1, 1, 1, 1, 2, 2, 2, 2, 2, 2, 2, 3, 3, 3, 3, 1, 1, 1])
-
-def forward_algorithm(observations):
-  global transition_mat, transition_mat
-  alphas = np.zeros((len(observations), len(states)))
-
-  alpha = None
-  for i, o in enumerate(observations):
-    idx = o - 1
-    if alpha is None:
-      alpha = start * emission_mat[idx]
-      alphas[i] = alpha
-      continue
-
-    alpha = np.matmul(alpha, transition_mat)
-    alpha *= emission_mat[idx]
-    alphas[i] = alpha
-  return alphas, np.matmul(alpha, np.transpose(end))
-
-def backward_algorithm(observations):
-  global transition_mat, transition_mat
-  betas = np.zeros((len(observations), len(states)))
-
-  beta = end
-  betas[len(observations) - 1] = beta
-  for i, o in enumerate(reversed(observations)):
-    idx = o - 1
-    beta *= emission_mat[idx]
-    if i < len(observations) - 1:
-      beta = np.matmul(beta, np.transpose(transition_mat))
-      betas[len(observations) - i - 2] = beta
-  return betas, np.matmul(beta, np.transpose(start))
-
-def viterbi(observations):
-  global states
-  backprobs = np.zeros((len(observations), len(states)))
-  backpointers = np.zeros((len(observations), len(states)))
-
-  alpha = None
-  for i, o in enumerate(observations):
-    idx = o - 1
-    if alpha is None:
-      alpha = start * emission_mat[idx]
-      backprobs[i] = alpha
-      continue
-
-    alpha_mat = transition_mat * emission_mat[idx]
-    alpha_mat = np.transpose(alpha_mat) * alpha
-    alpha = np.amax(alpha_mat, axis=1)
-    pointers = np.argmax(alpha_mat, axis=1)
-
-    backprobs[i] = np.amax(alpha_mat, axis=1)
[…]

### 2018-09-16 keras_test/conll_dataset.py

@@ -1,78 +1,0 @@
-class Conll2003():
-  def __init__(self, word_embeddings, f, max_sentence_len=0, max_token_len=0):
-    self.we = word_embeddings
-    self.labels = []
-    self.label2Idx = {}
-    self.num_sentences    = 0
-    self.num_labels       = 0
-    self.max_sentence_len = max_sentence_len
-    self.max_token_len    = max_token_len
-    self.X1 = None
-    self.X2 = None
-    self.X3 = None
-    self.Y = None
-    self.T = None
-    self.load_dataset(f)
-
-  def load_dataset(self, f):
-    with open(f, 'r') as f:
-      sentences = f.read().strip().split('\n\n')
-      sentences = [s for s in sentences if not s.startswith('-DOCSTART-')]
-      sentences = [[t.split(' ') for t in s.split('\n') if len(s) > 0] for s in sentences]
-
-      self.labels = ['O', 'I-LOC', 'B-LOC', 'I-PER', 'B-PER', 'I-MISC', 'B-MISC', 'I-ORG', 'B-ORG']
-      for idx, w in enumerate(self.labels):  
-        self.label2Idx[w] = idx
-
-      f1 = ['EX', 'VBZ', 'VBG', '(', 'RBR', '$', 'UH', "''", 'SYM', ',', 'VB', 'FW', 'JJS', 'WDT', 'JJ', 'MD', '"', 'RBS', 'RP', 'IN', 'CD', 'NNS', 'NN', 'VBN', 'POS', 'WRB', 'WP$', ':', 'JJR', 'NNPS', 'NNP', 'NN|SYM', 'PRP', 'LS', 'RB', 'DT', 'VBP', 'PRP$', 'WP', 'VBD', '.', 'PDT', 'TO', 'CC', ')']
-      f2 = ['I-VP', 'I-LST', 'B-SBAR', 'B-ADVP', 'I-NP', 'I-SBAR', 'B-VP', 'O', 'I-CONJP', 'I-ADVP', 'I-PRT', 'I-INTJ', 'I-ADJP', 'B-NP', 'I-PP', 'B-PP', 'B-ADJP']
-
-      # f1 = list(set([t[1] for s in sentences for t in s]))
-      # f2 = list(set([t[2] for s in sentences for t in s]))
-
-      self.num_sentences    = len(sentences)
-      self.num_labels       = len(self.labels)
-
-      # self.max_token_len    = max([len(t[0]) for s in sentences for t in s])
[…]

### 2018-09-16 keras_test/crawler/crawler.py

@@ -1,185 +1,0 @@
-#!/usr/bin/python
-# coding=UTF-8
-
-import os
-import re
-import sys
-import time
-import threading
-import requests
-from urlparse import urljoin
-from urlparse import urlparse
-from bs4 import BeautifulSoup
-
-def strip_url(url):
-  if url == None or len(url) == 0:
-    return ''
-
-  url = re.sub('(^http\:\/\/)|(^https\:\/\/)', '', url)
-  url = re.sub('^www\.', '', url)
-  if url == None or len(url) == 0:
-    return ''
-
-  if url[-1] == '/':
-    url = url[:-1]
-  return url.strip()
-
-def get_main_domain(url): 
-  top_level_domains = [
-    'com', 'edu', 'gov', 'org', 'net', 'int', 'mil', 'ac', 'ad', 'ae', 
-    'af', 'ag', 'ai', 'al', 'am', 'an', 'ao', 'aq', 'ar', 'as', 'at', 
-    'au', 'aw', 'ax', 'az', 'ba', 'bb', 'bd', 'be', 'bf', 'bg', 'bh', 
-    'bi', 'bj', 'bl', 'bm', 'bn', 'bo', 'bq', 'br', 'bs', 'bt', 'bv', 
-    'bw', 'by', 'bz', 'ca', 'cc', 'cd', 'cf', 'cg', 'ch', 'ci', 'ck', 
-    'cl', 'cm', 'cn', 'co', 'cr', 'cu', 'cv', 'cw', 'cx', 'cy', 'cz', 
-    'de', 'dj', 'dk', 'dm', 'do', 'dz', 'ec', 'ee', 'eg', 'eh', 'er', 
-    'es', 'et', 'eu', 'fi', 'fj', 'fk', 'fm', 'fo', 'fr', 'ga', 'gb', 
-    'gd', 'ge', 'gf', 'gg', 'gh', 'gi', 'gl', 'gm', 'gn', 'gp', 'gq', 
-    'gr', 'gs', 'gt', 'gu', 'gw', 'gy', 'hk', 'hm', 'hn', 'hr', 'ht', 
-    'hu', 'id', 'ie', 'il', 'im', 'in', 'io', 'iq', 'ir', 'is', 'it', 
[…]

### 2018-09-16 keras_test/crawler/x.sh

@@ -1,6 +1,0 @@
-count=1393
-while read p; do
-  echo "$p"
-  count=$((count+1))
-  curl $p > htmls/$count.html
-done < unis.txt

### 2018-09-16 keras_test/crawler/y.sh

@@ -1,4 +1,0 @@
-for f in bla/*; do
-  echo "$f"
-  python ../tokenize_html.py $f >> joelma.txt
-done < unis.txt

### 2018-09-16 keras_test/create_dataset.sh

@@ -1,7 +1,0 @@
-for i in $(seq -f "%03g" 1 149)
-do
-  echo $i
-  python tokenizer.py $i > dataset/$i.txt
-done
-
-python merge_datasets.py

### 2018-09-16 keras_test/embedding.py

@@ -1,35 +1,0 @@
-from gensim.models import KeyedVectors
-import np
-
-class WordEmbeddings:
-  def __init__(emb_type=''):
-    self.words    = []
-    self.word2Idx = {}
-    self.embedding_matrix = None
-
-    if emb_type == 'glove-50':
-      self.load_glove(50)
-    elif emb_type == 'glove-100':
-      self.load_glove(100)
-    elif emb_type == 'glove-200':
-      self.load_glove(200)
-    elif emb_type == 'glove-300':
-      self.load_glove(300)
-    elif emb_type == 'word2vec-300':
-      self.load_word2vec()
-  
-  def load_glove(dimensions):
-    self.embedding_matrix = np.zeros((400001, dimensions), dtype=float)
-    with open('embeddings/glove.6B.' + str(dimensions) + 'd.txt') as f:
-      counter = 1
-      for vector in f:
-        features = vector.strip().split(' ')
-        w = features[0]
-        words.append(w)
-        word2Idx[w] = counter
-        embedding_matrix[counter,:] = np.array(features[1:], dtype=float)
-        counter += 1
-
-  def load_word2vec(dimensions):
-    # model = KeyedVectors.load_word2vec_format('embeddings/GoogleNews-vectors-negative300.bin', binary=True)
-    pass

### 2018-09-16 keras_test/gazetteer_matcher.py

@@ -1,39 +1,0 @@
-from util import Dataset, WordEmbeddings
-from metric import evaluate, get_names, one_hot_to_labels
-from tokenizer import is_punctuation
-import np
-
-we       = WordEmbeddings('glove-50')
-test     = Dataset('dataset/validate.txt', we, max_sentence_len=50, max_token_len=20)
-# test     = Dataset(we, 'dataset/test.txt', max_sentence_len=50, max_token_len=20)
-
-def gazetteer_predict(X, T, mode='partial'):
-  Y = np.zeros((X.shape[0], X.shape[1], 4))
-
-  last_was_name = False
-  for i in range(X.shape[0]):
-    for j in range(X.shape[1]):
-      if X[i,j,1] == 0:
-        last_was_name = False 
-
-      if not T[i,j] is None and is_punctuation(T[i,j]):
-        Y[i,j] = np.array([0, 0, 0, 1])
-
-      # Exact.
-      elif mode == 'exact':
-        if X[i,j,0] == 1:
-          if last_was_name:
-            Y[i,j] = np.array([0, 0, 1, 0])
-          else:
-            Y[i,j] = np.array([0, 1, 0, 0])
-            last_was_name = True
-
-      # Partial .
-      else:
-        if X[i,j,1] == 1:
-          if last_was_name:
-            Y[i,j] = np.array([0, 0, 1, 0])
-          else:
-            Y[i,j] = np.array([0, 1, 0, 0])
-            last_was_name = True
-  return Y      

### 2018-09-16 keras_test/hmm.py

@@ -1,148 +1,0 @@
-import np
-import re
-from matplotlib import pyplot as plt
-from sklearn.metrics import confusion_matrix, f1_score, precision_score, recall_score
-
-import sys
-import numpy as np
-
-X = np.array([1, 1, 1, 1, 1, 1, 1, 2, 2, 2, 2, 2, 2, 2, 3, 3, 3, 3, 1, 1, 1])
-Y = np.array([1, 1, 2, 1, 1, 2, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 1, 2])
-
-labels = np.array(['O', 'B-NAME', 'I-NAME'])
-
-num_labels = 3
-time_steps = 3
-vocab_size = 3
-
-num_states = num_labels ** time_steps
-transition_mat = np.ones((num_states, num_labels))
-emission_mat = np.ones((vocab_size, num_labels))
-
-start = np.zeros((num_states, 1))
-start[0,:] = 1
-end = np.ones((num_states, 1))
-
-def idx_to_states(idx):
-  states = []
-  multiplier = num_labels ** (time_steps - 1)
-  for i in range(time_steps):
-    states.append(int(idx) // int(multiplier))
-    idx %= multiplier
-    multiplier /= num_labels
-  return states 
-
-def states_to_idx(states):
-  if len(states) < time_steps:
-    raise Exception('Wrong states length.')
-
-  acc = 0
-  multiplier = 1
-  for s in reversed(states):
-    acc += int(multiplier) * int(s)
-    multiplier *= num_labels
-  return acc
-
-def load_gazetteer(name_file, word_file):
-  o, b_name, i_name = {'$UNK': 1}, {'$UNK': 1}, {'$UNK': 1}
-  with open(name_file) as f:
-    for line in f:
-      tkns = line.strip().split(' ')
-      if len(tkns) == 0:
-        continue
-
-      if not tkns[0] in b_name:
-        b_name[tkns[0]] = 2 # Laplace smoothing.
-      else:
-        b_name[tkns[0]] += 1
-
-      for t in tkns[1:]: 
-        if not t in i_name:
-          i_name[t] = 2
-        else:
-          i_name[t] += 1
-
-  with open(word_file) as f:
-    for line in f:
-      tkns = line.strip().split(' ')
-      for t in tkns: 
-        if not t in o:
-          o[t] = 2
-        else:
-          o[t] += 1
-
[…]

### 2018-09-16 keras_test/hmm_proto.py

@@ -1,169 +1,0 @@
-import np
-from util import load_raw_dataset
-from tokenizer import remove_accents, tokenize_text
-from metric import evaluate, get_names, one_hot_to_labels
-
-class HiddenMarkov:
-  def __init__(self, timesteps, use_gazetteer=True, use_features=True, self_train=False):
-    self.time_steps   = timesteps
-    self.use_gazetteer = use_gazetteer
-    self.use_features = use_features
-    self.do_self_train = self_train
-
-    self.num_labels   = 4
-    self.num_features = 10
-    self.num_secondary_features = 5
-    self.num_all_features = self.num_features + self.num_secondary_features
-    self.num_states = self.num_labels ** self.time_steps
-    self.transition_mat = np.zeros((self.num_states, self.num_labels))
-    self.start = np.zeros((self.num_states, 1))
-    self.start[0,:] = 1 # All previous states are label O ("other").
-    self.end = np.ones((self.num_states, 1)) # All ending states are equally probable.
-
-    self.feature_counts = []
-    for i in range(self.num_all_features):
-      self.feature_counts.append([])
-      for j in range(self.num_labels):
-        self.feature_counts[i].append({'$UNK': 1})
-
-  def idx_to_states(self, idx):
-    states = []
-    multiplier = self.num_labels ** (self.time_steps - 1)
-    for i in range(self.time_steps):
-      states.append(int(idx) // int(multiplier))
-      idx %= multiplier
-      multiplier /= self.num_labels
-    return states 
-  
-  def states_to_idx(self, states):
-    if len(states) < self.time_steps:
-      raise Exception('Wrong states length.')
-  
-    acc = 0
-    multiplier = 1
-    for s in reversed(states):
-      acc += int(multiplier) * int(s)
-      multiplier *= self.num_labels
-    return acc
-
-  def train_features(self, X, Y, which_features=[]):
-    if len(which_features) != self.num_all_features:
-      which_features = [0] * self.num_all_features
-
-    label_count = np.ones((self.num_labels))
-    for i in range(len(Y)):
-      for j in range(50):
-        if np.sum(Y[i,j]) == 0:
-          break
-  
-        label_count += Y[i,j]
-        y = np.where(Y[i,j] == 1)[0][0]
-  
-        f = X[i][j][1:1+self.num_all_features]
-        for k in range(self.num_all_features):
-          if which_features[k] == 0:
-            continue
-
[…]

### 2018-09-16 keras_test/lstm_crf.py

@@ -1,176 +1,0 @@
-import keras
-import np
-import re
-from util import Dataset, WordEmbeddings
-from keras.models import Model
-from keras.layers import Input, Dense, Dropout, Activation, Flatten, SimpleRNN, TimeDistributed, GRU, Bidirectional, LSTM, Embedding, concatenate, Conv1D, GlobalMaxPooling1D
-from ChainCRF import ChainCRF
-from keras.datasets import mnist
-from keras.utils import np_utils
-from keras.callbacks import Callback
-from keras import optimizers
-from metric import evaluate, get_names, one_hot_to_labels
-
-class Metrics(Callback):
-  def __init__(self, the_model):
-    self.max_f_measure = 0
-    self.the_model = the_model
-
-  def on_epoch_end(self, epoch, logs={}):
-    val_predict, val_targ, T = self.the_model.validate()
-    
-    a, p, r, f1, c, i, m = evaluate(val_predict, val_targ, T)
-    
-    print('Accuracy:', a)
-    print('Precision:', p)
-    print('Recall:', r)
-    print('F1:', f1)
-    print('Correct:', c)
-    print('Incorrect:', i)
-    print('Missed:', m)
-
-    if f1 > self.max_f_measure:
-      self.max_f_measure = f1
-      self.the_model.save()
-    else:
-      print("No improvement")
-   
-class LstmCrf():
-  def __init__(
-    self, 
-    name,
-    lstm_cells=100, 
-    use_gazetteer=True, 
-    use_features=True, 
-    char_embedding_size=30,
-    num_cnn_filters=30,
-    num_labels=4,
-    char_lstm_size=25,
-    model_type=['lstm-crf', 'lstm-crf-cnn', 'lstm-crf-lstm', 'crf'][0],
-    dev_dataset=None,
-    validate_dataset=None,
-    test_dataset=None,
-  ):
-    self.name = name
-    self.lstm_cells = lstm_cells
-    self.num_cnn_filters = num_cnn_filters
-    self.num_labels = num_labels
-    self.char_lstm_size = char_lstm_size
-    self.model_type = model_type
-    self.dev_dataset = dev_dataset
-    self.validate_dataset = validate_dataset
-    self.test_dataset = test_dataset
-    self.use_gazetteer = use_gazetteer
-    self.use_features = use_features
-
-  def create(self, word_embedding_matrix):
[…]

### 2018-09-16 keras_test/merge_datasets.py

@@ -1,34 +1,0 @@
-# import random
-
-# arr = list(range(1, 149))
-# 
-# random.shuffle(arr)
-# 
-# dev = arr[0:95]
-# validate = arr[95:120]
-# test = arr[120:149]
-
-# print(dev)
-# print(validate)
-# print(test)
-
-dev = [88, 87, 131, 19, 47, 23, 48, 108, 45, 96, 55, 57, 26, 70, 128, 97, 140, 135, 66, 139, 138, 24, 106, 71, 18, 142, 34, 115, 134, 32, 2, 60, 86, 77, 54, 52, 46, 101, 43, 68, 81, 51, 13, 29, 56, 126, 6, 121, 69, 123, 63, 133, 9, 59, 76, 104, 33, 112, 103, 83, 114, 14, 122, 7, 39, 144, 85, 99, 113, 130, 36, 62, 93, 74, 3, 148, 89, 94, 27, 75, 21, 12, 64, 127, 98, 149, 65, 4, 15, 8, 16, 145, 38, 44]
-small_dev = [113, 36, 16, 104, 21, 108, 69, 26, 14, 4, 57, 103, 56, 45, 114, 83, 60, 88, 34, 59]
-validate = [117, 90, 80, 41, 105, 5, 102, 49, 129, 143, 137, 11, 91, 132, 100, 82, 72, 17, 22, 118, 42, 50, 67, 124, 84]
-test = [20, 35, 136, 73, 110, 31, 1, 120, 78, 141, 61, 147, 58, 109, 37, 116, 79, 111, 53, 146, 95, 92, 30, 119, 25, 40, 28, 10, 107]
-
-def write_man(dataset, filename):
-  data = ''
-  for idx, num in enumerate(dataset):
-      with open('dataset/' + str(num).zfill(3) + '.txt') as f:
-        data += '-DOCSTART- ' + str(num).zfill(3) + '\n\n'
-        data += f.read() 
-        if idx < len(dev) - 1:
-          data += '\n' 
-  with open('dataset/' + filename + '.txt', 'w') as fw:
-    fw.write(data)
-
-write_man(test, 'test')
-write_man(dev, 'dev')
-write_man(validate, 'validate')
-write_man(small_dev, 'small_dev')

### 2018-09-16 keras_test/metric.py

@@ -1,109 +1,0 @@
-import np
-import re
-
-def remove_titles(text):
-  name = []
-  for tkn in text.split(' '):
-    titles = ['m\.sc\.','sc\.nat\.','rer\.nat\.','sc\.nat\.','md\.',
-      'b\.sc\.', 'bs\.sc\.', 'ph\.d\.', 'ed\.d\.', 'm\.s\.', 'hon\.', 
-      'a\.d\.', 'em\.', 'apl\.', 'prof\.', 'prof\.dr\.', 'conf\.dr\.',
-      'asist\.dr\.', 'dr\.', 'mr\.', 'mrs\.']
-
-    match = False
-    for title in titles:
-      if re.match('^' + title + '$', tkn, re.IGNORECASE):
-        match = True
-        break
-
-    if not match:
-      name.append(tkn)
-        
-  return ' '.join(name)
-
-def get_names(val_predict, sentences):
-  names, name = [], []
-  for i, tokens in enumerate(sentences):
-    for j, t in enumerate(tokens):
-      if val_predict[i][j] == 1:
-        if len(name) > 0:
-          names.append(' '.join(name))
-          name = []
-        if not t is None:
-          name.append(t)
-      elif val_predict[i][j] == 2:
-        if not t is None:
-          name.append(t)
-      elif val_predict[i][j] == 3:
-        if len(name) > 0 and j+1 < len(tokens):
-          if val_predict[i][j+1] == 2:
-            name.append(t)
-      elif len(name) > 0:
-        names.append(' '.join(name))
-        name = []
-
-    if len(name) > 0:
-      names.append(' '.join(name))
-  names = [remove_titles(n) for n in names]
-  return [n for n in names if len(n.split(' ')) > 1]
-
-def one_hot_to_labels(Y):
-  res = np.zeros((Y.shape[0], Y.shape[1]), dtype=int)
-  for i in range(Y.shape[0]):
-    for j in range(Y.shape[1]):
-      if np.sum(Y[i,j]) == 0:
-        res[i,j] = -1
-      else: 
-        res[i,j] = int(np.argmax(Y[i,j], axis=-1))
-  return res
-
-def evaluate(val_predict, val_targ, tokens):
-  val_predict = one_hot_to_labels(val_predict)
-  val_targ = one_hot_to_labels(val_targ)
-
-  confusion_matrix = np.zeros((4,4))
-
-  accuracy = 0
-  total = 0
[…]

### 2018-09-16 keras_test/numerical_test.py

@@ -1,123 +1,0 @@
-import keras
-import np
-from matplotlib import pyplot as plt
-
-from keras.models import Model
-from keras.layers import Input, Dense, Dropout, Activation, Flatten, SimpleRNN, TimeDistributed, GRU, Bidirectional, LSTM
-from ChainCRF import ChainCRF
-from keras.datasets import mnist
-from keras.utils import np_utils
-from keras import optimizers
-
-X_ = np.array([0, 0, 0, 0, 0, 0, 0, 1, 1, 1, 1, 1, 1, 1, 2, 2, 2, 2, 0, 0, 0])
-Y_ = np.array([1, 1, 1, 1, 1, 1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 1, 1])
-
-X = np_utils.to_categorical(X_, 3)
-Y = np_utils.to_categorical(Y_, 2)
-
-
-# Softmax regression.
-
-print('Softmax regression')
-x = Input(shape=(3, ), dtype='float32') 
-y = Dense(2, activation='softmax')(x)
-
-model = Model(inputs=x, outputs=y)
-sgd = keras.optimizers.SGD(lr=0.01, decay=1e-6, momentum=0.9, nesterov=True)
-model.compile(loss='categorical_crossentropy', optimizer=sgd)
-model.fit(x=X, y=Y, batch_size=1, epochs=10)
-predictions = model.predict(x=X)
-
-print('Expected:', Y_)
-print('Actual:  ', predictions.argmax(axis=-1))
-
-
-# RNN.
-
-print('RNN')
-X = np.expand_dims(X, axis=0)
-Y = np.expand_dims(Y, axis=0)
-
-x = Input(shape=(21, 3), dtype='float32') 
-rnn = SimpleRNN(5, return_sequences=True)(x)
-y = Dense(2, activation='softmax')(rnn)
-
-model = Model(inputs=x, outputs=y)
-sgd = keras.optimizers.SGD(lr=0.1, decay=1e-6, momentum=0.9, nesterov=True)
-model.compile(loss='categorical_crossentropy', optimizer=sgd)
-model.fit(x=X, y=Y, epochs=15)
-predictions = model.predict(x=X)
-print('Expected:', Y_)
-print('Actual:  ', predictions.argmax(axis=-1)[0])
-
-
-# Bidirectional RNN.
-
-print('Bidirectional RNN')
[…]

### 2018-09-16 keras_test/print_names.py

@@ -1,51 +1,0 @@
-import sys
-from tokenizer import Tokenizer
-
-if __name__ == '__main__':
-  if len(sys.argv) != 2:
-    print('Wrong arguments')
-    quit()
-
-  tokenizer = Tokenizer()
-
-  zero_padded = sys.argv[1].zfill(3)  
-  html_file = 'htmls/' + zero_padded + '.html'
-  target_file = 'target_names/target_names_' + zero_padded + '.txt'
-
-  target_names = []
-  with open(target_file) as f:
-    for name in f:
-      if len(name) == 0: 
-        continue
-      name = " ".join(tokenizer.tokenize_text(name.strip()))
-      target_names.append(name.strip())
-
-  names = [] 
-  with open(html_file) as f:
-    sentences = tokenizer.tokenize(f.read(), target_names)
- 
-    name = [] 
-    for i, s in enumerate(sentences):
-      for t in s:
-        if t.bio_tag == 'I-PER':
-          name.append(t.tkn)
-        elif t.bio_tag == 'B-PER':
-          if len(name) > 0:
-            names.append(' '.join(name))
-            name = []
-          name.append(t.tkn)
-        elif len(name) > 0:
-          names.append(' '.join(name))
-          name = []
-
-  for n in names:
-    if not n in target_names:
-      print('Oh noes', n)
-      quit()
-
-  for n in target_names:
-    if not n in names:
-      print('Oh noes', n)
-      quit()
-
-  print('Oh yeah')

### 2018-09-16 keras_test/test_model.py

@@ -1,17 +1,0 @@
-from util import Dataset, WordEmbeddings
-from lstm_crf import LstmCrf
-from sklearn.metrics import confusion_matrix, f1_score, precision_score, recall_score
-from metric import evaluate, get_names, one_hot_to_labels
-import np
-
-we       = WordEmbeddings('glove-50')
-# test     = Dataset(we, 'dataset/test.txt', max_sentence_len=50, max_token_len=20)
-test     = Dataset('dataset/validate.txt', we, max_sentence_len=50, max_token_len=20)
-
-lstm_crf = LstmCrf(
-  'lstm-crf-cnn',
-  model_type='lstm-crf-cnn',
-  dev_dataset=test,
-  validate_dataset=test,
-  test_dataset=test
-)

### 2018-09-16 keras_test/tokenize_html.py

@@ -1,18 +1,0 @@
-#!/usr/bin/python
-# coding=UTF-8
-
-import sys
-from tokenizer import Tokenizer
-
-if __name__ == '__main__':
-  if len(sys.argv) != 2:
-    print('Wrong arguments')
-    quit()
-
-  tokenizer = Tokenizer()
-
-  with open(sys.argv[1]) as f:
-    sentences = tokenizer.tokenize(f.read())
-    for s in sentences:
-      for t in s:
-        sys.stdout.write(t.tkn + ' ')

### 2018-09-16 keras_test/tokenizer.py

@@ -1,319 +1,0 @@
-#!/usr/bin/python
-# coding=UTF-8
-
-import sys
-import re
-from math import log
-from bs4 import BeautifulSoup, Tag
-from bs4.element import NavigableString
-
-def remove_accents(tkn):
-  text = tkn.strip().lower()
-
-  special_chars = "ÀÁÂÃÄÅÆÇÈÉÊËÌÍİÎÏÐÑÒÓÔÕÖĞ×ØÙÚÛÜÝÞßàáâãäåæçèéêëìíîïðñòóôõö÷øùúûüýþÿšŽčžŠšČłńężśćŞ"
-  chars         = "aaaaaaeceeeeiiiiidnooooogxouuuuypsaaaaaaeceeeeiiiionooooooouuuuypyszczssclnezscs"
-
-  new_text = ""
-  for c in text:
-    index = special_chars.find(c)
-    if index != -1:
-      new_text += chars[index]
-    else:
-      new_text += c
-
-  return new_text 
-
-class HtmlToken():
-  def __init__(self, tkn, element):
-    self.tkn = tkn
-    self.element = element
-    self.features = []
-    self.bio_tag = 'O'
-    self.set_features()
-
-  def is_email(self):
-    return 1 if re.match('\S+@\S+(\.\S+)+', self.tkn) else 0
-
-  def is_url(self):
-    regex = 'http[s]?://(?:[a-zA-Z]|[0-9]|[$-_@.&+]|[!*\(\),]|(?:%[0-9a-fA-F][0-9a-fA-F]))+'
-    return 1 if re.match(regex, self.tkn) else 0
-
-  def is_number(self):
-    return 1 if any(c.isdigit() for c in self.tkn) else 0
-
-  def is_capitalized(self):
-    if len(self.tkn) > 0:
-      return 1 if self.tkn[0].isupper() else 0
-    return 0
-
-  def is_title(self):
-    titles = ['m.sc.','sc.nat.','rer.nat.','sc.nat.','md.',
-      'b.sc.', 'bs.sc.', 'ph.d.', 'ed.d.', 'm.s.', 'hon.', 
-      'a.d.', 'em.', 'apl.', 'prof.', 'prof.dr.', 'conf.dr.',
-      'asist.dr.', 'dr.', 'mr.', 'mrs.']
-
-    for t in titles:
-      if re.match(t, self.tkn, re.IGNORECASE):
-        return 1
-    return 0
-
-  def get_parent(self, element):
-    if element.parent != None:
[…]

### 2018-09-16 keras_test/train_conll.py

@@ -1,23 +1,0 @@
-from util import Conll2003, Dataset, WordEmbeddings
-from lstm_crf import LstmCrf
-
-
-we       = WordEmbeddings('glove-50')
-dev      = Conll2003(we, 'conll-2003/eng.train', max_sentence_len=50, max_token_len=20)
-validate = Conll2003(we, 'conll-2003/eng.testa', max_sentence_len=50, max_token_len=20)
-test     = Conll2003(we, 'conll-2003/eng.testb', max_sentence_len=50, max_token_len=20)
-
-# print(dev.X2.shape)
-# print(validate.X2.shape)
-# print(test.X2.shape)
-
-lstm_crf = LstmCrf(
-  'lstm-crf-conll',
-  model_type='lstm-crf', 
-  num_labels=9,
-  dev_dataset=dev,
-  validate_dataset=validate,
-  test_dataset=test
-)
-lstm_crf.create(we.matrix)
-lstm_crf.fit(epochs=5)

### 2018-09-16 keras_test/train_model.py

@@ -1,116 +1,0 @@
-import sys
-from optparse import OptionParser
-from metric import evaluate, get_names, one_hot_to_labels
-from util import load_raw_dataset
-from util import Dataset, WordEmbeddings
-from lstm_crf import LstmCrf
-from gazetteer_matcher import gazetteer_predict
-from hmm_proto import HiddenMarkov
-
-parser = OptionParser()
-parser.add_option("-g", "--gazetteer", dest="use_gazetteer", action="store_true")
-parser.add_option("-f", "--features", dest="use_features", action="store_true")
-parser.add_option("-s", "--self-train", dest="self_train", action="store_true")
-parser.add_option("-r", "--reduced-dataset", dest="reduced_dataset", action="store_true")
-
-if len(sys.argv) < 2:
-  print('Wrong number of arguments')
-
-model = sys.argv[1]
-
-if not model in [
-  'partial_match',
-  'exact_match',
-  'hmm-1',
-  'hmm-2',
-  'hmm-3',
-  'hmm-4',
-  'crf',
-  'lstm-crf',
-  'lstm-crf-cnn',
-  'lstm-crf-lstm',
-]:
-  print('Wrong model')
-  quit()
-
-(options, args) = parser.parse_args()
-options = vars(options)
-
-use_gazetteer = not options['use_gazetteer'] is None
-use_features = not options['use_features'] is None
-self_train = not options['self_train'] is None
-
-if model in ['partial_match', 'exact_match']:
-  we = WordEmbeddings('glove-50')
-  test = Dataset('dataset/test.txt', we, max_sentence_len=50, max_token_len=20)
-
-  mode = 'exact'
-  if model == 'partial_match':
-    mode = 'partial'
-
-  val_predict = gazetteer_predict(test.X2, test.T, mode=mode)
-  val_targ = test.Y
-  a, p, r, f1, c, i, m = evaluate(val_predict, val_targ, test.T)
-
-  print('Accuracy:', a)
-  print('Precision:', p)
-  print('Recall:', r)
-  print('F1:', f1)
-  print('Correct:', c)
-  print('Incorrect:', i)
-  print('Missed:', m)
-
-elif model in ['hmm-1', 'hmm-2', 'hmm-3', 'hmm-4']:
-  X, Y, T    = load_raw_dataset('dataset/dev.txt')
[…]

### 2018-09-16 keras_test/util.py

@@ -1,114 +1,0 @@
-import np
-import re
-from keras.utils import np_utils
-
-class WordEmbeddings():
-  def __init__(self, emb_type):
-    self.words  = []
-    self.word2Idx  = {}
-    self.matrix = None
-    self.load_embeddings(emb_type)
-
-  def load_glove(self, dimensions):
-    self.matrix = np.zeros((400002, dimensions), dtype=float)
-    with open('embeddings/glove.6B.' + str(dimensions) + 'd.txt') as f:
-      counter = 2
-      for vector in f:
-        features = vector.strip().split(' ')
-        w = features[0]
-        self.words.append(w)
-        self.word2Idx[w] = counter
-        self.matrix[counter,:] = np.array(features[1:], dtype=float)
-        counter += 1
-
-  def load_embeddings(self, emb_type):
-    if emb_type == 'glove-50':
-      self.load_glove(50)
-    elif emb_type == 'glove-100':
-      self.load_glove(100)
-    elif emb_type == 'glove-200':
-      self.load_glove(200)
-    elif emb_type == 'glove-300':
-      self.load_glove(300)
-
-def load_raw_dataset(f, max_sentence_len=50):
-  with open(f, 'r') as f:
-    sentences = f.read().strip().split('\n\n')
-    sentences = [s for s in sentences if not s.startswith('-DOCSTART-')]
-    X = [[t.split(' ') for t in s.split('\n') if len(s) > 0] for s in sentences]
-    Y = np.zeros((len(X), max_sentence_len, 4))
-    T = np.ndarray(shape=(len(X), max_sentence_len), dtype=object)
-    for i, s in enumerate(X):
-      tkns, labels = [], []
-      if len(X[i]) > max_sentence_len:
-        X[i] = X[i][:max_sentence_len]
-
-      for j, t in enumerate(s[:max_sentence_len]):
-        l = ['O', 'B-PER', 'I-PER', 'O-PUNCT'].index(t[1])
-        labels.append(np_utils.to_categorical(l, 4))
-        tkns.append(t[0])
-        X[i][j] = [X[i][j][0]] + X[i][j][2:]
-      Y[i,:len(labels)] = np.expand_dims(labels, axis=0)
-      T[i,:len(tkns)] = tkns
-    return X, Y, T
-
-class Dataset():
-  def __init__(self, f, word_embeddings, max_sentence_len=50, max_token_len=20):
-    self.we = word_embeddings
-    self.num_sentences    = 0
[…]

### 2018-09-16 logistic_regression.py

@@ -1,48 +1,0 @@
-import numpy as np
-import matplotlib.pyplot as plt
-import math
-
-data = [
-  (0.50, 0), (0.75, 0), (1.00, 0), (1.25, 0),
-  (1.50, 0), (1.75, 0), (1.75, 1), (2.00, 0),
-  (2.25, 1), (2.50, 0), (2.75, 1), (3.00, 0),
-  (3.25, 1), (3.50, 0), (4.00, 1), (4.25, 1),
-  (4.50, 1), (4.75, 1), (5.00, 1), (5.50, 1)
-]
-
-beta = [0.1, 0.1]
-learning_rate = 0.01
-
-def sigmoid(x):
-  return 1 / (1 + math.exp(-(beta[0] + beta[1]*x)))
-
-def steepest_descent():
-  global beta0, beta1
-  for i in range(0, 10000):
-    total_error = 0
-    step = [0, 0]
-    for case in data:
-      error = case[1] - sigmoid(case[0])
-      step[0] += error
-      step[1] += error * case[0]
-      total_error += error
-
-    beta[0] = beta[0] + learning_rate * step[0]
-    beta[1] = beta[1] + learning_rate * step[1]
-    print 'Average error:', total_error / len(data)
-
-steepest_descent()
-
-print 'Beta 0:', beta[0], 
-print 'Beta 1:', beta[1]
-
-# Show charts.
-x = np.arange(0, 6, 0.1);
-y = []
-for x_ in x:
-  y.append(sigmoid(x_))
-
-data_x = [d[0] for d in data]
-data_y = [d[1] for d in data]
-plt.plot(x, y, '-', data_x, data_y, 'ro')
-plt.show()

### 2018-09-16 lstm.py

@@ -1,195 +1,0 @@
-import sys
-import math
-import numpy as np
-
-states = np.array(['H', 'C'])
-features = np.array(['1', '2', '3'])
-
-labels       = np.array([1, 1, 1, 1, 1, 1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 1, 1])
-observations = np.array([1, 1, 1, 1, 1, 1, 1, 2, 2, 2, 2, 2, 2, 2, 3, 3, 3, 3, 1, 1, 1])
-
-t = len(observations)
-n_x = 3
-n_y = 2
-n_a = 2
-np.random.seed(1)
-
-Wf = np.random.randn(n_a, n_a + n_x)
-Wu = np.random.randn(n_a, n_a + n_x)
-Wc = np.random.randn(n_a, n_a + n_x)
-Wo = np.random.randn(n_a, n_a + n_x)
-Wy = np.random.randn(n_y, n_a)
-bf  = np.random.randn(n_a, 1  )
-bu  = np.random.randn(n_a, 1  )
-bc  = np.random.randn(n_a, 1  )
-bo  = np.random.randn(n_a, 1  )
-by  = np.random.randn(n_y, 1  )
-caches = []
-
-def one_hot(target, num_classes):
-  v = np.zeros(num_classes)
-  v[target] = 1
-  return v
-
-def softmax(x):
-  # Numerically stable.
-  shift_x = x - np.max(x)
-  exps = np.exp(shift_x)
-  res = exps / np.sum(exps, axis=0)
-  return res
-
-def create_dataset():
-  X = np.zeros((n_x, t))
-  Y = np.zeros((n_y, t))
-  for i in range(t):
-    X[:,i] = one_hot(observations[i] - 1, n_x)
-    Y[:,i] = one_hot(labels[i], n_y)
-  return X, Y
-
-def lstm_cell_forward(xt, a_prev, c_prev):
-  concat = np.zeros((n_a + n_x, 1))
-  concat[:n_a,] = a_prev
-  concat[n_a:,] = xt
-
-  ft      = softmax(np.dot(Wf, concat) + bf)
-  ut      = softmax(np.dot(Wu, concat) + bu)
-  cct     = np.tanh(np.dot(Wc, concat) + bc)
-  c_next  = ft * c_prev + ut * cct
-  ot      = softmax(np.dot(Wo, concat) + bo)
[…]

### 2018-09-16 old_crf.py

@@ -1,136 +1,0 @@
-import sys
-import math
-import numpy as np
-
-states = np.array(['H', 'C'])
-features = np.array(['1', '2', '3'])
-
-labels       = np.array([1, 1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1])
-observations = np.array([1, 1, 1, 1, 2, 2, 2, 2, 2, 2, 2, 3, 3, 3, 3, 1])
-
-def get_features(y, prev_y, x):
-  return np.array([
-    1 if y == 0 and prev_y == 0 else 0, # C C 1
-    1 if y == 1 and prev_y == 0 else 0, # C C 2
-    1 if y == 0 and prev_y == 1 else 0, # C C 3
-    1 if y == 1 and prev_y == 1 else 0, # C H 1
-    1 if y == 1 and x == 1 else 0, # H C 1
-    1 if y == 1 and x == 2 else 0, # H C 2
-    1 if y == 1 and x == 3 else 0, # H C 3
-    1 if y == 0 and x == 1 else 0, # H H 1
-    1 if y == 0 and x == 2 else 0, # H H 2
-    1 if y == 0 and x == 3 else 0  # H H 3
-
-    # 1 if y == 1 and prev_y == 1 and x == 1 else 0, # C C 1
-    # 1 if y == 1 and prev_y == 1 and x == 2 else 0, # C C 2
-    # 1 if y == 1 and prev_y == 1 and x == 3 else 0, # C C 3
-    # 1 if y == 0 and prev_y == 1 and x == 1 else 0, # C H 1
-    # 1 if y == 0 and prev_y == 1 and x == 2 else 0, # C H 2
-    # 1 if y == 0 and prev_y == 1 and x == 3 else 0, # C H 3
-    # 1 if y == 1 and prev_y == 0 and x == 1 else 0, # H C 1
-    # 1 if y == 1 and prev_y == 0 and x == 2 else 0, # H C 2
-    # 1 if y == 1 and prev_y == 0 and x == 3 else 0, # H C 3
-    # 1 if y == 0 and prev_y == 0 and x == 1 else 0, # H H 1
-    # 1 if y == 0 and prev_y == 0 and x == 2 else 0, # H H 2
-    # 1 if y == 0 and prev_y == 0 and x == 3 else 0  # H H 3
-  ])
-params = np.random.randn(get_features(0, 0, 0).size)
-
-def prob(x):
-  probs = np.zeros((len(states), len(states)))
[…]

### 2018-09-16 process_log.py

@@ -1,0 +1,43 @@
+import sys
+import re
+
+def print_model(attrs):
+  if len(attrs) == 0:
+    return
+
+  f  = '+F' if attrs['V-Use features'] == 'True' else ''
+  st = '+ST' if attrs['V-Self train'] == 'True' else ''
+
+  s = attrs['Model'] + f + st + '\t'
+  s += attrs['V-Precision'] + '\t'
+  s += attrs['V-Recall'] + '\t'
+  s += attrs['V-F1'] + '\t'
+  s += attrs['V-Accuracy'] + '\t'
+  s += attrs['T-Precision'] + '\t'
+  s += attrs['T-Recall'] + '\t'
+  s += attrs['T-F1'] + '\t'
+  s += attrs['T-Accuracy'] + '\t'
+  s += attrs['Time']
+  print(s)
+
+with open(sys.argv[1], 'r') as f:
+  is_validate = True
+  attrs = {}
+  lines = [l.strip() for l in f if not re.match(r'^[A-Z]', l) is None]
+  for l in lines:
+    if l.startswith('Model'):
+      print_model(attrs)
+      attrs = {'Model': l.split(': ')[1]}
+      is_validate = True
+    elif l.startswith('Validate'):
+      pass
+    elif l.startswith('Test'):
+      is_validate = False
+    elif l.startswith('Time elapsed'):
+      x = l.split(' ')
+      attrs['Time'] = x[2]
+    else:
+      x = l.split(': ')
+      mark = 'V-' if is_validate else 'T-'
+      attrs[mark + x[0]] = x[1]
+  print_model(attrs)

### 2018-09-16 rnn.py

@@ -1,136 +1,0 @@
-import sys
-import math
-import numpy as np
-
-states = np.array(['H', 'C'])
-features = np.array(['1', '2', '3'])
-
-labels       = np.array([1, 1, 1, 1, 1, 1, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 1, 1])
-observations = np.array([1, 1, 1, 1, 1, 1, 1, 2, 2, 2, 2, 2, 2, 2, 3, 3, 3, 3, 1, 1, 1])
-
-t = len(observations)
-n_x = 3
-n_y = 2
-n_a = 2
-np.random.seed(2)
-Waa = np.random.randn(n_a, n_a)
-Wax = np.random.randn(n_a, n_x)
-Wya = np.random.randn(n_y, n_a)
-ba  = np.random.randn(n_a, 1  )
-by  = np.random.randn(n_y, 1  )
-caches = []
-
-def one_hot(target, num_classes):
-  v = np.zeros(num_classes)
-  v[target] = 1
-  return v
-
-def softmax(x):
-  return np.exp(x) / np.sum(np.exp(x))
-
-def create_dataset():
-  X = np.zeros((n_x, t))
-  Y = np.zeros((n_y, t))
-  for i in range(t):
-    X[:,i] = one_hot(observations[i] - 1, n_x)
-    Y[:,i] = one_hot(labels[i], n_y)
-  return X, Y
-
-def rnn_cell_forward(xt, a_prev):
-  a_next = np.tanh(np.dot(Wax, xt) + np.dot(Waa, a_prev) + ba)
-  yt_pred = softmax(np.dot(Wya, a_next) + by)
-
-  cache = (a_prev, a_next, xt) # For backpropagation.
-  return a_next, yt_pred, cache
-
-def rnn_forward(x):
-  a_next = np.zeros((n_a, 1))
-  y_pred = np.zeros((n_y, t))
-  a = np.zeros((n_a, t))
-  caches = []
-
-  for i in range(t):
-    xt = x[:,i,np.newaxis]
-    a_next, yt_pred, cache = rnn_cell_forward(xt, a_next)
-    y_pred[:,i] = np.ravel(yt_pred)
-    a[:,i] = np.ravel(a_next)
-    caches.append(cache)
-
-  return a, y_pred, caches
-
-def rnn_cell_backward(da_next, cache):
-  a_prev, a_next, xt = cache
-
-  dtanh    = da_next * (1 - a_next**2)
[…]

### 2018-09-16 softmax_regression.py

@@ -1,49 +1,0 @@
-import numpy as np
-import matplotlib.pyplot as plt
-import math
-np.set_printoptions(threshold=np.inf)
-
-learning_rate = 0.000000001
-data = []
-w = np.full((10, 785), 0.00001, dtype=float)
-
-def load_data():
-  with open('mnist.data') as f:
-    for line in f:
-      arr = line.strip().split(',')
-      features = np.concatenate([[1], np.asarray(arr[1:], dtype=int)])
-      data.append((features, int(arr[0])))
-
-def softmax(x):
-  # Numerically stable.
-  logit = np.matmul(w, x)
-  shift_x = logit - np.max(logit)
-  exps = np.exp(shift_x)
-  return exps / np.sum(exps)
-
-def fit(epochs):
-  global w, data
-  for i in range(0, epochs):
-    neg_log_likelihood = 0
-    correct = 0
- 
-    avg = np.zeros((len(data)))
-    w_update = np.full((10, 785), 0, dtype=float)
-    count = 0
-    for d in data:
-      expected_class = d[1]
-      probs = softmax(d[0])
-      if np.argmax(probs) == expected_class:
-        correct += 1
-  
-      # print probs[expected_class]
-      avg[count] = -math.log(probs[expected_class])
-      count += 1
-      neg_log_likelihood += -math.log(0.1 + probs[expected_class]) 
-      derivative = probs[expected_class] - 1
-      w_update[expected_class] += d[0] * (derivative * learning_rate)
-    w = np.add(w, -w_update)
-    print 'Epoch:', i+1, '; Accuracy:', float(correct) / len(data), '; Negative log likelihood:', float(neg_log_likelihood) / len(data)
-
-load_data()
-fit(10000)

### 2018-09-16 test.py

@@ -1,81 +1,0 @@
-# !/usr/bin/python
-
-import sys
-import os
-import collections
-import string
-from chunker import NamedEntityChunker
-from nltk import pos_tag, word_tokenize
-from nltk.chunk import conlltags2tree, tree2conlltags
-import nltk
-
-directory = 'gmb-2.2.0/'
-
-def to_conll_iob(annotated_sentence):
-  """
-  `annotated_sentence` = list of triplets [(w1, t1, iob1), ...]
-  Transform a pseudo-IOB notation: O, PERSON, PERSON, O, O, LOCATION, O
-  to proper IOB notation: O, B-PERSON, I-PERSON, O, O, B-LOCATION, O
-  """
-  proper_iob_tokens = []
-  for idx, annotated_token in enumerate(annotated_sentence):
-    tag, word, ner = annotated_token
- 
-    if ner != 'O':
-      if idx == 0:
-        ner = "B-" + ner
-      elif annotated_sentence[idx - 1][2] == ner:
-        ner = "I-" + ner
-      else:
-        ner = "B-" + ner
-    proper_iob_tokens.append((tag, word, ner))
-  return proper_iob_tokens
-
-def reader():
-  with open(directory + 'ner_dataset.csv', 'r') as f:
-    f.readline() # Ignore first line.
-    
-    tokens = []
-    for line in f:
-      data = line.strip().split(',')
-      if data[0].startswith('Sentence: ') and len(tokens) > 0:
-        conll_tokens = to_conll_iob(tokens)
-        # Make it NLTK Classifier compatible - [(w1, t1, iob1), ...] to [((w1, t1), iob1), ...]
-        # Because the classfier expects a tuple as input, first item input, second the class
-        yield [((w, t), iob) for w, t, iob in conll_tokens]
-
-        tokens = []
-      tokens.append((data[1], data[2], data[3]))
-
-data = list(reader())
-print len(data)
-
-training_samples = data[:int(len(data) * 0.9)]
-test_samples = data[int(len(data) * 0.9):]
- 
-print "#training samples = %s" % len(training_samples)    # training samples = 55809
-print "#test samples = %s" % len(test_samples)
-
-chunker = NamedEntityChunker(training_samples[:2000])
-print chunker.parse(pos_tag(word_tokenize("I'm going to Germany this Monday.")))
-
-test = [conlltags2tree([(w, t, iob) for (w, t), iob in iobs]) for iobs in test_samples[:500]]
-score = chunker.evaluate(test)
[…]

### 2018-09-16 train_conll.py

@@ -1,0 +1,183 @@
+#!/usr/bin/python
+# coding=UTF-8
+
+import np
+from keras.utils import np_utils
+from keras.callbacks import Callback
+from models.util import WordEmbeddings
+from models.lstm_crf import LstmCrf
+
+def is_punctuation(text):
+  return re.match("^[\,\;\:\-\"\(\)“”]$", text)
+
+def print_results(dataset, val_predict, val_targ, T, verbose=False):
+    correct = 0
+    incorrect = 0
+    missed = 0
+    for i, sentence in enumerate(val_targ):
+      for j, tkn in enumerate(val_targ[i]):
+        if np.sum(val_targ[i,j]) > 0:
+          y_hat = int(np.argmax(val_predict[i,j], axis=-1))
+          y = int(np.argmax(val_targ[i,j], axis=-1))
+
+          if y_hat == y and y != 0:
+            correct += 1
+
+          elif y_hat != y and y == 0:
+            incorrect += 1
+
+          elif y_hat != y and y > 0:
+            missed += 1
+            if y_hat > 0:
+              incorrect += 1
+
+    p  = correct / float(correct + incorrect)
+    r  = correct / float(correct + missed)
+    f1 = 2 * p * r / float(p + r)
+
+    if verbose:
+      print('----------------')
+      print(dataset)
+      print('----------------')
+      print('Correct:', correct)
+      print('Incorrect:', incorrect)
+      print('Missed:', missed)
+      print('Precision:', p)
+      print('Recall:', r)
+      print('F1:', f1)
+
+    return correct, incorrect, missed, p, r, f1
+
+class Metrics(Callback):
+  def __init__(self, the_model):
+    self.max_f_measure = 0
+    self.the_model = the_model
+
+  def on_epoch_end(self, epoch, logs={}):
+    val_predict, val_targ, T = self.the_model.validate()
+
+    correct, incorrect, missed, p, r, f1 = print_results('Validate', val_predict, val_targ, T, verbose=False)
+
+    improved = False
+    if f1 > self.max_f_measure:
+      self.max_f_measure = f1
+      self.the_model.save()
+      improved = True
+
[…]

### 2018-09-16 train_model.py

@@ -1,0 +1,191 @@
+import sys
+import time
+import np
+from optparse import OptionParser
+from keras.callbacks import Callback
+from models.util import load_raw_dataset, Dataset, WordEmbeddings, evaluate
+from models.lstm_crf import LstmCrf
+from models.gazetteer_matcher import gazetteer_predict
+from models.hmm import HiddenMarkov
+
+class Metrics(Callback):
+  def __init__(self, the_model):
+    self.max_f_measure = 0
+    self.the_model = the_model
+
+  def on_epoch_end(self, epoch, logs={}):
+    val_predict, val_targ, T = self.the_model.validate()
+    a, p, r, f1, c, i, m = evaluate(val_predict, val_targ, T)
+    
+    improved = False
+    if f1 > self.max_f_measure:
+      self.max_f_measure = f1
+      self.the_model.save()
+      improved = True
+
+    print('Epoch: %d, Loss: %f, F1: %f %s' % (epoch, logs['loss'], f1, '- IMPROVED' if improved else ''))
+ 
+start = time.time()
+
+parser = OptionParser()
+parser.add_option("-f", "--features", dest="use_features", action="store_true")
+parser.add_option("-s", "--self-train", dest="self_train", action="store_true")
+parser.add_option("-v", "--verbose", dest="verbose", action="store_true")
+parser.add_option("-d", "--dataset", dest="dataset")
+verbose = False
+
+if len(sys.argv) < 2:
+  print('Wrong number of arguments')
+
+model = sys.argv[1]
+
+def print_results(dataset, val_predict, val_targ, T):
+  a, p, r, f1, c, i, m = evaluate(val_predict, val_targ, T, verbose=verbose)
+
+  print('----------------')
+  print(dataset)
+  print('----------------')
+  print('Accuracy:', a)
+  print('Precision:', p)
+  print('Recall:', r)
+  print('F1:', f1)
+  print('Correct:', c)
+  print('Incorrect:', i)
+  print('Missed:', m)
+  print('')
+
+if not model in [
+  'partial_match',
+  'exact_match',
+  'nb',
+  'hmm-1',
+  'hmm-2',
+  'hmm-3',
+  'hmm-4',
+  'maxent',
+  'crf',
+  'lstm-crf',
+  'lstm-crf-cnn',
+  'lstm-crf-lstm',
+]:
+  print('Wrong model')
+  quit()
+
[…]

### 2018-09-16 x.sh

@@ -1,0 +1,7 @@
+./collect_results.sh dataset/dev.txt > logs/dev.log
+./collect_results.sh dataset/small_dev_1.txt > logs/small_dev_1.log
+./collect_results.sh dataset/small_dev_2.txt > logs/small_dev_2.log
+./collect_results.sh dataset/small_dev_3.txt > logs/small_dev_3.log
+./collect_results.sh dataset/small_dev_4.txt > logs/small_dev_4.log
+./collect_results.sh dataset/small_dev_5.txt > logs/small_dev_5.log
+./collect_results.sh conll > logs/conll_train.log

### 2018-09-18 tex/article.tex
Dataset and LSTM explanation.

\documentclass[sigconf]{acmart}
\settopmatter{printacmref=false} % Removes citation information below abstract
\renewcommand\footnotetextcopyrightpermission[1]{} % removes footnote with conference information in first column
\pagestyle{plain} % removes running headers
\setcopyright{none}

\usepackage{booktabs} % For formal tables
\usepackage[ruled]{algorithm2e} % For algorithms
\renewcommand{\algorithmcfname}{ALGORITHM}
\SetAlFnt{\small}
\SetAlCapFnt{\small}
\SetAlCapNameFnt{\small}
\SetAlCapHSkip{0pt}
\IncMargin{-\parindent}

\usepackage[latin1]{inputenc}
\usepackage{graphicx}
\usepackage{mathtools}
\usepackage{amsfonts}
\usepackage{multirow}

\DeclareMathOperator*{\argmax}{arg\,max\,}

\begin{document}

\title{Named Entity Recognition on HTML as a web data extraction subtask}

\author{João Mateus de Freitas Veneroso}
\affiliation{%
  \institution{Universidade Federal de Minas Gerais}
  \streetaddress{Av. Pres. Antônio Carlos, 6627 - Pampulha}
  \city{Belo Horizonte}
  \state{MG}
  \postcode{31270-901}
  \country{Brazil}}
\email{jmfveneroso@gmail.com}

\author{Berthier Ribeiro-Neto}
\affiliation{%
  \institution{Universidade Federal de Minas Gerais}
  \streetaddress{Av. Pres. Antônio Carlos, 6627 - Pampulha}
  \city{Belo Horizonte}
  \state{MG}
  \postcode{31270-901}
  \country{Brazil}}
\email{berthier.dcc.ufmg@gmail.com}

\begin{abstract}

Reliable researcher affiliation data is necessary to allow enquiring
about international research group productivity and publication patterns.
Public bibliographic databases such as DBLP and Google Scholar hold
invaluable data about the academic environment. However, the researcher
affiliation information is frequently missing or outdated.
We propose a statistical data extraction method to acquire affiliation 
information directly from university websites and solve the name extraction
task in general.
Previous approaches to web data extraction either lack in flexibility,
because wrappers do not generalize well on cross website tasks, or 
they lack in precision, because domain agnostic methods neglect 
useful properties of this particular application domain.
Our statistical approach solves the name extraction task with 
a framework that incorporates both textual and structural features to
yield an outstanding tradeoff between generality and precision. 
We conducted experiments over a collection of 152 faculty 
web pages in multiple languages from universities in 49 countries
and obtained 94.40\% precision, 97.61\% recall and 0.9597 F-measure at
the extraction task.

\end{abstract}

% \keywords{Named entity recognition, information extraction, web data extraction}

\maketitle

% ==========================================
% Beginning of text.                       |
% ==========================================

\section{Introduction}

Web information extraction is the task of automatically extracting structured information
from unstructured or semi-structured web documents. The input usually consists of
web documents containing a number of predetermined entities organized in a similar 
manner and the information extraction task consists of identifying these entities
and organizing them according to a template. In this context, named entity recognition
(NER) is a subtask that aims to detect named entities in the text and classify them into 
predetermined categories such as person names, locations or organizations.

Once we are able
to reliably detect relevant entities, we may employ an information extraction 
algorithm to extract structured data. In this paper, we investigate different NER 
approaches from the perspective of web information extraction.

HTML documents most often lie in between the structured / unstructured data paradigm, 
which means that authors take quite a casual approach regarding formal structure. 
However, DOM hierarchy, element disposition, class names, and other features related to 
the document structure and indirectly associated with the data itself can be valuable 
information in the task of identifying entities and determining relationships. Yet we 
cannot expect these features to be completely constrained by an underlying pattern. 
Organization patterns tend to follow some guidelines but are in no way subject to 
strict rules. That is why classical information extraction systems such as automatic
wrapper generators usually do not translate well across different websites. Contrastingly, 
statistical based approaches can be much more flexible.

NER systems are frequently trained and tested on news corpora such as the 
dataset introduced at the Language-Independent Named Entity Recognition Shared Task
at CONLL-2003 \cite{Sang2003}. State-of-the-art approaches have recently achieved 
F1-scores of 90.10 \cite{Huang2015}, 90.94 \cite{Lample2016}, and 91.21 \cite{Ma2016} 
in this task using different combinations of bidirectional LSTM layers, word and 
character representations.

Even if focusing on web documents, records also may
contain pure text that needs appropriate IE algorithms to extract the inherent data. Most WDE algorithms certainly can exploit the semi-structured nature of web documents, but can surely not restrict ourselves to that, because deeper processing is necessary. When looking through the algorithms and searching for the Swiss army knife, most algorithms can be ruled out for some incapability restricting the algorithms strongly. B.

NER on HTML poses a different type of challenge, because web pages are often
very different from the plain text found in news corpora. Named entities may be present 
inside tables, lists, graphs or other types of visual elements that provide
little to no textual information that could give hints about the semantic category of 
a word. Systems trained on news or similar corpora do not translate well to the web
NER task without retraining, since in this task we cannot profit
as much from contextual hints or transfer learning approaches such as word embeddings.
Besides, deep learning approaches can require a lot of data to reach peak performance.

To test different NER approaches from the perspective of web information extraction,
we will explore the task of person names extraction from university faculty websites.
Researcher affiliation is often missing from many entries in public databases such as DBLP  
\footnote{
  http://dblp.uni-trier.de/
} and the display of information varies significantly between different university 
websites, so this task can provide a good measure of the expected performance and
data need for other web information extraction tasks. Also, with the lack of a large amount
of training data, we show that feature engineering and resources such as a gazetteer 
may be invaluable.

\section{Related Work}

In the last 20 years, the astonishing growth of public information in the web has 
led to the development of a number of different approaches to the problem of web 
information extraction. Traditionally, the task was solved by designing special purpose
programs called wrappers to recognize relevant data and store records in a structured
format. These early tools varied wildly relative to their degree of automation.

It was readily perceived that manual wrapper generation was a rather tedious and
error prone process, unsuited for large scale operations. Wrappers tend to
break frequently because they rely heavily on web page features that can change 
often. So, in the late nineties, several authors advocated for wrapper induction, a technique 
that consists of automatically constructing wrappers from a small set of examples by 
identifying delimiters or context tokens that single out the desired attributes. 
Some remarkable wrapper induction methods are WIEN \cite{Kushmerick2000}, Soft 
Mealy \cite{Hsu1998} and STALKER \cite{Muslea1999}.

Despite being better than constructing wrappers manually, wrapper induction methods 
still suffered from a lack of expressive power and flexibility. These methods had 
trouble handling records with missing attributes or unusual structures because
patterns could only be identified if they happened at least once in the examples.

Other approaches such as NoDoSE (\cite{Adelberg1998}) and Debye (\cite{Laender2002a}) 
brought greater flexibility to wrapper induction methods by requiring a greater level 
of human interaction through graphical user interfaces. Web data extraction techniques often 
require some sort of assistance from human experts to boost accuracy. One of the main challenges 
in the field lies in determining an adequate tradeoff between the degree of automation and 
the precision and recall of the data extraction tool.

To automate the task of web data extraction completely some approaches,
such as Road Runner \cite{Crescenzi2001}, removed entirely the need for data examples.
Road Runner parses documents belonging to a same class (e.g. books on Amazon) and 
generates wrappers based on their similarities and differences, yielding comparable results 
to those obtained by wrapper induction methods. However like previous approaches, it was 
unsuited for cross site extraction tasks because the learned rules were not general enough.

NLP based approaches aimed at extracting more general rules that could possibly
be employed over multiple websites. RAPIER \cite{Califf1999} is a method of rule
extraction that uses information such as part-of-speech tags and semantic classes from
a lexicon to derive patterns from a set of training examples. This approach is more
flexible than the wrapper induction methods, however it achieves much lower rates of 
recall and precision.

In 2002, a survey by Laender et al. \cite{Laender2002} made a thorough classification of the
early approaches with a taxonomy based on their main technology, being them: languages for
wrapper development, HTML-aware tools, NLP-based tools, Wrapper Induction Tools,
Modeling-based tools and Ontology-based tools. Some noteworthy examples from this era
are:

\begin{itemize}
\item TSIMMIS \cite{Hammer1997} and WebOQL \cite{Arocena1999}, which are special purpose 
languages for building wrappers.

\item Road Runner \cite{Crescenzi2001}, XWRAP \cite{Liu2000} and W4F \cite{Sahuguet1999}, 
which are HTML-aware tools that infer meaningful patterns from the HTML structure.

\item RAPIER \cite{Califf1999}, SRV \cite{Freitag1998}, WHISK \cite{Soderland1999}, which 
are NLP-based tools.

\item WIEN \cite{Kushmerick2000}, Soft Mealy \cite{Hsu1998} and STALKER \cite{Muslea1999} which 
are wrapper induction methods.

\item NoDoSE \cite{Adelberg1998} and Debye \cite{Laender2002a}, which are semi supervised modeling
based tools that require some interaction with the user by means of a graphical
user interface.
\end{itemize}

In 2006, Chang et al. \cite{Chang2006} complemented the previous surveys with semisupervised 
technologies such as Thresher \cite{Hogue2005}, IEPAD \cite{Chang2001} and 
OLERA \cite{Chang2004}. They differed from supervised 
and unsupervised methods because they either needed only a rough description of
data from users for extraction rule generation or some level of post processing
that needed user attention. The survey also mentioned newer unsupervised methods
such as DeLa \cite{Wang2003}, Exalg \cite{Arasu2003} and Depta \cite{Zhai2005}.

Most of the early information extraction systems were rule-based with either 
manual rule description or automatic rule learning from examples, thus they
suffered from a lack of flexibility when dealing with noisy and unstructured data.
Huge progress in the field of statistical learning led to the development of
statistical models that tried to solve this problem.

In 2008, Sarawagi \cite{Sarawagi2008} produced a survey that classified wrappers into
rule-based methods, statistical methods and hybrid models, bringing together 
the fields of named entity recognition, relationship extraction and information extraction. 
The rule based methods encompass most of the 
previous models. The statistical methods convert the extraction task into a token labeling 
task, identifying the target entities through the assignment of labels as in a typical 
Named Entity Recognition task. Traditionally, Hidden Markov Models \cite{Leek1997, Freitag1999}, 
Linear Chain Conditional Random Fields \cite{Lafferty2001}, and Maximum Entropy Taggers 
\cite{McCallum2000} have been the usual choice for linear sequence tagging models.
More recently, with the advancement in Natural Language Processing and Deep Learning, 
neural models outperformed previous NER methods. Huang \cite{Huang2015} introduced the 
bidirectional Long Short-Term Memory (LSTM) model with a Conditional Random Field (CRF) output layer
for NER. Lample \cite{Lample2016} incorporated Convolutional Neural Network based character representations 
on top of the architecture. And Ma \cite{Ma2016} introduced
LSTM based character representations. Both obtaining improvements with systems that are less reliant
on feature engineering.

Surveys by Ferrara et al. \cite{Ferrara2014}, Schulz et al. \cite{Schulz2016} and 
Varlamov et al. \cite{Varlamov2016} updated the previous surveys on information 
extraction methods with some interesting innovations. 
Some examples are: the Visual Box Model \cite{Krupl2005}, a data extraction system that produces 
a visualization of the web page to exploit visual cues to identify data presented in a tabular form;
automatic wrapper adaptation \cite{Ferrara2011}, a technique that tries to reduce the cost of 
wrapper maintenance by measuring the similarity of HTML trees and adapting
wrappers to the new page structure; AutoRM \cite{Shi2015}, a method to mine
records from a single web page by identifying similar data regions through DOM
tree analysis; Knowledge Vault \cite{Dong2014}, a method that combines different 
extraction approaches to feed a probabilistic knowledge base.

Most data extraction systems focus on extracting information from single websites
and thus are unsuited for cross website extraction tasks. Even unsupervised
approaches that are domain independent, such as RoadRunner \cite{Crescenzi2001} 
and EXALG \cite{Arasu2003} only work well for extracting data from pages generated 
from the same underlying template. A statistical approach to unsupervised domain 
independent web data extraction was described by Zhu et al \cite{Zhu2005}. The 2D CRF 
model takes a web page segmented into data blocks and employs a two dimensional conditional 
random field model to perform attribute labelling. The model was further improved in 
\cite{Zhu2006} to model record segmentation and attribute labeling as a joint task.
Some of the limitations of early unsupervised methods 
were also tackled by ObjectRunner (\cite{Abdessalem2010}) and AMBER (\cite{Furche2012}). 
These methods work by annotating webpages automatically with regular expressions, gazetteers and 
knowledge bases. They can rectify low quality annotations and even improve the annotators
by exploring regular structures in the DOM during the record segmentation phase.

In summary, web data extraction methods have undoubtedly improved extraordinarily, but
as pointed by Schulz et al. \cite{Schulz2016}, it is difficult to compare the results 
achieved by competing tools, and many seem to rely excessively on certain heuristics.
In that regard, the impressive advancements in NLP may provide for more robust and
flexible extraction tools.

\section{Named Entity Recognition Models}

Most web data extraction systems rely on hand crafted rules or gazetteers to perform
attribute annotation. Machine learning approaches to NER can improve annotations of 
more complex entities and even manage entity detection without resorting to a gazetteer.
We explored multiple approaches to the Named Entity Recognition problem in the context 
of a web information extraction task. We first introduce two traditional approaches, 
namely: Hidden Markov Models and Linear Chain Conditional Random Fields. And further
we explore the neural architectures.

\subsection{Hidden Markov Models}

A Markov Model is a stochastic model that computes the most probable sequence of states 
given a limited set of observable states $ \S = \{s_1, s_2, ..., s_n \} $.
The Hidden Markov Model (HMM) differs from the Markov Model in that it
does not observe the states directly, but rather a probabilistic function of those 
states. For example in NER, the words are observed, however the Named Entity labels
associated with these words are not. Formally, we want to compute the most probable
sequence of labels $ Y = \{y_1, y_2, ..., y_n\} $ for a sequence of observed tokens
$ X = \{x_1, x_2, ..., x_n\} $.

\begin{equation}
Y* = \argmax_{Y} P(Y|X)
\end{equation}

With Bayes theorem, we can write $ P(Y|X) $ as:

\begin{equation}
P(Y|X) = \frac{P(X|Y) P(Y)}{P(X)}
\end{equation}

Since $ P(X) $ is the same for all label sequences $ Y $, we can simply maximize:

\begin{equation}
P(Y|X) \propto P(X|Y) P(Y)
\end{equation}

A HMM makes two assumptions. First, the probability of being in a given state depends 
only on a fixed number of previous states. That is 
$ P(y_i|y_{i-1}x_{i-1}, y_{i-2}x_{i-2}, ..., y_1x_1) = P(y_i|y_{i-1}, y_{i-2},..., y_{i-k}) $. 
In fact, we can get much better results on the NER task by looking at trigrams
or quadrigrams ($ k = 2 $ or $ k = 3 $) instead of bigrams as a regular HMM. 
Some label assignments are highly improbable, such as single token named entities 
separated by a common word, and these kinds of patterns can be caught by a higher order HMM.
Second, the probability of a word depends only on its assigned label 
$ P(x_i|y_{i-1}x_{i-1}, ..., y_1x_1) = P(x_i|y_i) $. With these assumptions, 
the probability $ P(Y|X) $ can be approximated by the expression:

\begin{equation}
P(Y|X) \propto \prod_{i=k+1}^{n} P(y_i|y_{i-1}, y_{i-2}, ..., y_{i-k}) P(x_i|y_i)
\end{equation}

The probabilities can be calculated through maximum likelihood estimation from the relative
frequencies of labels and features in the corpus. The best sequence of labels can be computed 
with a variable state Viterbi approach \cite{Li2000}. However, as we increase $ k $, this computation 
becomes exponentially more expensive. The beam-search strategy may be employed for a faster 
search, but we found that for $ k \leq 4 $, the Viterbi algorithm is still viable.

HMM based taggers have been succesfully apllied in many NLP and IE tasks 
\cite{Rabiner1989, Leek1997, Freitag2000}. They are incredibly fast to train and very 
interpretable, making them a good choice for a first approximation. However, these models 
are highly dependent on the right selection of features, what may outweigh the benefit of a 
small training cost.

\subsubsection{Self training} \label{sssec:self_training}

In the particular case of NER on HTML, there are useful features related to the HTML
structure that can be used to identify named entities. In a particular website, named
entities tend to occur inside the same HTML tags with the same CSS classes. This fact
can be used as an additional piece of evidence in the HMM tagger. However, if we train 
the HMM for a particular set of websites, and then we feed it with new websites, almost 
surely there will be small correlation between the HTML features estimated in the training 
set and the distribution of these features in the new websites, simply because websites 
use very different templates. Therefore, we propose to use a self training strategy to train 
these HTML features. This is only possible because the HMM can be trained very quickly. The 
self training strategy is implemented like this:

\begin{itemize}
\item Train the HMM in a given training set without the HTML features.
\item Compute labels for the new websites with the trained HMM.
\item Use these computed labels as a proxy for the actual labels in the 
new websites and estimate HTML feature frequencies only in the new websites.
\item Recompute the labels using the HTML features.
\end{itemize}

This adds very little overhead to the original model while improving precision and recall
modestly.

\subsection{Linear Chain Conditional Random Fields}

A Linear Chain Conditional Random Field (CRF) is the discriminative analog to the HMM,
it was first introduced by \cite{Lafferty2001}. It is a distribution $ P(Y|X) $ that takes the form:

\begin{equation}
P(Y|X) = \frac{1}{Z(x)} \prod_{t=1}^{T} exp \left( \sum_{k=1}^{K} \theta_k f_k(y_{t-1}, y_t, X) \right)
\end{equation}

where $ \theta $ is the parameter vector that we are going to learn, $ f_k(y_{t-1}, y_{t}, X) $ 
are feature functions over the current timestep $ t_y $, the previous timestep $ y_{t-1}$, 
and the observation vector $ X $. And the partition function $ Z(x) $, takes the form:

\begin{equation}
Z(x) = \sum_{Y} \prod_{t=1}^{T} exp \left( \sum_{k=1}^{K} \theta_k f_k(y_{t-1}, y_t, x) \right)
\end{equation}

which is a sum over all possible label assignments $ Y $. The partition function can be efficiently
and exactly calculated with the sum-product algorithm. Parameter estimation is usually done through 
negative log likelihood minimization. The function can be optimized with techniques suitable for other 
maximum entropy models such as L-BFGS \cite{Liu1989}. The most likely label sequences can be decoded 
with the Viterbi algorithm like in the case of HMMs.

CRFs are more general than HMMs because the transitions from $ y_{t-1} $ to $ y_{t} $ can also depend 
on the vector of observations $ X $. This flexibility of feature functions allow for a wide range of
possibilities. Recently, CRFs have been succesfully employed as the output layer in complex neural 
architectures bringing improvements over models that classify labels independently.

\subsection{Neural Models}

Recurrent neural networks (RNN) have been succesfully employed on numerous NLP tasks such as
language modelling, POS tagging, speech recognition and NER. Different from feedforward neural networks, 
RNNs can retain information in their internal state, making them more suitable for processing sequences, 
and consequently for solving text related tasks. In NER, the network outputs one label for each input 
vector as Figure YYY.

<INSERT FIGURE YYY>

Although RNNs are theoretically capable of learning long term dependencies, in practice 
it might be difficult. Long short term memory networks (LSTM) were introduced by Hochreiter 
and Schmidhuber \cite{Hochreiter1997} with this problem in mind and have been 
popularized since them. LSTM cell implementations vary slightly in the literature.
Our implementation has the following definition:

\begin{flalign*}
\Gamma_i^{<t>} &= \sigma(W_i[x^{<t>},h^{<t-1>}] + b_i) &\\
\Gamma_f^{<t>} &= \sigma(W_f[x^{<t>},h^{<t-1>}] + b_f) &\\ 
c^{<t>}        &= \Gamma_f^{<t>} \circ c^{<t-1>} + \Gamma_i^{<t>} tanh(W_{c,x} x^{t} + W_{c,a} a^{t-1} + b_c) &\\
\Gamma_o^{<t>} &= \sigma(W_o[x^{<t>},h^{<t-1>}] + b_o) &\\
h^{<t>}        &= \Gamma_o^{<t>} \circ tanh(c^{t}) &
\end{flalign*}

where $ \sigma $ is the logistic sigmoid function. $ \Gamma_i $, $ \Gamma_f $, and $ \Gamma_o $ are the input,
forget and output gates, respectively. And $ W $ with a subscript is the weight 
matrix corresponding to that gate. Variable $ c^{<t>} $ is the cell 
state and $ h^{<t>} $ is the hidden state, with the vector $ [x^{<t>},h^{<t-1>}] $ 
being formed by concatenating the current input vector $ x^{<t>} $ and the hidden vector 
from the previous timestep $ h^{<t-1>} $. A visual description of our LSTM cell is 
provided in figure XXX.
This implementation differs from the LSTM cell described in Huang et al. \cite{Huang2015}
in that the input gate $ \Gamma_i $ and the forget gate $ \Gamma_f $
do not take input from the previous cell state $ c^{<t-1>} $ and the output gate does
not take input from the current cell state $ c^{<t>} $. The cell state and the control
gates are what makes the LSTM cell better at modelling long term dependencies in comparison
to a regular RNN.

XXX Insert figure explaining equations XXX

In NER related tasks, both past and future words are important when deciding the
label at time $ t $, but a regular LSTM network only takes past features in consideration. 
A bidirectional LSTM solves this problem by stacking two regular LSTMs, and feeding
them with observations in opposite directions. The first LSTM receives the forward
states and the second LSTM receives the backward states. The hidden states from both 
networks can be concatenated at each time step to produce the output label. With this 
architecture, Bidirectional LSTMs have information from all input features in the sequence at 
any given timestep.

\subsubsection{LSTM-CRF}

Huang et al. \cite{Huang2015} proposed a bidirectional LSTM with a CRF layer (LSTM-CRF) on the output to tackle
the sequence tagging problem. The CRF layer jointly decodes labels for the whole sentence instead
of predicting each label individually. This architecture achieved an F1 score of 90.10 in the 
ConL2003 dataset, in contrast to 85.17 for a bidirectional LSTM without the CRF layer. 
In our experiments, the LSTM-CRF architecture used a bidirectional LSTM with 100 
hidden states, no peepholes and an input and output dropout layers with a dropout
rate of 0.5. The dropout layers have proven to be very important to prevent overfitting 
and allow better generalization.

\subsubsection{LSTM-CRF + CNN character representations}

Ma and Hovy \cite{Ma2016} proposed adding a convolutional neural networks (CNN) layer 
on top of a bidirectional LSTM-CRF to encode character-level information. Those character
representations are combined with word level representations and then fed to the
Bidirectional LSTM. This architecture possesses the capacity to learn morphological
token features that are extremely useful on the NER task, since similar named entities 
often present morphological similarities. This improvement obtained an F1 score of 
91.21 at the ConLL2003 dataset. In our experiments, the LSTM-CRF architecture with
CNN character representations used a one dimensional convolutional neural network with 30 
filters and a window size of three characters on top of the LSTM-CRF architecture,
the character embeddings fed to the CNN had 30 dimensions that were randomly initialized.

\subsubsection{LSTM-CRF + LSTM character representations}

Lample et al \cite{Lample2016} suggested using an a bidirectional LSTM to model character-level 
representations on a bidirectional LSTM-CRF. Combining both the forward and backward 
LSTM representations to form the character representation. This character
representation is also combined with a word representation. The forward LSTM is expected to be a better
representation of the suffix of a token, and the backward LSTM is expected to be a
better representation of the prefix of a token. This differentiates the architecture
from the CNN based approach, because CNN filters discover positional invariant
features, while LSTMs can better represent suffixes and prefixes. In our experiments, 
the LSTM-CRF architecture with LSTM character embeddings was implemented by a bidirectional LSTM
with 25 hidden states, producing character representations of size 50. The character embeddings
also had 30 dimensions that were randomly initialized.

\subsubsection{Network training}

The neural models were trained with Stochastic Gradient Descent over 50 epochs using a learning 
rate of 0.01 and momentum of 0.9. We used early stopping \cite{Caruana2000} to select the best 
parameters,  considering the F1 measure in the validation set. All neural models used 
GloVe 100-dimensional word embeddings \cite{Pennington2014} that were fine tuned during training,
they have a vocabulary size of 400.000 words.
In the case of NER on HTML, word embeddings work as a rather satisfactory gazetteer. Named entities 
of a same type have similar embeddings, so with good word embeddings we can achieve exceptional 
performance with little training data and without a gazetteer. Figure XXX illustrates the differences
between the three neural models mentioned previously.

XXX Insert picture here explaining the models Figure 1 XXX

\section{NER on HTML Dataset}

We constructed a novel dataset to evaluate the performance of multiple NER models
at the web information extraction task. The task consists of finding researcher
names in faculty listings from multiple web pages. This would be the 
first step in linking researcher profiles from university websites to their entries
in public databases such as DBLP \footnote{http://dblp.uni-trier.de/}. Unlike many
information extraction datasets, each web page in the dataset comes from a different 
university, and therefore has a different format, what makes many information
extraction approaches impractical. The idea is to explore systems that are general 
enough to allow efficient name extraction from many different sources without requiring
any supervision between different websites.

This task would be similar to the task of labeling authors in comments
from many different sources or labeling authors in articles collected from many
publishing platforms. Another similar task would be NER on tweets. Because of the character
limitation present on tweets, we end up with constraints comparable to the ones 
found in the NER on HTML task, so we expect similar systems to have comparable performances
on both of these tasks.

We collected 145 computer science faculty pages from 42 different countries in 
multiple languages, although the English version was prefered when it was available. 
We gathered faculty web pages randomly in proportion to 
the number of universities in each country\footnote{A detailed list of universities can 
be found in https://univ.cc/world.php}. Each HTML page was preprocessed and converted
to the CONLL 2003 data format. That is, one word per line with empty lines representing
sentence boundaries. Sentence boundaries were determined by line break HTML tags
(div, p, table, li, br, etc.) in contrast to inline tags (span, em, a, td, etc.). Sentences
that were more than 50 tokens were also split according to punctuation.

A proper HTML segmenter poses many challenges by itself as discussed for example in \cite{Cai2003}.
However, we wanted to evaluate models without relying on any sophisticated data record
segmentation system. In many cases, entity annotation may precede the segmentation
phase in web data extraction methods, so annotators have to be able to work with
raw HTML data. Because of the type of documents present in the dataset, many sentences 
contained only one or two tokens, while other documents contained long texts.
Finally, all tokens were tagged using the IOB scheme put forward by
Ramshaw and Marcus \cite{Ramshaw1995} with a modification. O stands for Outside, 
B-PER is the beginning of a person name, I-PER inside a person name and PUNCT is any 
punctuation sign other than ".". Many name representations contain punctuation signs 
and the PUNCT label helps predicting label transitions properly, especially when using 
simpler algorithms like HMMs. A name for example never ends with a punctuation sign,
but it may be split by a punctuation sign.

\subsection{Data}

\begin{table}[h]
  \small
  \begin{center}
    \begin{tabular}{ |l|l|l|l|l| }
      \hline
      Data file & Documents & Sentences & Tokens & Names \\
      \hline
      Training    & 92 & 28958 & 124984 & 6382 \\
      Validation  & 28 & 9117  & 39748  & 2258 \\
      Test        & 25 & 5790  & 26995  & 1949 \\
      \hline
    \end{tabular}
  \end{center}
  \caption{Number of HTML pages, sentences and tokens in each data file}
  \label{tab:dataset}
\end{table}

The dataset was divided in a training, validation and test set. Table \ref{tab:dataset} contains
a description of the data files. The validation set was used in the early stopping validation strategy
on neural model and CRF training, while results were evaluated by comparing results in the test set.

\subsection{Features}

Twelve categorical features were also present with each token in the dataset. They 
are presented in table \ref{tab:features}.

\begin{table}[h]
  \small
  \begin{center}
    \begin{tabular}{ |l|l| }
      \hline
      Feature & Description \\
      \hline
      1  & Unaccented lowercase token \\
      2  & Exact gazetteer match \\
      3  & Partial gazetteer match \\
      4  & Log name gazetteer count\\
      5  & Log word gazetteer count\\
      6  & Email \\
      7  & Number \\
      8  & Honorific \\
      9  & URL \\
      10 & Is capitalized \\
      11 & HTML tag + parent \\
      12 & CSS class \\
      \hline
    \end{tabular}
  \end{center}
  \caption{Features present in the bla dataset}
  \label{tab:features}
\end{table}

The unaccented lowercase token was used as the key for the Glove-100 embedding lookup.
A gazetteer was constructed from a researcher list extracted from DBLP with 1.595.771
names. Feature 2 represents an exact match of a sequence of tokens to any of the 1.595.771 
names, and feature 3 represents a partial match. Feature 4 is the rounded logarithm of 
the frequency of a token in the gazetteer, and feature 5 is the rounded logarithm of the frequency
of a token in a word corpus obtained through a random crawl in university websites.
Features 6 to 9 represent a simple regular expression match to an email, number, 
honorific or URL, respectively. Feature 10 represents if a word is capitalized.

Feature 11 represents the HTML enclosing tag and its parent concatenated. Feature 12
represents all CSS classes concatenated. These features are not very useful in a general
sense, because every HTML document has a different format, so only because a named entity
occurs inside a given HTML tag in a document we cannot say it is more likely to be the case 
in other documents. However, these features can be trained with the self-training strategy 
for HMMs described in section \ref{sssec:self_training}. For all other models these features 
were ignored.

\section{Experiments}

We conducted two experiments to evaluate the best models for named entity recognition
on HTML in the context of web data extraction. In the first experiment, we used the
whole training set (90 documents). In the second experiment, the training set was split 
into five non overlapping sets with only 18 documents and the validation set was reduced 
to 5 documents, but the test set was kept unchanged. The goal of this second experiment 
was to evaluate models when training data is scarce, since labelling data can be a very 
time consuming task.

Evaluation of model performance in this task was measured with the precision, recall and 
F1 scores (Van Rijsbergen, 1975). Precision is the percentage of named entities found by 
the model that are correct. Recall is the percentage of named entities that are present
in the corpus and were found by the model. The F1 score is a composite measure that combines
precision and recall with the formula:

\begin{equation}
F1 = \frac{2 * precision * recall}{precision + recall}
\end{equation}

\begin{table}[h]
  \small
  \begin{center}
    \begin{tabular}{ |l|l| }
      \hline
      Model & Description \\
      \hline
      hmm-1         & Regular HMM \\
      hmm-2         & HMM with $ k=2 $ \\
      hmm-3         & HMM with $ k=3 $ \\
      crf           & Linear chain conditional random fields \\
      lstm-crf      & LSTM-CRF model \cite{Huang2015} \\
      lstm-crf-cnn  & LSTM-CRF with CNN character representations \cite{Ma2016} \\
      lstm-crf-lstm & LSTM-CRF with LSTM character representations \cite{Lample2016} \\
      \hline
    \end{tabular}
  \end{center}
  \caption{Model descriptions}
  \label{tab:models}
\end{table}

Named entities were only considered to be correct if they were a complete match of the 
corresponding entity in the dataset. The models evaluated are presented in Table \ref{tab:models}.
We evaluated the models using the complete set of features, presented in 
table \ref{tab:features} and no features besides word embeddings for neural models and
CRFs, and unaccented words for HMMs. To represent models with the complete set of features
we added a "+F" suffix to the model name. Additionally, HMMs were evaluated with and
without the self training strategy. To represent HMMs that use the self training strategy
we added the suffix "+ST" to the model name.
Results were reported for the validation and test sets in experiment 1 and only for the
test set in experiment 2. In the second experiment, precision, recall and F1 scores were 
averaged over the five runs. The standard deviation is presented next to the measures.

\subsection{Experiment 1: complete dataset}

\begin{table}[h]
  \small
  \begin{center}
    \begin{tabular}{ |l|l|l|l|l|l|l| }
      \hline
      \multirow{2}{*}{Model} & \multicolumn{3}{c|}{Validation} & \multicolumn{3}{c|}{Test} \\
                             & \multicolumn{1}{c}{Precision} & \multicolumn{1}{c}{Recall} & \multicolumn{1}{c|}{F1}
                             & \multicolumn{1}{c}{Precision} & \multicolumn{1}{c}{Recall} & \multicolumn{1}{c|}{F1} \\
      \hline
      hmm-1           & 0.5282 & 0.9226 & 0.6718 & 0.5333 & 0.8409 & 0.6527 \\
      hmm-2           & 0.5282 & 0.9226 & 0.6718 & 0.5333 & 0.8409 & 0.6527 \\
      hmm-3           & 0.5282 & 0.9226 & 0.6718 & 0.5333 & 0.8409 & 0.6527 \\
      crf             & 0.5282 & 0.9226 & 0.6718 & 0.5333 & 0.8409 & 0.6527 \\
      lstm-crf        & 0.5282 & 0.9226 & 0.6718 & 0.5333 & 0.8409 & 0.6527 \\
      lstm-crf-cnn    & 0.5282 & 0.9226 & 0.6718 & 0.5333 & 0.8409 & 0.6527 \\
      lstm-crf-lstm   & 0.5282 & 0.9226 & 0.6718 & 0.5333 & 0.8409 & 0.6527 \\
      hmm-1+F         & 0.5282 & 0.9226 & 0.6718 & 0.5333 & 0.8409 & 0.6527 \\
      hmm-2+F         & 0.5282 & 0.9226 & 0.6718 & 0.5333 & 0.8409 & 0.6527 \\
      hmm-3+F         & 0.5282 & 0.9226 & 0.6718 & 0.5333 & 0.8409 & 0.6527 \\
      hmm-3+F+ST      & 0.5282 & 0.9226 & 0.6718 & 0.5333 & 0.8409 & 0.6527 \\
      crf+F           & 0.5282 & 0.9226 & 0.6718 & 0.5333 & 0.8409 & 0.6527 \\
      lstm-crf+F      & 0.5282 & 0.9226 & 0.6718 & 0.5333 & 0.8409 & 0.6527 \\
      lstm-crf-cnn+F  & 0.5282 & 0.9226 & 0.6718 & 0.5333 & 0.8409 & 0.6527 \\
      lstm-crf-lstm+F & 0.5282 & 0.9226 & 0.6718 & 0.5333 & 0.8409 & 0.6527 \\
      \hline
    \end{tabular}
  \end{center}
  \caption{Precision, recall and F1 in the complete dataset}
  \label{tab:experiment1}
\end{table}

A named entity was only considered correct when 
it was an exact match of the corresponding entity in the data file. 
Models were trained on each of the five sets separately and tested
in the same test set, and each model was trained on each of the five 
sets and evaluated on the same validation and test sets.

\subsection{Experiment 2: reduced dataset}

\begin{table}[h]
  \small
  \begin{center}
    \begin{tabular}{ |l|l|l|l|}
      \hline
      \multirow{2}{*}{Model} & \multicolumn{3}{c|}{Test} \\
                             & \multicolumn{1}{c}{Precision} & \multicolumn{1}{c}{Recall} & \multicolumn{1}{c|}{F1} \\
      \hline
      hmm-1           & 0.5333 (0.111) & 0.8409 (0.111) & 0.6527 (0.111) \\
      hmm-2           & 0.5333 (0.111) & 0.8409 (0.111) & 0.6527 (0.111) \\
      hmm-3           & 0.5333 (0.111) & 0.8409 (0.111) & 0.6527 (0.111) \\
      crf             & 0.5333 (0.111) & 0.8409 (0.111) & 0.6527 (0.111) \\
      lstm-crf        & 0.5333 (0.111) & 0.8409 (0.111) & 0.6527 (0.111) \\
      lstm-crf-cnn    & 0.5333 (0.111) & 0.8409 (0.111) & 0.6527 (0.111) \\
      lstm-crf-lstm   & 0.5333 (0.111) & 0.8409 (0.111) & 0.6527 (0.111) \\
      hmm-1+F         & 0.5333 (0.111) & 0.8409 (0.111) & 0.6527 (0.111) \\
      hmm-2+F         & 0.5333 (0.111) & 0.8409 (0.111) & 0.6527 (0.111) \\
      hmm-3+F         & 0.5333 (0.111) & 0.8409 (0.111) & 0.6527 (0.111) \\
      hmm-3+F+ST      & 0.5333 (0.111) & 0.8409 (0.111) & 0.6527 (0.111) \\
      crf+F           & 0.5333 (0.111) & 0.8409 (0.111) & 0.6527 (0.111) \\
      lstm-crf+F      & 0.5333 (0.111) & 0.8409 (0.111) & 0.6527 (0.111) \\
      lstm-crf-cnn+F  & 0.5333 (0.111) & 0.8409 (0.111) & 0.6527 (0.111) \\
      lstm-crf-lstm+F & 0.5333 (0.111) & 0.8409 (0.111) & 0.6527 (0.111) \\
      \hline
    \end{tabular}
  \end{center}
  \caption{Precision, recall and F1 in the small dataset}
  \label{tab:experiment2}
\end{table}

were trained 
consisted of training
all models with the whole training set (90 documents) and the second experiment trained
them on five subsets with 18 documents
Table X presents the results for X models in the NER-HTML dataset. Results
for each model are presented when incorporating all features and no features.

Deep learning models are better blabla.

HMMs are competitive but demand feature engineering blabla.

Token morphology is necessary.

Label dependency is necessary.

\section{Conclusion}

Our name extraction method achieved 94.40\% precision, 97.61\% recall 
and 0.9597 F-measure on a corpus of 152 faculty directory web pages from
49 different countries with 11782 researcher names. 
The model is tuned for the particular problem of name extraction, 
but we believe this result can be generalized to solve other data extraction

\end{document}

### 2018-09-18 tex/exemplo.tex
Dataset and LSTM explanation.

@@
 
-\title{Named Entity Recognition on HTML as an information extraction subtask}
+\title{Named Entity Recognition on HTML as a web data extraction subtask}
 
@@
 (NER) is a subtask that aims to detect named entities in the text and classify them into 
-predetermined categories such as person names, locations or organizations. Once we are able
-to reliably detect the relevant entities, we may employ an information extraction 
+predetermined categories such as person names, locations or organizations.
+
+Once we are able
+to reliably detect relevant entities, we may employ an information extraction 
 algorithm to extract structured data. In this paper, we investigate different NER 
@@
 
-% \begin{figure}
-%   \centering
-%   \includegraphics[width=0.5\textwidth]{pics/jap_osaka_lab}
-%   \caption{Example of a faculty directory}
-%   \label{fig:faculty_directory}
-% \end{figure}
-% 
-% To acknowledge the complexity of this extraction task, take for example a snippet of 
-% the staff page for the intelligent robotics laboratory from Osaka University shown in figure 
-% \ref{fig:faculty_directory}. There is some structure to the way member profiles are arranged, 
-% but the organization is rather flexible, also note that there is little text to contextualize
-% each named entity.
+Even if focusing on web documents, records also may
+contain pure text that needs appropriate IE algorithms to extract the inherent data.
+Most WDE algorithms certainly can exploit the semi-structured nature of web documents, but can surely not restrict ourselves to that, because deeper processing is necessary.
+When looking through the algorithms and searching for the Swiss army knife, most algorithms can be ruled out for some incapability restricting the algorithms strongly.
+B.
 
@@
 
-Despite being better than constructing wrappers manually, wrapper induction methods 
-still suffered from a lack of expressive power and flexibility. These methods had 
 trouble handling records with missing attributes or unusual structures because
@@
 
-In 2008, Sarawagi \cite{Sarawagi2008} produced a survey that classified wrappers in
+statistical models that tried to solve this problem.
+
+In 2008, Sarawagi \cite{Sarawagi2008} produced a survey that classified wrappers into
 rule-based methods, statistical methods and hybrid models, bringing together 
-the fields of named entity recognition, relationship 
-extraction and information extraction. The rule based methods encompass most of the 
+the fields of named entity recognition, relationship extraction and information extraction. 
+The rule based methods encompass most of the 
 previous models. The statistical methods convert the extraction task into a token labeling 
 task, identifying the target entities through the assignment of labels as in a typical 
-Named Entity Recognition task. Traditionally, Hidden Markov Models, Linear Chain Conditional 
-Random Fields \cite{Lafferty2001}, and Maximum Entropy Taggers have been the usual choice 
-for linear sequence tagging models.
-
+Named Entity Recognition task. Traditionally, Hidden Markov Models \cite{Leek1997, Freitag1999}, 
+Linear Chain Conditional Random Fields \cite{Lafferty2001}, and Maximum Entropy Taggers 
+\cite{McCallum2000} have been the usual choice for linear sequence tagging models.
 More recently, with the advancement in Natural Language Processing and Deep Learning, 
-neural models outperformed previous NER methods. Using a bidirectional Long Short-Term
-Memory (LSTM) model with a Conditional Random Field (CRF) output layer, \cite{Huang2015} 
-obtained 90.10 F1 score on the CoNLL 2003 corpus for named entity recognition. A similar model
-by \cite{Lample2016} incorporates a Convolutional Neural Network over character embeddings
-as an input to the bidirectional LSTM reaching an F-score of 90.94 at the same task. Finally, 
-\cite{Ma2016} constructed word representations with the hidden layer of a bidirectional 
-LSTM obtaining an F-score of 91.21. The latter two models make use of orthographic and 
-morphological evidence to detect named entities, making the models less reliant on feature
-engineering and surrounding words. Up to our knowledge, these models still have not been
-employed at the web information extraction task.
+neural models outperformed previous NER methods. Huang \cite{Huang2015} introduced the 
+bidirectional Long Short-Term Memory (LSTM) model with a Conditional Random Field (CRF) output layer
+for NER. Lample \cite{Lample2016} incorporated Convolutional Neural Network based character representations 
+on top of the architecture. And Ma \cite{Ma2016} introduced
+LSTM based character representations. Both obtaining improvements with systems that are less reliant
+on feature engineering.
 
@@
 Domain specific methods are designed for extracting data about a particular 
-application domain across multiple websites.
-Domain specific methods integrate information about the particular application domain in the 
-course of its development and thus are able to achieve superior performance in
-comparison to domain agnostic methods. One example is the method of comment extraction 
-from blog posts described by Kao et al. \cite{Kao2010}.
+application domain across multiple websites. Domain specific methods integrate information 
+about the particular application domain in the course of its development and thus are 
+able to achieve superior performance in comparison to domain agnostic methods. 
+Domain agnostic methods are the most general extraction methods. They can extract
+information from any application domain and from multiple websites with different
+templates. This problem can be decomposed into at least two subtasks: web page
+segmentation, and attribute labeling. The system proposed by Zhu \cite{Zhu2005} and improved 
+in \cite{Zhu2006} relies on \cite{Cai2004} to solve the web page segmentation task and 
+on conditional random fields for the attribute labeling task. ObjectRunner (\cite{Abdessalem2010}) 
+and AMBER (\cite{Furche2012}) rely on user provided ontologies to m
 
-Domain agnostic methods are the most general extraction methods. They can extract
-information from any application domain from multiple websites. They pose the hardest
-challenge because the tool must infer data relevance without any prior training in
-that particular application domain. Some examples are: ODE (\cite{Su2009}), ObjectRunner 
-(\cite{Abdessalem2010}), and AMBER (\cite{Furche2012}). These approaches are more flexible but 
-yield worse results than domain specific methods.
+to develop entity recognizers based on 
+gazetteer, knowledge bases or regular expressions.
 
-In this paper, we are exploring NLP based approaches to solve a domain specific problem.
+Some systems can rely on some sort of automatic web page segmentation to
+identify data blocks and then CRFs to label attributes.
+
+Domain agnostic extraction systems may benefit the most from the recent 
+advancements on NLP.
+
+ The steps to that operate entity annotation, record 
+segmentation, and data extraction
+. These systems can operate with relatively noisy annotators
+by
+
+works by annotating entity instances, 
+then infering templates from a sample of test pages, and extracting all instances
+further improving the entity recognizers.
 
@@
 of a web information extraction task.
+
+Why are NER based approaches superior?
 
@@
 label assignments are highly improbable, such as single token named entities separated 
-by an Other label, and these kinds of patterns can be caught by a higher order Hidden
+by a common word, and these kinds of patterns can be caught by a higher order Hidden
 Markov Model. Second, the probability of a word depends only on its assigned label 
@@
 exponentially more expensive. The beam-search strategy may be employed for a faster search,
-but we found that for $ k \leq 3 $, the Viterbi algorithm is still viable.
+but we found that for $ k \leq 4 $, the Viterbi algorithm is still viable.
 
@@
 is a feature function over the current and previous timesteps and the current word $ x_t $, and
-$ Z(x) $ is a partition function that depends on the input. Linear chain conditional random fields
 are more general than Hidden Markov Models because the transition from $ y_{t-1} $ to $ y_{t} $ can
@@
 
-Linear Chain CRFs are a natural fit to Named Entity Recognition problems because of the
+Linear Chain CRFs are a natural fit to Named Entity Recognition problems
+
+ because of the
 high label dependency. Therefore, sequence taggers that do not take this output dependency into
@@
 filters and a window size of three characters on top of the LSTM-CRF architecture,
-the character embeddings fed to the CNN had 30 dimensions and were randomly initialized.
+the character embeddings fed to the CNN had 30 dimensions that were randomly initialized.
 
@@
 representations on a bidirectional LSTM-CRF. Combining both the forward and backward 
-LSTM representations forming the complete character representation that is also combined 
-with a word
-representation as in the previous model. The forward LSTM is expected to be a better
+LSTM representations to form the character representation. This character
+representation is also combined with a word representation. The forward LSTM is expected to be a better
 representation of the suffix of a token, and the backward LSTM is expected to be a
-better representation of the prefix of a token. This differentiates this architecture
+better representation of the prefix of a token. This differentiates the architecture
 from the CNN based approach, because CNN filters discover positional invariant
 features while LSTMs can better represent suffixes and prefixes. In our experiments, 
-the LSTM-CRF architecture with LSTM character embeddings used a bidirectional LSTM
+the LSTM-CRF architecture with LSTM character embeddings was implemented with a bidirectional LSTM
 with 25 hidden states, thus producing character representations with 50 dimensions.
@@
 All neural models used GloVe 100-dimensional word embeddings \cite{Pennington2014}
-that were fine tuned during training. The models were trained with Stochastic Gradient 
-Descent over 50 epochs using a learning rate of 0.01 and momentum 0.9.
+that were fine tuned during the training. The models were trained with Stochastic Gradient 
+Descent over 50 epochs using a learning rate of 0.01 and momentum of 0.9.
 
@@
 university, and therefore has a different format, what makes many information
-extraction systems impractical. The idea is to construct a system that is general 
+extraction approaches impractical. The idea is to explore systems that are general 
 enough to allow efficient name extraction from many different sources without requiring
@@
 extracting comments from different news sources, in which we must recognize author 
-names in different formattings before infering structure and extracting the structured 
-tuple author, timestamp, comment, likes. Another similar example would be acquiring 
+names in different formattings before infering structure and extracting the
+tuple: author, timestamp, and comment. Another similar example would be acquiring 
 author information from different publishing platforms before extracting structured 
-information in the format author, article, timestamp. Of course, similar systems
+information in the format: author, timestamp, and text. Similarly, the same systems
 could be used to recognize different named entities in other contexts.
@@
 multiple languages, although the English version was prefered when it was available. 
-We tried to gathering web pages from each country in proportion to their number 
+We tried gathering web pages from each country in proportion to their number 
 of universities relative to the total number of universities worldwide as in 
-\footnote{https://univ.cc/world.php}. Each HTML page was preprocessed and converted to 
+\footnote{https://univ.cc/world.php}. Each HTML page was preprocessed and converted
 to the CONLL 2003 data format, that is one word per line with empty lines representing
-sentence boundaries. Sentence were determined by the enclosing HTML tag, that is,
-except for span, em, td, a, strong, b, font and sup, all other HTML tag closings were
-considered to be sentence boundaries. This aimed to preserve the natural flow of reading
-in HTML documents. 
-CSS classes can be used to style those elements in very unexpected ways,
-however this complexity was not encoded in the database. A proper HTML chunker poses many
-challenges by itself. 
-Take note that by the nature of these documents, many sentences contained
-only one or two tokens.
+sentence boundaries. Sentences were determined by the encompassing HTML tags, that is,
+except for \{ span, em, td, a, strong, b, font and sup \} tags, all other HTML closing tags were
+treated as sentence boundaries. This aimed to preserve the natural flow of reading
+in HTML documents. Sentences that were composed of more than 50 tokens were also chunked
+according to punctuation. CSS classes can be used to style HTML elements in unexpected ways,
+however this complexity was not taken into account. A proper HTML chunker poses 
+many challenges by itself.
 
-Finally, all tokens were tagged with the IOB scheme put forward by
+Take note that because of the type of documents present in the dataset, many sentences 
+contained only one or two tokens.
+
+Finally, all tokens were tagged using the IOB scheme put forward by
 \cite{Ramshaw and Marcus (1995)} with a modification. O stands for Outside, 
@@
 and the PUNCT label helps predicting label transitions properly, especially when using 
-simpler algorithms like HMMs. A name for example never ends with a punctuation sign.
-Also, 12 categorical features are present in the dataset, they are presented in table X.
+simpler algorithms like HMMs. A name for example never ends with a punctuation sign,
+but it may be split by a punctuation sign.
 
-Finally the dataset was divided in a training, development and test set.
+\subsection{Data}
 
-Table 1 contains
+Finally the dataset was divided in a training, development and test set. Table 1 contains
 a description of the data files.
@@
 
+\subsection{Features}
+
+Twelve categorical features were added to each token in the dataset, they are presented in table X.
+
 \begin{table}[h]
@@
       \hline
-      Training    & unaccented token \\
+      Training    & unaccented lowercase token \\
       Training    & exact gazetteer match \\
       Training    & partial gazetteer match \\
+      Development & log name gazetteer count\\
+      Development & log word gazetteer count\\
       Development & is email \\
       Development & is number \\
-      Development & is title \\
+      Development & is honorific \\
       Development & is URL \\
       Development & is capitalized \\
-      Development & log name gazetteer count\\
-      Development & log word gazetteer count\\
-      Development & HTML tag parent + second parent \\
+      Development & HTML tag + parent \\
       Development & CSS class \\
@@
 
-\subsection{Features}
+The unaccented lowercase token was used as the key for the Glove-100 embedding lookup.
 
-\subsection{Gazetteer}
+A gazetteer was constructed from the researcher list extracted from DBLP with 1.595.771
+names. Feature 2 represents an exact match of a sequence of tokens to any of the 1.595.771 
+names, and feature 3 represents a partial match. Feature 4 is the rounded logarithm of 
+the frequency of a token in the gazetteer, and feature 5 is the rounded logarithm of the frequency
+of a token in word corpus obtained through a random crawl in university websites.
 
-\subsection{Evaluation}
+Features 5 to 8 represent a simple regular expression match to an email, number, 
+honorific or url, respectively. Feature 9 represents if a word is capitalized.
+
+Feature 10 represents the HTML enclosing tag and its parent concatenated. Feature 11
+represents all CSS classes concatenated. These features are not very useful in a general
+sense, because every HTML document has a different format, so only because a named entity
+occurs inside a given tag in a document we cannot say it is more likely to be so in other 
+documents. However, these features can be trained with the self training strategy described
+in section XXX to detect named entities in similar contexts in the same document.
+
+\section{Results}
 
 Performance was measured based on the F1 score (Van Rijsbergen, 1975)
-obtained in the test set. As in the ConLL dataset a named entity was
-only considered correct when it was an exact match of the corresponding 
-entity in the data file.
-
-\section{Results}
+obtained in the test set. A named entity was only considered correct when 
+it was an exact match of the corresponding entity in the data file.
 
@@
 \end{document}
+\documentclass[sigconf]{acmart}
+\settopmatter{printacmref=false} % Removes citation information below abstract
+\renewcommand\footnotetextcopyrightpermission[1]{} % removes footnote with conference information in first column
+\pagestyle{plain} % removes running headers
+\setcopyright{none}
+
+\usepackage{booktabs} % For formal tables
+\usepackage[ruled]{algorithm2e} % For algorithms
+\renewcommand{\algorithmcfname}{ALGORITHM}
+\SetAlFnt{\small}
+\SetAlCapFnt{\small}
+\SetAlCapNameFnt{\small}

### 2018-09-21 tex/article.tex
Modifications to paper.

@@
 
-Web information extraction is the task of automatically extracting structured information
+Web data extraction (WDE) is the task of automatically extracting structured information
 from unstructured or semi-structured web documents. The input usually consists of
@@
 
-Once we are able
-to reliably detect relevant entities, we may employ an information extraction 
-algorithm to extract structured data. In this paper, we investigate different NER 
-approaches from the perspective of web information extraction.
-
-HTML documents most often lie in between the structured / unstructured data paradigm, 
-which means that authors take quite a casual approach regarding formal structure. 
-However, DOM hierarchy, element disposition, class names, and other features related to 
+HTML documents most often lie in between the structured / unstructured data paradigm.
+DOM hierarchy, element disposition, class names, and other features related to 
 the document structure and indirectly associated with the data itself can be valuable 
@@
 strict rules. That is why classical information extraction systems such as automatic
-wrapper generators usually do not translate well across different websites. Contrastingly, 
-statistical based approaches can be much more flexible.
+wrapper generators usually do not translate well across different websites.
 
-NER systems are frequently trained and tested on news corpora such as the 
-dataset introduced at the Language-Independent Named Entity Recognition Shared Task
-at CONLL-2003 \cite{Sang2003}. State-of-the-art approaches have recently achieved 
-F1-scores of 90.10 \cite{Huang2015}, 90.94 \cite{Lample2016}, and 91.21 \cite{Ma2016} 
-in this task using different combinations of bidirectional LSTM layers, word and 
-character representations.
+Most existing web data extraction methods are tailored to extract data from a single
+web page \cite{Crescenzi2001, Arasu2003, Freitag1998, Califf1999, Soderland1999,
+Kushmerick2000, Hsu1998, Muslea1999}, producing different compromises between efficacy
+and degree of human supervision. More recent unsupervised approaches proposed to
+tackle the problem of data extraction for whole application domains \cite{Zhu2005, Zhu2006, 
+Abdessalem2010, Furche2012, Furche2012a}. Unsupervised WDE methods usually operate in at
+least two steps: record segmentation and attribute labelling. Record segmentation
+is essentially clustering visually and structurally similar web page regions and 
+identifying repeating data records. Attribute labelling is the task of identifying
+attributes in data records. Doing any of these tasks well can help performing the 
+other task, since patterns that are present in some data records can help identifying 
+attributes in other data records. And by properly identifying attributes, we are better 
+able to determine the boundaries of data records and segment them with increased accuracy.
 
-Even if focusing on web documents, records also may
-contain pure text that needs appropriate IE algorithms to extract the inherent data.
-Most WDE algorithms certainly can exploit the semi-structured nature of web documents, but can surely not restrict ourselves to that, because deeper processing is necessary.
-When looking through the algorithms and searching for the Swiss army knife, most algorithms can be ruled out for some incapability restricting the algorithms strongly.
-B.
+In recent years, we saw an astonishing progress in Natural Language Processing.
+However, despite WDE being a closely related field of research,
+many tools rely on heuristics or hand coded rules to perform record segmentation,
+and many methods resort to regular expressions or gazetteer matching to perform attribute
+labelling. While these approaches can be sufficient to extract information from webpages
+with similar templates, and identifying attributes with distinct formats like prices and
+dates, we still lack a sufficiently flexible and intelligent approach to handle more complicated cases.
+Even when extracting data from web documents only, data records may contain pure text with 
+relevant named entities. Also, many WDE algorithms can effectively exploit the semi-
+structure of web documents, but when a method relies too much on structural features, it
+often produces poor generalization on cross website extraction tasks. Contrastingly, we 
+understand that statistical based approaches can be much more flexible.
 
-NER on HTML poses a different type of challenge, because web pages are often
-very different from the plain text found in news corpora. Named entities may be present 
+In this paper, we investigate the attribute labelling task in WDE with a named entity 
+recognition framework. Recently proposed neural architectures have achieved exciting results 
+on the NER task on plain text \cite{Huang2015, Lample2016, Ma2016} while requiring almost 
+no feature engineering or gazetteers. NER on HTML poses a different type of challenge, 
+because web pages are often very different from plain text. Named entities may be present 
 inside tables, lists, graphs or other types of visual elements that provide
 little to no textual information that could give hints about the semantic category of 
-a word. Systems trained on news or similar corpora do not translate well to the web
-NER task without retraining, since in this task we cannot profit
-as much from contextual hints or transfer learning approaches such as word embeddings.
-Besides, deep learning approaches can require a lot of data to reach peak performance.
+a word. However we show that we can get exceptional performance even with this limitation
+and small training sets.
 
-To test different NER approaches from the perspective of web information extraction,
-we will explore the task of person names extraction from university faculty websites.
-Researcher affiliation is often missing from many entries in public databases such as DBLP  
-\footnote{
-  http://dblp.uni-trier.de/
-} and the display of information varies significantly between different university 
+By reliably detecting named entities, we can improve the performance of existing WDE 
+approaches or even construct a full machine learning based tool to tackle domain wide
+extraction with great flexibility. To test different NER approaches from the perspective 
+of web data extraction,
+we explored the task of person names extraction from university faculty listings.
+Researcher affiliation is often missing from many entries in public databases 
+and the display of information varies significantly between different university 
 websites, so this task can provide a good measure of the expected performance and
-data need for other web information extraction tasks. Also, with the lack of a large amount
-of training data, we show that feature engineering and resources such as a gazetteer 
-may be invaluable.
+data need for other web data extraction tasks.
 
@@
 Most data extraction systems focus on extracting information from single websites
-and thus are unsuited for cross website extraction tasks. Even unsupervised
+and are therefore unsuited for cross website extraction tasks. Even unsupervised
 approaches that are domain independent, such as RoadRunner \cite{Crescenzi2001} 
 and EXALG \cite{Arasu2003} only work well for extracting data from pages generated 
-from the same underlying template. A statistical approach to unsupervised domain 
+from the same template. A statistical approach to unsupervised domain 
 independent web data extraction was described by Zhu et al \cite{Zhu2005}. The 2D CRF 
@@
 
-In summary, web data extraction methods have undoubtedly improved extraordinarily, but
+Web data extraction methods have undoubtedly improved extraordinarily, but
 as pointed by Schulz et al. \cite{Schulz2016}, it is difficult to compare the results 
@@
 namely: Hidden Markov Models and Linear Chain Conditional Random Fields. And further
-we explore the neural architectures.
+we explore neural architectures.
 
@@
 \begin{itemize}
-\item Train the HMM in a given training set without the HTML features.
+\item Train the HMM with the training set without HTML features.
 \item Compute labels for the new websites with the trained HMM.
@@
 
+\begin{figure}
+  \centering
+  \includegraphics[width=0.5\textwidth]{pics/rnn_network}
+  \caption{RNN for NER}
+  \label{fig:rnn_network}
+\end{figure}
+
 Recurrent neural networks (RNN) have been succesfully employed on numerous NLP tasks such as
@@
 and consequently for solving text related tasks. In NER, the network outputs one label for each input 
-vector as Figure YYY.
-
-<INSERT FIGURE YYY>
+vector as showed in Figure \ref{fig:rnn_network}.
 
@@
 \Gamma_f^{<t>} &= \sigma(W_f[x^{<t>},h^{<t-1>}] + b_f) &\\ 
-c^{<t>}        &= \Gamma_f^{<t>} \circ c^{<t-1>} + \Gamma_i^{<t>} tanh(W_{c,x} x^{t} + W_{c,a} a^{t-1} + b_c) &\\
+c^{<t>}        &= \Gamma_f^{<t>} \circ c^{<t-1>} + \Gamma_i^{<t>} tanh(W_c[x^{<t>},h^{<t-1>}] + b_c) &\\
 \Gamma_o^{<t>} &= \sigma(W_o[x^{<t>},h^{<t-1>}] + b_o) &\\
@@
 \end{flalign*}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.5\textwidth]{pics/lstm_cell}
+  \caption{LSTM Cell}
+  \label{fig:lstm_cell}
+\end{figure}
 
@@
 from the previous timestep $ h^{<t-1>} $. A visual description of our LSTM cell is 
-provided in figure XXX.
+provided in figure \ref{fig:lstm_cell}.
 This implementation differs from the LSTM cell described in Huang et al. \cite{Huang2015}
@@
 do not take input from the previous cell state $ c^{<t-1>} $ and the output gate does
-not take input from the current cell state $ c^{<t>} $. The cell state and the control
-gates are what makes the LSTM cell better at modelling long term dependencies in comparison
+not take input from the current cell state $ c^{<t>} $. The cell state and the control gates 
+are what makes the LSTM cell better at modelling long term dependencies in comparison
 to a regular RNN.
-
-XXX Insert figure explaining equations XXX
 
@@
 \subsubsection{LSTM-CRF}
+\label{sssec:lstm_crf}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.5\textwidth]{pics/bi_lstm_crf}
+  \caption{Bidirectional LSTM-CRF}
+  \label{fig:bi_lstm_crf}
+\end{figure}
 
@@
 the sequence tagging problem. The CRF layer jointly decodes labels for the whole sentence instead
-of predicting each label individually. This architecture achieved an F1 score of 90.10 in the 
-ConL2003 dataset, in contrast to 85.17 for a bidirectional LSTM without the CRF layer. 
+of predicting each label individually. This architecture achieved an F1 score of 90.10 on the English
+data from CONLL-2003 shared task \cite{Sang2003}, in contrast to 85.17 for a bidirectional LSTM without the CRF layer. 
 In our experiments, the LSTM-CRF architecture used a bidirectional LSTM with 100 
@@
 \subsubsection{LSTM-CRF + CNN character representations}
+\ref{sssec:lstm_crf_cnn}
 
-Ma and Hovy \cite{Ma2016} proposed adding a convolutional neural networks (CNN) layer 
-on top of a bidirectional LSTM-CRF to encode character-level information. Those character
-representations are combined with word level representations and then fed to the
-Bidirectional LSTM. This architecture possesses the capacity to learn morphological
-token features that are extremely useful on the NER task, since similar named entities 
-often present morphological similarities. This improvement obtained an F1 score of 
-91.21 at the ConLL2003 dataset. In our experiments, the LSTM-CRF architecture with
-CNN character representations used a one dimensional convolutional neural network with 30 
-filters and a window size of three characters on top of the LSTM-CRF architecture,
-the character embeddings fed to the CNN had 30 dimensions that were randomly initialized.
+\begin{figure}
+  \centering
+  \includegraphics[width=0.5\textwidth]{pics/cnn}
+  \caption{CNN}
+  \label{fig:cnn}
+\end{figure}
+
+Ma and Hovy \cite{Ma2016} proposed adding a convolutional neural network (CNN) layer 
+on top of a bidirectional LSTM-CRF to encode character-level information. The CNN
+layer is described visually in Figure \ref{fig:cnn}, it receives
+only character embeddings as inputs. The character representations generated by the CNN 
+are combined with word level representations and then fed to the Bidirectional LSTM with
+a CRF output layer described in section \ref{sssec:lstm_crf}.
+This architecture can learn morphological features that are very
+useful in the NER task, since similar named entities often present morphological similarities. 
+This architecture obtained an F1 score of 91.21 in the ConLL2003 dataset. In our experiments, 
+the LSTM-CRF architecture with CNN character representations uses a one dimensional convolutional 
+neural network with 30 filters and a window size of three characters on top of the LSTM-CRF architecture.
+The character embeddings fed to the CNN had 30 dimensions that were randomly initialized.
 
@@
 
+\begin{figure}
+  \centering
+  \includegraphics[width=0.5\textwidth]{pics/lstm_char_representations}
+  \caption{LSTM character representations}
+  \label{fig:lstm_char}
+\end{figure}
+
 Lample et al \cite{Lample2016} suggested using an a bidirectional LSTM to model character-level 
 representations on a bidirectional LSTM-CRF. Combining both the forward and backward 
-LSTM representations to form the character representation. This character
-representation is also combined with a word representation. The forward LSTM is expected to be a better
+LSTM representations to form the character representation, as described in figure \ref{fig:lstm_char}. 
+This character representation is also combined with a word representation and fed to a LSTM-CRF network. 
+The forward LSTM is expected to be a better
 representation of the suffix of a token, and the backward LSTM is expected to be a
 better representation of the prefix of a token. This differentiates the architecture
-from the CNN based approach, because CNN filters discover positional invariant
-features, while LSTMs can better represent suffixes and prefixes. In our experiments, 
-the LSTM-CRF architecture with LSTM character embeddings was implemented by a bidirectional LSTM
+from the CNN based approach described in Section \ref{sssec:lstm_crf_cnn}, because CNN filters 
+discover positional invariant features, while LSTMs can better represent suffixes and prefixes. In our experiments, 
+the LSTM-CRF architecture with LSTM character representations was implemented with a bidirectional LSTM
 with 25 hidden states, producing character representations of size 50. The character embeddings
-also had 30 dimensions that were randomly initialized.
+had 30 dimensions that were randomly initialized.
 
@@
 
-The neural models were trained with Stochastic Gradient Descent over 50 epochs using a learning 
-rate of 0.01 and momentum of 0.9. We used early stopping \cite{Caruana2000} to select the best 
+The neural models were trained with mini batch Stochastic Gradient Descent over 50 epochs with batch size 10,
+learning rate 0.01, momentum 0.9 and decay rate 0.05. We used early stopping \cite{Caruana2000} to select the best 
 parameters, considering the F1 measure in the validation set. All neural models used 
@@
 they have a vocabulary size of 400.000 words.
-In the case of NER on HTML, word embeddings work as a rather satisfactory gazetteer. Named entities 
-of a same type have similar embeddings, so with good word embeddings we can achieve exceptional 
-performance with little training data and without a gazetteer. Figure XXX illustrates the differences
-between the three neural models mentioned previously.
-
-XXX Insert picture here explaining the models Figure 1 XXX
+In the case of NER on HTML, word embeddings work similar to a gazetteer. Named entities 
+of a same type have similar embeddings, so good word embeddings can achieve exceptional 
+performance with little training and without a gazetteer.
 
@@
 information extraction datasets, each web page in the dataset comes from a different 
-university, and therefore has a different format, what makes many information
+website, and therefore has a different format, what makes many information
 extraction approaches impractical. The idea is to explore systems that are general 
-enough to allow efficient name extraction from many different sources without requiring
-any supervision between different websites.
+enough to allow efficient name extraction from many different sources while requiring
+no supervision between different websites.
 
 This task would be similar to the task of labeling authors in comments
-from many different sources or labeling authors in articles collected from many
-publishing platforms. Another similar task would be NER on tweets. Because of the character
-limitation present on tweets, we end up with constraints comparable to the ones 
-found in the NER on HTML task, so we expect similar systems to have comparable performances
-on both of these tasks.
-
-We collected 145 computer science faculty pages from 42 different countries in 
-multiple languages, although the English version was prefered when it was available. 
-We gathered faculty web pages randomly in proportion to 
-the number of universities in each country\footnote{A detailed list of universities can 
-be found in https://univ.cc/world.php}. Each HTML page was preprocessed and converted
-to the CONLL 2003 data format. That is, one word per line with empty lines representing
-sentence boundaries. Sentence boundaries were determined by line break HTML tags
-(div, p, table, li, br, etc.) in contrast to inline tags (span, em, a, td, etc.). Sentences
-that were more than 50 tokens were also split according to punctuation.
-
-A proper HTML segmenter poses many challenges by itself as discussed for example in \cite{Cai2003}.
 However, we wanted to evaluate models without relying on any sophisticated data record
@@
 Finally, all tokens were tagged using the IOB scheme put forward by
-Ramshaw and Marcus \cite{Ramshaw1995} with a modification. O stands for Outside, 
-B-PER is the beginning of a person name, I-PER inside a person name and PUNCT is any 
-punctuation sign other than ".". Many name representations contain punctuation signs 
-and the PUNCT label helps predicting label transitions properly, especially when using 
-simpler algorithms like HMMs. A name for example never ends with a punctuation sign,
-but it may be split by a punctuation sign.
+Ramshaw and Marcus \cite{Ramshaw1995}.
 
@@
       10 & Is capitalized \\
-      11 & HTML tag + parent \\
-      12 & CSS class \\
+      11 & Is a punctuation sign \\
+      12 & HTML tag + parent \\
+      13 & CSS class \\
       \hline
@@
 of a token in a word corpus obtained through a random crawl in university websites.
-Features 6 to 9 represent a simple regular expression match to an email, number, 
-honorific or URL, respectively. Feature 10 represents if a word is capitalized.
+Features 6 to 11 represent a simple regular expression match to an email, number, 
+honorific, URL, capitalization and punctuation sign.
 
-Feature 11 represents the HTML enclosing tag and its parent concatenated. Feature 12
+Feature 12 represents the HTML enclosing tag and its parent concatenated. Feature 13
 represents all CSS classes concatenated. These features are not very useful in a general
@@
 in other documents. However, these features can be trained with the self-training strategy 
-for HMMs described in section \ref{sssec:self_training}. For all other models these features 
+for HMMs described in section \ref{sssec:self_training}. In all other models these features 
 were ignored.
@@
 whole training set (90 documents). In the second experiment, the training set was split 
-into five non overlapping sets with only 18 documents and the validation set was reduced 
-to 5 documents, but the test set was kept unchanged. The goal of this second experiment 
+into five non overlapping sets with only 18 documents, but the test set was kept unchanged. 
+The goal of this second experiment 
 was to evaluate models when training data is scarce, since labelling data can be a very 
@@
       \hline
-      hmm-1           & 0.5282 & 0.9226 & 0.6718 & 0.5333 & 0.8409 & 0.6527 \\
-      hmm-2           & 0.5282 & 0.9226 & 0.6718 & 0.5333 & 0.8409 & 0.6527 \\
-      hmm-3           & 0.5282 & 0.9226 & 0.6718 & 0.5333 & 0.8409 & 0.6527 \\
-      crf             & 0.5282 & 0.9226 & 0.6718 & 0.5333 & 0.8409 & 0.6527 \\
-      lstm-crf        & 0.5282 & 0.9226 & 0.6718 & 0.5333 & 0.8409 & 0.6527 \\
-      lstm-crf-cnn    & 0.5282 & 0.9226 & 0.6718 & 0.5333 & 0.8409 & 0.6527 \\
-      lstm-crf-lstm   & 0.5282 & 0.9226 & 0.6718 & 0.5333 & 0.8409 & 0.6527 \\
-      hmm-1+F         & 0.5282 & 0.9226 & 0.6718 & 0.5333 & 0.8409 & 0.6527 \\
-      hmm-2+F         & 0.5282 & 0.9226 & 0.6718 & 0.5333 & 0.8409 & 0.6527 \\
-      hmm-3+F         & 0.5282 & 0.9226 & 0.6718 & 0.5333 & 0.8409 & 0.6527 \\
-      hmm-3+F+ST      & 0.5282 & 0.9226 & 0.6718 & 0.5333 & 0.8409 & 0.6527 \\
-      crf+F           & 0.5282 & 0.9226 & 0.6718 & 0.5333 & 0.8409 & 0.6527 \\
-      lstm-crf+F      & 0.5282 & 0.9226 & 0.6718 & 0.5333 & 0.8409 & 0.6527 \\
-      lstm-crf-cnn+F  & 0.5282 & 0.9226 & 0.6718 & 0.5333 & 0.8409 & 0.6527 \\
-      lstm-crf-lstm+F & 0.5282 & 0.9226 & 0.6718 & 0.5333 & 0.8409 & 0.6527 \\
+      hmm-1	      & 0.6965 & 0.5749 & 0.6299 & 0.6263 & 0.4431 & 0.5190 \\
+      hmm-2	      & 0.7047 & 0.6286 & 0.6645 & 0.6480 & 0.5222 & 0.5783 \\
+      hmm-3	      & 0.6127 & 0.6141 & 0.6134 & 0.5471 & 0.4634 & 0.5018 \\
+      crf	      & 0.7237 & 0.6650 & 0.6931 & 0.6734 & 0.5879 & 0.6278 \\
+      lstm-crf        & 0.8607 & 0.8848 & 0.8726 & 0.8546 & 0.8294 & 0.8418 \\
+      lstm-crf-cnn    & 0.9221 & 0.9206 & 0.9214 & 0.9030 & 0.8283 & 0.8640 \\
+      lstm-crf-lstm   & 0.9129 & 0.9441 & 0.9282 & 0.8906 & 0.8807 & 0.8856 \\
       \hline
@@
 
-A named entity was only considered correct when 
-it was an exact match of the corresponding entity in the data file. 
-Models were trained on each of the five sets separately and tested
-in the same test set, and each model was trained on each of the five 
-sets and evaluated on the same validation and test sets.
+Experiment 1 consists of testing the models on the complete NER on HTML dataset 
+described in section \ref{sec:ner_dataset}. Table \ref{tab:experiment1} shows the 
+results for models that employed no features, except for the words in the text
+in the case of HMMs and Glove-100 word embeddings in the case of CRFs and Neural Models.
+Without carefully designed features and a gazetteer, HMMs and CRFs have a very 
+poor performance, achieving only 57.83 for HMM-2 and 62.78 for CRF in the test set. 
+The neural models however achieved high F-scores, even with no features. The
+plain LSTM-CRF architecture improved significantly in comparison to the conventional CRF,
+and the LSTM-CRF architectures with neural character representations boosted the F1 score
+by 2.32 for CNN representations and 4.38 for LSTM representations, showing that they are 
+able to learn morphological features automatically, and that at least in the NER tasks LSTM 
+character representations are superior, perhaps because they are able to differentiate 
+suffixes and prefixes, while CNNs are position invariant. This experiment also shows that
+pretrained word embeddings can be used to identify named entities in HTML, where
+textual context is very limited without resorting to gazetteers.
+
+\begin{table}[h]
+  \small
+  \begin{center}
+    \begin{tabular}{ |l|l|l|l|l|l|l| }
+      \hline
+      \multirow{2}{*}{Model} & \multicolumn{3}{c|}{Validation} & \multicolumn{3}{c|}{Test} \\
+                             & \multicolumn{1}{c}{Precision} & \multicolumn{1}{c}{Recall} & \multicolumn{1}{c|}{F1}
+                             & \multicolumn{1}{c}{Precision} & \multicolumn{1}{c}{Recall} & \multicolumn{1}{c|}{F1} \\
+      \hline
+      hmm-1+F	      & 0.6061 & 0.7282 & 0.6616 & 0.7106 & 0.7633 & 0.7360 \\
+      hmm-2+F	      & 0.6279 & 0.7550 & 0.6856 & 0.7521 & 0.7810 & 0.7663 \\
+      hmm-3+F	      & 0.6573 & 0.7819 & 0.7142 & 0.7523 & 0.7795 & 0.7657 \\
+      hmm-1+F+ST      & 0.7032 & 0.9077 & 0.7925 & 0.7522 & 0.8663 & 0.8052 \\
+      hmm-2+F+ST      & 0.7321 & 0.9172 & 0.8143 & 0.7737 & 0.8789 & 0.8230 \\
+      hmm-3+F+ST      & 0.7551 & 0.9172 & 0.8283 & 0.7961 & 0.8534 & 0.8237 \\
+      crf+F	      & 0.8982 & 0.9128 & 0.9054 & 0.8812 & 0.8298 & 0.8547 \\
+      lstm-crf+F      & 0.9378 & 0.9441 & 0.9409 & 0.8959 & 0.8807 & 0.8883 \\
+      lstm-crf-cnn+F  & 0.8998 & 0.9799 & 0.9382 & 0.8910 & 0.9295 & 0.9098 \\
+      lstm-crf-lstm+F & 0.9495 & 0.9569 & 0.9532 & 0.9163 & 0.8888 & 0.9023 \\
+      \hline
+    \end{tabular}
+  \end{center}
+  \caption{Precision, recall and F1 in the complete dataset}
+  \label{tab:experiment1f}
+\end{table}
+
+Table \ref{tab:experiment1f} shows the results on experiment 1 for models
+that employed all features described on Table \ref{tab:features}. In this case
+we see that conventional models like HMMs, and CRFs can become competitive with
+the right selection of features and a good gazetteer, however they still lose
+to the best neural model without features showing their limitation. We can also
+see that the self training strategy for HMMs improved the quality of the results
+significantly on all cases, boosting both precision and recall.
+
+The neural models also improved a little with the addition of features. The fact that 
+the LSTM-CRF gets much closer to the neural models with character representations
+shows that the LSTM and CNN character representations were probably able to learn 
+at least part of the features automatically, and when we add them explicitly,
+the difference in performance becomes less noticeable.
 
@@
       lstm-crf-lstm   & 0.5333 (0.111) & 0.8409 (0.111) & 0.6527 (0.111) \\
+      \hline
+    \end{tabular}
+  \end{center}
+  \caption{Precision, recall and F1 in the small dataset}
+  \label{tab:experiment2}
+\end{table}
+
+The second experiment aimed at evaluating the performance of sequence models
+when the dataset is reduced to only 18 labeled documents. A feasible amount of 
+labelling in most WDE tasks. The experiment was repeated in five non overlapping 
+sets of training data, and the results were averaged. Table \ref{tab:experiment2} 
+describes the results for models without any features. We only present results
+for the test set in this experiment. The standard deviation is shown next to each
+measure.
+
+We can see that the performance of all models was reduced in comparison 
+to experiment 1. That is to be expected.
+
+\begin{table}[h]
+  \small
+  \begin{center}
+    \begin{tabular}{ |l|l|l|l|}
+      \hline
+      \multirow{2}{*}{Model} & \multicolumn{3}{c|}{Test} \\
+                             & \multicolumn{1}{c}{Precision} & \multicolumn{1}{c}{Recall} & \multicolumn{1}{c|}{F1} \\
+      \hline
       hmm-1+F         & 0.5333 (0.111) & 0.8409 (0.111) & 0.6527 (0.111) \\
@@
       hmm-3+F         & 0.5333 (0.111) & 0.8409 (0.111) & 0.6527 (0.111) \\
+      hmm-1+F+ST        & 0.5333 (0.111) & 0.8409 (0.111) & 0.6527 (0.111) \\
+      hmm-2+F+ST        & 0.5333 (0.111) & 0.8409 (0.111) & 0.6527 (0.111) \\
       hmm-3+F+ST        & 0.5333 (0.111) & 0.8409 (0.111) & 0.6527 (0.111) \\
@@
   \caption{Precision, recall and F1 in the small dataset}
-  \label{tab:experiment2}
+  \label{tab:experiment2f}
 \end{table}
 
-were trained 
-consisted of training
-all models with the whole training set (90 documents) and the second experiment trained
-them on five subsets with 18 documents
-Table X presents the results for X models in the NER-HTML dataset. Results
-for each model are presented when incorporating all features and no features.
+We can see that the performance of all models was reduced in comparison 
+to experiment 1. That is to be expected.
+
+\section{Conclusion}
 
@@
 Label dependency is necessary.
-
-\section{Conclusion}
-
 Our name extraction method achieved 94.40\% precision, 97.61\% recall 

### 2018-09-21 train_model.py

@@ -176,7 +176,7 @@ elif model in ['maxent', 'crf', 'lstm-crf', 'lstm-crf-cnn', 'lstm-crf-lstm']:
   )
   
   lstm_crf.create(we.matrix)
-  lstm_crf.fit(callbacks=[Metrics(lstm_crf)], epochs=5)
+  lstm_crf.fit(callbacks=[Metrics(lstm_crf)], epochs=10)
 
   lstm_crf.load_best_model()
   val_predict, val_targ, T = lstm_crf.validate()

### 2018-09-21 x.sh

@@ -4,4 +4,4 @@
 ./collect_results.sh dataset/small_dev_3.txt > logs/small_dev_3.log
 ./collect_results.sh dataset/small_dev_4.txt > logs/small_dev_4.log
 ./collect_results.sh dataset/small_dev_5.txt > logs/small_dev_5.log
-./collect_results.sh conll > logs/conll_train.log
+# ./collect_results.sh conll > logs/conll_train.log

### 2018-09-21 tex/article.tex
Nice tables.

@@
 \DeclareMathOperator*{\argmax}{arg\,max\,}
+\renewcommand{\arraystretch}{1.2}
 
@@
   \begin{center}
-    \begin{tabular}{ |l|l|l|l|l| }
-      \hline
+    \begin{tabular}{ lllll }
+      \toprule
       Data file & Documents & Sentences & Tokens & Names \\
-      \hline
-      Training    & 92 & 28958 & 124984 & 6382 \\
-      Validation  & 28 & 9117  & 39748  & 2258 \\
-      Test        & 25 & 5790  & 26995  & 1949 \\
-      \hline
+      \midrule
+      Training    & 85 & 24728 & 110269 & 5822 \\  
+      Validation  & 30 & 8743  & 36757  & 1788 \\
+      Test        & 30 & 10399 & 44795  & 2708 \\
+      \bottomrule
     \end{tabular}
@@
   \begin{center}
-    \begin{tabular}{ |l|l| }
-      \hline
+    \begin{tabular}{ ll }
+      \toprule
       Feature & Description \\
-      \hline
+      \midrule
       1  & Unaccented lowercase token \\
@@
       13 & CSS class \\
-      \hline
+      \bottomrule
     \end{tabular}
   \end{center}
-  \caption{Features present in the bla dataset}
+  \caption{Features used in the NER on HTML dataset}
   \label{tab:features}
+\end{table}
+
+\begin{table}[h]
+  \small
+  \begin{center}
+    \begin{tabular}{ lllll }
+      \toprule
+      Data file & Precision & Recall & F1 & Correct names \\
+      \midrule
+      Training   & 0.7316 & 0.2303 & 0.3504 & 1341 from 5822 \\ 
+      Validation & 0.8474 & 0.2858 & 0.4274 & 511 from 1788 \\ 
+      Test       & 0.8717 & 0.3287 & 0.4773 & 890 from 2708 \\ 
+      \bottomrule
+    \end{tabular}
+  \end{center}
+  \caption{Gazetteer coverage in each data file}
+  \label{tab:gazetteer}
 \end{table}
@@
 A gazetteer was constructed from a researcher list extracted from DBLP with 1.595.771
-names. Feature 2 represents an exact match of a sequence of tokens to any of the 1.595.771 
+names. Table \ref{tab:gazetteer} shows the precision, recall and F1 score obtained with an
+exact gazetteer matching strategy in each data file as a baseline.
+Feature 2 represents an exact match of a sequence of tokens to any of the 1.595.771 
 names, and feature 3 represents a partial match. Feature 4 is the rounded logarithm of 
@@
   \begin{center}
-    \begin{tabular}{ |l|l| }
-      \hline
+    \begin{tabular}{ ll }
+      \toprule
       Model & Description \\
-      \hline
+      \midrule
       hmm-1         & Regular HMM \\
@@
       lstm-crf-lstm & LSTM-CRF with LSTM character representations \cite{Lample2016} \\
-      \hline
+      \bottomrule
     \end{tabular}
@@
   \begin{center}
-    \begin{tabular}{ |l|l|l|l|l|l|l| }
-      \hline
-      \multirow{2}{*}{Model} & \multicolumn{3}{c|}{Validation} & \multicolumn{3}{c|}{Test} \\
-                             & \multicolumn{1}{c}{Precision} & \multicolumn{1}{c}{Recall} & \multicolumn{1}{c|}{F1}
-                             & \multicolumn{1}{c}{Precision} & \multicolumn{1}{c}{Recall} & \multicolumn{1}{c|}{F1} \\
-      \hline
+    \begin{tabular}{ lllllll }
+      \toprule
+      \multirow{2}{*}{Model} & \multicolumn{3}{c}{Validation} & \multicolumn{3}{c}{Test} \\
+                             & \multicolumn{1}{c}{P} & \multicolumn{1}{c}{R} & \multicolumn{1}{c}{F1}
+                             & \multicolumn{1}{c}{P} & \multicolumn{1}{c}{R} & \multicolumn{1}{c}{F1} \\
+      \midrule
       hmm-1	    & 0.6965 & 0.5749 & 0.6299 & 0.6263 & 0.4431 & 0.5190 \\
@@
       hmm-3	    & 0.6127 & 0.6141 & 0.6134 & 0.5471 & 0.4634 & 0.5018 \\
-      crf	      & 0.7237 & 0.6650 & 0.6931 & 0.6734 & 0.5879 & 0.6278 \\
-      lstm-crf        & 0.8607 & 0.8848 & 0.8726 & 0.8546 & 0.8294 & 0.8418 \\
-      lstm-crf-cnn    & 0.9221 & 0.9206 & 0.9214 & 0.9030 & 0.8283 & 0.8640 \\
-      lstm-crf-lstm   & 0.9129 & 0.9441 & 0.9282 & 0.8906 & 0.8807 & 0.8856 \\
-      \hline
+      crf	    & 0.7173 & 0.6683 & 0.6920 & 0.6671 & 0.5868 & 0.6244 \\
+      lstm-crf	    & 0.8484 & 0.9044 & 0.8755 & 0.8358 & 0.8497 & 0.8427 \\
+      lstm-crf-cnn  & 0.9058 & 0.9575 & 0.9309 & 0.8779 & 0.8737 & 0.8758 \\
+      lstm-crf-lstm & 0.9134 & 0.9435 & 0.9282 & 0.8920 & 0.8815 & 0.8867 \\
+      \bottomrule
     \end{tabular}
@@
   \begin{center}
-    \begin{tabular}{ |l|l|l|l|l|l|l| }
-      \hline
-      \multirow{2}{*}{Model} & \multicolumn{3}{c|}{Validation} & \multicolumn{3}{c|}{Test} \\
-                             & \multicolumn{1}{c}{Precision} & \multicolumn{1}{c}{Recall} & \multicolumn{1}{c|}{F1}
-                             & \multicolumn{1}{c}{Precision} & \multicolumn{1}{c}{Recall} & \multicolumn{1}{c|}{F1} \\
-      \hline
+    \begin{tabular}{ lllllll }
+      \toprule
+      \multirow{2}{*}{Model} & \multicolumn{3}{c}{Validation} & \multicolumn{3}{c}{Test} \\
+                             & \multicolumn{1}{c}{P} & \multicolumn{1}{c}{R} & \multicolumn{1}{c}{F1}
+                             & \multicolumn{1}{c}{P} & \multicolumn{1}{c}{R} & \multicolumn{1}{c}{F1} \\
+      \midrule
       hmm-1+F	      & 0.6061 & 0.7282 & 0.6616 & 0.7106 & 0.7633 & 0.7360 \\
@@
       hmm-3+F+ST      & 0.7551 & 0.9172 & 0.8283 & 0.7961 & 0.8534 & 0.8237 \\
-      crf+F	      & 0.8982 & 0.9128 & 0.9054 & 0.8812 & 0.8298 & 0.8547 \\
-      lstm-crf+F      & 0.9378 & 0.9441 & 0.9409 & 0.8959 & 0.8807 & 0.8883 \\
-      lstm-crf-cnn+F  & 0.8998 & 0.9799 & 0.9382 & 0.8910 & 0.9295 & 0.9098 \\
-      lstm-crf-lstm+F & 0.9495 & 0.9569 & 0.9532 & 0.9163 & 0.8888 & 0.9023 \\
-      \hline
+      crf+F	      & 0.9024 & 0.9049 & 0.9037 & 0.8751 & 0.8227 & 0.8481 \\
+      lstm-crf+F      & 0.9430 & 0.9530 & 0.9480 & 0.8998 & 0.8527 & 0.8756 \\
+      lstm-crf-cnn+F  & 0.9244 & 0.9715 & 0.9474 & 0.9017 & 0.8973 & 0.8995 \\
+      lstm-crf-lstm+F & 0.9465 & 0.9692 & 0.9577 & 0.9108 & 0.8715 & 0.8907 \\
+      \bottomrule
     \end{tabular}
@@
   \begin{center}
-    \begin{tabular}{ |l|l|l|l|}
-      \hline
-      \multirow{2}{*}{Model} & \multicolumn{3}{c|}{Test} \\
-                             & \multicolumn{1}{c}{Precision} & \multicolumn{1}{c}{Recall} & \multicolumn{1}{c|}{F1} \\
-      \hline
-      hmm-1           & 0.5333 (0.111) & 0.8409 (0.111) & 0.6527 (0.111) \\
-      hmm-2           & 0.5333 (0.111) & 0.8409 (0.111) & 0.6527 (0.111) \\
-      hmm-3           & 0.5333 (0.111) & 0.8409 (0.111) & 0.6527 (0.111) \\
-      crf             & 0.5333 (0.111) & 0.8409 (0.111) & 0.6527 (0.111) \\
-      lstm-crf        & 0.5333 (0.111) & 0.8409 (0.111) & 0.6527 (0.111) \\
-      lstm-crf-cnn    & 0.5333 (0.111) & 0.8409 (0.111) & 0.6527 (0.111) \\
-      lstm-crf-lstm   & 0.5333 (0.111) & 0.8409 (0.111) & 0.6527 (0.111) \\
-      \hline
+    \begin{tabular}{ lllllll }
+      \toprule
+      \multirow{2}{*}{Model} & \multicolumn{2}{c}{Precision} & \multicolumn{2}{c}{Recall} & \multicolumn{2}{c}{F1} \\
+                             & \multicolumn{1}{c}{\tiny{M}} & \multicolumn{1}{c}{\tiny{SD}}
+			     & \multicolumn{1}{c}{\tiny{M}} & \multicolumn{1}{c}{\tiny{SD}}
+			     & \multicolumn{1}{c}{\tiny{M}} & \multicolumn{1}{c}{\tiny{SD}} \\
+      \midrule
+      hmm-1	      & 0.2856 & 0.1127 & 0.1623 & 0.0810 & 0.2036 & 0.0892 \\
+      hmm-2	      & 0.3436 & 0.1134 & 0.2060 & 0.1058 & 0.2483 & 0.0997 \\
+      hmm-3	      & 0.2707 & 0.0955 & 0.2163 & 0.0927 & 0.2316 & 0.0793 \\
+      crf	      & 0.6249 & 0.0433 & 0.5272 & 0.0348 & 0.5711 & 0.0301 \\
+      lstm-crf	      & 0.6982 & 0.0495 & 0.6538 & 0.0532 & 0.6751 & 0.0499 \\
+      lstm-crf-cnn    & 0.7906 & 0.0557 & 0.7431 & 0.0687 & 0.7652 & 0.0572 \\
+      lstm-crf-lstm   & 0.7935 & 0.0345 & 0.7360 & 0.0424 & 0.7626 & 0.0237 \\
+      \bottomrule
     \end{tabular}
@@
   \begin{center}
-    \begin{tabular}{ |l|l|l|l|}
-      \hline
-      \multirow{2}{*}{Model} & \multicolumn{3}{c|}{Test} \\
-                             & \multicolumn{1}{c}{Precision} & \multicolumn{1}{c}{Recall} & \multicolumn{1}{c|}{F1} \\
-      \hline
-      hmm-1+F         & 0.5333 (0.111) & 0.8409 (0.111) & 0.6527 (0.111) \\
-      hmm-2+F         & 0.5333 (0.111) & 0.8409 (0.111) & 0.6527 (0.111) \\
-      hmm-3+F         & 0.5333 (0.111) & 0.8409 (0.111) & 0.6527 (0.111) \\
-      hmm-1+F+ST        & 0.5333 (0.111) & 0.8409 (0.111) & 0.6527 (0.111) \\
-      hmm-2+F+ST        & 0.5333 (0.111) & 0.8409 (0.111) & 0.6527 (0.111) \\
-      hmm-3+F+ST        & 0.5333 (0.111) & 0.8409 (0.111) & 0.6527 (0.111) \\
-      crf+F           & 0.5333 (0.111) & 0.8409 (0.111) & 0.6527 (0.111) \\
-      lstm-crf+F      & 0.5333 (0.111) & 0.8409 (0.111) & 0.6527 (0.111) \\
-      lstm-crf-cnn+F  & 0.5333 (0.111) & 0.8409 (0.111) & 0.6527 (0.111) \\
-      lstm-crf-lstm+F & 0.5333 (0.111) & 0.8409 (0.111) & 0.6527 (0.111) \\
-      \hline
+    \begin{tabular}{lllllll}
+      \toprule
+      \multirow{2}{*}{Model} & \multicolumn{2}{c}{Precision} & \multicolumn{2}{c}{Recall} & \multicolumn{2}{c}{F1} \\
+                             & \multicolumn{1}{c}{\tiny{M}} & \multicolumn{1}{c}{\tiny{SD}}
+			     & \multicolumn{1}{c}{\tiny{M}} & \multicolumn{1}{c}{\tiny{SD}}
+			     & \multicolumn{1}{c}{\tiny{M}} & \multicolumn{1}{c}{\tiny{SD}} \\
+      \midrule
+      hmm-1+F	      & 0.6205 & 0.0927 & 0.6402 & 0.0717 & 0.6290 & 0.0774 \\
+      hmm-2+F	      & 0.5999 & 0.0879 & 0.6527 & 0.0389 & 0.6229 & 0.0595 \\
+      hmm-3+F	      & 0.5712 & 0.0957 & 0.6258 & 0.0494 & 0.5954 & 0.0722 \\
+      hmm-1+F+ST      & 0.6536 & 0.0886 & 0.7579 & 0.1118 & 0.7012 & 0.0963 \\
+      hmm-2+F+ST      & 0.7044 & 0.0726 & 0.7810 & 0.1039 & 0.7397 & 0.0834 \\
+      hmm-3+F+ST      & 0.6619 & 0.0722 & 0.7174 & 0.0892 & 0.6879 & 0.0777 \\
+      crf+F	      & 0.8419 & 0.0326 & 0.7530 & 0.0823 & 0.7933 & 0.0541 \\
+      lstm-crf+F      & 0.8376 & 0.0225 & 0.7838 & 0.0518 & 0.8093 & 0.0345 \\
+      lstm-crf-cnn+F  & 0.8542 & 0.0336 & 0.7820 & 0.0767 & 0.8149 & 0.0478 \\
+      lstm-crf-lstm+F & 0.8554 & 0.0219 & 0.8013 & 0.0825 & 0.8255 & 0.0478 \\
+      \bottomrule
     \end{tabular}

### 2018-09-21 tex/article.tex
Final version for article.

@@
 
-\usepackage[latin1]{inputenc}
+\usepackage[utf8]{inputenc}
 \usepackage{graphicx}
@@
 
-Reliable researcher affiliation data is necessary to allow enquiring
-about international research group productivity and publication patterns.
-Public bibliographic databases such as DBLP and Google Scholar hold
-invaluable data about the academic environment. However, the researcher
-affiliation information is frequently missing or outdated.
-We propose a statistical data extraction method to acquire affiliation 
-information directly from university websites and solve the name extraction
-task in general.
-Previous approaches to web data extraction either lack in flexibility,
-because wrappers do not generalize well on cross website tasks, or 
-they lack in precision, because domain agnostic methods neglect 
-useful properties of this particular application domain.
-Our statistical approach solves the name extraction task with 
-a framework that incorporates both textual and structural features to
-yield an outstanding tradeoff between generality and precision. 
-We conducted experiments over a collection of 152 faculty 
-web pages in multiple languages from universities in 49 countries
-and obtained 94.40\% precision, 97.61\% recall and 0.9597 F-measure at
-the extraction task.
+Web data extraction (WDE) methods often rely on hand-coded rules to 
+identify and extract data from web pages. These methods 
+may be suited to extract information from single websites, but
+they usually perform poorly on extraction tasks across different 
+websites or different application domains. Statistical methods
+are more flexible in this regard. In this paper, we investigate
+different approaches to Named Entity Recognition (NER) on HTML, an
+essential substask in statistical models of web data extraction.
+Webpages can be very different from plain text due to their 
+semistructured nature, so we introduced a novel dataset that focuses
+on researcher name extraction from faculty listings from numerous
+university websites to evaluate different models in the 
+NER on HTML task. We found that neural network
+architectures with a Conditional Random Fields output layer and
+neural character representations are able to achieve an F1-score
+of 0.8867 with no inputs besides word embeddings. These NER models 
+can be part of a flexible and effective approach to WDE that does not
+rely on gazetteers, regular expressions or any hand-coded rules.
 
@@
 \maketitle
-
-% ==========================================
-% Beginning of text.                       |
-% ==========================================
 
@@
 the document structure and indirectly associated with the data itself can be valuable 
-information in the task of identifying entities and determining relationships. Yet we 
+information on the task of identifying entities and determining relationships. Yet we 
 cannot expect these features to be completely constrained by an underlying pattern. 
@@
 However, despite WDE being a closely related field of research,
-many tools rely on heuristics or hand coded rules to perform record segmentation,
+many tools rely on heuristics or hand-coded rules to perform record segmentation,
 and many methods resort to regular expressions or gazetteer matching to perform attribute
 labelling. While these approaches can be sufficient to extract information from webpages
-with similar templates, and identifying attributes with distinct formats like prices and
+with similar templates and identifying attributes with distinct formats like prices and
 dates, we still lack a sufficiently flexible and intelligent approach to handle more complicated cases.
@@
 \cite{McCallum2000} have been the usual choice for linear sequence tagging models.
-More recently, with the advancement in Natural Language Processing and Deep Learning, 
-neural models outperformed previous NER methods. Huang \cite{Huang2015} introduced the 
+More recently, with the advancement of Natural Language Processing and Deep Learning, 
+neural models outperformed previous NER methods. Huang et. al. \cite{Huang2015} introduced the 
 bidirectional Long Short-Term Memory (LSTM) model with a Conditional Random Field (CRF) output layer
-for NER. Lample \cite{Lample2016} incorporated Convolutional Neural Network based character representations 
-on top of the architecture. And Ma \cite{Ma2016} introduced
+for NER. Lample et. al. \cite{Lample2016} incorporated Convolutional Neural Network based character representations 
+on top of the architecture. And Ma and Hovy \cite{Ma2016} introduced
 LSTM based character representations. Both obtaining improvements with systems that are less reliant
@@
 random field model to perform attribute labelling. The model was further improved in 
-\cite{Zhu2006} to model record segmentation and attribute labeling as a joint task.
+\cite{Zhu2006} to model record segmentation and attribute labelling as a joint task.
 Some of the limitations of early unsupervised methods 
-were also tackled by ObjectRunner (\cite{Abdessalem2010}) and AMBER (\cite{Furche2012}). 
+were also tackled by ObjectRunner \cite{Abdessalem2010} and AMBER \cite{Furche2012}. 
 These methods work by annotating webpages automatically with regular expressions, gazetteers and 
@@
 of a web information extraction task. We first introduce two traditional approaches, 
-namely: Hidden Markov Models and Linear Chain Conditional Random Fields. And further
-we explore neural architectures.
+namely: Hidden Markov Models and Linear Chain Conditional Random Fields. And then
+we explore neural network architectures.
 
@@
 A Markov Model is a stochastic model that computes the most probable sequence of states 
-given a limited set of observable states $ \S = \{s_1, s_2, ..., s_n \} $.
+given a limited set of observable states $ S = \{s_1, s_2, ..., s_n \} $.
 The Hidden Markov Model (HMM) differs from the Markov Model in that it
@@
 \begin{equation}
-Y* = \argmax_{Y} P(Y|X)
+Y^* = \argmax_{Y} P(Y|X)
 \end{equation}
@@
 
-Since $ P(X) $ is the same for all label sequences $ Y $, we can simply maximize:
-
-\begin{equation}
-P(Y|X) \propto P(X|Y) P(Y)
-\end{equation}
+Since $ P(X) $ is the same for all label sequences $ Y $, we can simply maximize
+$ P(X|Y) P(Y) $.
 
@@
 
-HMM based taggers have been succesfully apllied in many NLP and IE tasks 
-\cite{Rabiner1989, Leek1997, Freitag2000}. They are incredibly fast to train and very 
+HMM based taggers have been succesfully apllied in many NLP and WDE tasks 
+\cite{Rabiner1990, Leek1997, Freitag2000}. They are incredibly fast to train and very 
 interpretable, making them a good choice for a first approximation. However, these models 
@@
 A Linear Chain Conditional Random Field (CRF) is the discriminative analog to the HMM,
-it was first introduced by \cite{Lafferty2001}. It is a distribution $ P(Y|X) $ that takes the form:
+it was first introduced by Lafferty \cite{Lafferty2001}. It is a distribution $ P(Y|X) $ that takes the form:
 
@@
 \end{equation}
+\\
 
@@
 maximum entropy models such as L-BFGS \cite{Liu1989}. The most likely label sequences can be decoded 
-with the Viterbi algorithm like in the case of HMMs.
+with the Viterbi algorithm, as was the case on HMMs.
 
@@
 
-\subsection{Neural Models}
+\subsection{Neural Network Models}
 
@@
 	  \includegraphics[width=0.5\textwidth]{pics/cnn}
-  \caption{CNN}
+  \caption{CNN based character representations}
   \label{fig:cnn}
@@
   \includegraphics[width=0.5\textwidth]{pics/lstm_char_representations}
-  \caption{LSTM character representations}
+  \caption{LSTM based character representations}
   \label{fig:lstm_char}
@@
 \section{NER on HTML Dataset}
+\label{sec:ner_dataset}
 
@@
 
-This task would be similar to the task of labeling authors in comments
+This task would be similar to the task of labeling authors in comments.
 However, we wanted to evaluate models without relying on any sophisticated data record
@@
 Finally, all tokens were tagged using the IOB scheme put forward by
-Ramshaw and Marcus \cite{Ramshaw1995}.
+Ramshaw and Marcus \cite{Ramshaw1999}.
 
@@
       \midrule
-      Training   & 0.7316 & 0.2303 & 0.3504 & 1341 from 5822 \\ 
-      Validation & 0.8474 & 0.2858 & 0.4274 & 511 from 1788 \\ 
-      Test       & 0.8717 & 0.3287 & 0.4773 & 890 from 2708 \\ 
+      Training   & 0.7316 & 0.2303 & 0.3504 & 1341 of 5822 \\ 
+      Validation & 0.8474 & 0.2858 & 0.4274 & 511 of 1788 \\ 
+      Test       & 0.8717 & 0.3287 & 0.4773 & 890 of 2708 \\ 
       \bottomrule
@@
 
-We conducted two experiments to evaluate the best models for named entity recognition
-on HTML in the context of web data extraction. In the first experiment, we used the
-whole training set (90 documents). In the second experiment, the training set was split 
-into five non overlapping sets with only 18 documents, but the test set was kept unchanged. 
-The goal of this second experiment 
-was to evaluate models when training data is scarce, since labelling data can be a very 
-time consuming task.
+Two experiments were conducted to evaluate the best models for named entity recognition
+on HTML in the context of web data extraction. In the first experiment, we trained the NER models
+using the entire training set (85 documents). In the second experiment, the training set was 
+split into five non overlapping sets with 17 documents, and every model was trained
+and tested once using each set, while the test data was kept unchanged. We wanted to verify empirically 
+how the models behaved when training data is limited, since labelling NER datasets can be a
+very time consuming effort.
 
-Evaluation of model performance in this task was measured with the precision, recall and 
-F1 scores (Van Rijsbergen, 1975). Precision is the percentage of named entities found by 
+Evaluation of model performance in this task was performend with the precision, recall and 
+F1 score \cite{Rijsbergen1979}. Precision is the percentage of named entities found by 
 the model that are correct. Recall is the percentage of named entities that are present
@@
 Named entities were only considered to be correct if they were a complete match of the 
-corresponding entity in the dataset. The models evaluated are presented in Table \ref{tab:models}.
-We evaluated the models using the complete set of features, presented in 
-table \ref{tab:features} and no features besides word embeddings for neural models and
-CRFs, and unaccented words for HMMs. To represent models with the complete set of features
-we added a "+F" suffix to the model name. Additionally, HMMs were evaluated with and
-without the self training strategy. To represent HMMs that use the self training strategy
-we added the suffix "+ST" to the model name.
-Results were reported for the validation and test sets in experiment 1 and only for the
-test set in experiment 2. In the second experiment, precision, recall and F1 scores were 
-averaged over the five runs. The standard deviation is presented next to the measures.
+corresponding entity in the dataset. The models tested in both experiments are described in Table \ref{tab:models}.
+In each experiment, we evaluated variants of each model using the complete set of features described in 
+Table \ref{tab:features} and variants that used only lowercase unaccented words for HMMs, 
+and only word embeddings in the case of neural models and CRFs. In Tables \ref{tab:experiment1} to 
+\ref{tab:experiment2f}, models that used the complete set of features have the suffix "+F". For example,
+"lstm-crf+F" is the LSTM-CRF model with all features including GloVe word embeddings, and "lstm-crf" is 
+the LSTM-CRF model with only GloVe word embeddings as input.
+Additionally, HMMs were also evaluated using the self training strategy. In tables \ref{tab:experiment1f} 
+and \ref{tab:experiment2f}, these models have the suffix "+ST".
 
-\subsection{Experiment 1: complete dataset}
+\subsection{Experiment 1: Complete Dataset}
 
@@
   \end{center}
-  \caption{Precision, recall and F1 in the complete dataset}
+  \caption{Precision, recall and F1 in the complete dataset for models using no features}
   \label{tab:experiment1}
@@
 
-Experiment 1 consists of testing the models on the complete NER on HTML dataset 
-described in section \ref{sec:ner_dataset}. Table \ref{tab:experiment1} shows the 
-results for models that employed no features, except for the words in the text
+Experiment 1 consisted of testing the models in the complete NER on HTML dataset 
+described in Section \ref{sec:ner_dataset}. Table \ref{tab:experiment1} shows the 
+Precision (P), Recall (R), and F1-scores (F1) for models that employed no features, 
+except for lowercase unaccented words
 in the case of HMMs and Glove-100 word embeddings in the case of CRFs and Neural Models.
+
 Without carefully designed features and a gazetteer, HMMs and CRFs have a very 
-poor performance, achieving only 57.83 for HMM-2 and 62.78 for CRF in the test set. 
-The neural models however achieved high F-scores, even with no features. The
-plain LSTM-CRF architecture improved significantly in comparison to the conventional CRF,
-and the LSTM-CRF architectures with neural character representations boosted the F1 score
-by 2.32 for CNN representations and 4.38 for LSTM representations, showing that they are 
-able to learn morphological features automatically, and that at least in the NER tasks LSTM 
-character representations are superior, perhaps because they are able to differentiate 
-suffixes and prefixes, while CNNs are position invariant. This experiment also shows that
-pretrained word embeddings can be used to identify named entities in HTML, where
-textual context is very limited without resorting to gazetteers.
+poor performance, achieving an F1-score of only 0.5783 for hmm-2 and 0.6244 for crf
+in the test set. This is to be expected, as these models rely on a good feature selection.
+The neural models however achieved high F1-scores in the test
+data, even with the absence of features. The plain LSTM-CRF architecture improved performance 
+significantly in comparison to the conventional CRF, 0.8427 against 0.6244 (a difference 
+of 0.2183). Also, the neural character representations boosted performance a little further
+reaching an F1-score of 0.8758 for CNN based representations and 0.8867 for LSTM based
+representations. The LSTM based representations were superior in modelling
+morphological features, perhaps because they are able to differentiate suffixes and prefixes, 
+while CNNs filters are position invariant.
+
+The results in experiment 1 also show that pretrained word embeddings can work as a sort of
+universal gazetteer. Words with similar embeddings, are likely to belong to the same class.
+This knowledge combined with the ability to learn morphological features can make up for 
+the scarcity of textual data in some webpages.
 
@@
   \end{center}
-  \caption{Precision, recall and F1 in the complete dataset}
+  \caption{Precision, recall and F1 in the complete dataset for models using all features}
   \label{tab:experiment1f}
@@
 Table \ref{tab:experiment1f} shows the results on experiment 1 for models
-that employed all features described on Table \ref{tab:features}. In this case
-we see that conventional models like HMMs, and CRFs can become competitive with
+that employed all the features described in Table \ref{tab:features}.
+Conventional models like HMMs, and CRFs can become competitive with
 the right selection of features and a good gazetteer, however they still lose
-to the best neural model without features showing their limitation. We can also
-see that the self training strategy for HMMs improved the quality of the results
-significantly on all cases, boosting both precision and recall.
-
-The neural models also improved a little with the addition of features. The fact that 
-the LSTM-CRF gets much closer to the neural models with character representations
-shows that the LSTM and CNN character representations were probably able to learn 
-at least part of the features automatically, and when we add them explicitly,
-the difference in performance becomes less noticeable.
+to the best neural model without features, demonstrating their inherent limitations.
+We can also see that the self training strategy for HMMs improved the quality of 
+the models significantly in all cases, boosting both precision and recall. Finally,
+HMMs that employed trigrams or quadrigrams (hmm-2, hmm-3) also performed better in
+comparison to regular HMMs.
+The neural models also improved a little with the new features. The plain LSTM-CRF
+model gets a closer performance to the models that employed neural character 
+representations. A fact that hints that the LSTM and CNN character representations 
+were able to learn at least part of the morphological features automatically in the
+models with no features. So, when these features are added explicitly, the differences 
+in performance become less noticeable.
 
@@
   \end{center}
-  \caption{Precision, recall and F1 in the small dataset}
+  \caption{Mean Precision, recall and F1 in the test set for models with no features
+   trained in five sets with 17 documents}
   \label{tab:experiment2}
@@
 
-The second experiment aimed at evaluating the performance of sequence models
-when the dataset is reduced to only 18 labeled documents. A feasible amount of 
-labelling in most WDE tasks. The experiment was repeated in five non overlapping 
-sets of training data, and the results were averaged. Table \ref{tab:experiment2} 
-describes the results for models without any features. We only present results
-for the test set in this experiment. The standard deviation is shown next to each
-measure.
+The second experiment aimed to evaluate the performance of sequence models when 
+the amount of training data is small. The same training data used in Experiment 1 was
+split into five non overlapping sets with 17 documents. Each model was trained once 
+with each of the five sets and tested with the same test set used in Experiment 1. 
+Seventeen documents seem to be a feasible amount of documents to label in most WDE 
+tasks. The results for each model was averaged over the five runs.
 
-We can see that the performance of all models was reduced in comparison 
-to experiment 1. That is to be expected.
+Table \ref{tab:experiment2} shows the precision, recall and F1-score for the same models
+used in Experiment 1, but in this case we only show results for the Test set.
+As expected, we can see that the performance of all models with no features was reduced in comparison 
+to Experiment 1. HMMs show a terrible performance while CRFs are not 
+impacted as much by the reduction in the amount of training examples. Neural models
+keep performing better, but they were unable to learn patterns as efficiently in
+the smaller training sets. The neural models show a small standard deviation, what
+points to the fact that they can retain a consistent performance between different training 
+datasets. In this matter, the dropout layers are crucial to produce better generalizations 
+and prevent overfitting.
 
@@
   \end{center}
-  \caption{Precision, recall and F1 in the small dataset}
+  \caption{Mean Precision, recall and F1 in the test set for models with all features
+   trained in five sets with 17 documents}
   \label{tab:experiment2f}
@@
 
-We can see that the performance of all models was reduced in comparison 
-to experiment 1. That is to be expected.
+Table \ref{tab:experiment2f} shows the results in the small training sets 
+for models that employed all features. Take note that the difference between CRFs
+and neural models was reduced with the reduction in the training set. However, the
+addition of features impacted the performance of neural models much more that in 
+Experiment 1. This indicates that the models with neural character representations
+may need more data to extract good morphological features. However, they keep performing 
+better than the other models, and have the lowest standard deviations.
+
+Finally, all the results presented in this section considered a dataset with a minimum
+amount of preprocessing and no trimming strategy to delimitate named entities. In many cases, 
+for example, a model may miss a few named entities because it includes a punctuation sign
+or an honorific at the start or end of a named entity. In fact, we can boost the F1-score up
+by a few percentage points with some simple heuristics. However, these strategies would 
+probably not apply to other NER on HTML tasks, so we did not include them in the results.
 
@@
 
-Deep learning models are better blabla.
+In this paper we compared the performance of multiple sequence models in the task of
+NER on HTML, introducing a novel dataset that is publicly available. We showed that
+neural networks can be employed effectively to solve this task while demanding no 
+feature engineering (F1-score of 0.8867), and they can retain acceptable performance 
+even when the training data is dramatically reduced (F1-score of 0.8255), even though 
+in this case the feature selection can become more meaningful. We found that there are 
+two components to the most successful models: neural based character representations
+constructed with convolutional neural networks or bidirectional LSTMs and joint modelling 
+of the output labels provided by a linear chain CRF output layer. The effective recognition 
+of named entities on HTML is an essential step in most general web data extraction methods. 
+However it may also point to the possibility of constructing a truly flexible approach to
+cross domain data extraction based on neural networks.
 
-HMMs are competitive but demand feature engineering blabla.
-
-Token morphology is necessary.
-
-Label dependency is necessary.
-Our name extraction method achieved 94.40\% precision, 97.61\% recall 
-and 0.9597 F-measure on a corpus of 152 faculty directory web pages from
-49 different countries with 11782 researcher names. 
-The model is tuned for the particular problem of name extraction, 
-but we believe this result can be generalized to solve other data extraction
+\bibliographystyle{unsrt}
+\bibliography{bibfile}
 

### 2018-09-21 train_conll.py

@@ -1,183 +1,0 @@
-#!/usr/bin/python
-# coding=UTF-8
-
-import np
-from keras.utils import np_utils
-from keras.callbacks import Callback
-from models.util import WordEmbeddings
-from models.lstm_crf import LstmCrf
-
-def is_punctuation(text):
-  return re.match("^[\,\;\:\-\"\(\)“”]$", text)
-
-def print_results(dataset, val_predict, val_targ, T, verbose=False):
-    correct = 0
-    incorrect = 0
-    missed = 0
-    for i, sentence in enumerate(val_targ):
-      for j, tkn in enumerate(val_targ[i]):
-        if np.sum(val_targ[i,j]) > 0:
-          y_hat = int(np.argmax(val_predict[i,j], axis=-1))
-          y = int(np.argmax(val_targ[i,j], axis=-1))
-
-          if y_hat == y and y != 0:
-            correct += 1
-
-          elif y_hat != y and y == 0:
-            incorrect += 1
-
-          elif y_hat != y and y > 0:
-            missed += 1
-            if y_hat > 0:
-              incorrect += 1
-
-    p  = correct / float(correct + incorrect)
-    r  = correct / float(correct + missed)
-    f1 = 2 * p * r / float(p + r)
-
-    if verbose:
-      print('----------------')
-      print(dataset)
-      print('----------------')
-      print('Correct:', correct)
-      print('Incorrect:', incorrect)
-      print('Missed:', missed)
-      print('Precision:', p)
-      print('Recall:', r)
-      print('F1:', f1)
-
-    return correct, incorrect, missed, p, r, f1
-
-class Metrics(Callback):
-  def __init__(self, the_model):
-    self.max_f_measure = 0
-    self.the_model = the_model
-
-  def on_epoch_end(self, epoch, logs={}):
-    val_predict, val_targ, T = self.the_model.validate()
-
-    correct, incorrect, missed, p, r, f1 = print_results('Validate', val_predict, val_targ, T, verbose=False)
-
-    improved = False
-    if f1 > self.max_f_measure:
-      self.max_f_measure = f1
-      self.the_model.save()
-      improved = True
-
[…]

### 2018-09-23 tex/article.tex
Correções no paper.

@@
 
-Other approaches such as NoDoSE (\cite{Adelberg1998}) and Debye (\cite{Laender2002a}) 
+Other approaches such as NoDoSE \cite{Adelberg1998} and Debye \cite{Laender2002a} 
 brought greater flexibility to wrapper induction methods by requiring a greater level 
@@
 We explored multiple approaches to the Named Entity Recognition problem in the context 
-of a web information extraction task. We first introduce two traditional approaches, 
-namely: Hidden Markov Models and Linear Chain Conditional Random Fields. And then
+of a web information extraction task. First, we introduce two traditional approaches, 
+namely: Hidden Markov Models and Linear Chain Conditional Random Fields. Then
 we explore neural network architectures.
@@
 and consequently for solving text related tasks. In NER, the network outputs one label for each input 
-vector as showed in Figure \ref{fig:rnn_network}.
+vector as shown in Figure \ref{fig:rnn_network}.
 
@@
 of predicting each label individually. This architecture achieved an F1 score of 90.10 on the English
-data from CONLL-2003 shared task \cite{Sang2003}, in contrast to 85.17 for a bidirectional LSTM without the CRF layer. 
-In our experiments, the LSTM-CRF architecture used a bidirectional LSTM with 100 
+data from the ConLL-2003 NER shared task \cite{Sang2003}, in contrast to 85.17 for a bidirectional LSTM without the CRF layer. 
+In our experiments, the LSTM-CRF architecture uses a bidirectional LSTM with 100 
 hidden states, no peepholes and an input and output dropout layers with a dropout
@@
 \subsubsection{LSTM-CRF + CNN character representations}
-\ref{sssec:lstm_crf_cnn}
+\label{sssec:lstm_crf_cnn}
 
@@
 neural network with 30 filters and a window size of three characters on top of the LSTM-CRF architecture.
-The character embeddings fed to the CNN had 30 dimensions that were randomly initialized.
+The character embeddings fed to the CNN have 30 dimensions that were randomly initialized.
 
@@
 with 25 hidden states, producing character representations of size 50. The character embeddings
-had 30 dimensions that were randomly initialized.
+have 30 dimensions that were randomly initialized.
 
@@
 
-This task would be similar to the task of labeling authors in comments.
+This task would be similar to the task of labeling authors in comments
+from many different sources or labeling authors in articles collected from many
+publishing platforms. Another similar task would be NER on tweets. Because of the character
+limitation present on tweets, we end up with constraints comparable to the ones
+found in the NER on HTML task, so we expect similar systems to have comparable performances
+on both of these tasks.
+
+We collected 145 computer science faculty pages from 42 different countries in
+multiple languages, although the English version was prefered when it was available.
+We gathered faculty web pages randomly in proportion to
+the number of universities in each country\footnote{A detailed list of universities can
+be found in https://univ.cc/world.php}. Each HTML page was preprocessed and converted
+to the CONLL 2003 data format. That is, one word per line with empty lines representing
+sentence boundaries. Sentence boundaries were determined by line break HTML tags
+(div, p, table, li, br, etc.) in contrast to inline tags (span, em, a, td, etc.). 
+Sentences that were more than 50 tokens were also split according to punctuation.
+
+A proper HTML segmenter poses many challenges by itself.
 However, we wanted to evaluate models without relying on any sophisticated data record
@@
 a description of the data files. The validation set was used in the early stopping validation strategy
-on neural model and CRF training, while results were evaluated by comparing results in the test set.
+for the neural netowrks and CRF training, while the performance was evaluated by comparing results in the test set.
 
@@
 
-Twelve categorical features were also present with each token in the dataset. They 
-are presented in table \ref{tab:features}.
+Thirteen categorical features were also associated with each token in the dataset. They 
+are presented in Table \ref{tab:features}.
 
@@
 
-Table \ref{tab:experiment1f} shows the results on experiment 1 for models
+Table \ref{tab:experiment1f} shows the results on Experiment 1 for models
 that employed all the features described in Table \ref{tab:features}.
@@
 model gets a closer performance to the models that employed neural character 
-representations. A fact that hints that the LSTM and CNN character representations 
+representations. It points to the fact that the LSTM and CNN character representations 
 were able to learn at least part of the morphological features automatically in the
@@
 Seventeen documents seem to be a feasible amount of documents to label in most WDE 
-tasks. The results for each model was averaged over the five runs.
+tasks. The results for each model were averaged over the five runs.
 
@@
 keep performing better, but they were unable to learn patterns as efficiently in
-the smaller training sets. The neural models show a small standard deviation, what
+the smaller training sets, the best model achieves an F1 score of 0.7652 in contrast to
+0.8815 with the entire dataset. The neural models show a small standard deviation, what
 points to the fact that they can retain a consistent performance between different training 
@@
 or an honorific at the start or end of a named entity. In fact, we can boost the F1-score up
-by a few percentage points with some simple heuristics. However, these strategies would 
-probably not apply to other NER on HTML tasks, so we did not include them in the results.
+by a few points with some simple heuristics. However, these strategies are specific to this
+NER on HTML problem.
 
@@
 even when the training data is dramatically reduced (F1-score of 0.8255), even though 
-in this case the feature selection can become more meaningful. We found that there are 
+in this case the feature selection becomes more meaningful. We found that there are 
 two components to the most successful models: neural based character representations

### 2018-10-29 tex/article.tex
models

@@
   \country{Brazil}}
-\email{berthier.dcc.ufmg@gmail.com}
+\email{berthier@dcc.ufmg.br}
+\email{berthier@google.com}
 
@@
 In our experiments, the LSTM-CRF architecture uses a bidirectional LSTM with 100 
-hidden states, no peepholes and an input and output dropout layers with a dropout
+hidden states, no peepholes and input and output dropout layers with a dropout
 rate of 0.5. The dropout layers have proven to be very important to prevent overfitting 
@@
 neural network with 30 filters and a window size of three characters on top of the LSTM-CRF architecture.
-The character embeddings fed to the CNN have 30 dimensions that were randomly initialized.
+The character embeddings fed to the CNN have 30 dimensions that are randomly initialized.
 
@@
 with 25 hidden states, producing character representations of size 50. The character embeddings
-have 30 dimensions that were randomly initialized.
+have 30 dimensions that are randomly initialized.
 
@@
 In the case of NER on HTML, word embeddings work similar to a gazetteer. Named entities 
-of a same type have similar embeddings, so good word embeddings can achieve exceptional 
+with the same type have similar embeddings, so good word embeddings can achieve exceptional 
 performance with little training and without a gazetteer.
@@
 (div, p, table, li, br, etc.) in contrast to inline tags (span, em, a, td, etc.). 
-Sentences that were more than 50 tokens were also split according to punctuation.
+Sentences that were more than fifty tokens long were also split according to punctuation.
 
@@
 segmentation system. In many cases, entity annotation may precede the segmentation
-phase in web data extraction methods, so annotators have to be able to work with
+phase in web data extraction methods, so annotators should be able to work with
 raw HTML data. Because of the type of documents present in the dataset, many sentences 
@@
 a description of the data files. The validation set was used in the early stopping validation strategy
-for the neural netowrks and CRF training, while the performance was evaluated by comparing results in the test set.
+for the neural networks and CRF training, while the performance was evaluated by comparing results in the test set.
 
@@
 
-\subsection{Experiment 2: reduced dataset}
+\subsection{Experiment 2: Reduced Dataset}
 

### 2018-10-29 models/gazetteer_matcher.py

@@ -1,0 +1,31 @@
+#!/usr/bin/python
+# coding=UTF-8
+
+import np
+import re
+
+def is_punctuation(text):
+  return re.match("^[\,\;\:\-\"\(\)“”]$", text)
+
+def gazetteer_predict(X, T, mode='partial'):
+  Y = np.zeros((X.shape[0], X.shape[1], 3))
+
+  for i in range(X.shape[0]):
+    for j in range(X.shape[1]):
+      if T[i,j] is None:
+        continue
+
+      Y[i,j] = np.array([1, 0, 0])
+      # if is_punctuation(T[i,j]):
+      #   Y[i,j] = np.array([0, 0, 1])
+
+      # Exact.
+      if mode == 'exact':
+        if X[i,j,0] == 1:
+          Y[i,j] = np.array([0, 0, 1])
+
+      # Partial .
+      else:
+        if X[i,j,1] == 1:
+          Y[i,j] = np.array([0, 1, 0])
+  return Y      

### 2018-10-29 models/hmm.py

@@ -1,0 +1,250 @@
+import np
+import re
+from models.util import load_raw_dataset
+
+def is_punctuation(text):
+  return re.match("^[\,\;\:\-\"\(\)“”；]$", text)
+
+class HiddenMarkov:
+  def __init__(self, timesteps, naive_bayes=False, use_gazetteer=True, use_features=True, self_train=False):
+    self.time_steps   = timesteps
+    self.use_gazetteer = use_gazetteer
+    self.use_features = use_features
+    self.do_self_train = self_train
+    self.naive_bayes = naive_bayes
+
+    self.num_labels   = 3
+    self.num_features = 11
+    self.num_secondary_features = 2
+    # self.num_secondary_features = 5
+    self.num_all_features = self.num_features + self.num_secondary_features
+    self.num_states = self.num_labels ** self.time_steps
+    self.transition_mat = np.ones((self.num_states, self.num_labels))
+    self.start = np.zeros((self.num_states, 1))
+    self.start[0,:] = 1 # All previous states are label O ("other").
+    self.end = np.ones((self.num_states, 1)) # All ending states are equally probable.
+
+    self.feature_counts = []
+    for i in range(self.num_all_features):
+      self.feature_counts.append([])
+      for j in range(self.num_labels):
+        self.feature_counts[i].append({'$UNK': 1})
+
+  def idx_to_states(self, idx):
+    states = []
+    multiplier = self.num_labels ** (self.time_steps - 1)
+    for i in range(self.time_steps):
+      states.append(int(idx) // int(multiplier))
+      idx %= multiplier
+      multiplier /= self.num_labels
+    return states 
+  
+  def states_to_idx(self, states):
+    if len(states) < self.time_steps:
+      raise Exception('Wrong states length.')
+  
+    acc = 0
+    multiplier = 1
+    for s in reversed(states):
+      acc += int(multiplier) * int(s)
+      multiplier *= self.num_labels
+    return acc
+
+  def train_features(self, X, Y, which_features=[]):
+    if len(which_features) != self.num_all_features:
+      which_features = [0] * self.num_all_features
+
+    label_count = np.ones((self.num_labels))
+    for i in range(len(Y)):
+      for j in range(50):
+        if np.sum(Y[i,j]) == 0:
+          break
+  
+        label_count += Y[i,j]
+        y = np.where(Y[i,j] == 1)[0][0]
+  
+        f = X[i][j][1:1+self.num_all_features]
[…]

### 2018-10-29 models/lstm_crf.py

@@ -1,0 +1,152 @@
+import keras
+import np
+import re
+from models.util import Dataset, WordEmbeddings, evaluate, get_names, one_hot_to_labels
+from keras.models import Model
+from keras.layers import Input, Dense, Dropout, Flatten, TimeDistributed, Bidirectional, LSTM, Embedding, concatenate, Conv1D, GlobalMaxPooling1D
+from models.ChainCRF import ChainCRF, create_custom_objects
+from keras.utils import np_utils
+from keras import optimizers
+  
+class LstmCrf():
+  def __init__(
+    self, 
+    name,
+    lstm_cells=100, 
+    use_gazetteer=True, 
+    use_features=True, 
+    char_embedding_size=30,
+    num_cnn_filters=30,
+    char_lstm_size=25,
+    model_type=['lstm-crf', 'lstm-crf-cnn', 'lstm-crf-lstm', 'crf', 'maxent'][0],
+    dev_dataset=None,
+    validate_dataset=None,
+    test_dataset=None,
+  ):
+    self.name = name
+    self.lstm_cells = lstm_cells
+    self.num_cnn_filters = num_cnn_filters
+    self.char_lstm_size = char_lstm_size
+    self.model_type = model_type
+    self.dev_dataset = dev_dataset
+    self.validate_dataset = validate_dataset
+    self.test_dataset = test_dataset
+    self.use_gazetteer = use_gazetteer
+    self.use_features = use_features
+    self.num_labels = self.dev_dataset.Y.shape[2]
+
+  def create(self, word_embedding_matrix):
+    x1_shape = self.dev_dataset.X1.shape
+    x2_shape = self.dev_dataset.X2.shape
+    x3_shape = self.dev_dataset.X3.shape
+    x4_shape = self.dev_dataset.X4.shape
+
+    char_embedding_matrix = np.random.randn(128, 30)
+
+    x = Input(shape=(x1_shape[1], x1_shape[2]), dtype='int32')
+    inputs = [x]
+    
+    # Word embeddings.
+    word_emb = Embedding(
+      input_dim=word_embedding_matrix.shape[0], 
+      output_dim=word_embedding_matrix.shape[1], 
+      weights=[word_embedding_matrix], 
+      trainable=False
+    )(Flatten()(x))
+
+    # Feature embeddings.
+    shared_layer = [word_emb]
+
+    if self.use_gazetteer:
+      x2 = Input(shape=(x2_shape[1], x2_shape[2]), dtype='float32')
[…]

### 2018-10-29 models/util.py

@@ -1,0 +1,413 @@
+import np
+import re
+from keras.utils import np_utils
+# np.set_printoptions(suppress=True)
+
+num_labels = 3
+
+def is_punctuation(text):
+  return re.match("^[\,\;\:\-\"\(\)“”；]$", text)
+
+class WordEmbeddings():
+  def __init__(self, emb_type):
+    self.words  = []
+    self.word2Idx  = {}
+    self.matrix = None
+    self.load_embeddings(emb_type)
+
+  def load_glove(self, dimensions):
+    self.matrix = np.zeros((400002, dimensions), dtype=float)
+    with open('embeddings/glove.6B.' + str(dimensions) + 'd.txt') as f:
+      counter = 2
+      for vector in f:
+        features = vector.strip().split(' ')
+        w = features[0]
+        self.words.append(w)
+        self.word2Idx[w] = counter
+        self.matrix[counter,:] = np.array(features[1:], dtype=float)
+        counter += 1
+
+  def load_embeddings(self, emb_type):
+    if emb_type == 'glove-50':
+      self.load_glove(50)
+    elif emb_type == 'glove-100':
+      self.load_glove(100)
+    elif emb_type == 'glove-200':
+      self.load_glove(200)
+    elif emb_type == 'glove-300':
+      self.load_glove(300)
+
+def load_raw_dataset(f, max_sentence_len=50):
+  with open(f, 'r') as f:
+    sentences = f.read().strip().split('\n\n')
+    sentences = [s for s in sentences if not s.startswith('-DOCSTART-')]
+    X = [[t.split(' ') for t in s.split('\n') if len(s) > 0] for s in sentences]
+    Y = np.zeros((len(X), max_sentence_len, num_labels))
+    T = np.ndarray(shape=(len(X), max_sentence_len), dtype=object)
+    for i, s in enumerate(X):
+      tkns, labels = [], []
+      if len(X[i]) > max_sentence_len-1:
+        X[i] = X[i][:max_sentence_len-1]
+
+      for j, t in enumerate(s[:max_sentence_len-1]):
+        # l = ['O', 'B-PER', 'I-PER', 'PUNCT'].index(t[1])
+        l = ['O', 'B-PER', 'I-PER'].index(t[1])
+        labels.append(np_utils.to_categorical(l, num_labels))
+        tkns.append(t[0])
+        X[i][j] = [X[i][j][0]] + X[i][j][2:]
+
+      # EOS.
[…]

### 2018-11-29 tex/article.tex
New article.

@@
-\documentclass[sigconf]{acmart}
-\settopmatter{printacmref=false} % Removes citation information below abstract
-\renewcommand\footnotetextcopyrightpermission[1]{} % removes footnote with conference information in first column
-\pagestyle{plain} % removes running headers
-\setcopyright{none}
+\documentclass{nle}
+
+% \documentclass[sigconf]{acmart}
+% \settopmatter{printacmref=false} % Removes citation information below abstract
+% \renewcommand\footnotetextcopyrightpermission[1]{} % removes footnote with conference information in first column
+% \pagestyle{plain} % removes running headers
+% \setcopyright{none}
 
@@
 
-\title{Named Entity Recognition on HTML as a web data extraction subtask}
+\title{Web data extraction through named entity labeling}
 
 \author{João Mateus de Freitas Veneroso}
-\affiliation{%
-  \institution{Universidade Federal de Minas Gerais}
-  \streetaddress{Av. Pres. Antônio Carlos, 6627 - Pampulha}
-  \city{Belo Horizonte}
-  \state{MG}
-  \postcode{31270-901}
-  \country{Brazil}}
-\email{jmfveneroso@gmail.com}
-
-\author{Berthier Ribeiro-Neto}
-\affiliation{%
-  \institution{Universidade Federal de Minas Gerais}
-  \streetaddress{Av. Pres. Antônio Carlos, 6627 - Pampulha}
-  \city{Belo Horizonte}
-  \state{MG}
-  \postcode{31270-901}
-  \country{Brazil}}
-\email{berthier@dcc.ufmg.br}
-\email{berthier@google.com}
+% \affiliation{%
+%   \institution{Universidade Federal de Minas Gerais}
+%   \streetaddress{Av. Pres. Antônio Carlos, 6627 - Pampulha}
+%   \city{Belo Horizonte}
+%   \state{MG}
+%   \postcode{31270-901}
+%   \country{Brazil}}
+% \email{jmfveneroso@gmail.com}
+% 
+% \author{Berthier Ribeiro-Neto}
+% \affiliation{%
+%   \institution{Universidade Federal de Minas Gerais}
+%   \streetaddress{Av. Pres. Antônio Carlos, 6627 - Pampulha}
+%   \city{Belo Horizonte}
+%   \state{MG}
+%   \postcode{31270-901}
+%   \country{Brazil}}
+% \email{berthier@dcc.ufmg.br}
+% \email{berthier@google.com}
 
@@
 
-Web data extraction (WDE) methods often rely on hand-coded rules to 
-identify and extract data from web pages. These methods 
-may be suited to extract information from single websites, but
-they usually perform poorly on extraction tasks across different 
-websites or different application domains. Statistical methods
-are more flexible in this regard. In this paper, we investigate
-different approaches to Named Entity Recognition (NER) on HTML, an
-essential substask in statistical models of web data extraction.
-Webpages can be very different from plain text due to their 
-semistructured nature, so we introduced a novel dataset that focuses
-on researcher name extraction from faculty listings from numerous
-university websites to evaluate different models in the 
-NER on HTML task. We found that neural network
-architectures with a Conditional Random Fields output layer and
-neural character representations are able to achieve an F1-score
-of 0.8867 with no inputs besides word embeddings. These NER models 
-can be part of a flexible and effective approach to WDE that does not
-rely on gazetteers, regular expressions or any hand-coded rules.
+Web data extraction methods often rely on hand-coded rules to 
+identify and extract data from web pages. These methods are usually
+suited for extracting information from repeating templates inside
+the same website, however they perform poorly on extraction 
+tasks across different websites. Alternatively, statistical and 
+machine-learning-based sequence labeling methods provide a more flexible 
+approach to Web data extraction. HTML text is ocasionally very different 
+from plain text because sentences can be too short to provide adequate 
+context for conventional Named Entity Recognition methods to work 
+properly. Also, the HTML structure can encode information that is not 
+replicated in the text. Nonetheless, these limitations can be overcome by
+adequate feature engineering, the use of pre-trained word 
+embeddings and neural character representations. In this article, we 
+evaluate the performance of different methods of named entity recognition 
+on the task of Web data extraction. In particular, we introduce a novel 
+dataset consisting of faculty listings from university webpages across
+the world in multiple languages and test the NER models on the task of 
+extracting researcher names from these listings. We found that a 
+neural network architecture that combines a bidirectional LSTM with
+a Conditional Random Fields output layer and LSTM-based character 
+representations outperforms other methods on the researcher name 
+extraction task, achieving an F1-score of 0.8867 with no feature engineering. 
+With the addition of hand crafted features, the F1-score can be slightly 
+improved to 0.8995 with another neural architecture that incorporates
+CNN-based character representations.
 
@@
 
-Web data extraction (WDE) is the task of automatically extracting structured information
-from unstructured or semi-structured web documents. The input usually consists of
-web documents containing a number of predetermined entities organized in a similar 
-manner and the information extraction task consists of identifying these entities
-and organizing them according to a template. In this context, named entity recognition
-(NER) is a subtask that aims to detect named entities in the text and classify them into 
-predetermined categories such as person names, locations or organizations.
+Web data extraction (WDE) is the task of automatically extracting structured 
+information from unstructured or semi-structured Web documents. The input 
+usually consists of Web documents containing a number of predetermined entities 
+organized in a similar manner. The web data extraction task consists of 
+identifying these entities and organizing them according to a template.
 
-HTML documents most often lie in between the structured / unstructured data paradigm.
-DOM hierarchy, element disposition, class names, and other features related to 
-the document structure and indirectly associated with the data itself can be valuable 
-information on the task of identifying entities and determining relationships. Yet we 
-cannot expect these features to be completely constrained by an underlying pattern. 
-Organization patterns tend to follow some guidelines but are in no way subject to 
-strict rules. That is why classical information extraction systems such as automatic
-wrapper generators usually do not translate well across different websites.
+HTML documents most often lie in between the structured/unstructured 
+data paradigm. DOM hierarchy, element disposition, CSS classes, and other 
+features related to the document structure and indirectly associated with the 
+data itself can be valuable information on the task of identifying
+entities. Yet, we cannot expect these features to be completely constrained 
+by an underlying pattern. Organization patterns tend to follow some guidelines 
+but they are in no way subject to strict rules. That is why classical web data 
+extraction systems such as automatic wrapper generators 
+\cite{Kushmerick2000,Hsu1998,Muslea1999}
+do not translate very well across different websites.
 
-Most existing web data extraction methods are tailored to extract data from a single
-web page \cite{Crescenzi2001, Arasu2003, Freitag1998, Califf1999, Soderland1999,
-Kushmerick2000, Hsu1998, Muslea1999}, producing different compromises between efficacy
-and degree of human supervision. More recent unsupervised approaches proposed to
-tackle the problem of data extraction for whole application domains \cite{Zhu2005, Zhu2006, 
-Abdessalem2010, Furche2012, Furche2012a}. Unsupervised WDE methods usually operate in at
-least two steps: record segmentation and attribute labelling. Record segmentation
-is essentially clustering visually and structurally similar web page regions and 
-identifying repeating data records. Attribute labelling is the task of identifying
-attributes in data records. Doing any of these tasks well can help performing the 
-other task, since patterns that are present in some data records can help identifying 
-attributes in other data records. And by properly identifying attributes, we are better 
-able to determine the boundaries of data records and segment them with increased accuracy.
+Most existing Web data extraction methods are tailored to extract data 
+from a single Web page, producing different compromises between efficacy and 
+degree of human supervision. Some unsupervised approaches proposed to tackle 
+the problem of data extraction for whole application domains 
+\cite{Zhu2005,Zhu2006,Abdessalem2010,Furche2012,Furche2012a}. Usually, 
+unsupervised WDE methods work in two stages. In the record segmentation stage,
+WDE systems seek to cluster visually and structurally similar web page regions 
+and identify repeating data records, usually with heuristics and 
+hand-coded rules. In the attribute labelling stage, WDE systems seek to identify 
+the correct attributes on data records, many times resorting to regular expressions 
+or gazetteer matching strategies. The outcome of each of these stages can aid one 
+another. The inner patterns of data records can help identifying attributes in other 
+data records. Also, by properly identifying data record attributes, it becomes 
+easier to determine boundaries and perform record segmentation.
 
-In recent years, we saw an astonishing progress in Natural Language Processing.
-However, despite WDE being a closely related field of research,
-many tools rely on heuristics or hand-coded rules to perform record segmentation,
-and many methods resort to regular expressions or gazetteer matching to perform attribute
-labelling. While these approaches can be sufficient to extract information from webpages
-with similar templates and identifying attributes with distinct formats like prices and
-dates, we still lack a sufficiently flexible and intelligent approach to handle more complicated cases.
-Even when extracting data from web documents only, data records may contain pure text with 
-relevant named entities. Also, many WDE algorithms can effectively exploit the semi-
-structure of web documents, but when a method relies too much on structural features, it
-often produces poor generalization on cross website extraction tasks. Contrastingly, we 
-understand that statistical based approaches can be much more flexible.
+While unsupervised approaches can be sometimes adequate to extract information from 
+webpages with similar templates, they usually fail on cross-website data extraction 
+tasks. Also, more sophisticated approaches may be needed when we are not dealing
+with easily distinguishable attributes such as prices and dates. In this regard, 
+machine-learning-based sequence labeling methods can provide a more flexible 
+approach that works regardless of website structure.
 
-In this paper, we investigate the attribute labelling task in WDE with a named entity 
-recognition framework. Recently proposed neural architectures have achieved exciting results 
-on the NER task on plain text \cite{Huang2015, Lample2016, Ma2016} while requiring almost 
-no feature engineering or gazetteers. NER on HTML poses a different type of challenge, 
-because web pages are often very different from plain text. Named entities may be present 
-inside tables, lists, graphs or other types of visual elements that provide
-little to no textual information that could give hints about the semantic category of 
-a word. However we show that we can get exceptional performance even with this limitation
-and small training sets.
+In recent years, we saw an amazing progress in the field of Natural Language Processing, 
+particularly with the introduction of deep recurrent neural network architectures
+for sequence labeling. However, despite web data extraction being a closely 
+related field, there is a lack of extraction tools that make use of these recent 
+advancements. The attribute labelling stage in web data extraction systems
+is essentialy a Named Entity Recognition (NER) problem, the problem of 
+detecting named entities in the text and classifying them into predetermined 
+categories such as person names, locations, dates or organizations.
 
-By reliably detecting named entities, we can improve the performance of existing WDE 
-approaches or even construct a full machine learning based tool to tackle domain wide
-extraction with great flexibility. To test different NER approaches from the perspective 
-of web data extraction,
-we explored the task of person names extraction from university faculty listings.
-Researcher affiliation is often missing from many entries in public databases 
-and the display of information varies significantly between different university 
-websites, so this task can provide a good measure of the expected performance and
-data need for other web data extraction tasks.
+In many cases, such as when we are extracting researcher names from faculty listings,
+detecting named entities is sufficient to solve the data extraction task. However, when we are
+dealing with multi attribute data records or complex relationships, we may need to 
+perform additional steps. Nevertheless, even in the latter cases, flexible NER methods 
+are still desirable because, while many WDE algorithms can effectively exploit the 
+semi-structured nature of web documents, too much reliance on structural webpage 
+features often produce poor generalizations on cross website extraction. Also, 
+data records may enclose plain text with relevant named entities.
+
+In this paper, we investigate methods of named entity recognition for web data extraction.
+Recently proposed neural architectures have achieved exciting results 
+on the NER task in plain text while requiring almost 
+no feature engineering or access to gazetteers \cite{Huang2015,Lample2016,Ma2016}. 
+NER on HTML poses a slightly different type of challenge. Named entities may occur inside 
+tables, lists, graphs or other types of visual elements that provide little to no textual 
+information that could give hints about the semantic category of a word. Still, even 
+with this limitation, we show that it is possible to obtain very good results with a 
+relatively small training set.
+
+By reliably detecting named entities on HTML, we can improve the performance of existing WDE 
+approaches or even construct an end-to-end neural network architecture to tackle domain 
+wide extraction with considerable flexibility. To test different NER approaches to
+web data extraction, we explored the task of researcher name extraction from university 
+faculty listings across the world, introducing a novel NER dataset.
+
+Reliable researcher affiliation information is often missing from public researcher 
+databases (especially in departments other than Computer Science). Also, the display of 
+faculty information varies significantly between different university websites, so 
+this task can provide a good measure of the expected performance and data need of
+NER methods on other web data extraction tasks.
 
@@
 led to the development of a number of different approaches to the problem of web 
-information extraction. Traditionally, the task was solved by designing special purpose
+data extraction. Traditionally, the task was solved by designing special purpose
 programs called wrappers to recognize relevant data and store records in a structured
@@
 generates wrappers based on their similarities and differences, yielding comparable results 
-to those obtained by wrapper induction methods. However like previous approaches, it was 
+to those obtained by wrapper induction methods. However, like previous approaches, it was 
 unsuited for cross site extraction tasks because the learned rules were not general enough.
@@
 task, identifying the target entities through the assignment of labels as in a typical 
-Named Entity Recognition task. Traditionally, Hidden Markov Models \cite{Leek1997, Freitag1999}, 
+Named Entity Recognition task. Traditionally, Hidden Markov Models \cite{Leek1997,Freitag1999}, 
 Linear Chain Conditional Random Fields \cite{Lafferty2001}, and Maximum Entropy Taggers 
@@
 More recently, with the advancement of Natural Language Processing and Deep Learning, 
-neural models outperformed previous NER methods. Huang et. al. \cite{Huang2015} introduced the 
+neural models outperformed previous NER methods for plain text. Huang et. al. \cite{Huang2015} introduced the 
 bidirectional Long Short-Term Memory (LSTM) model with a Conditional Random Field (CRF) output layer
-for NER. Lample et. al. \cite{Lample2016} incorporated Convolutional Neural Network based character representations 
-on top of the architecture. And Ma and Hovy \cite{Ma2016} introduced
-LSTM based character representations. Both obtaining improvements with systems that are less reliant
-on feature engineering.
+for NER. Ma and Hovy \cite{Ma2016} incorporated Convolutional Neural Network based character representations 
+on top of the architecture. And Lample et. al. \cite{Lample2016} introduced
+LSTM based character representations.
 
@@
 and EXALG \cite{Arasu2003} only work well for extracting data from pages generated 
-from the same template. A statistical approach to unsupervised domain 
+from a same template.
+
+A statistical approach to unsupervised domain 
 independent web data extraction was described by Zhu et al \cite{Zhu2005}. The 2D CRF 
 model takes a web page segmented into data blocks and employs a two dimensional conditional 
-random field model to perform attribute labelling. The model was further improved in 
+random field model to perform attribute labelling. The model was further improved
 \cite{Zhu2006} to model record segmentation and attribute labelling as a joint task.
@@
 as pointed by Schulz et al. \cite{Schulz2016}, it is difficult to compare the results 
-achieved by competing tools, and many seem to rely excessively on certain heuristics.
-In that regard, the impressive advancements in NLP may provide for more robust and
+achieved by competing tools, and many seem to rely excessively on heuristic methods.
+In that regard, the recent advancements in sequence taggers may provide more robust and
 flexible extraction tools.
@@
 
-Most web data extraction systems rely on hand crafted rules or gazetteers to perform
+Many web data extraction systems rely on hand crafted rules or gazetteers to perform
 attribute annotation. Machine learning approaches to NER can improve annotations of 
-more complex entities and even manage entity detection without resorting to a gazetteer.
-We explored multiple approaches to the Named Entity Recognition problem in the context 
-of a web information extraction task. First, we introduce two traditional approaches, 
-namely: Hidden Markov Models and Linear Chain Conditional Random Fields. Then
+more complex entities and even perform entity detection without any feature
+engineering. We explored many methods of Named Entity Recognition
+in the context of a web data extraction task. First, we discuss two traditional 
+approaches: Hidden Markov Models, and Linear Chain Conditional Random Fields. Then,
 we explore neural network architectures.
@@
 Since $ P(X) $ is the same for all label sequences $ Y $, we can simply maximize
-$ P(X|Y) P(Y) $.
+the probability $ P(X|Y) P(Y) $.
 
 A HMM makes two assumptions. First, the probability of being in a given state depends 
-only on a fixed number of previous states. That is 
-$ P(y_i|y_{i-1}x_{i-1}, y_{i-2}x_{i-2}, ..., y_1x_1) = P(y_i|y_{i-1}, y_{i-2},..., y_{i-k}) $. 
+only on a fixed number of previous states. That is:
+
+\begin{equation}
+P(y_i|y_{i-1}x_{i-1}, y_{i-2}x_{i-2}, ..., y_1x_1) = P(y_i|y_{i-1}, y_{i-2},..., y_{i-k})
+\end{equation}
+
 In fact, we can get much better results on the NER task by looking at trigrams
@@
 Some label assignments are highly improbable, such as single token named entities 
-separated by a common word, and these kinds of patterns can be caught by a higher order HMM.
-Second, the probability of a word depends only on its assigned label 
-$ P(x_i|y_{i-1}x_{i-1}, ..., y_1x_1) = P(x_i|y_i) $. With these assumptions, 
+separated by a common word. These kinds of patterns can be perceived by a higher order HMM.
+Second, the probability of a word depends only on its assigned label. That is:
+
+\begin{equation}
+P(x_i|y_{i-1}x_{i-1}, ..., y_1x_1) = P(x_i|y_i)
+\end{equation}
+
+With these assumptions, 
 the probability $ P(Y|X) $ can be approximated by the expression:
@@
 
-The probabilities can be calculated through maximum likelihood estimation from the relative
+All relevant probabilities can be estimated through maximum likelihood estimation from the relative
 frequencies of labels and features in the corpus. The best sequence of labels can be computed 
@@
 
-HMM based taggers have been succesfully apllied in many NLP and WDE tasks 
-\cite{Rabiner1990, Leek1997, Freitag2000}. They are incredibly fast to train and very 
+HMM based taggers have been succesfully applied in many NLP and WDE tasks 
+\cite{Rabiner1990,Leek1997,Freitag2000}. They are incredibly fast to train and also they are very 
 interpretable, making them a good choice for a first approximation. However, these models 
@@
 
-In the particular case of NER on HTML, there are useful features related to the HTML
-structure that can be used to identify named entities. In a particular website, named
-entities tend to occur inside the same HTML tags with the same CSS classes. This fact
-can be used as an additional piece of evidence in the HMM tagger. However, if we train 
-the HMM for a particular set of websites, and then we feed it with new websites, almost 
-surely there will be small correlation between the HTML features estimated in the training 
-set and the distribution of these features in the new websites, simply because websites 
-use very different templates. Therefore, we propose to use a self training strategy to train 
-these HTML features. This is only possible because the HMM can be trained very quickly. The 
-self training strategy is implemented like this:
+In the task of NER on HTML, there are useful features related to the HTML
+structure that can help in identifying named entities. On a given website, named
+entities tend to occur inside the same HTML tags. The HTML tag feature or other
+HTML features could easily be incorporated in the HMM. However, these 
+features are only useful inside a single website and they cannot be generalized, 
+because different websites use distinct HTML templates. 
+Therefore, we propose a self training strategy to obtain probabilities for
+these HTML features. It is implemented like this:
 
 \begin{itemize}
-\item Train the HMM with the training set without HTML features.
-\item Compute labels for the new websites with the trained HMM.
-\item Use these computed labels as a proxy for the actual labels in the 
-new websites and estimate HTML feature frequencies only in the new websites.
-\item Recompute the labels using the HTML features.
+\item Train the HMM without any HTML features.
+\item Compute labels for a website with the trained HMM.
+\item Use the computed labels as a proxy for the actual labels in the 
+website and estimate HTML feature frequencies for this website alone.
+\item Recompute the labels now using the HTML feature probabilities.
 \end{itemize}
 
-This adds very little overhead to the original model while improving precision and recall
-modestly.
+In theory, this strategy could be used with any sequence tagger, however
+retraining a classifier with new features can become prohibitively expensive.
+This strategy is only possible because the computation of HTML feature
+frequencies can be performed very quickly. This adds very little overhead 
+to the original HMM and improves precision and recall by a considerable 
+margin.
 
@@
 maximum entropy models such as L-BFGS \cite{Liu1989}. The most likely label sequences can be decoded 
-with the Viterbi algorithm, as was the case on HMMs.
+with the Viterbi algorithm, as was the case for HMMs.
 
-CRFs are more general than HMMs because the transitions from $ y_{t-1} $ to $ y_{t} $ can also depend 
-on the vector of observations $ X $. This flexibility of feature functions allow for a wide range of
+CRFs are more general than HMMs because the transitions from $ y_{t-1} $ to $ y_{t} $ can depend 
+on the whole vector of observations $ X $. This flexibility of feature functions allows for a wide range of
 possibilities. Recently, CRFs have been succesfully employed as the output layer in complex neural 
-architectures bringing improvements over models that classify labels independently.
+architectures bringing improvements over models that compute labels independently.
 
-\subsection{Neural Network Models}
+\subsection{Neural Network Architectures}
 
@@
   \centering
-  \includegraphics[width=0.5\textwidth]{pics/rnn_network}
+  % \includegraphics[width=0.5\textwidth]{pics/rnn_network}
+  \includegraphics[width=400px]{pics/rnn_network}
   \caption{RNN for NER}
@@
 Although RNNs are theoretically capable of learning long term dependencies, in practice 
-it might be difficult. Long short term memory networks (LSTM) were introduced by Hochreiter 
-and Schmidhuber \cite{Hochreiter1997} with this problem in mind and have been 
-popularized since them. LSTM cell implementations vary slightly in the literature.
+it becomes difficult due to vanishing gradients. Long short term memory networks (LSTM) were 
+introduced by Hochreiter and Schmidhuber \cite{Hochreiter1997} with this problem in mind and 
+they have been popularized since then. LSTM cell implementations vary slightly in the literature.
 Our implementation has the following definition:
@@
 In NER related tasks, both past and future words are important when deciding the
-label at time $ t $, but a regular LSTM network only takes past features in consideration. 
+label at time $ t $, but a regular LSTM network only takes past features into consideration. 
 A bidirectional LSTM solves this problem by stacking two regular LSTMs, and feeding
@@
 The unaccented lowercase token was used as the key for the Glove-100 embedding lookup.
-A gazetteer was constructed from a researcher list extracted from DBLP with 1.595.771
+A gazetteer was constructed from a researcher list extracted from DBLP with 1,595,771
 names. Table \ref{tab:gazetteer} shows the precision, recall and F1 score obtained with an
 exact gazetteer matching strategy in each data file as a baseline.
-Feature 2 represents an exact match of a sequence of tokens to any of the 1.595.771 
+Feature 2 represents an exact match of a sequence of tokens to any of the 1,595,771 
 names, and feature 3 represents a partial match. Feature 4 is the rounded logarithm of 
 the frequency of a token in the gazetteer, and feature 5 is the rounded logarithm of the frequency
-of a token in a word corpus obtained through a random crawl in university websites.
+of a token in a word corpus obtained through a random crawl on university websites.
 Features 6 to 11 represent a simple regular expression match to an email, number, 
@@
 in other documents. However, these features can be trained with the self-training strategy 
-for HMMs described in section \ref{sssec:self_training}. In all other models these features 
-were ignored.
+for HMMs described in section \ref{sssec:self_training}.
 
@@
 split into five non overlapping sets with 17 documents, and every model was trained
-and tested once using each set, while the test data was kept unchanged. We wanted to verify empirically 
+and tested once using each set, while the test data was kept unchanged. We wanted to verify 
 how the models behaved when training data is limited, since labelling NER datasets can be a
@@
 
-\bibliographystyle{unsrt}
-\bibliography{bibfile}
+% \bibliographystyle{unsrt}
+% \bibliography{bibfile}
+
+\begin{thebibliography}{}
+  \bibitem[\protect\citename{Akmajian and Lehrer }1976]{Crescenzi2001}
+   Akmajian, A. and Lehrer, A. (1976) NP-like quantifiers and the
+   problem of determining the head of an NP. {\it Linguistic
+   Analysis\/} {\bf 2}: 295--313.
+  \bibitem[\protect\citename{Akmajian and Lehrer }1976]{Arasu2003}
+   Akmajian, A. and Lehrer, A. (1976) NP-like quantifiers and the
+   problem of determining the head of an NP. {\it Linguistic
+   Analysis\/} {\bf 2}: 295--313.
+\end{thebibliography}
 

### 2018-11-29 tex/nleguide.tex
New article.

% nleguide.tex
% v1.14, released 30th September 1998
% Copyright 1995, 1997, 1998 Cambridge University Press

\documentclass{nle}

\title[Natural Language Engineering]
      {Natural Language Engineering \LaTeX\ Supplement}
\author[\LaTeX\ Supplement]
       {C\ls A\ls M\ls B\ls R\ls I\ls D\ls G\ls E\ns
        \TeX\ls -\ls T\ls O\ls -\ls T\ls Y\ls P\ls E\\
        Electronic Products and Composition Group,\\
        Printing Division, Cambridge University Press,
        CB2 2BS.}

\received{20 March 1995; revised 30 September 1998}

\pagerange{\pageref{firstpage}--\pageref{lastpage}}
\pubyear{1998}

\newcommand\eg{{\it e.g.\ }}
\newcommand\etc{{\it etc}}

\begin{document}

\label{firstpage}
\maketitle

\begin{abstract}
This guide is for authors who are preparing papers for the {\em Natural
Language Engineering\/} journal using the \LaTeX\ document preparation
system and the CUP NLE style file.
\end{abstract}

\section{Introduction}

The layout design for the {\em Natural Language Engineering\/} journal
has been implemented as a \LaTeX\ style file. The NLE style file is based
on the ARTICLE style as discussed in the \LaTeX\ manual. Commands which
differ from the standard \LaTeX\ interface, or which are provided in addition
to the standard interface, are explained in this guide. This guide is not a
substitute for the \LaTeX\ manual itself.

\subsection{Introduction to \LaTeX}

The \LaTeX\ document preparation system is a special version of the
\TeX\ typesetting program. \LaTeX\ adds to \TeX\ a collection of
commands which simplify typesetting by allowing the author to
concentrate on the logical structure of the document rather than
its visual layout.

\LaTeX\ provides a consistent and comprehensive document preparation
interface. There are simple-to-use commands for generating a table of
contents, lists of figures and/or tables, and indexes. \LaTeX\ can
automatically number list entries, equations, figures, tables, and
footnotes, as well as parts, chapters, sections and subsections.
Using this numbering system, bibliographic citations, page references
and cross references to any other numbered entity (\eg chapter,
section, equation, figure, list entry) are quite straightforward.

\subsection{The NLE Document Style}

The use of document styles allows a simple change of style (or style option)
to transform the appearance of your document. The CUP NLE style file preserves
the standard \LaTeX\ interface such that any document which can be produced
using the standard \LaTeX\ ARTICLE style can also be produced with the
NLE style. However, the measure (or width of text) is slightly different
from that for ARTICLE, therefore line breaks will change and it is possible
that equations may need re-setting.

\section{Using the NLE style}

First, copy the file \verb"NLE.sty" into the correct subdirectory on your
system. The NLE document style is implemented as a complete document style,
{\em not\/} as a document style option. In order to use the NLE style,
replace \verb"article" by \verb"nle" in the \verb"\documentstyle" command
at the beginning of your document:
%
\begin{verbatim}
  \documentstyle{article}
\end{verbatim}
%
is replaced by
%
\begin{verbatim}
  \documentstyle{nle}
\end{verbatim}
%
None of the standard document style options should be used.

\section{Additional facilities}

In addition to all the standard \LaTeX\ design elements, the NLE style
includes the following feature:
\begin{itemize}
  \item Extended commands for specifying a short version
        of the title and author(s) for the running
        headlines.
\end{itemize}
Once you have used this additional facility in your document,
do not process it with a standard \LaTeX\ style file.

\subsection{Titles and authors' names}

In the NLE style, the title of the article and the author's name (or authors'
names) are used both at the beginning of the article for the main title and
throughout the article as running headlines at the top of every page.
The title is used on odd-numbered pages (rectos) and the author's name appears
on even-numbered pages (versos).
Although the main heading can run to several lines of text, the running head
line must be a single line.
Moreover, the main heading can also incorporate new line commands
(\eg \verb"\\") but these are not acceptable in a running headline.
To enable you to specify an alternative short title and author's name, the
standard \verb"\title" and \verb"\author" commands have been extended to take
an optional argument to be used as the running headline:
%
\begin{verbatim}
  \title[A short title]{The full title which can be as long
   as necessary}
  \author[Author's name]{The full author's name, followed by\\
   the affiliation if necessary}
\end{verbatim}
%
The following example is taken from Abadi et~al. (1991) and
shows several authors and their affiliations.
%
\begin{verbatim}
  \title{Explicit substitutions}
  \author[M. Abadi and others]
   {M.\ns A\ls B\ls A\ls D\ls I,\ns
    L.\ns C\ls A\ls R\ls D\ls E\ls L\ls L\ls I\\
   Digital Equipment Corp., Systems Research Center,\\
   130 Lytton Avenue, Palo Alto, California, USA 94301
   \and
   P.-L.\ns C\ls U\ls R\ls I\ls E\ls N\\
   Laboratoire d'Informatique, Ecole Normale Sup'erieure,
   45 Rue d'Ulm 75005, Paris, France
   \and
   and\ns J.-J.\ns L\ls \'E\ls V\ls Y\\
   INRIA, Domaine de Voluceau, Roquencourt, B.P.105, 78153,
   Le Chesnay, Cedex, France.}
\end{verbatim}
Notice the use of the predefined macros \verb"\ls" and \verb"\ns" to
letter-space the author's name. As you can see from this example, when
there are four or more authors, the short author name argument should
contain the first authors name followed by the text `and others'.

\subsection{Abstract}

The NLE style provides for an abstract which is produced by the following
commands
%
\begin{verbatim}
  \begin{abstract}
    ...
  \end{abstract}
\end{verbatim}

\subsection{Lists}

The NLE style provides the three standard list environments.
\begin{itemize}
  \item Bulleted lists, created using the \verb"itemize" environment.
  \item Numbered lists, created using the \verb"enumerate" environment.
  \item Labelled lists, created using the \verb"description" environment.
\end{itemize}

\subsection{Footnotes}

The NLE journal style uses superior numbers for footnote
references.\footnote{This shows how a footnote is typeset.}

\section{Some guidelines for using standard facilities}

The following notes may help you achieve the best effects with the NLE style
file.

\subsection{Sections}

\LaTeX\ provides five levels of section headings and they are all
defined in the NLE style file:
\begin{itemize}
  \item \verb"\section".
  \item \verb"\subsection".
  \item \verb"\subsubsection".
  \item \verb"\paragraph".
  \item \verb"\subparagraph".
\end{itemize}
Section numbers are given for sections, subsection and subsubsection headings.

\subsection{Running headlines}

As described above, the title of the article and the author's name (or authors'
names) are used as running headlines at the top of every page.
The title is used on odd-numbered pages (rectos) and the author's name appears
on even-numbered pages (versos).

The \verb"\pagestyle" and \verb"\thispagestyle" commands should {\em not\/} be
used.
Similarly, the commands \verb"\markright" and \verb"\markboth" should not be
necessary.

\subsection{Tables}

The {\tt figure} and {\tt table} environments are implemented as described in
the \LaTeX\ Manual to
provide consecutively numbered floating inserts for illustrations and tables
respectively.
The standard inserts and their captions are formatted centred.
Line breaks in captions can be inserted as required using \verb"\\".

The NLE style file will cope with most positioning of your tables
and you should not normally use the optional positional qualifiers on the
\verb"table" environment which would override these decisions.
Normal journal style sets the table caption first, followed by a double
rule, the table body and a double rule at the bottom.  Single rules and
spanner rules (\verb"\cline") can be used to separate headings from the
columns.  For example, Table~\ref{sample-table} is produced using the
following commands:\par
%
{\small
\begin{verbatim}
\begin{table}
  \caption{Results of Overloading for 3 Experimental Setups}
  \begin{minipage}{\textwidth}
    \begin{tabular}{lcrrrrr}
    \hline\hline
    Program& Expt.&
     CPU\footnote{Seconds of elapsed time on an unloaded Sun 3/50.}&
     RelCPU\footnote{CPU Time relative to experiment (a).}&
     GC& Mem\footnote{Bytes of heap used over the duration of the program.}&
     RelMem\footnote{Memory usage relative to experient (a).}\\
    \hline
    8 Queens& (a)&   2\hpt 88&  1\hpt 00&    6&   1\hpt 7M&  1\hpt 00\\
    &         (b)&  32\hpt 51& 11\hpt 29&  193&  48\hpt 9M& 28\hpt 76\\
    &         (c)&   7\hpt 90&  2\hpt 74&   42&  11\hpt 3M&  6\hpt 65\\
    \noalign{\vspace {.5cm}}
    Primes&   (a)&   4\hpt 89&  1\hpt 00&   19&   5\hpt 3M&  1\hpt 00\\
    &         (b)&  47\hpt 54&  9\hpt 72&  204&  54\hpt 5M& 10\hpt 28\\
    &         (c)&  10\hpt 08&  2\hpt 06&   47&  13\hpt 0M&  2\hpt 45\\
    \noalign{\vspace {.5cm}}
    Nfib&     (a)&  21\hpt 65&  1\hpt 00&  161&  40\hpt 4M&  1\hpt 00\\
    &         (b)& 221\hpt 65& 10\hpt 24& 1382& 349\hpt 0M&  8\hpt 64\\
    &         (c)&  21\hpt 30&  0\hpt 98&  161&  42\hpt 0M&  1\hpt 03\\
    \noalign{\vspace {.5cm}}
    KWIC&     (a)&   7\hpt 07&  1\hpt 00&   15&   6\hpt 3M&  1\hpt 00\\
    &         (b)&  34\hpt 55&  4\hpt 89&  109&  47\hpt 8M&  7\hpt 59\\
    &         (c)&  31\hpt 62&  4\hpt 47&   53&  45\hpt 0M&  7\hpt 14\\
    \hline\hline
    \end{tabular}
    \vspace{-2\baselineskip}
  \end{minipage}
  \label{sample-table}
\end{table}
\end{verbatim}}
%
\noindent Notice the use of the \verb"\hpt" macro to obtain the centered
decimal points, inside the body of the table.

\begin{table}
  \caption{Results of Overloading for 3 Experimental Setups}
  \begin{minipage}{\textwidth}
    \begin{tabular}{lcrrrrr}
    \hline\hline
    Program& Expt.&
     CPU\footnote{Seconds of elapsed time on an unloaded Sun 3/50.}&
     RelCPU\footnote{CPU Time relative to experiment (a).}&
     GC& Mem\footnote{Bytes of heap used over the duration of the program.}&
     RelMem\footnote{Memory usage relative to experient (a).}\\
    \hline
    8 Queens& (a)&   2\hpt 88&  1\hpt 00&    6&   1\hpt 7M&  1\hpt 00\\
    &         (b)&  32\hpt 51& 11\hpt 29&  193&  48\hpt 9M& 28\hpt 76\\
    &         (c)&   7\hpt 90&  2\hpt 74&   42&  11\hpt 3M&  6\hpt 65\\
    \noalign{\vspace {.5cm}}
    Primes&   (a)&   4\hpt 89&  1\hpt 00&   19&   5\hpt 3M&  1\hpt 00\\
    &         (b)&  47\hpt 54&  9\hpt 72&  204&  54\hpt 5M& 10\hpt 28\\
    &         (c)&  10\hpt 08&  2\hpt 06&   47&  13\hpt 0M&  2\hpt 45\\
    \noalign{\vspace {.5cm}}
    Nfib&     (a)&  21\hpt 65&  1\hpt 00&  161&  40\hpt 4M&  1\hpt 00\\
    &         (b)& 221\hpt 65& 10\hpt 24& 1382& 349\hpt 0M&  8\hpt 64\\
    &         (c)&  21\hpt 30&  0\hpt 98&  161&  42\hpt 0M&  1\hpt 03\\
    \noalign{\vspace {.5cm}}
    KWIC&     (a)&   7\hpt 07&  1\hpt 00&   15&   6\hpt 3M&  1\hpt 00\\
    &         (b)&  34\hpt 55&  4\hpt 89&  109&  47\hpt 8M&  7\hpt 59\\
    &         (c)&  31\hpt 62&  4\hpt 47&   53&  45\hpt 0M&  7\hpt 14\\
    \hline\hline
    \end{tabular}
    \vspace{-2\baselineskip}
  \end{minipage}
  \label{sample-table}
\end{table}

The \verb"tabular" environment should be used to produce ruled tables;
it has been modified for the NLE style in the following ways:
\begin{enumerate}
  \item Additional vertical space is inserted above and below a horizontal rule
        (produced by \verb"\hline");
  \item Tables are centred, and span the full width of the page; that is,
  they are similar to the tables that would be produced by
  \verb"\begin{minipage}{\textwidth}".
\end{enumerate}
Because of this reformatting, vertical rules should not be used;
furthermore, commands to
redefine quantities such as \verb"\arraystretch" should be omitted. If
the old tabular facilities are needed, there is a new environment,
\verb"oldtabular", which has none of the reformatting; it should be used
in exactly the same way.

\subsection{Illustrations (or figures)}

The NLE style will cope with most positioning of your illustrations
and you should not normally use the optional positional qualifiers on
the \verb"figure" environment which would override these decisions.
Figure captions should be below the figure itself, therefore the \verb"\caption"
command should appear after the figure or space left for an illustration.

Figure~\ref{sample-figure} shows an example of space left above a
caption for artwork to be pasted in. This was produced with the
following commands:
%
\begin{verbatim}
  \begin{figure}
    \vspace{5cm} % the vertical depth of the artwork
    \caption{An example figure with space for artwork.}
    \label{sample-figure}
  \end{figure}
\end{verbatim}
%
\begin{figure}
  \vspace{5cm} % the vertical depth of the artwork
  \caption{An example figure with space for artwork.}
  \label{sample-figure}
\end{figure}
%
The vertical depth should correspond roughly to the artwork you will submit;
it will be adjusted to fit the final artwork exactly.

\subsection{Bibliography}

As with standard \LaTeX, there are two ways of producing a bibliography;
either by compiling a list of references by hand (using a
\verb"thebibliography" environment), or by using BibTeX with a suitable
bibliographic database. However, contributors are encouraged to format
their list of references in NLE style outlined in section~\ref{fullref}
below.

\subsubsection{References in the Text}

References in the text are given by author and date.
Whichever method is used to produce the bibliography, the references in
the text are done in the same way. Each bibliographical entry has a key,
which is assigned by the author and used to refer to that entry in the
text. There is one form of citation -- \verb"\cite{key}" -- to produce the
author and date, and another form -- \verb"\shortcite{key}" -- which
produces the date only. Thus,
Akmajian and Lehrer \shortcite{akm76} is produced by
%
\begin{verbatim}
  Akmajian and Lehrer \shortcite{akm76}
\end{verbatim}
%
while \cite{sal90} is produced by
%
\begin{verbatim}
  \cite{sal90}.
\end{verbatim}

\subsubsection{List of References}\label{fullref}

The following listing shows some references prepared in the style of the
journal.
%
\begin{verbatim}
  \begin{thebibliography}{}
    \bibitem[\protect\citename{Akmajian and Lehrer }1976]{akm76}
     Akmajian, A. and Lehrer, A. (1976) NP-like quantifiers and the
     problem of determining the head of an NP. {\it Linguistic
     Analysis\/} {\bf 2}: 295--313.
    \bibitem[\protect\citename{Huddleston }1984]{hud84}
     Huddleston, Rodney. (1984) {\it Introduction to the Grammar of
     English}. Cambridge: Cambridge University Press.
    \bibitem[\protect\citename{McCord }1990]{mcc90}
     McCord, Michael C. (1990) Slot grammar: a system for simpler
     construction of practical natural language grammars. In R.
     Studer (ed.), {\it Natural Language and Logic: International
     Scientific Symposium}, pp.~118--45. Lecture Notes in Computer
     Science. Berlin: Springer-Verlag.
    \bibitem[\protect\citename{Salton {\it et al.}\ }1990]{sal90}
     Salton, Gerald, Zhao, Zhongnan and Buckley, Chris. (1990)
     A simple syntactic approach for the generation of indexing
     phrases. Technical Report 90--1137, Department of Computer
     Science, Cornell University.
  \end{thebibliography}
\end{verbatim}
%
This list typesets as shown at the end of this guide.
Each entry takes the form
%
\begin{verbatim}
  \bibitem[\protect\citename{Author(s), }Date]{tag}
    Bibliography entry
\end{verbatim}
%
where \verb"Author(s)"\ should be the author names as they are cited in
the text, \verb"Date" is the date to be cited in the text, and \verb"tag"
is the tag that is to be used as an argument for the \verb"\cite{}" and
\verb"\shortcite{}" commands. \verb"Bibliography entry" should be the
material that is to appear in the bibliography, suitably formatted.  This
rather unwieldy scheme makes up for the lack of an author-date system in
\LaTeX.

\appendix
\section{Special commands in {\tt nle.sty}}

The following is a summary of the new commands, optional
arguments and environments which have been added to the
standard \LaTeX\ user-interface in creating the NLE style file.

\vspace{6pt}

\noindent
\begin{tabular}{lp{8cm}}
{\em New commands}      & \\
\ifprodtf
\verb"\cite"            & the optional argument has changed it's use. This
                          allows author-date citations to be changed without
                          loosing the link to the bibliography entry.\\
\fi
\verb"\hpt"             & to typeset a centered decimal point (\eg 1\hpt1).
                          These are normally used inside the body of tables.\\
\verb"\ls", \verb"\ns"  & to letter space the author's name. \\
\verb"\proofbox"        & used with \verb"\usebox" to place a proof-box
                          in the text. \\[6.5pt]
{\em New optional arguments} & \\
\verb"[<short title>]"  & in the \verb"\title" command: to define a right running
                          headline that is different from the article title. \\
\verb"[<short author>]" & in the \verb"\author" command: to define a left running
                          headline with text that is different from the
                          authors' names as typeset at the article opening. \\[6.5pt]
{\em New environments}  & \\
\verb"proof"            & to typeset mathematical proofs. \\
\verb"proof*"           & to typeset mathematical proofs without the
                          terminating proof-box.
\end{tabular}

\ifprodtf
%
\section{Notes for Editors}

This appendix contains additional information which may be useful to
those who are involved with the final production stages of an article.
Authors, who are generally not typesetting the final pages in the
journal's typeface (Monotype Times), do not need this information.

\subsection{Catchline and date commands}

To be placed in the preamble; for example:
\begin{itemize}
  \item \verb"\pubyear{1998}"
  \item \verb"\volume{{\bf 1} (1):}"
  \item \verb"\pagerange{35--48}"
  \item \verb"\received{1 April 1993; revised 30 October 1993}"
\end{itemize}

\subsection{Macros provided by {\tt NLEsym.sty}}

None at present.

\subsection{Editing citations (when the author has used the
 {\tt cite} command)}

In the past when an automatic \verb"\cite" command produced text in the output
which needed to be changed, the argument (in [ ]) from the bibliography entry
was copied to the location of the \verb"\cite" command and then modified.
The \verb"\cite" command would then be removed as part of this process.

In the near future, we will probably have to supply \TeX\ output which will
need to contain `PDF marks' for interactive browsing.  Clearly by removing
the automatic link to the bibliographic entry (referenced by the \verb"\cite"),
we are making extra work for ourselves later on.

To avoid this, the function of the \verb"\cite" command's optional argument
has been changed. For example, the \verb"\cite" command for the
`\verb"mcc90"' entry gives:
\[ \hbox{(McCord 1990)} \]
but you want the following to appear in the text:
\[ \hbox{(McCord 1990, see p.~119)} \]
you would then use:
\[ \hbox{\verb"\cite[(McCord 1990, see p.~119)]{mcc90}"} \]
to obtain the desired result. Notice that you have to supply
the round brackets as well in the optional argument.
This modification also works for the \verb"\shortcite" command.
%
\fi

\begin{thebibliography}{}
  \bibitem[\protect\citename{Akmajian and Lehrer }1976]{akm76}
   Akmajian, A. and Lehrer, A. (1976) NP-like quantifiers and the
   problem of determining the head of an NP. {\it Linguistic
   Analysis\/} {\bf 2}: 295--313.
  \bibitem[\protect\citename{Huddleston }1984]{hud84}
   Huddleston, Rodney. (1984) {\it Introduction to the Grammar of
   English}. Cambridge: Cambridge University Press.
  \bibitem[\protect\citename{McCord }1990]{mcc90}
   McCord, Michael C. (1990) Slot grammar: a system for simpler
   construction of practical natural language grammars. In R.
   Studer (ed.), {\it Natural Language and Logic: International
   Scientific Symposium}, pp.~118--45. Lecture Notes in Computer
   Science. Berlin: Springer-Verlag.
  \bibitem[\protect\citename{Salton {\it et al.}\ }1990]{sal90}
   Salton, Gerald, Zhao, Zhongnan and Buckley, Chris. (1990)
   A simple syntactic approach for the generation of indexing
   phrases. Technical Report 90--1137, Department of Computer
   Science, Cornell University.
\end{thebibliography}

\label{lastpage}

\end{document}

### 2018-11-29 models/util.py

@@ -39,7 +39,13 @@ class WordEmbeddings():
 
 def load_raw_dataset(f, max_sentence_len=50):
   with open(f, 'r') as f:
-    sentences = f.read().strip().split('\n\n')
+    data = f.read().strip()
+
+    # sentences = re.compile("-DOCSTART-.+\n\n").split(data)
+    # sentences = [s for s in sentences if len(s) > 0]
+    # X = [[t.split(' ') for t in re.compile("\n+").split(s) if not re.match("^\s+$", s)] for s in sentences]
+
+    sentences = data.split('\n\n')
     sentences = [s for s in sentences if not s.startswith('-DOCSTART-')]
     X = [[t.split(' ') for t in s.split('\n') if len(s) > 0] for s in sentences]
     Y = np.zeros((len(X), max_sentence_len, num_labels))

### 2018-11-29 train_model.py

@@ -155,7 +155,7 @@ elif model in ['nb', 'hmm-1', 'hmm-2', 'hmm-3', 'hmm-4']:
   print_results('Test', hmm.predict(X3), Y3, T3)
 
 elif model in ['maxent', 'crf', 'lstm-crf', 'lstm-crf-cnn', 'lstm-crf-lstm']:
-  we = WordEmbeddings('glove-100')
+  we = WordEmbeddings('glove-300')
 
   if dataset:
     dev = Dataset(dataset, we, max_sentence_len=50, max_token_len=20)
@@ -176,7 +176,7 @@ elif model in ['maxent', 'crf', 'lstm-crf', 'lstm-crf-cnn', 'lstm-crf-lstm']:
   )
   
   lstm_crf.create(we.matrix)
-  lstm_crf.fit(callbacks=[Metrics(lstm_crf)], epochs=10)
+  lstm_crf.fit(callbacks=[Metrics(lstm_crf)], epochs=50)
 
   lstm_crf.load_best_model()
   val_predict, val_targ, T = lstm_crf.validate()

### 2018-11-29 tex/article.tex
LSTM explanation.

@@
 Recurrent neural networks (RNN) have been succesfully employed on numerous NLP tasks such as
-language modelling, POS tagging, speech recognition and NER. Different from feedforward neural networks, 
-RNNs can retain information in their internal state, making them more suitable for processing sequences, 
-and consequently for solving text related tasks. In NER, the network outputs one label for each input 
-vector as shown in Figure \ref{fig:rnn_network}.
-
-Although RNNs are theoretically capable of learning long term dependencies, in practice 
-it becomes difficult due to vanishing gradients. Long short term memory networks (LSTM) were 
-introduced by Hochreiter and Schmidhuber \cite{Hochreiter1997} with this problem in mind and 
-they have been popularized since then. LSTM cell implementations vary slightly in the literature.
-Our implementation has the following definition:
+language modelling, POS tagging, speech recognition and NER. Different from feedforward 
+neural networks, RNNs can retain information in their internal state, making them more 
+suitable for processing sequences, and consequently for solving text related tasks. 
+Figure~\ref{fig:rnn_network} describes an RNN for sequence labeling unrolled through multiple 
+timesteps. At each timestep, the neural network computes a hidden state $ h_t $ using an input 
+vector $ x_t $ and the previous hidden state $ h_{t-1} $, that retains information from past 
+iterations. Finally, the RNN produces an output vector $ y_t $ representing the label for that 
+timestep. A common definition for an RNN cell is given by the equations:
 
 \begin{flalign*}
-\Gamma_i^{<t>} &= \sigma(W_i[x^{<t>},h^{<t-1>}] + b_i) &\\
-\Gamma_f^{<t>} &= \sigma(W_f[x^{<t>},h^{<t-1>}] + b_f) &\\ 
-c^{<t>}        &= \Gamma_f^{<t>} \circ c^{<t-1>} + \Gamma_i^{<t>} tanh(W_c[x^{<t>},h^{<t-1>}] + b_c) &\\
-\Gamma_o^{<t>} &= \sigma(W_o[x^{<t>},h^{<t-1>}] + b_o) &\\
-h^{<t>}        &= \Gamma_o^{<t>} \circ tanh(c^{t}) &
+h_t &= tanh(W_x x_t + W_h h_{t-1}) &\\
+y_t &= softmax(W_y h_t) &
+\end{flalign*}
+
+Where $ W_x $, $ W_h $ and $ W_y $ are weight matrices that can be trained with the 
+Backpropagation Through Time (BPTT) algorithm. Theoretically, RNNs are capable of learning
+and retaining long term dependencies through their internal state $ h_t $. However, in practice,
+it becomes difficult due to the vanishing gradient problem. Long short term memory networks (LSTM) were 
+introduced by Hochreiter and Schmidhuber \cite{Hochreiter1997} with this problem in mind and 
+have been popularized since then.
+
+LSTMs incorporate a memory cell $ c $ in the RNN definition and three gates to control 
+the flow of information that comes in and out of the memory cell.
+The input gate $ \Gamma_{i} $ controls the amount of new information that will flow into the memory cell,
+the forget gate $ \Gamma_{f} $ controls the amount of previous information that will be retained in the memory
+cell, and the output gate $ \Gamma_{o} $ controls the amount of information stored in the memory cell that
+will be used to compute the output activation of the LSTM unit. LSTM cell implementations vary slightly in 
+the literature, so we give the definition for our implementation below:
+
+\begin{flalign*}
+\Gamma_{i} &= \sigma(W_i[x_t,h_{t-1}] + b_i) &\\
+\Gamma_{f} &= \sigma(W_f[x_t,h_{t-1}] + b_f) &\\ 
+\Gamma_{o} &= \sigma(W_o[x_{t},h_{t-1}] + b_o) &\\
+c_t      &= \Gamma_{f} \circ c_{t-1} + \Gamma_{i} \circ tanh(W_c[x_{t},h_{t-1}] + b_c) &\\
+h_t      &= \Gamma_{o} \circ tanh(c_t) &
 \end{flalign*}
@@
 forget and output gates, respectively. And $ W $ with a subscript is the weight 
-matrix corresponding to that gate. Variable $ c^{<t>} $ is the cell 
-state and $ h^{<t>} $ is the hidden state, with the vector $ [x^{<t>},h^{<t-1>}] $ 
-being formed by concatenating the current input vector $ x^{<t>} $ and the hidden vector 
-from the previous timestep $ h^{<t-1>} $. A visual description of our LSTM cell is 
+matrix corresponding to that gate. Variable $ c_{t} $ is the cell 
+state and $ h_{t} $ is the hidden state, with the vector $ [x_{t},h_{t-1}] $ 
+formed by concatenating the current input vector $ x_{t} $ and the hidden vector 
+from the previous timestep $ h_{t-1} $. A visual description of our LSTM cell is 
 provided in figure \ref{fig:lstm_cell}.
+
 This implementation differs from the LSTM cell described in Huang et al. \cite{Huang2015}
@@
 do not take input from the previous cell state $ c^{<t-1>} $ and the output gate does
-not take input from the current cell state $ c^{<t>} $. The cell state and the control gates 
+not take input from the current cell state $ c^{<t>} $.
+
+The cell state and the control gates 
 are what makes the LSTM cell better at modelling long term dependencies in comparison
@@
 they have a vocabulary size of 400.000 words.
-In the case of NER on HTML, word embeddings work similar to a gazetteer. Named entities 
+In the case of NER on HTML, word embeddings work similarly to a gazetteer. Named entities 
 with the same type have similar embeddings, so good word embeddings can achieve exceptional 

### 2018-11-30 tex/article.tex
Experiments and conclusion.

@@
 approaches: Hidden Markov Models, and Linear Chain Conditional Random Fields. Then,
-we explore neural network architectures.
+we discuss neural network architectures.
 
@@
   \centering
-  % \includegraphics[width=0.5\textwidth]{pics/rnn_network}
-  \includegraphics[width=400px]{pics/rnn_network}
+  \includegraphics[width=0.75\textwidth]{pics/rnn_network}
   \caption{RNN for NER}
@@
 cell, and the output gate $ \Gamma_{o} $ controls the amount of information stored in the memory cell that
-will be used to compute the output activation of the LSTM unit. LSTM cell implementations vary slightly in 
-the literature, so we give the definition for our implementation below:
+will be used to compute the output activation of the LSTM unit. 
+LSTM cell implementations vary slightly in the literature, a visual description of 
+our LSTM cell is also provided in Figure~\ref{fig:lstm_cell}.
 
-\begin{flalign*}
-\Gamma_{i} &= \sigma(W_i[x_t,h_{t-1}] + b_i) &\\
-\Gamma_{f} &= \sigma(W_f[x_t,h_{t-1}] + b_f) &\\ 
-\Gamma_{o} &= \sigma(W_o[x_{t},h_{t-1}] + b_o) &\\
-c_t      &= \Gamma_{f} \circ c_{t-1} + \Gamma_{i} \circ tanh(W_c[x_{t},h_{t-1}] + b_c) &\\
-h_t      &= \Gamma_{o} \circ tanh(c_t) &
-\end{flalign*}
-
-\begin{figure}
+\begin{figure}[h]
   \centering
-  \includegraphics[width=0.5\textwidth]{pics/lstm_cell}
+  \includegraphics[width=0.75\textwidth]{pics/lstm_cell}
   \caption{LSTM Cell}
@@
 
-where $ \sigma $ is the logistic sigmoid function. $ \Gamma_i $, $ \Gamma_f $, and $ \Gamma_o $ are the input,
-forget and output gates, respectively. And $ W $ with a subscript is the weight 
-matrix corresponding to that gate. Variable $ c_{t} $ is the cell 
-state and $ h_{t} $ is the hidden state, with the vector $ [x_{t},h_{t-1}] $ 
-formed by concatenating the current input vector $ x_{t} $ and the hidden vector 
-from the previous timestep $ h_{t-1} $. A visual description of our LSTM cell is 
-provided in figure \ref{fig:lstm_cell}.
+The equations for the LSTM cell are:
+
+\begin{flalign*}
+\Gamma_{i} &= \sigma(W_i \cdot [x_t,h_{t-1}] + b_i) &\\
+\Gamma_{f} &= \sigma(W_f \cdot [x_t,h_{t-1}] + b_f) &\\ 
+\Gamma_{o} &= \sigma(W_o \cdot [x_{t},h_{t-1}] + b_o) &\\
+c_t        &= \Gamma_{f} \ast c_{t-1} + \Gamma_{i} \ast tanh(W_c \cdot [x_{t},h_{t-1}] + b_c) &\\
+h_t        &= \Gamma_{o} \ast tanh(c_t) &
+\end{flalign*}
+
+Where $ \sigma $ is the logistic sigmoid function. $ \Gamma_i $, $ \Gamma_f $, and $ \Gamma_o $ are the input,
+forget and output gates, respectively, and $ W_i $, $ W_f $, $ W_o $ are the weight 
+matrices corresponding to each gate. $ c_{t} $ is the cell 
+state at time $ t $ and $ h_{t} $ is the hidden state at time $ t $. 
+The vector $ [x_{t},h_{t-1}] $ is formed by concatenating the current input vector 
+$ x_{t} $ and the hidden vector from a previous timestep $ h_{t-1} $. Finally,
+$ A \ast B $ represents the element-wise multiplication of matrices $ A $ and $ B $
+and $ A \cdot B $ represents the dot product of $ A $ and $ B $.
 
 This implementation differs from the LSTM cell described in Huang et al. \cite{Huang2015}
-in that the input gate $ \Gamma_i $ and the forget gate $ \Gamma_f $
-do not take input from the previous cell state $ c^{<t-1>} $ and the output gate does
-not take input from the current cell state $ c^{<t>} $.
+in that the gates $ \Gamma_i $ and $ \Gamma_f $ do not receive inputs from the previous 
+cell state $ c_{t-1} $ and the output gate does not receive inputs from the current cell 
+state $ c_{t} $. This variation produces little difference in terms of model accuracy on
+the performed task, but it reduces model complexity.
 
-The cell state and the control gates 
-are what makes the LSTM cell better at modelling long term dependencies in comparison
-to a regular RNN.
-
-In NER related tasks, both past and future words are important when deciding the
-label at time $ t $, but a regular LSTM network only takes past features into consideration. 
-A bidirectional LSTM solves this problem by stacking two regular LSTMs, and feeding
-them with observations in opposite directions. The first LSTM receives the forward
-states and the second LSTM receives the backward states. The hidden states from both 
-networks can be concatenated at each time step to produce the output label. With this 
-architecture, Bidirectional LSTMs have information from all input features in the sequence at 
-any given timestep.
-
-\subsubsection{LSTM-CRF}
+\subsubsection{BI-LSTM-CRF}
 \label{sssec:lstm_crf}
 
-\begin{figure}
+On named entity recognition tasks, both past and future words are important 
+to attribute a label at time $ t $, however a regular LSTM network only takes 
+past states into consideration. A bidirectional LSTM solves this problem by stacking 
+two regular LSTMs, and feeding them with observations in opposite directions. The first LSTM 
+receives forward states and the second LSTM receives backward states. The hidden states from both 
+networks can then be concatenated at each timestep to produce output labels. With this 
+architecture, LSTM cells may use information from past and future timesteps to decide 
+the label at time $ t $.
+
+Huang et al. \cite{Huang2015} proposed a bidirectional LSTM with a CRF layer (BI-LSTM-CRF) on 
+the output to tackle the sequence tagging problem. The main benefit of adding a CRF layer 
+in the neural sequence model is that the labels are jointly decoded for a whole sentence 
+instead of being predicted individually. Another possibility would be to use a beam search
+decoder to find an optimal sequence of labels. Predicted tags should be highly correlated 
+in a named entity recognition task, so it is desirable to predict sequences conjointly.
+The BI-LSTM-CRF is described in Figure~\ref{fig:bi_lstm_crf}.
+
+\begin{figure}[h]
   \centering
-  \includegraphics[width=0.5\textwidth]{pics/bi_lstm_crf}
+  \includegraphics[width=0.75\textwidth]{pics/bi_lstm_crf}
   \caption{Bidirectional LSTM-CRF}
@@
 
-Huang et al. \cite{Huang2015} proposed a bidirectional LSTM with a CRF layer (LSTM-CRF) on the output to tackle
-the sequence tagging problem. The CRF layer jointly decodes labels for the whole sentence instead
-of predicting each label individually. This architecture achieved an F1 score of 90.10 on the English
-data from the ConLL-2003 NER shared task \cite{Sang2003}, in contrast to 85.17 for a bidirectional LSTM without the CRF layer. 
+This architecture achieved an F1 score of 90.10 on the English data from the ConLL-2003 
+NER shared task \cite{Sang2003}, in contrast to 85.17 for a bidirectional LSTM without 
+a CRF layer. 
 In our experiments, the LSTM-CRF architecture uses a bidirectional LSTM with 100 
@@
 
-\subsubsection{LSTM-CRF + CNN character representations}
+\subsubsection{CNN character representations}
 \label{sssec:lstm_crf_cnn}
 
-\begin{figure}
+Ma and Hovy \cite{Ma2016} proposed to add a convolutional neural network (CNN) layer 
+on top of a bidirectional LSTM-CRF to encode character-level information. The CNN
+layer is described visually in Figure \ref{fig:cnn}.
+
+\begin{figure}[h]
   \centering
-	  \includegraphics[width=0.5\textwidth]{pics/cnn}
+	  \includegraphics[width=0.75\textwidth]{pics/cnn}
   \caption{CNN based character representations}
@@
 
-Ma and Hovy \cite{Ma2016} proposed adding a convolutional neural network (CNN) layer 
-on top of a bidirectional LSTM-CRF to encode character-level information. The CNN
-layer is described visually in Figure \ref{fig:cnn}, it receives
-only character embeddings as inputs. The character representations generated by the CNN 
-are combined with word level representations and then fed to the Bidirectional LSTM with
-a CRF output layer described in section \ref{sssec:lstm_crf}.
+The convolutional neural netwrok receives character embeddings as inputs. The character 
+representations generated by the CNN are combined with word level representations 
+and fed to the BI-LSTM-CRF in section \ref{sssec:lstm_crf}.
 This architecture can learn morphological features that are very
@@
 the LSTM-CRF architecture with CNN character representations uses a one dimensional convolutional 
-neural network with 30 filters and a window size of three characters on top of the LSTM-CRF architecture.
-The character embeddings fed to the CNN have 30 dimensions that are randomly initialized.
+neural network with 30 filters and a window size of three characters on top of the LSTM-CRF 
+architecture. The character embeddings fed to the CNN have 30 dimensions that are randomly 
+initialized.
 
-\subsubsection{LSTM-CRF + LSTM character representations}
+\subsubsection{LSTM character representations}
 
-\begin{figure}
+Lample et al \cite{Lample2016} proposed to use a bidirectional LSTM to model character-level 
+representations on top of a BI-LSTM-CRF. Combining the forward and backward LSTM hidden states 
+to form the character representation, as described in Figure~\ref{fig:lstm_char}.
+
+\begin{figure}[h]
   \centering
-  \includegraphics[width=0.5\textwidth]{pics/lstm_char_representations}
+  \includegraphics[width=0.75\textwidth]{pics/lstm_char_representations}
   \caption{LSTM based character representations}
@@
 
-Lample et al \cite{Lample2016} suggested using an a bidirectional LSTM to model character-level 
-representations on a bidirectional LSTM-CRF. Combining both the forward and backward 
-LSTM representations to form the character representation, as described in figure \ref{fig:lstm_char}. 
-This character representation is also combined with a word representation and fed to a LSTM-CRF network. 
-The forward LSTM is expected to be a better
-representation of the suffix of a token, and the backward LSTM is expected to be a
-better representation of the prefix of a token. This differentiates the architecture
-from the CNN based approach described in Section \ref{sssec:lstm_crf_cnn}, because CNN filters 
-discover positional invariant features, while LSTMs can better represent suffixes and prefixes. In our experiments, 
-the LSTM-CRF architecture with LSTM character representations was implemented with a bidirectional LSTM
-with 25 hidden states, producing character representations of size 50. The character embeddings
-have 30 dimensions that are randomly initialized.
+This character representation is also combined with a word 
+representation and fed to a BI-LSTM-CRF network. 
+The forward state is expected to be a better representation of the suffix of 
+a token, and the backward state is expected to be a better representation of 
+the prefix of a token. This differentiates the architecture
+from the CNN based approach described in Section~\ref{sssec:lstm_crf_cnn}, because CNN filters 
+discover positional invariant features, while LSTMs can better represent 
+suffixes and prefixes. In our experiments, 
+the LSTM-CRF architecture with LSTM character representations was implemented with a bidirectional 
+LSTM with 25 hidden states, producing character representations of 
+size 50. The character embeddings have 30 dimensions that are randomly initialized.
 
@@
 
-The neural models were trained with mini batch Stochastic Gradient Descent over 50 epochs with batch size 10,
+All neural models were trained using mini batch Stochastic Gradient Descent over 50 epochs with batch size 10,
 learning rate 0.01, momentum 0.9 and decay rate 0.05. We used early stopping \cite{Caruana2000} to select the best 
 parameters, considering the F1 measure in the validation set. All neural models used 
-GloVe 100-dimensional word embeddings \cite{Pennington2014} that were fine tuned during training,
-they have a vocabulary size of 400.000 words.
+GloVe 100-dimensional word embeddings \cite{Pennington2014} that were fine tuned during training.
 In the case of NER on HTML, word embeddings work similarly to a gazetteer. Named entities 
@@
 
-We constructed a novel dataset to evaluate the performance of multiple NER models
-at the web information extraction task. The task consists of finding researcher
-names in faculty listings from multiple web pages. This would be the 
-first step in linking researcher profiles from university websites to their entries
+We built a novel dataset to evaluate the performance of NER models
+on the web data extraction task. The task consists of finding researcher
+names in faculty listings from university web pages across the world. This would be a
+necessary step when linking researcher profiles from university websites to their entries
 in public databases such as DBLP \footnote{http://dblp.uni-trier.de/}. Unlike many
@@
 extraction approaches impractical. The idea is to explore systems that are general 
-enough to allow efficient name extraction from many different sources while requiring
+enough to allow efficient entity extraction from different sources while requiring
 no supervision between different websites.
 
-This task would be similar to the task of labeling authors in comments
-from many different sources or labeling authors in articles collected from many
-publishing platforms. Another similar task would be NER on tweets. Because of the character
-limitation present on tweets, we end up with constraints comparable to the ones
-found in the NER on HTML task, so we expect similar systems to have comparable performances
-on both of these tasks.
+This task is similar to labeling authors in comments or articles collected
+from different publishing platforms. Another similar task is NER on tweets,
+because of the character limitation that is comparable to what we find in 
+HTML text.
 
@@
 (div, p, table, li, br, etc.) in contrast to inline tags (span, em, a, td, etc.). 
-Sentences that were more than fifty tokens long were also split according to punctuation.
+Sentences that were more than fifty tokens long were also split according to the
+punctuation.
 
-A proper HTML segmenter poses many challenges by itself.
-However, we wanted to evaluate models without relying on any sophisticated data record
-segmentation system. In many cases, entity annotation may precede the segmentation
-phase in web data extraction methods, so annotators should be able to work with
-raw HTML data. Because of the type of documents present in the dataset, many sentences 
-contained only one or two tokens, while other documents contained long texts.
+A proper HTML segmenter poses many challenges by itself. We wanted to evaluate 
+models without relying on any sophisticated data record segmentation system.
+In many cases, entity annotation may precede the segmentation
+phase on web data extraction methods, so annotators that are able to work 
+with raw HTML data allow for more flexible systems.
+
 Finally, all tokens were tagged using the IOB scheme put forward by
@@
 a description of the data files. The validation set was used in the early stopping validation strategy
-for the neural networks and CRF training, while the performance was evaluated by comparing results in the test set.
+for the neural networks and CRF training, while the model performance was evaluated by comparing 
+results in the test set.
 
@@
 
-Thirteen categorical features were also associated with each token in the dataset. They 
+Thirteen categorical features were associated with each token in the dataset. They 
 are presented in Table \ref{tab:features}.
@@
       7  & Number \\
-      8  & Honorific \\
+      8  & Honorific (Mr., Mrs., Dr., etc.)\\
       9  & URL \\
@@
 Features 6 to 11 represent a simple regular expression match to an email, number, 
-honorific, URL, capitalization and punctuation sign.
+honorific, URL, capitalization or punctuation sign.
 
@@
 occurs inside a given HTML tag in a document we cannot say it is more likely to be the case 
-in other documents. However, these features can be trained with the self-training strategy 
-for HMMs described in section \ref{sssec:self_training}.
+in other documents. However, these features can be useful for the HMM self-training strategy 
+described in section \ref{sssec:self_training}.
 
@@
 
-Two experiments were conducted to evaluate the best models for named entity recognition
-on HTML in the context of web data extraction. In the first experiment, we trained the NER models
-using the entire training set (85 documents). In the second experiment, the training set was 
-split into five non overlapping sets with 17 documents, and every model was trained
-and tested once using each set, while the test data was kept unchanged. We wanted to verify 
-how the models behaved when training data is limited, since labelling NER datasets can be a
-very time consuming effort.
-
-Evaluation of model performance in this task was performend with the precision, recall and 
-F1 score \cite{Rijsbergen1979}. Precision is the percentage of named entities found by 
-the model that are correct. Recall is the percentage of named entities that are present
-in the corpus and were found by the model. The F1 score is a composite measure that combines
-precision and recall with the formula:
-
-\begin{equation}
-F1 = \frac{2 * precision * recall}{precision + recall}
-\end{equation}
+We conducted experiments to evaluate sequence labeling methods of named entity 
+recognition on HTML in the context of web data extraction using the dataset 
+described in Section~\ref{sec:ner_dataset}. The tested models are described in
+Table~\ref{tab:models}.
 
@@
       crf              & Linear chain conditional random fields \\
-      lstm-crf      & LSTM-CRF model \cite{Huang2015} \\
-      lstm-crf-cnn  & LSTM-CRF with CNN character representations \cite{Ma2016} \\
-      lstm-crf-lstm & LSTM-CRF with LSTM character representations \cite{Lample2016} \\
+      bi-lstm-crf      & BI-LSTM-CRF model \cite{Huang2015} \\
+      bi-lstm-crf-cnn  & BI-LSTM-CRF with CNN character representations \cite{Ma2016} \\
+      bi-lstm-crf-lstm & BI-LSTM-CRF with LSTM character representations \cite{Lample2016} \\
       \bottomrule
@@
 
+The evaluation of model performance was done through the precision, recall and 
+F1 scores \cite{Rijsbergen1979}. Precision is the percentage of named entities found by 
+the model that are correct. Recall is the percentage of named entities that are present
+in the corpus and were found by the model. The F1 score is a composite measure that combines
+precision and recall with the formula:
+
+\begin{equation}
+F1 = \frac{2 * precision * recall}{precision + recall}
+\end{equation}
+
 Named entities were only considered to be correct if they were a complete match of the 
-corresponding entity in the dataset. The models tested in both experiments are described in Table \ref{tab:models}.
-In each experiment, we evaluated variants of each model using the complete set of features described in 
-Table \ref{tab:features} and variants that used only lowercase unaccented words for HMMs, 
-and only word embeddings in the case of neural models and CRFs. In Tables \ref{tab:experiment1} to 
-\ref{tab:experiment2f}, models that used the complete set of features have the suffix "+F". For example,
-"lstm-crf+F" is the LSTM-CRF model with all features including GloVe word embeddings, and "lstm-crf" is 
-the LSTM-CRF model with only GloVe word embeddings as input.
-Additionally, HMMs were also evaluated using the self training strategy. In tables \ref{tab:experiment1f} 
-and \ref{tab:experiment2f}, these models have the suffix "+ST".
+corresponding entity in the dataset.
 
-\subsection{Experiment 1: Complete Dataset}
+% We evaluated variants of each model using the complete set of features described in 
+% Table \ref{tab:features} and variants that used only lowercase unaccented words for HMMs, 
+% and only word embeddings for neural models and CRFs. 
+% 
+% In Table \ref{tab:experiment1} and 
+% Table \ref{tab:experiment2f}, models that used the complete set of features have the suffix "+F". For example,
+% "lstm-crf+F" is the LSTM-CRF model with all features including GloVe word embeddings, and "lstm-crf" is 
+% the LSTM-CRF model with only GloVe word embeddings as input.
+% Additionally, HMMs were also evaluated using the self training strategy. In tables \ref{tab:experiment1f} 
+% and \ref{tab:experiment2f}, these models have the suffix "+ST".
+
+\subsection{Experiment 1: No features}
+
+Experiment 1 aimed to evaluate the performance of sequence model with no features
+besides GloVe-100 embeddings. In the case of HMMs, only the lowercase
+unaccented token was used as a feature. Table \ref{tab:experiment1} 
+shows the Precision (P), Recall (R), and F1-scores (F1) for this
+experiment.
 
@@
       crf	       & 0.7173 & 0.6683 & 0.6920 & 0.6671 & 0.5868 & 0.6244 \\
-      lstm-crf	    & 0.8484 & 0.9044 & 0.8755 & 0.8358 & 0.8497 & 0.8427 \\
-      lstm-crf-cnn  & 0.9058 & 0.9575 & 0.9309 & 0.8779 & 0.8737 & 0.8758 \\
-      lstm-crf-lstm & 0.9134 & 0.9435 & 0.9282 & 0.8920 & 0.8815 & 0.8867 \\
+      bi-lstm-crf      & 0.8484 & 0.9044 & 0.8755 & 0.8358 & 0.8497 & 0.8427 \\
+      bi-lstm-crf-cnn  & 0.9058 & 0.9575 & 0.9309 & 0.8779 & 0.8737 & 0.8758 \\
+      bi-lstm-crf-lstm & 0.9134 & 0.9435 & 0.9282 & \textbf{0.8920} & \textbf{0.8815} & \textbf{0.8867} \\
       \bottomrule
@@
   \end{center}
-  \caption{Precision, recall and F1 in the complete dataset for models using no features}
+  \caption{Precision, recall and F1 in the NER on HTML dataset for models that incorporate no features}
   \label{tab:experiment1}
@@
 
-Experiment 1 consisted of testing the models in the complete NER on HTML dataset 
-described in Section \ref{sec:ner_dataset}. Table \ref{tab:experiment1} shows the 
-Precision (P), Recall (R), and F1-scores (F1) for models that employed no features, 
-except for lowercase unaccented words
-in the case of HMMs and Glove-100 word embeddings in the case of CRFs and Neural Models.
+Without carefully designed features or gazetteers, HMMs and CRFs have a very 
+poor performance, achieving an F1-score of only 0.5783 for HMM-2 and 0.6244 for CRF
+at the test set. This is expected, since these models rely on good feature selections.
 
-Without carefully designed features and a gazetteer, HMMs and CRFs have a very 
-poor performance, achieving an F1-score of only 0.5783 for hmm-2 and 0.6244 for crf
-in the test set. This is to be expected, as these models rely on a good feature selection.
-The neural models however achieved high F1-scores in the test
-data, even with the absence of features. The plain LSTM-CRF architecture improved performance 
-significantly in comparison to the conventional CRF, 0.8427 against 0.6244 (a difference 
-of 0.2183). Also, the neural character representations boosted performance a little further
-reaching an F1-score of 0.8758 for CNN based representations and 0.8867 for LSTM based
-representations. The LSTM based representations were superior in modelling
-morphological features, perhaps because they are able to differentiate suffixes and prefixes, 
-while CNNs filters are position invariant.
+The neural models achieved high F1-scores in the test
+set even with the absence of features. The plain LSTM-CRF architecture improved performance 
+significantly in comparison with the conventional CRF (0.8427 against 0.6244). 
+Also, neural character representations boosted performance by a significant margin
+reaching an F1-score of 0.8758 for CNN-based representations and 0.8867 for LSTM-based
+representations. LSTM based representations were superior in modelling
+morphological features, perhaps because they are able to differentiate suffixes 
+and prefixes, while CNN filters are position invariant.
 
-The results in experiment 1 also show that pretrained word embeddings can work as a sort of
-universal gazetteer. Words with similar embeddings, are likely to belong to the same class.
-This knowledge combined with the ability to learn morphological features can make up for 
-the scarcity of textual data in some webpages.
+The results in Experiment 1 also show that pretrained word embeddings can work 
+as a kind of universal gazetteer. Words with similar embeddings are likely to 
+belong to the same class. This knowledge combined with the ability to learn 
+morphological features can make up for the scarcity of textual data on some 
+webpages.
+
+\subsection{Experiment 2: All features}
+
+Experiment 2 aimed to evaluate the performance of sequence model with all
+the features described in Table~\ref{tab:features}. In this experiment, we
+also evaluate the self training strategy for HMMs described in Section 
+\label{sssec:self_training}. The self trained HMMs are described with the 
+suffix "+ST". Table \ref{tab:experiment2} shows the results for Experiment 2.
 
@@
       \midrule
-      hmm-1+F	      & 0.6061 & 0.7282 & 0.6616 & 0.7106 & 0.7633 & 0.7360 \\
-      hmm-2+F	      & 0.6279 & 0.7550 & 0.6856 & 0.7521 & 0.7810 & 0.7663 \\
-      hmm-3+F	      & 0.6573 & 0.7819 & 0.7142 & 0.7523 & 0.7795 & 0.7657 \\
-      hmm-1+F+ST      & 0.7032 & 0.9077 & 0.7925 & 0.7522 & 0.8663 & 0.8052 \\
-      hmm-2+F+ST      & 0.7321 & 0.9172 & 0.8143 & 0.7737 & 0.8789 & 0.8230 \\
-      hmm-3+F+ST      & 0.7551 & 0.9172 & 0.8283 & 0.7961 & 0.8534 & 0.8237 \\
-      crf+F	      & 0.9024 & 0.9049 & 0.9037 & 0.8751 & 0.8227 & 0.8481 \\
-      lstm-crf+F      & 0.9430 & 0.9530 & 0.9480 & 0.8998 & 0.8527 & 0.8756 \\
-      lstm-crf-cnn+F  & 0.9244 & 0.9715 & 0.9474 & 0.9017 & 0.8973 & 0.8995 \\
-      lstm-crf-lstm+F & 0.9465 & 0.9692 & 0.9577 & 0.9108 & 0.8715 & 0.8907 \\
+      hmm-1	         & 0.6061 & 0.7282 & 0.6616 & 0.7106 & 0.7633 & 0.7360 \\
+      hmm-2	         & 0.6279 & 0.7550 & 0.6856 & 0.7521 & 0.7810 & 0.7663 \\
+      hmm-3	         & 0.6573 & 0.7819 & 0.7142 & 0.7523 & 0.7795 & 0.7657 \\
+      hmm-1+ST           & 0.7032 & 0.9077 & 0.7925 & 0.7522 & 0.8663 & 0.8052 \\
+      hmm-2+ST           & 0.7321 & 0.9172 & 0.8143 & 0.7737 & 0.8789 & 0.8230 \\
+      hmm-3+ST           & 0.7551 & 0.9172 & 0.8283 & 0.7961 & 0.8534 & 0.8237 \\
+      crf	         & 0.9024 & 0.9049 & 0.9037 & 0.8751 & 0.8227 & 0.8481 \\
+      bi-lstm-crf        & 0.9430 & 0.9530 & 0.9480 & 0.8998 & 0.8527 & 0.8756 \\
+      bi-lstm-crf-cnn    & 0.9244 & 0.9715 & 0.9474 & 0.9017 & \textbf{0.8973} & \textbf{0.8995} \\
+      bi-lstm-crf-lstm   & 0.9465 & 0.9692 & 0.9577 & \textbf{0.9108} & 0.8715 & 0.8907 \\
       \bottomrule
@@
   \end{center}
-  \caption{Precision, recall and F1 in the complete dataset for models using all features}
-  \label{tab:experiment1f}
+  \caption{Precision, recall and F1 in the NER on HTML dataset for models that incorporate all features}
+  \label{tab:experiment2}
 \end{table}
 
-Table \ref{tab:experiment1f} shows the results on Experiment 1 for models
-that employed all the features described in Table \ref{tab:features}.
 Conventional models like HMMs, and CRFs can become competitive with
@@
 comparison to regular HMMs.
-The neural models also improved a little with the new features. The plain LSTM-CRF
+
+The neural models also improved a little with the addition of features. The plain LSTM-CRF
 model gets a closer performance to the models that employed neural character 
-representations. It points to the fact that the LSTM and CNN character representations 
+representations. It suggests that the LSTM and CNN character representations 
 were able to learn at least part of the morphological features automatically in the
-models with no features. So, when these features are added explicitly, the differences 
+first experiment. So, when these features are added explicitly, the differences 
 in performance become less noticeable.
 
-\subsection{Experiment 2: Reduced Dataset}
-
-\begin{table}[h]
-  \small
-  \begin{center}
-    \begin{tabular}{ lllllll }
-      \toprule
-      \multirow{2}{*}{Model} & \multicolumn{2}{c}{Precision} & \multicolumn{2}{c}{Recall} & \multicolumn{2}{c}{F1} \\
-                             & \multicolumn{1}{c}{\tiny{M}} & \multicolumn{1}{c}{\tiny{SD}}
-			     & \multicolumn{1}{c}{\tiny{M}} & \multicolumn{1}{c}{\tiny{SD}}
-			     & \multicolumn{1}{c}{\tiny{M}} & \multicolumn{1}{c}{\tiny{SD}} \\
-      \midrule
-      hmm-1	      & 0.2856 & 0.1127 & 0.1623 & 0.0810 & 0.2036 & 0.0892 \\
-      hmm-2	      & 0.3436 & 0.1134 & 0.2060 & 0.1058 & 0.2483 & 0.0997 \\
-      hmm-3	      & 0.2707 & 0.0955 & 0.2163 & 0.0927 & 0.2316 & 0.0793 \\
-      crf	      & 0.6249 & 0.0433 & 0.5272 & 0.0348 & 0.5711 & 0.0301 \\
-      lstm-crf	      & 0.6982 & 0.0495 & 0.6538 & 0.0532 & 0.6751 & 0.0499 \\
-      lstm-crf-cnn    & 0.7906 & 0.0557 & 0.7431 & 0.0687 & 0.7652 & 0.0572 \\
-      lstm-crf-lstm   & 0.7935 & 0.0345 & 0.7360 & 0.0424 & 0.7626 & 0.0237 \\
-      \bottomrule
-    \end{tabular}
-  \end{center}
-  \caption{Mean Precision, recall and F1 in the test set for models with no features
-   trained in five sets with 17 documents}
-  \label{tab:experiment2}
-\end{table}
-
-The second experiment aimed to evaluate the performance of sequence models when 
-the amount of training data is small. The same training data used in Experiment 1 was
-split into five non overlapping sets with 17 documents. Each model was trained once 
-with each of the five sets and tested with the same test set used in Experiment 1. 
-Seventeen documents seem to be a feasible amount of documents to label in most WDE 
-tasks. The results for each model were averaged over the five runs.
-
-Table \ref{tab:experiment2} shows the precision, recall and F1-score for the same models
-used in Experiment 1, but in this case we only show results for the Test set.
-As expected, we can see that the performance of all models with no features was reduced in comparison 
-to Experiment 1. HMMs show a terrible performance while CRFs are not 
-impacted as much by the reduction in the amount of training examples. Neural models
-keep performing better, but they were unable to learn patterns as efficiently in
-the smaller training sets, the best model achieves an F1 score of 0.7652 in contrast to
-0.8815 with the entire dataset. The neural models show a small standard deviation, what
-points to the fact that they can retain a consistent performance between different training 
-datasets. In this matter, the dropout layers are crucial to produce better generalizations 
-and prevent overfitting.
-
-\begin{table}[h]
-  \small
-  \begin{center}
-    \begin{tabular}{lllllll}
-      \toprule
-      \multirow{2}{*}{Model} & \multicolumn{2}{c}{Precision} & \multicolumn{2}{c}{Recall} & \multicolumn{2}{c}{F1} \\
-                             & \multicolumn{1}{c}{\tiny{M}} & \multicolumn{1}{c}{\tiny{SD}}
-			     & \multicolumn{1}{c}{\tiny{M}} & \multicolumn{1}{c}{\tiny{SD}}
-			     & \multicolumn{1}{c}{\tiny{M}} & \multicolumn{1}{c}{\tiny{SD}} \\
-      \midrule
-      hmm-1+F	      & 0.6205 & 0.0927 & 0.6402 & 0.0717 & 0.6290 & 0.0774 \\
-      hmm-2+F	      & 0.5999 & 0.0879 & 0.6527 & 0.0389 & 0.6229 & 0.0595 \\
-      hmm-3+F	      & 0.5712 & 0.0957 & 0.6258 & 0.0494 & 0.5954 & 0.0722 \\
-      hmm-1+F+ST      & 0.6536 & 0.0886 & 0.7579 & 0.1118 & 0.7012 & 0.0963 \\
-      hmm-2+F+ST      & 0.7044 & 0.0726 & 0.7810 & 0.1039 & 0.7397 & 0.0834 \\
-      hmm-3+F+ST      & 0.6619 & 0.0722 & 0.7174 & 0.0892 & 0.6879 & 0.0777 \\
-      crf+F	      & 0.8419 & 0.0326 & 0.7530 & 0.0823 & 0.7933 & 0.0541 \\
-      lstm-crf+F      & 0.8376 & 0.0225 & 0.7838 & 0.0518 & 0.8093 & 0.0345 \\
-      lstm-crf-cnn+F  & 0.8542 & 0.0336 & 0.7820 & 0.0767 & 0.8149 & 0.0478 \\
-      lstm-crf-lstm+F & 0.8554 & 0.0219 & 0.8013 & 0.0825 & 0.8255 & 0.0478 \\
-      \bottomrule
-    \end{tabular}
-  \end{center}
-  \caption{Mean Precision, recall and F1 in the test set for models with all features
-   trained in five sets with 17 documents}
-  \label{tab:experiment2f}
-\end{table}
-
-Table \ref{tab:experiment2f} shows the results in the small training sets 
-for models that employed all features. Take note that the difference between CRFs
-and neural models was reduced with the reduction in the training set. However, the
-addition of features impacted the performance of neural models much more that in 
-Experiment 1. This indicates that the models with neural character representations
-may need more data to extract good morphological features. However, they keep performing 
-better than the other models, and have the lowest standard deviations.
-
-Finally, all the results presented in this section considered a dataset with a minimum
+Finally, all results presented in this section considered a dataset with a minimum
 amount of preprocessing and no trimming strategy to delimitate named entities. In many cases, 
-for example, a model may miss a few named entities because it includes a punctuation sign
-or an honorific at the start or end of a named entity. In fact, we can boost the F1-score up
-by a few points with some simple heuristics. However, these strategies are specific to this
-NER on HTML problem.
+a model may miss a few named entities because it includes a punctuation sign
+or an honorific at the start or end of a named entity. Some simple strategies could 
+be used to boost the F1-score modestly.
 
@@
 
-In this paper we compared the performance of multiple sequence models in the task of
+In this paper we compared the performance of different sequence models in the task of
 NER on HTML, introducing a novel dataset that is publicly available. We showed that
-neural networks can be employed effectively to solve this task while demanding no 
-feature engineering (F1-score of 0.8867), and they can retain acceptable performance 
-even when the training data is dramatically reduced (F1-score of 0.8255), even though 
-in this case the feature selection becomes more meaningful. We found that there are 
-two components to the most successful models: neural based character representations
-constructed with convolutional neural networks or bidirectional LSTMs and joint modelling 
-of the output labels provided by a linear chain CRF output layer. The effective recognition 
+LSTM-CRF neural networks with LSTM-based character representations can be employed 
+effectively to solve this task while demanding no feature engineering (F1-score of 0.8867).
+We found that there are two components to the most successful models: neural based character 
+representations constructed with convolutional neural networks or bidirectional LSTMs and joint 
+modelling of the output labels provided by a linear chain CRF output layer. The effective recognition 
 of named entities on HTML is an essential step in most general web data extraction methods. 

### 2018-11-30 tex/article.tex
Final JNLE version.

@@
 
-\author{João Mateus de Freitas Veneroso}
+% \author{
+%   João Mateus de Freitas Veneroso
+%   % Universidade Federal de Minas Gerais
+% }
+\author[João Mateus de Freitas Veneroso and Berthier Ribeiro-Neto]
+       {João Mateus de Freitas Veneroso \and
+        Berthier Ribeiro-Neto\\
+	Universidade Federal de Minas Gerais\\
+	Belo Horizonte - MG, Brazil}
+
 % \affiliation{%
@@
 identify and extract data from web pages. These methods are usually
-suited for extracting information from repeating templates inside
+suited for extracting information from pages with repeating templates within
 the same website, however they perform poorly on extraction 
@@
 machine-learning-based sequence labeling methods provide a more flexible 
-approach to Web data extraction. HTML text is ocasionally very different 
-from plain text because sentences can be too short to provide adequate 
+approach to Web data extraction. Many times, HTML pages are very different 
+from plain text, because sentences are too short to provide adequate 
 context for conventional Named Entity Recognition methods to work 
-properly. Also, the HTML structure can encode information that is not 
+properly. Also, the HTML structure may encode information that is not 
 replicated in the text. Nonetheless, these limitations can be overcome by
-adequate feature engineering, the use of pre-trained word 
+adequate feature engineering, the use of pretrained word 
 embeddings and neural character representations. In this article, we 
@@
 on the task of Web data extraction. In particular, we introduce a novel 
-dataset consisting of faculty listings from university webpages across
+dataset~\footnote{The dataset and all models discussed in this article are available in: https://github.com/jmfveneroso/ner.} 
+consisting of faculty listings from university web pages across
 the world in multiple languages and test the NER models on the task of 
@@
 With the addition of hand crafted features, the F1-score can be slightly 
-improved to 0.8995 with another neural architecture that incorporates
-CNN-based character representations.
+improved to 0.8995.
 
@@
 
+\maketitle
+
+% \textbf{Declarations of interest: none} \\
+% \\
+% \\
+João Mateus de Freitas Veneroso \\
+Mailing address: Universidade Federal de Minas Gerais, Departmento de Ciência da Computação, sala 4304\\
+Av. Pres. Antônio Carlos, 6627 - Pampulha, Belo Horizonte - MG, 31270-901 \\
+Tel: +55 (31) 99436-0909 \\
+Email: jmfveneroso@gmail.com \\
+
+Berthier Ribeiro-Neto \\
+Mailing address: Universidade Federal de Minas Gerais, Departmento de Ciência da Computação, sala 4321\\
+Av. Pres. Antônio Carlos, 6627 - Pampulha, Belo Horizonte - MG, 31270-901 \\
+Tel: +55 (31) 99313-0961 \\
+Email: berthier@dcc.ufmg.br \\
+
 % \keywords{Named entity recognition, information extraction, web data extraction}
-
-\maketitle
 
@@
 unsupervised WDE methods work in two stages. In the record segmentation stage,
-WDE systems seek to cluster visually and structurally similar web page regions 
-and identify repeating data records, usually with heuristics and 
-hand-coded rules. In the attribute labelling stage, WDE systems seek to identify 
+WDE systems seek to cluster visually and structurally similar Web page regions 
+and identify repeating data records with heuristics and 
+hand-coded rules. In the attribute labeling stage, WDE systems seek to identify 
 the correct attributes on data records, many times resorting to regular expressions 
 or gazetteer matching strategies. The outcome of each of these stages can aid one 
-another. The inner patterns of data records can help identifying attributes in other 
+another. The inner patterns of data records can help in identifying attributes of other 
 data records. Also, by properly identifying data record attributes, it becomes 
@@
 While unsupervised approaches can be sometimes adequate to extract information from 
-webpages with similar templates, they usually fail on cross-website data extraction 
+Web pages with similar templates, they usually fail on cross-website data extraction 
 tasks. Also, more sophisticated approaches may be needed when we are not dealing
@@
 particularly with the introduction of deep recurrent neural network architectures
-for sequence labeling. However, despite web data extraction being a closely 
+for sequence labeling. However, despite Web data extraction being a closely 
 related field, there is a lack of extraction tools that make use of these recent 
-advancements. The attribute labelling stage in web data extraction systems
-is essentialy a Named Entity Recognition (NER) problem, the problem of 
+advancements. The attribute labeling stage in Web data extraction systems
+is essentially a Named Entity Recognition (NER) problem, the problem of 
 detecting named entities in the text and classifying them into predetermined 
@@
 detecting named entities is sufficient to solve the data extraction task. However, when we are
-dealing with multi attribute data records or complex relationships, we may need to 
+dealing with multi-attribute data records or complex relationships, we may need to 
 perform additional steps. Nevertheless, even in the latter cases, flexible NER methods 
 are still desirable because, while many WDE algorithms can effectively exploit the 
-semi-structured nature of web documents, too much reliance on structural webpage 
+semi-structured nature of Web documents, too much reliance on structural Web page 
 features often produce poor generalizations on cross website extraction. Also, 
@@
 
-In this paper, we investigate methods of named entity recognition for web data extraction.
+In this paper, we investigate methods of named entity recognition for Web data extraction.
 Recently proposed neural architectures have achieved exciting results 
@@
 NER on HTML poses a slightly different type of challenge. Named entities may occur inside 
-tables, lists, graphs or other types of visual elements that provide little to no textual 
+tables, lists, or other types of visual elements that provide little to no textual 
 information that could give hints about the semantic category of a word. Still, even 
@@
 By reliably detecting named entities on HTML, we can improve the performance of existing WDE 
-approaches or even construct an end-to-end neural network architecture to tackle domain 
-wide extraction with considerable flexibility. To test different NER approaches to
-web data extraction, we explored the task of researcher name extraction from university 
+approaches or even construct an end-to-end neural network architecture to solve domain 
+wide data extraction with considerable flexibility. To test different NER approaches to
+Web data extraction, we explored the task of researcher name extraction from university 
 faculty listings across the world, introducing a novel NER dataset.
@@
 this task can provide a good measure of the expected performance and data need of
-NER methods on other web data extraction tasks.
+NER methods on other Web data extraction tasks.
 
@@
 
-In the last 20 years, the astonishing growth of public information in the web has 
-led to the development of a number of different approaches to the problem of web 
+In the last 20 years, the astonishing growth of public information in the Web has 
+led to the development of a number of different approaches to the problem of Web 
 data extraction. Traditionally, the task was solved by designing special purpose
@@
 error prone process, unsuited for large scale operations. Wrappers tend to
-break frequently because they rely heavily on web page features that can change 
+break frequently because they rely heavily on Web page features that can change 
 often. So, in the late nineties, several authors advocated for wrapper induction, a technique 
@@
 require some sort of assistance from human experts to boost accuracy. One of the main challenges 
-in the field lies in determining an adequate tradeoff between the degree of automation and 
+in the field lies in determining an adequate trade-off between the degree of automation and 
 the precision and recall of the data extraction tool.
 
-To automate the task of web data extraction completely some approaches,
+To automate the task of Web data extraction completely some approaches,
 such as Road Runner \cite{Crescenzi2001}, removed entirely the need for data examples.
@@
 
-In 2002, a survey by Laender et al. \cite{Laender2002} made a thorough classification of the
+In 2002, a survey by Laender et al. \shortcite{Laender2002} made a thorough classification of the
 early approaches with a taxonomy based on their main technology, being them: languages for
@@
 
-In 2006, Chang et al. \cite{Chang2006} complemented the previous surveys with semisupervised 
+In 2006, Chang et al. \shortcite{Chang2006} complemented the previous surveys with semi-supervised 
 technologies such as Thresher \cite{Hogue2005}, IEPAD \cite{Chang2001} and 
@@
 
-In 2008, Sarawagi \cite{Sarawagi2008} produced a survey that classified wrappers into
+In 2008, Sarawagi \shortcite{Sarawagi2008} produced a survey that classified wrappers into
 rule-based methods, statistical methods and hybrid models, bringing together 
@@
 More recently, with the advancement of Natural Language Processing and Deep Learning, 
-neural models outperformed previous NER methods for plain text. Huang et. al. \cite{Huang2015} introduced the 
+neural models outperformed previous NER methods for plain text. Huang et. al. \shortcite{Huang2015} introduced the 
 bidirectional Long Short-Term Memory (LSTM) model with a Conditional Random Field (CRF) output layer
-for NER. Ma and Hovy \cite{Ma2016} incorporated Convolutional Neural Network based character representations 
-on top of the architecture. And Lample et. al. \cite{Lample2016} introduced
+for NER. Ma and Hovy \shortcite{Ma2016} incorporated Convolutional Neural Network based character representations 
+on top of the architecture. And Lample et. al. \shortcite{Lample2016} introduced
 LSTM based character representations.
 
-Surveys by Ferrara et al. \cite{Ferrara2014}, Schulz et al. \cite{Schulz2016} and 
-Varlamov et al. \cite{Varlamov2016} updated the previous surveys on information 
+Surveys by Ferrara et al. \shortcite{Ferrara2014}, Schulz et al. \shortcite{Schulz2016} and 
+Varlamov et al. \shortcite{Varlamov2016} updated the previous surveys on information 
 extraction methods with some interesting innovations. 
 Some examples are: the Visual Box Model \cite{Krupl2005}, a data extraction system that produces 
-a visualization of the web page to exploit visual cues to identify data presented in a tabular form;
+a visualization of the Web page to exploit visual cues to identify data presented in a tabular form;
 automatic wrapper adaptation \cite{Ferrara2011}, a technique that tries to reduce the cost of 
@@
 wrappers to the new page structure; AutoRM \cite{Shi2015}, a method to mine
-records from a single web page by identifying similar data regions through DOM
+records from a single Web page by identifying similar data regions through DOM
 tree analysis; Knowledge Vault \cite{Dong2014}, a method that combines different 
@@
 A statistical approach to unsupervised domain 
-independent web data extraction was described by Zhu et al \cite{Zhu2005}. The 2D CRF 
-model takes a web page segmented into data blocks and employs a two dimensional conditional 
-random field model to perform attribute labelling. The model was further improved
-\cite{Zhu2006} to model record segmentation and attribute labelling as a joint task.
+independent Web data extraction was described by Zhu et al \shortcite{Zhu2005}. The 2D CRF 
+model takes a Web page segmented into data blocks and employs a two dimensional conditional 
+random field model to perform attribute labeling. The model was further improved
+\cite{Zhu2006} to model record segmentation and attribute labeling as a joint task.
 Some of the limitations of early unsupervised methods 
 were also tackled by ObjectRunner \cite{Abdessalem2010} and AMBER \cite{Furche2012}. 
-These methods work by annotating webpages automatically with regular expressions, gazetteers and 
+These methods work by annotating Web pages automatically with regular expressions, gazetteers and 
 knowledge bases. They can rectify low quality annotations and even improve the annotators
@@
 Web data extraction methods have undoubtedly improved extraordinarily, but
-as pointed by Schulz et al. \cite{Schulz2016}, it is difficult to compare the results 
+as pointed by Schulz et al. \shortcite{Schulz2016}, it is difficult to compare the results 
 achieved by competing tools, and many seem to rely excessively on heuristic methods.
@@
 
-Many web data extraction systems rely on hand crafted rules or gazetteers to perform
+Many Web data extraction systems rely on hand crafted rules or gazetteers to perform
 attribute annotation. Machine learning approaches to NER can improve annotations of 
@@
 engineering. We explored many methods of Named Entity Recognition
-in the context of a web data extraction task. First, we discuss two traditional 
+in the context of a Web data extraction task. First, we discuss two traditional 
 approaches: Hidden Markov Models, and Linear Chain Conditional Random Fields. Then,
@@
 In fact, we can get much better results on the NER task by looking at trigrams
-or quadrigrams ($ k = 2 $ or $ k = 3 $) instead of bigrams as a regular HMM. 
+or quadrigrams ($ k = 2 $ or $ k = 3 $) instead of bigrams as with a regular HMM. 
 Some label assignments are highly improbable, such as single token named entities 
@@
 
-HMM based taggers have been succesfully applied in many NLP and WDE tasks 
+HMM based taggers have been successfully applied in many NLP and WDE tasks 
 \cite{Rabiner1990,Leek1997,Freitag2000}. They are incredibly fast to train and also they are very 
@@
 A Linear Chain Conditional Random Field (CRF) is the discriminative analog to the HMM,
-it was first introduced by Lafferty \cite{Lafferty2001}. It is a distribution $ P(Y|X) $ that takes the form:
+it was first introduced by Lafferty \shortcite{Lafferty2001}. It is a distribution $ P(Y|X) $ that takes the form:
 
@@
 on the whole vector of observations $ X $. This flexibility of feature functions allows for a wide range of
-possibilities. Recently, CRFs have been succesfully employed as the output layer in complex neural 
+possibilities. Recently, CRFs have been successfully employed as the output layer in complex neural 
 architectures bringing improvements over models that compute labels independently.
@@
 
-Recurrent neural networks (RNN) have been succesfully employed on numerous NLP tasks such as
-language modelling, POS tagging, speech recognition and NER. Different from feedforward 
+Recurrent neural networks (RNN) have been successfully employed on numerous NLP tasks such as
+language modelling, POS tagging, speech recognition and NER. Different from feed-forward 
 neural networks, RNNs can retain information in their internal state, making them more 
@@
 it becomes difficult due to the vanishing gradient problem. Long short term memory networks (LSTM) were 
-introduced by Hochreiter and Schmidhuber \cite{Hochreiter1997} with this problem in mind and 
+introduced by Hochreiter and Schmidhuber \shortcite{Hochreiter1997} with this problem in mind and 
 have been popularized since then.
@@
 
-This implementation differs from the LSTM cell described in Huang et al. \cite{Huang2015}
+This implementation differs from the LSTM cell described in Huang et al. \shortcite{Huang2015}
 in that the gates $ \Gamma_i $ and $ \Gamma_f $ do not receive inputs from the previous 
@@
 
-Huang et al. \cite{Huang2015} proposed a bidirectional LSTM with a CRF layer (BI-LSTM-CRF) on 
+Huang et al. \shortcite{Huang2015} proposed a bidirectional LSTM with a CRF layer (BI-LSTM-CRF) on 
 the output to tackle the sequence tagging problem. The main benefit of adding a CRF layer 
@@
 
-This architecture achieved an F1 score of 90.10 on the English data from the ConLL-2003 
+This architecture achieved an F1 score of 90.10 on the English data from the CoNLL-2003 
 NER shared task \cite{Sang2003}, in contrast to 85.17 for a bidirectional LSTM without 
@@
 
-Ma and Hovy \cite{Ma2016} proposed to add a convolutional neural network (CNN) layer 
+Ma and Hovy \shortcite{Ma2016} proposed to add a convolutional neural network (CNN) layer 
 on top of a bidirectional LSTM-CRF to encode character-level information. The CNN
@@
 
-The convolutional neural netwrok receives character embeddings as inputs. The character 
+The convolutional neural network receives character embeddings as inputs. The character 
 representations generated by the CNN are combined with word level representations 
@@
 useful in the NER task, since similar named entities often present morphological similarities. 
-This architecture obtained an F1 score of 91.21 in the ConLL2003 dataset. In our experiments, 
+This architecture obtained an F1 score of 91.21 in the CoNLL2003 dataset. In our experiments, 
 the LSTM-CRF architecture with CNN character representations uses a one dimensional convolutional 
@@
 
-Lample et al \cite{Lample2016} proposed to use a bidirectional LSTM to model character-level 
+Lample et al \shortcite{Lample2016} proposed to use a bidirectional LSTM to model character-level 
 representations on top of a BI-LSTM-CRF. Combining the forward and backward LSTM hidden states 
@@
 We built a novel dataset to evaluate the performance of NER models
-on the web data extraction task. The task consists of finding researcher
-names in faculty listings from university web pages across the world. This would be a
+on the Web data extraction task. The task consists of finding researcher
+names in faculty listings from university Web pages across the world. This would be a
 necessary step when linking researcher profiles from university websites to their entries
 in public databases such as DBLP \footnote{http://dblp.uni-trier.de/}. Unlike many
-information extraction datasets, each web page in the dataset comes from a different 
+information extraction datasets, each Web page in the dataset comes from a different 
 website, and therefore has a different format, what makes many information
@@
 We collected 145 computer science faculty pages from 42 different countries in
-multiple languages, although the English version was prefered when it was available.
-We gathered faculty web pages randomly in proportion to
+multiple languages, although the English version was preferred when it was available.
+We gathered faculty Web pages randomly in proportion to
 the number of universities in each country\footnote{A detailed list of universities can
 be found in https://univ.cc/world.php}. Each HTML page was preprocessed and converted
-to the CONLL 2003 data format. That is, one word per line with empty lines representing
+to the CoNLL 2003 data format. That is, one word per line with empty lines representing
 sentence boundaries. Sentence boundaries were determined by line break HTML tags
@@
 In many cases, entity annotation may precede the segmentation
-phase on web data extraction methods, so annotators that are able to work 
+phase on Web data extraction methods, so annotators that are able to work 
 with raw HTML data allow for more flexible systems.
@@
 Finally, all tokens were tagged using the IOB scheme put forward by
-Ramshaw and Marcus \cite{Ramshaw1999}.
+Ramshaw and Marcus \shortcite{Ramshaw1999}.
 
@@
 
-The unaccented lowercase token was used as the key for the Glove-100 embedding lookup.
+The unaccented lowercase token was used as the key for the GloVe-100 embedding lookup.
 A gazetteer was constructed from a researcher list extracted from DBLP with 1,595,771
@@
 We conducted experiments to evaluate sequence labeling methods of named entity 
-recognition on HTML in the context of web data extraction using the dataset 
+recognition on HTML in the context of Web data extraction using the dataset 
 described in Section~\ref{sec:ner_dataset}. The tested models are described in
@@
 corresponding entity in the dataset.
-
-% We evaluated variants of each model using the complete set of features described in 
-% Table \ref{tab:features} and variants that used only lowercase unaccented words for HMMs, 
-% and only word embeddings for neural models and CRFs. 
-% 
-% In Table \ref{tab:experiment1} and 
-% Table \ref{tab:experiment2f}, models that used the complete set of features have the suffix "+F". For example,
-% "lstm-crf+F" is the LSTM-CRF model with all features including GloVe word embeddings, and "lstm-crf" is 
-% the LSTM-CRF model with only GloVe word embeddings as input.
-% Additionally, HMMs were also evaluated using the self training strategy. In tables \ref{tab:experiment1f} 
-% and \ref{tab:experiment2f}, these models have the suffix "+ST".
 
@@
 morphological features can make up for the scarcity of textual data on some 
-webpages.
+Web pages.
 
@@
 
-Finally, all results presented in this section considered a dataset with a minimum
-amount of preprocessing and no trimming strategy to delimitate named entities. In many cases, 
-a model may miss a few named entities because it includes a punctuation sign
-or an honorific at the start or end of a named entity. Some simple strategies could 
-be used to boost the F1-score modestly.
-
 \section{Conclusion}
 
-In this paper we compared the performance of different sequence models in the task of
-NER on HTML, introducing a novel dataset that is publicly available. We showed that
-LSTM-CRF neural networks with LSTM-based character representations can be employed 
-effectively to solve this task while demanding no feature engineering (F1-score of 0.8867).
+Machine-learning-based sequence labeling models provide a flexible approach to web data 
+extraction, in contrast to more traditional methods. In simple cases, a neural
+named entity tagger may be sufficient to solve the entire data extraction task. In 
+other cases, the sequence tagger remains an important part of the web data extraction
+system, as it performs attribute labeling on data records with accuracy and flexibility.
+
+In this article, we compared the performance of different sequence models on the task of
+named entity recognition on HTML, introducing a novel dataset that is publicly available. 
 We found that there are two components to the most successful models: neural based character 
-representations constructed with convolutional neural networks or bidirectional LSTMs and joint 
-modelling of the output labels provided by a linear chain CRF output layer. The effective recognition 
-of named entities on HTML is an essential step in most general web data extraction methods. 
-However it may also point to the possibility of constructing a truly flexible approach to
-cross domain data extraction based on neural networks.
-
-% \bibliographystyle{unsrt}
+representations that extract morphological features automatically, and the joint modelling 
+of output labels.
+
+We showed that a BI-LSTM-CRF neural network with LSTM-based character representations can 
+be employed effectively to solve a web data extraction task, achieving an F1-score of 
+0.8867 with no feature engineering on the faculty listings dataset.
+
+The effective recognition of named entities on HTML is an essential step in most general 
+Web data extraction methods. The accuracy achieved by deep neural architectures even
+on web pages that are very different from the plain text for which these architectures 
+were initially designed shows the potential for a truly flexible approach to cross domain 
+web data extraction.
+
+% \bibliographystyle{named}
 % \bibliography{bibfile}
@@
 \begin{thebibliography}{}
-  \bibitem[\protect\citename{Akmajian and Lehrer }1976]{Crescenzi2001}
-   Akmajian, A. and Lehrer, A. (1976) NP-like quantifiers and the
-   problem of determining the head of an NP. {\it Linguistic
-   Analysis\/} {\bf 2}: 295--313.
-  \bibitem[\protect\citename{Akmajian and Lehrer }1976]{Arasu2003}
-   Akmajian, A. and Lehrer, A. (1976) NP-like quantifiers and the
-   problem of determining the head of an NP. {\it Linguistic
-   Analysis\/} {\bf 2}: 295--313.
+\bibitem[\protect\citename{Abdessalem \bgroup \em et al.\egroup\ }{2010}]{Abdessalem2010}
+Talel Abdessalem, B~Cautis, and Nora Derouiche.
+\newblock {ObjectRunner: lightweight, targeted extraction and querying of
+  structured web data}.
+\newblock {\em Proceedings of the VLDB {\ldots}}, 3(2):1585--1588, 2010.
+
+\bibitem[\protect\citename{Adelberg }{1998}]{Adelberg1998}
+Brad Adelberg.
+\newblock {NoDoSE---a tool for semi-automatically extracting structured and
+  semistructured data from text documents}.
+\newblock {\em ACM SIGMOD Record}, 27(2):283--294, 1998.
+
+\bibitem[\protect\citename{Arasu \bgroup \em et al.\egroup\ }{2003}]{Arasu2003}
+A.~Arasu, H.~Garcia-Molina, Arvind Arasu, and Hector Garcia-Molina.
+\newblock {Extracting structured data from Web pages}.
+\newblock {\em 2003 ACM SIGMOD International Conference on Management of Data},
+  pages 337 -- 348, 2003.
+
+\bibitem[\protect\citename{Arocena and Mendelzon }{1999}]{Arocena1999}
+Gustavo~O. Arocena and Alberto~O. Mendelzon.
+\newblock {WebOQL: Restructuring documents, databases, and webs}.
+\newblock {\em Theory and Practice of Object Systems}, 5(3):127--141, 1999.
+
+\bibitem[\protect\citename{Califf and Mooney }{1999}]{Califf1999}
+Mary~Elaine Califf and Raymond~J Mooney.
+\newblock {Relational learning of pattern-match rules for information
+  extraction}.
+\newblock {\em Computational Linguistics}, 4:9--15, 1999.
+
+\bibitem[\protect\citename{Caruana \bgroup \em et al.\egroup\ }{2000}]{Caruana2000}
+Rich Caruana, Steve Lawrence, and Lee Giles.
+\newblock Overfitting in neural nets: Backpropagation, conjugate gradient, and
+  early stopping.
+\newblock In {\em Proceedings of the 13th International Conference on Neural
+  Information Processing Systems}, NIPS'00, pages 381--387, Cambridge, MA, USA,
+  2000. MIT Press.
+
+\bibitem[\protect\citename{Chang and Kuo }{2004}]{Chang2004}
+Chia~Hui Chang and Shih~Chien Kuo.
+\newblock {OLERA: Semisupervised Web-data extraction with visual support}.
+\newblock {\em IEEE Intelligent Systems}, 19(6):56--64, 2004.
+
+\bibitem[\protect\citename{Chang \bgroup \em et al.\egroup\ }{2001}]{Chang2001}
+C.H. Chang, C.H. Chang, S.C. Lui, and S.C. Lui.
+\newblock {IEPAD: information extraction based on pattern discovery}.
+\newblock {\em Proceedings of the 10th international conference on World Wide
+  Web}, pages 681--688, 2001.
+
+\bibitem[\protect\citename{Chang \bgroup \em et al.\egroup\ }{2006}]{Chang2006}
+Chia-Hui Chang, Mohammed Kayed, Moheb~Ramzy Girgis, and Khaled~F Shaalan.
+\newblock {A Survey of Web Information Extraction Systems}.
+\newblock {\em IEEE Transactions on Knowledge and Data Engineering},
+  18(10):1411--1428, 2006.
+
+\bibitem[\protect\citename{Crescenzi \bgroup \em et al.\egroup\ }{2001}]{Crescenzi2001}
+Valter Crescenzi, Giansalvatore Mecca, and Paolo Merialdo.
+\newblock {Roadrunner: Towards automatic data extraction from large web sites}.
+\newblock {\em Proceedings of the 27th International Conference on Very Large
+  Data Bases}, pages 109--118, 2001.
+
+\bibitem[\protect\citename{Dong \bgroup \em et al.\egroup\ }{2014}]{Dong2014}
+Xin Dong, Evgeniy Gabrilovich, Geremy Heitz, Wilko Horn, Ni~Lao, Kevin Murphy,
+  Thomas Strohmann, Shaohua Sun, and Wei Zhang.
+\newblock {Knowledge vault: a web-scale approach to probabilistic knowledge
+  fusion}.
+\newblock {\em Proceedings of the 20th ACM SIGKDD international conference on
+  Knowledge discovery and data mining - KDD '14}, pages 601--610, 2014.
+
+\bibitem[\protect\citename{Ferrara and Baumgartner }{2011}]{Ferrara2011}
+Emilio Ferrara and Robert Baumgartner.
+\newblock {Automatic wrapper adaptation by tree edit distance matching}.
+\newblock {\em Smart Innovation, Systems and Technologies}, 8:41--54, 2011.
+
+\bibitem[\protect\citename{Ferrara \bgroup \em et al.\egroup\ }{2014}]{Ferrara2014}
+Emilio Ferrara, Pasquale {De Meo}, Giacomo Fiumara, and Robert Baumgartner.
+\newblock {Web data extraction, applications and techniques: A survey}.
+\newblock {\em Knowledge-Based Systems}, 70:301--323, 2014.
+
+\bibitem[\protect\citename{Freitag and Mccallum }{1999}]{Freitag1999}
+Dayne Freitag and Andrew~Kachites Mccallum.
+\newblock Information extraction with hmms and shrinkage.
+\newblock In {\em In Proceedings of the AAAI-99 Workshop on Machine Learning
+  for Information Extraction}, pages 31--36, 1999.
+
+\bibitem[\protect\citename{Freitag and McCallum }{2000}]{Freitag2000}
+Dayne Freitag and Andrew McCallum.
+\newblock Information extraction with hmm structures learned by stochastic
+  optimization.
+\newblock In {\em Proceedings of the Seventeenth National Conference on
+  Artificial Intelligence and Twelfth Conference on Innovative Applications of
+  Artificial Intelligence}, pages 584--589. AAAI Press, 2000.
+
+\bibitem[\protect\citename{Freitag }{1998}]{Freitag1998}
+Dayne Freitag.
+\newblock {Information Extraction from HTML: Application of a General Machine
+  Learning Approach}.
+\newblock {\em Proceedings of the Fifteenth National/Tenth Conference on
+  Artificial Intelligence/Innovative Applications of Artificial Intelligence},
+  pages 517--523, 1998.
+
+\bibitem[\protect\citename{Furche \bgroup \em et al.\egroup\ }{2012a}]{Furche2012a}
+Tim Furche, Georg Gottlob, Giovanni Grasso, Omer Gunes, Xiaoanan Guo, Andrey
+  Kravchenko, Giorgio Orsi, Christian Schallhart, Andrew Sellers, and Cheng
+  Wang.
+\newblock Diadem: Domain-centric, intelligent, automated data extraction
+  methodology.
+\newblock In {\em Proceedings of the 21st International Conference on World
+  Wide Web}, WWW '12 Companion, pages 267--270, New York, NY, USA, 2012. ACM.
+
+\bibitem[\protect\citename{Furche \bgroup \em et al.\egroup\ }{2012b}]{Furche2012}
+Tim Furche, Georg Gottlob, Giovanni Grasso, Giorgio Orsi, Christian Schallhart,
+  and Cheng Wang.
+\newblock {AMBER: Automatic Supervision for Multi-Attribute Extraction}.
+\newblock {\em arXiv preprint}, 1210(5984):1--22, 2012.
+
+\bibitem[\protect\citename{Hammer \bgroup \em et al.\egroup\ }{1997}]{Hammer1997}
+Joachim Hammer, Jason Mchugh, and Hector Garcia-molina.
+\newblock {Semistructured Data : The TSIMMIS Experience}.
+\newblock {\em Proceedings of the First East-European Symposium on Advances in
+  Databases and Information Systems}, pages 1--8, 1997.
+
+\bibitem[\protect\citename{Hochreiter and Schmidhuber }{1997}]{Hochreiter1997}
+Sepp Hochreiter and J\"{u}rgen Schmidhuber.
+\newblock Long short-term memory.
+\newblock {\em Neural Comput.}, 9(8):1735--1780, November 1997.
+
+\bibitem[\protect\citename{Hogue and Karger }{2005}]{Hogue2005}
+Andrew Hogue and David Karger.
+\newblock {Thresher : Automating the Unwrapping of Semantic Content from the
+  World Wide Web}.
+\newblock {\em WWW '05: Proceedings of the 14th international conference on
+  World Wide Web}, pages 86--95, 2005.
+
+\bibitem[\protect\citename{Hsu and Dung }{1998}]{Hsu1998}
+Chun~Nan Hsu and Ming~Tzung Dung.
+\newblock {Generating finite-state transducers for semi-structured data
+  extraction from the Web}.
+\newblock {\em Information Systems}, 23(8):521--538, 1998.
+
+\bibitem[\protect\citename{Huang \bgroup \em et al.\egroup\ }{2015}]{Huang2015}
+Zhiheng Huang, Wei Xu, and Kai Yu.
+\newblock Bidirectional {LSTM-CRF} models for sequence tagging.
+\newblock {\em CoRR}, abs/1508.01991, 2015.
+
+\bibitem[\protect\citename{Kr{\"{u}}pl \bgroup \em et al.\egroup\ }{2005}]{Krupl2005}
+Bernhard Kr{\"{u}}pl, Marcus Herzog, and Wolfgang Gatterbauer.
+\newblock {Using visual cues for extraction of tabular data from arbitrary HTML
+  documents}.
+\newblock {\em Special interest tracks and posters of the 14th international
+  conference on World Wide Web - WWW '05}, pages 1000----1001, 2005.
+
+\bibitem[\protect\citename{Kushmerick }2000]{Kushmerick2000}
+Nicholas Kushmerick.
+\newblock {Wrapper induction: efficiency and expressiveness}.
+\newblock {\em Artificial Intelligence}, 118(1-2):15--68, 2000.
+
+\bibitem[\protect\citename{Laender \bgroup \em et al.\egroup\ }{2002a}]{Laender2002}
+A.H.F. Laender, B.~A. Ribeiro-Neto, and Juliana S.Teixeria.
+\newblock {A brief survey of web data extraction tools}.
+\newblock {\em ACM SIGMOD Record 31(2)}, pages 84--93, 2002.
+
+\bibitem[\protect\citename{Laender \bgroup \em et al.\egroup\ }{2002b}]{Laender2002a}
+Alberto H~F Laender, Berthier Ribeiro-Neto, and Altigran~S da~Silva.
+\newblock {DEByE - Date extraction by example}.
+\newblock {\em Data Knowl. Eng.}, 40(2):121--154, 2002.
+
+\bibitem[\protect\citename{Lafferty }{2001}]{Lafferty2001}
+John Lafferty.
+\newblock Conditional random fields: Probabilistic models for segmenting and
+  labeling sequence data.
+\newblock pages 282--289. Morgan Kaufmann, 2001.
+
+\bibitem[\protect\citename{Lample \bgroup \em et al.\egroup\ }{2016}]{Lample2016}
+Guillaume Lample, Miguel Ballesteros, Sandeep Subramanian, Kazuya Kawakami, and
+  Chris Dyer.
+\newblock Neural architectures for named entity recognition.
+\newblock {\em CoRR}, abs/1603.01360, 2016.
+
+\bibitem[\protect\citename{Leek }{1997}]{Leek1997}
+Timothy~Robert Leek.
+\newblock Information extraction using hidden markov models, 1997.
+
+\bibitem[\protect\citename{Li and Gray }{2000}]{Li2000}
+Jia Li and Robert~M. Gray.
+\newblock {\em Image Segmentation and Compression Using Hidden Markov Models}.
+\newblock Kluwer Academic Publishers, Norwell, MA, USA, 2000.
+
+\bibitem[\protect\citename{Liu and Nocedal }{1989}]{Liu1989}
+Dong~C. Liu and Jorge Nocedal.
+\newblock On the limited memory bfgs method for large scale optimization.
+\newblock {\em Mathematical Programming}, 45(1):503--528, Aug 1989.
+
+\bibitem[\protect\citename{Liu \bgroup \em et al.\egroup\ }{2000}]{Liu2000}
+L.~Liu, C.~Pu, and W.~Han.
+\newblock {XWRAP: an XML-enabled wrapper construction system for Web
+  information sources}.
+\newblock {\em Proceedings of 16th International Conference on Data
+  Engineering}, pages 611--621, 2000.
+
+\bibitem[\protect\citename{Ma and Hovy }{2016}]{Ma2016}
+Xuezhe Ma and Eduard~H. Hovy.
+\newblock End-to-end sequence labeling via bi-directional lstm-cnns-crf.
+\newblock {\em CoRR}, abs/1603.01354, 2016.
+
+\bibitem[\protect\citename{McCallum \bgroup \em et al.\egroup\ }{2000}]{McCallum2000}
+Andrew McCallum, Dayne Freitag, and Fernando C.~N. Pereira.
+\newblock Maximum entropy markov models for information extraction and
+  segmentation.
+\newblock In {\em Proceedings of the Seventeenth International Conference on
+  Machine Learning}, ICML '00, pages 591--598, San Francisco, CA, USA, 2000.
+  Morgan Kaufmann Publishers Inc.
+
+\bibitem[\protect\citename{Muslea \bgroup \em et al.\egroup\ }{1999}]{Muslea1999}
+Ion Muslea, Steve Minton, and Craig Knoblock.
+\newblock {A Hierarchical Approach to Wrapper Induction}.
+\newblock {\em Proc. of the Third Annual Conf. on Autonomous Agents, ACM},
+  pages 190--197, 1999.
+
+\bibitem[\protect\citename{Pennington \bgroup \em et al.\egroup\ }{2014}]{Pennington2014}
+Jeffrey Pennington, Richard Socher, and Christopher~D. Manning.
+\newblock Glove: Global vectors for word representation.
+\newblock In {\em In EMNLP}, 2014.
+
+\bibitem[\protect\citename{Rabiner }{1990}]{Rabiner1990}
+Lawrence~R. Rabiner.
+\newblock Readings in speech recognition.
+\newblock chapter A Tutorial on Hidden Markov Models and Selected Applications
+  in Speech Recognition, pages 267--296. Morgan Kaufmann Publishers Inc., San
+  Francisco, CA, USA, 1990.
+
+\bibitem[\protect\citename{Ramshaw and Marcus }{1999}]{Ramshaw1999}
+L.~A. Ramshaw and M.~P. Marcus.
+\newblock {\em Text Chunking Using Transformation-Based Learning}, pages
+  157--176.
+\newblock Springer Netherlands, Dordrecht, 1999.
+
+\bibitem[\protect\citename{Rijsbergen }{1979}]{Rijsbergen1979}
+C.~J.~Van Rijsbergen.
+\newblock {\em Information Retrieval}.
+\newblock Butterworth-Heinemann, Newton, MA, USA, 2nd edition, 1979.
+
+\bibitem[\protect\citename{Sahuguet and Azavant }{1999}]{Sahuguet1999}
+Arnaud Sahuguet and Fabien Azavant.
+\newblock {Building light-weight wrappers for legacy Web data-sources using
+  W4F}.
+\newblock {\em Proceedings of the 25th VLDB Conference}, 99:738--741, 1999.
+
+\bibitem[\protect\citename{Sarawagi }{2008}]{Sarawagi2008}
+Sunita Sarawagi.
+\newblock {Information extraction}.
+\newblock {\em Foundations and Trends in Databases}, 1(3):261--377, 2008.
+
+\bibitem[\protect\citename{Schulz \bgroup \em et al.\egroup\ }{2016}]{Schulz2016}
+Andreas Schulz, J{\"{o}}rg L{\"{a}}ssig, and Martin Gaedke.
+\newblock {Practical web data extraction: Are we there yet? --- A short
+  survey}.
+\newblock {\em IEEE/WIC/ACM International Conference on Web Intelligence (WI),
+  2016}, pages 562----567, 2016.
+
+\bibitem[\protect\citename{Shi \bgroup \em et al.\egroup\ }{2015}]{Shi2015}
+Shengsheng Shi, Chengfei Liu, Yi~Shen, Chunfeng Yuan, and Yihua Huang.
+\newblock {AutoRM: An effective approach for automatic Web data record mining}.
+\newblock {\em Knowledge-Based Systems}, 89:314--331, 2015.
+
+\bibitem[\protect\citename{Soderland }{1999}]{Soderland1999}
+Stephen Soderland.
+\newblock {Learning Information Extraction Rules for Semi-Structured and Free
+  Text}.
+\newblock {\em Machine Learning}, 34(1):233--272, 1999.
+
+\bibitem[\protect\citename{Tjong Kim~Sang and De~Meulder }{2003}]{Sang2003}
+Erik~F. Tjong Kim~Sang and Fien De~Meulder.
+\newblock Introduction to the conll-2003 shared task: Language-independent
+  named entity recognition.
+\newblock In {\em Proceedings of the Seventh Conference on Natural Language
+  Learning at HLT-NAACL 2003 - Volume 4}, CONLL '03, pages 142--147,
+  Stroudsburg, PA, USA, 2003. Association for Computational Linguistics.
+
+\bibitem[\protect\citename{Varlamov and Turdakov }{2016}]{Varlamov2016}
+M.~I. Varlamov and D.~Yu. Turdakov.
+\newblock {A survey of methods for the extraction of information from Web
+  resources}.
+\newblock {\em Programming and Computer Software}, 42(5):279--291, 2016.
+
+\bibitem[\protect\citename{Wang and Lochovsky }{2003}]{Wang2003}
+Jiying Wang and Fred~H. Lochovsky.
+\newblock {Data extraction and label assignment for web databases}.
+\newblock {\em Proceedings of the twelfth international conference on World
+  Wide Web - WWW '03}, page 187, 2003.
+
+\bibitem[\protect\citename{Zhai and Liu }{2005}]{Zhai2005}
+Yanhong Zhai and Bing Liu.
+\newblock {Web data extraction based on partial tree alignment}.
+\newblock {\em Proceedings of the 14th international conference on World Wide
+  Web - WWW '05}, page~76, 2005.
+
+\bibitem[\protect\citename{Zhu \bgroup \em et al.\egroup\ }{2005}]{Zhu2005}
+Jun Zhu, Zaiqing Nie, Ji-Rong Wen, Bo~Zhang, and Wei-Ying Ma.
+\newblock 2d conditional random fields for web information extraction.
+\newblock In {\em Proceedings of the 22Nd International Conference on Machine
+  Learning}, ICML '05, pages 1044--1051, New York, NY, USA, 2005. ACM.
+
+\bibitem[\protect\citename{Zhu \bgroup \em et al.\egroup\ }{2006}]{Zhu2006}
+Jun Zhu, Zaiqing Nie, Ji-Rong Wen, Bo~Zhang, and Wei-Ying Ma.
+\newblock Simultaneous record detection and attribute labeling in web data
+  extraction.
+\newblock In {\em Proceedings of the 12th ACM SIGKDD International Conference
+  on Knowledge Discovery and Data Mining}, KDD '06, pages 494--503, New York,
+  NY, USA, 2006. ACM.
 \end{thebibliography}

### 2018-11-30 tex/article.tex
Dataset and Readme.

@@
 Web data extraction methods often rely on hand-coded rules to 
-identify and extract data from web pages. These methods are usually
-suited for extracting information from pages with repeating templates within
+identify and extract data from webpages. These methods are usually
+suited for extracting information from pages within
 the same website, however they perform poorly on extraction 
@@
 on the task of Web data extraction. In particular, we introduce a novel 
-dataset~\footnote{The dataset and all models discussed in this article are available in: https://github.com/jmfveneroso/ner.} 
-consisting of faculty listings from university web pages across
+dataset\footnote{The dataset and all models discussed in this article are 
+available in: https://github.com/jmfveneroso/ner-on-html.} 
+consisting of faculty listings from university webpages across
 the world in multiple languages and test the NER models on the task of 
@@
 Most existing Web data extraction methods are tailored to extract data 
-from a single Web page, producing different compromises between efficacy and 
+from a single webpage, producing different compromises between efficacy and 
 degree of human supervision. Some unsupervised approaches proposed to tackle 
@@
 unsupervised WDE methods work in two stages. In the record segmentation stage,
-WDE systems seek to cluster visually and structurally similar Web page regions 
+WDE systems seek to cluster visually and structurally similar webpage regions 
 and identify repeating data records with heuristics and 
@@
 While unsupervised approaches can be sometimes adequate to extract information from 
-Web pages with similar templates, they usually fail on cross-website data extraction 
+webpages with similar templates, they usually fail on cross-website data extraction 
 tasks. Also, more sophisticated approaches may be needed when we are not dealing
@@
 are still desirable because, while many WDE algorithms can effectively exploit the 
-semi-structured nature of Web documents, too much reliance on structural Web page 
+semi-structured nature of Web documents, too much reliance on structural webpage 
 features often produce poor generalizations on cross website extraction. Also, 
@@
 
-In this paper, we investigate methods of named entity recognition for Web data extraction.
+In this article, we investigate methods of named entity recognition for Web data extraction.
 Recently proposed neural architectures have achieved exciting results 
@@
 error prone process, unsuited for large scale operations. Wrappers tend to
-break frequently because they rely heavily on Web page features that can change 
+break frequently because they rely heavily on webpage features that can change 
 often. So, in the late nineties, several authors advocated for wrapper induction, a technique 
@@
 Some examples are: the Visual Box Model \cite{Krupl2005}, a data extraction system that produces 
-a visualization of the Web page to exploit visual cues to identify data presented in a tabular form;
+a visualization of the webpage to exploit visual cues to identify data presented in a tabular form;
 automatic wrapper adaptation \cite{Ferrara2011}, a technique that tries to reduce the cost of 
@@
 wrappers to the new page structure; AutoRM \cite{Shi2015}, a method to mine
-records from a single Web page by identifying similar data regions through DOM
+records from a single webpage by identifying similar data regions through DOM
 tree analysis; Knowledge Vault \cite{Dong2014}, a method that combines different 
@@
 independent Web data extraction was described by Zhu et al \shortcite{Zhu2005}. The 2D CRF 
-model takes a Web page segmented into data blocks and employs a two dimensional conditional 
+model takes a webpage segmented into data blocks and employs a two dimensional conditional 
 random field model to perform attribute labeling. The model was further improved
@@
 were also tackled by ObjectRunner \cite{Abdessalem2010} and AMBER \cite{Furche2012}. 
-These methods work by annotating Web pages automatically with regular expressions, gazetteers and 
+These methods work by annotating webpages automatically with regular expressions, gazetteers and 
 knowledge bases. They can rectify low quality annotations and even improve the annotators
@@
 
-\subsubsection{Self training} \label{sssec:self_training}
+\subsubsection{Self training} 
+\label{sssec:self_training}
 
 In the task of NER on HTML, there are useful features related to the HTML
-structure that can help in identifying named entities. On a given website, named
+structure that can help in identifying named entities. In a given website, named
 entities tend to occur inside the same HTML tags. The HTML tag feature or other
@@
 because different websites use distinct HTML templates. 
-Therefore, we propose a self training strategy to obtain probabilities for
+Therefore, we propose a self-training strategy to obtain probabilities for
 these HTML features. It is implemented like this:
@@
 
-\begin{figure}
+Recurrent neural networks (RNN) have been successfully employed on numerous NLP tasks such as
+language modelling, POS tagging, speech recognition and NER. Different from feed-forward 
+neural networks, RNNs can retain information in their internal state, making them more 
+suitable for processing sequences, and consequently for solving text related tasks. 
+Figure~\ref{fig:rnn_network} describes an RNN for sequence labeling unrolled through multiple 
+timesteps.
+
+\begin{figure}[h]
   \centering
@@
 
-Recurrent neural networks (RNN) have been successfully employed on numerous NLP tasks such as
-language modelling, POS tagging, speech recognition and NER. Different from feed-forward 
-neural networks, RNNs can retain information in their internal state, making them more 
-suitable for processing sequences, and consequently for solving text related tasks. 
-Figure~\ref{fig:rnn_network} describes an RNN for sequence labeling unrolled through multiple 
-timesteps. At each timestep, the neural network computes a hidden state $ h_t $ using an input 
+At each timestep, the neural network computes a hidden state $ h_t $ using an input 
 vector $ x_t $ and the previous hidden state $ h_{t-1} $, that retains information from past 
@@
 will be used to compute the output activation of the LSTM unit. 
-LSTM cell implementations vary slightly in the literature, a visual description of 
-our LSTM cell is also provided in Figure~\ref{fig:lstm_cell}.
+LSTM cell implementations vary slightly in the literature. A visual description of 
+our LSTM cell is provided in Figure~\ref{fig:lstm_cell}.
 
@@
 in that the gates $ \Gamma_i $ and $ \Gamma_f $ do not receive inputs from the previous 
-cell state $ c_{t-1} $ and the output gate does not receive inputs from the current cell 
+cell state $ c_{t-1} $ and the output gate $ \Gamma_{o} $ does not receive inputs from the current cell 
 state $ c_{t} $. This variation produces little difference in terms of model accuracy on
@@
 representations generated by the CNN are combined with word level representations 
-and fed to the BI-LSTM-CRF in section \ref{sssec:lstm_crf}.
+and fed to the BI-LSTM-CRF described in section \ref{sssec:lstm_crf}.
 This architecture can learn morphological features that are very
@@
 on the Web data extraction task. The task consists of finding researcher
-names in faculty listings from university Web pages across the world. This would be a
+names in faculty listings from university webpages across the world. This would be a
 necessary step when linking researcher profiles from university websites to their entries
 in public databases such as DBLP \footnote{http://dblp.uni-trier.de/}. Unlike many
-information extraction datasets, each Web page in the dataset comes from a different 
+information extraction datasets, each webpage in the dataset comes from a different 
 website, and therefore has a different format, what makes many information
@@
 multiple languages, although the English version was preferred when it was available.
-We gathered faculty Web pages randomly in proportion to
+We gathered faculty webpages randomly in proportion to
 the number of universities in each country\footnote{A detailed list of universities can
@@
       crf              & Linear chain conditional random fields \\
-      bi-lstm-crf      & BI-LSTM-CRF model \cite{Huang2015} \\
-      bi-lstm-crf-cnn  & BI-LSTM-CRF with CNN character representations \cite{Ma2016} \\
-      bi-lstm-crf-lstm & BI-LSTM-CRF with LSTM character representations \cite{Lample2016} \\
+      bi-lstm-crf      & BI-LSTM-CRF model \\
+      bi-lstm-crf-cnn  & BI-LSTM-CRF with CNN character representations \\
+      bi-lstm-crf-lstm & BI-LSTM-CRF with LSTM character representations \\
       \bottomrule
@@
 The neural models achieved high F1-scores in the test
-set even with the absence of features. The plain LSTM-CRF architecture improved performance 
+set even with the absence of features. The plain BI-LSTM-CRF architecture improved performance 
 significantly in comparison with the conventional CRF (0.8427 against 0.6244). 
@@
 morphological features can make up for the scarcity of textual data on some 
-Web pages.
+webpages.
 
@@
 the features described in Table~\ref{tab:features}. In this experiment, we
-also evaluate the self training strategy for HMMs described in Section 
-\label{sssec:self_training}. The self trained HMMs are described with the 
+also evaluate the self-training strategy for HMMs described in Section 
+\ref{sssec:self_training}. The self trained HMMs are described with the 
 suffix "+ST". Table \ref{tab:experiment2} shows the results for Experiment 2.
@@
 to the best neural model without features, demonstrating their inherent limitations.
-We can also see that the self training strategy for HMMs improved the quality of 
-the models significantly in all cases, boosting both precision and recall. Finally,
-HMMs that employed trigrams or quadrigrams (hmm-2, hmm-3) also performed better in
-comparison to regular HMMs.
-
-The neural models also improved a little with the addition of features. The plain LSTM-CRF
+HMMs that employed trigrams or quadrigrams (hmm-2, hmm-3) performed better than
+regular HMMs. Also, we can see that the self-training strategy for HMMs improved 
+the quality of the models significantly in all cases, boosting both precision and recall. 
+This hints at the possibility to adapt this strategy to neural networks and boost
+the performance of neural models on the NER on HTML task.
+
+The neural models also improved a little with the addition of features. The plain BI-LSTM-CRF
 model gets a closer performance to the models that employed neural character 
@@
 first experiment. So, when these features are added explicitly, the differences 
-in performance become less noticeable.
+in performance between different neural models become less noticeable.
 
@@
 
-Machine-learning-based sequence labeling models provide a flexible approach to web data 
+Machine-learning-based sequence labeling models provide a flexible approach to Web data 
 extraction, in contrast to more traditional methods. In simple cases, a neural
@@
 Web data extraction methods. The accuracy achieved by deep neural architectures even
-on web pages that are very different from the plain text for which these architectures 
+on webpages that are very different from the plain text for which these architectures 
 were initially designed shows the potential for a truly flexible approach to cross domain 

### 2018-11-30 x.sh

@@ -1,7 +1,0 @@
-./collect_results.sh dataset/dev.txt > logs/dev.log
-./collect_results.sh dataset/small_dev_1.txt > logs/small_dev_1.log
-./collect_results.sh dataset/small_dev_2.txt > logs/small_dev_2.log
-./collect_results.sh dataset/small_dev_3.txt > logs/small_dev_3.log
-./collect_results.sh dataset/small_dev_4.txt > logs/small_dev_4.log
-./collect_results.sh dataset/small_dev_5.txt > logs/small_dev_5.log
-# ./collect_results.sh conll > logs/conll_train.log

### 2019-05-18 tex/article.tex
NLE article.

--- 2018-11-30 tex/article.tex
@@
 
-% \documentclass[sigconf]{acmart}
-% \settopmatter{printacmref=false} % Removes citation information below abstract
-% \renewcommand\footnotetextcopyrightpermission[1]{} % removes footnote with conference information in first column
-% \pagestyle{plain} % removes running headers
-% \setcopyright{none}
-
 \usepackage{booktabs} % For formal tables
-\usepackage[ruled]{algorithm2e} % For algorithms
-\renewcommand{\algorithmcfname}{ALGORITHM}
-\SetAlFnt{\small}
-\SetAlCapFnt{\small}
-\SetAlCapNameFnt{\small}
-\SetAlCapHSkip{0pt}
-\IncMargin{-\parindent}
-
 \usepackage[utf8]{inputenc}
@@
 \usepackage{multirow}
+\usepackage{glossaries}
+\usepackage{tikz}
+\usepackage{pgfplots}
 
@@
 
+\makeglossaries
+\newacronym{nlp}{NLP}{Natural Language Processing}
+\newacronym{wde}{WDE}{Web Data Extraction}
+\newacronym{ner}{NER}{Named Entity Recognition}
+\newacronym{hmm}{HMM}{Hidden Markov Models}
+\newacronym{crf}{CRF}{Conditional Random Fields}
+\newacronym{lstm}{LSTM}{Long Short-Term Memory Networks}
+\newacronym{ie}{IE}{Information Extraction}
+\newacronym{rne}{RNE}{Researcher Name Extraction}
+\newacronym{rnn}{RNN}{Recurrent Neural Networks}
+\newacronym{cnn}{CNN}{Convolutional Neural Networks}
+\newacronym{pos}{POS}{Part-of-Speech}
+
 \begin{document}
 
-\title{Web data extraction through named entity labeling}
-
-\author{João Mateus de Freitas Veneroso}
+\title{Named Entity Recognition for Web Data Extraction}
+
+% \author[João Mateus de Freitas Veneroso and Berthier Ribeiro-Neto]
+%        {João Mateus de Freitas Veneroso$^A$ \and
+%         Berthier Ribeiro-Neto$^B$\\
+% 	Universidade Federal de Minas Gerais$^{A,B}$ \\
+% 	Google Engineering$^A$, Belo Horizonte - MG, Brazil}
+
 % \affiliation{%
@@
 
+\maketitle
+
 \begin{abstract}
 
-Web data extraction methods often rely on hand-coded rules to 
-identify and extract data from web pages. These methods are usually
-suited for extracting information from repeating templates inside
+% \gls{wde} methods often rely on hand-coded rules to 
+% identify and extract data from webpages. These methods are usually
+% suited for extracting information from pages within
+% the same website, however they perform poorly on extraction 
+% tasks across different websites. Alternatively, statistical and 
+% machine-learning-based sequence labeling methods provide a more flexible 
+% approach to Web data extraction. Many times, HTML pages are very different 
+% from plain text, because sentences are too short to provide adequate 
+% context for conventional Named Entity Recognition methods to work 
+% properly. Also, the HTML structure may encode information that is not 
+% replicated in the text. Nonetheless, these limitations can be overcome by
+% adequate feature engineering, the use of pretrained word 
+% embeddings and neural character representations. In this article, we 
+% evaluate the performance of different methods of named entity recognition 
+% on the task of Web data extraction. In particular, we introduce a novel 
+% dataset\footnote{The dataset and all models discussed in this article are 
+% available in: https://github.com/jmfveneroso/ner-on-html.} 
+% consisting of faculty listings from university webpages across
+% the world in multiple languages and test the NER models on the task of 
+% extracting researcher names from these listings. We found that a 
+% neural network architecture that combines a bidirectional LSTM with
+% a Conditional Random Fields output layer and LSTM-based character 
+% representations outperforms other methods on the researcher name 
+% extraction task, achieving an F1-score of 0.8867 with no feature engineering. 
+% With the addition of hand crafted features, the F1-score can be slightly 
+% improved to 0.8995.
+
+Web Data Extraction methods often rely on hand-coded rules to 
+identify and extract data from webpages. These methods are
+suited for extracting information from pages within
 the same website, however they perform poorly on extraction 
-tasks across different websites. Alternatively, statistical and 
-machine-learning-based sequence labeling methods provide a more flexible 
-approach to Web data extraction. HTML text is ocasionally very different 
-from plain text because sentences can be too short to provide adequate 
-context for conventional Named Entity Recognition methods to work 
-properly. Also, the HTML structure can encode information that is not 
-replicated in the text. Nonetheless, these limitations can be overcome by
-adequate feature engineering, the use of pre-trained word 
-embeddings and neural character representations. In this article, we 
-evaluate the performance of different methods of named entity recognition 
-on the task of Web data extraction. In particular, we introduce a novel 
+tasks across different websites. Alternatively, 
+machine-learning-based Named Entity Recognition methods provide a more flexible 
+approach to Web Data Extraction. However, many times webpages are very different 
+from plain text, because sentences are too short to provide adequate 
+context for conventional Named Entity Recognition models to work 
+properly. 
+% Nonetheless, the HTML structure also encodes useful information that 
+% can be used by NER models to achieve a better performance. We propose a
+% method to use this information: the self-training strategy for Hidden Markov
+% Models.
+In this article, we 
+evaluate the performance of different methods of Named Entity Recognition
+in the task of Web Data Extraction. In particular, we introduce a novel 
 dataset consisting of faculty listings from university webpages across
-the world in multiple languages and test the NER models on the task of 
+the world in multiple languages and test different Named Entity Recognition 
+models in the task of 
 extracting researcher names from these listings. We found that a 
@@
 a Conditional Random Fields output layer and LSTM-based character 
-representations outperforms other methods on the researcher name 
-extraction task, achieving an F1-score of 0.8867 with no feature engineering. 
-With the addition of hand crafted features, the F1-score can be slightly 
-improved to 0.8995 with another neural architecture that incorporates
-CNN-based character representations.
+representations outperforms other methods achieving 90.2 F1 in 
+the task. However, with the self-training strategy, we can get a much simpler 
+model, the second-order Hidden Markov Model, to achieve 87.9 F1.
 
@@
 
-% \keywords{Named entity recognition, information extraction, web data extraction}
-
-\maketitle
-
 \section{Introduction}
 
-Web data extraction (WDE) is the task of automatically extracting structured 
-information from unstructured or semi-structured Web documents. The input 
-usually consists of Web documents containing a number of predetermined entities 
-organized in a similar manner. The web data extraction task consists of 
+\gls{wde} is the task of automatically extracting structured 
+information from unstructured or semi-structured web documents. The input 
+usually consists of web documents containing a number of predetermined entities 
+organized in a similar manner. The \gls{wde} task consists of 
 identifying these entities and organizing them according to a template.
@@
 by an underlying pattern. Organization patterns tend to follow some guidelines 
-but they are in no way subject to strict rules. That is why classical web data 
-extraction systems such as automatic wrapper generators 
+but they are in no way subject to strict rules. That is why classical \gls{wde} 
+systems such as automatic wrapper generators 
 \cite{Kushmerick2000,Hsu1998,Muslea1999}
@@
 
-Most existing Web data extraction methods are tailored to extract data 
-from a single Web page, producing different compromises between efficacy and 
+Most existing \gls{wde} methods are tailored to extract data 
+from a single webpage, producing different compromises between efficacy and 
 degree of human supervision. Some unsupervised approaches proposed to tackle 
 the problem of data extraction for whole application domains 
-\cite{Zhu2005,Zhu2006,Abdessalem2010,Furche2012,Furche2012a}. Usually, 
-unsupervised WDE methods work in two stages. In the record segmentation stage,
-WDE systems seek to cluster visually and structurally similar web page regions 
-and identify repeating data records, usually with heuristics and 
-hand-coded rules. In the attribute labelling stage, WDE systems seek to identify 
+\cite{Crescenzi2001}. Usually, 
+unsupervised \gls{wde} methods work in two stages. In the record segmentation stage,
+WDE systems seek to cluster visually and structurally similar webpage regions 
+and identify repeating data records with heuristics and 
+hand-coded rules. In the attribute labeling stage, WDE systems seek to identify 
 the correct attributes on data records, many times resorting to regular expressions 
 or gazetteer matching strategies. The outcome of each of these stages can aid one 
-another. The inner patterns of data records can help identifying attributes in other 
+another. The inner patterns of data records can help in identifying attributes of other 
 data records. Also, by properly identifying data record attributes, it becomes 
@@
 tasks. Also, more sophisticated approaches may be needed when we are not dealing
-with easily distinguishable attributes such as prices and dates. In this regard, 
-machine-learning-based sequence labeling methods can provide a more flexible 
-approach that works regardless of website structure.
-
-In recent years, we saw an amazing progress in the field of Natural Language Processing, 
-particularly with the introduction of deep recurrent neural network architectures
-for sequence labeling. However, despite web data extraction being a closely 
-related field, there is a lack of extraction tools that make use of these recent 
-advancements. The attribute labelling stage in web data extraction systems
-is essentialy a Named Entity Recognition (NER) problem, the problem of 
-detecting named entities in the text and classifying them into predetermined 
-categories such as person names, locations, dates or organizations.
-
-In many cases, such as when we are extracting researcher names from faculty listings,
-detecting named entities is sufficient to solve the data extraction task. However, when we are
-dealing with multi attribute data records or complex relationships, we may need to 
-perform additional steps. Nevertheless, even in the latter cases, flexible NER methods 
-are still desirable because, while many WDE algorithms can effectively exploit the 
-semi-structured nature of web documents, too much reliance on structural webpage 
-features often produce poor generalizations on cross website extraction. Also, 
-data records may enclose plain text with relevant named entities.
-
-In this paper, we investigate methods of named entity recognition for web data extraction.
-Recently proposed neural architectures have achieved exciting results 
-on the NER task in plain text while requiring almost 
-no feature engineering or access to gazetteers \cite{Huang2015,Lample2016,Ma2016}. 
-NER on HTML poses a slightly different type of challenge. Named entities may occur inside 
-tables, lists, graphs or other types of visual elements that provide little to no textual 
-information that could give hints about the semantic category of a word. Still, even 
-with this limitation, we show that it is possible to obtain very good results with a 
-relatively small training set.
-
-By reliably detecting named entities on HTML, we can improve the performance of existing WDE 
-approaches or even construct an end-to-end neural network architecture to tackle domain 
-wide extraction with considerable flexibility. To test different NER approaches to
-web data extraction, we explored the task of researcher name extraction from university 
-faculty listings across the world, introducing a novel NER dataset.
-
-Reliable researcher affiliation information is often missing from public researcher 
-databases (especially in departments other than Computer Science). Also, the display of 
-faculty information varies significantly between different university websites, so 
-this task can provide a good measure of the expected performance and data need of
-NER methods on other web data extraction tasks.
+with easily distinguishable attributes such as prices and dates. 
+Comparatively, statistical machine learning provides more robust and flexible methods
+of \gls{wde}. In recent years, we saw amazing progress in 
+the field of \gls{nlp} that is extremely relevant to
+the \gls{wde} community, particularly with the introduction of Deep Neural Networks 
+for Sequence Labeling~\cite{Collobert2011}, but these advancements were 
+not widely incorporated by \gls{wde} systems. Also, most of the attention of the \gls{nlp} community 
+regarding this topic is devoted to solving \gls{ie} tasks in plain text, such as 
+the identification of people and organizations in news texts.
+However, the difference between some types of webpages and plain text is significant, so
+\gls{ie} systems trained in plain text datasets tend to perform poorly 
+when confronted with some web extraction tasks, as we have confirmed in our experiments.
+
+A concrete example of a \gls{wde} problem that demands the type of
+flexible solution provided by statistical machine learning methods is the extraction of 
+researcher names from faculty directories. Automatically extracting researcher information 
+from university websites is important, for example, to construct researcher affiliation databases 
+and compare the academic impact of research groups using bibliographic indices~\cite{Ribas2015}. 
+The problem of \gls{rne} can be solved with machine learning methods of 
+\gls{ner}.
+
+Many \gls{wde} tasks in the web share a common
+factor with the \gls{rne} task. That is, they need to extract similar
+entities from different webpages or they need to extract entities from short snippets of text 
+instead of complete sentences. Some examples would be comment extraction from blog
+posts and \gls{ner} in tweets. Because of the lack of context in tweets, \gls{ner} methods trained 
+in conventional plain text corpora tend to perform badly for more or less the same reasons 
+they perform badly in other \gls{wde} tasks.
+
+In this article, we compare different machine learning approaches to 
+\gls{ner} on the web by evaluating their performance in the 
+\gls{rne} task. With this purpose in mind, we introduce a novel \gls{ner} dataset 
+with labeled entities, consisting of faculty directories from universities across the world. 
+We compare the models in terms of their Precision, Recall, F-scores and their 
+overall complexity. That is, even if a model has a slightly worse performance in terms of the
+objective evaluation metrics in comparison to other approaches, it may still be useful if it 
+is considerably simpler and faster to train.
+The tested models were the \gls{hmm} up to third order, \gls{crf}, and a range of Deep Learning 
+architectures based on Bidirectional \gls{lstm}. We also 
+introduce the self-training strategy that can boost the performance 
+of \gls{hmm}s in sequence labeling tasks for the web.
+
+The usability of the evaluated models is not limited to the particular problem of \gls{rne}. 
+By reliably detecting named entities on the web, we can boost the performance 
+of existing \gls{wde} approaches or even construct an end-to-end architecture that
+solves the problem of data extraction across different websites with improved robustness. Also, 
+the researcher affiliation database constructed with the application of these methods will
+be made public in the future to provide deeper insight in bibliometric studies about the
+scientific impact of research groups.
 
 \section{Related Work}
-
-In the last 20 years, the astonishing growth of public information in the web has 
-led to the development of a number of different approaches to the problem of web 
-data extraction. Traditionally, the task was solved by designing special purpose
+\label{cha:related_work}
+
+The \gls{rne} task is a problem in \gls{wde} that
+we proposed to solve with the application of machine learning methods of \gls{ner}.
+This chapter presents the related research in the fields of \gls{wde} 
+in Section~\ref{sec:wde} and \gls{ner} in Section~\ref{sec:ner}.
+
+\subsection{Web Data Extraction}
+\label{sec:wde}
+
+Since the early 1990s, the astonishing growth of public information in the web has 
+led to the development of a number of different approaches to the problem of \gls{wde}.
+Traditionally, the task was solved by designing special purpose
 programs called wrappers to recognize relevant data and store records in a structured
@@
 error prone process, unsuited for large scale operations. Wrappers tend to
-break frequently because they rely heavily on web page features that can change 
+break frequently because they rely on webpage features that can change 
 often. So, in the late nineties, several authors advocated for wrapper induction, a technique 
@@
 identifying delimiters or context tokens that single out the desired attributes. 
-Some remarkable wrapper induction methods are WIEN \cite{Kushmerick2000}, Soft 
-Mealy \cite{Hsu1998} and STALKER \cite{Muslea1999}.
+Some remarkable wrapper induction methods are WIEN~\cite{Kushmerick2000}, Soft 
+Mealy~\cite{Hsu1998} and STALKER~\cite{Muslea1999}.
 
@@
 
-Other approaches such as NoDoSE \cite{Adelberg1998} and Debye \cite{Laender2002a} 
+Other approaches such as NoDoSE~\cite{Adelberg1998} and Debye~\cite{Laender2002a} 
 brought greater flexibility to wrapper induction methods by requiring a greater level 
-of human interaction through graphical user interfaces. Web data extraction techniques often 
+of human interaction through graphical user interfaces. \gls{wde} techniques often 
 require some sort of assistance from human experts to boost accuracy. One of the main challenges 
-in the field lies in determining an adequate tradeoff between the degree of automation and 
-the precision and recall of the data extraction tool.
-
-To automate the task of web data extraction completely some approaches,
-such as Road Runner \cite{Crescenzi2001}, removed entirely the need for data examples.
-Road Runner parses documents belonging to a same class (e.g. books on Amazon) and 
+in the field lies in determining an adequate trade-off between the degree of automation and 
+the Precision and Recall of the data extraction tool.
+
+To automate the task of \gls{wde} completely some approaches,
+such as Road Runner~\cite{Crescenzi2001}, removed entirely the need for data examples.
+Road Runner parses documents belonging to a same class (e.g. books in Amazon) and 
 generates wrappers based on their similarities and differences, yielding comparable results 
@@
 
-NLP based approaches aimed at extracting more general rules that could possibly
-be employed over multiple websites. RAPIER \cite{Califf1999} is a method of rule
+Early NLP-based approaches aimed at extracting more general rules that could possibly
+be employed over multiple websites. RAPIER~\cite{Califf1999} is a method of rule
 extraction that uses information such as part-of-speech tags and semantic classes from
@@
 flexible than the wrapper induction methods, however it achieves much lower rates of 
-recall and precision.
-
-In 2002, a survey by Laender et al. \cite{Laender2002} made a thorough classification of the
+Precision and Recall.
+
+A survey by Laender, Ribeiro-Neto, da Silva and Teixeira~\shortcite{Laender2002b} made a thorough classification of the
 early approaches with a taxonomy based on their main technology, being them: languages for
@@
 are: 
-
+%
 \begin{itemize}
-\item TSIMMIS \cite{Hammer1997} and WebOQL \cite{Arocena1999}, which are special purpose 
+\item TSIMMIS~\cite{Hammer1997} and WebOQL~\cite{Arocena1999}, which are special purpose 
 languages for building wrappers.
-
-\item Road Runner \cite{Crescenzi2001}, XWRAP \cite{Liu2000} and W4F \cite{Sahuguet1999}, 
+\item Road Runner~\cite{Crescenzi2001}, XWRAP~\cite{Liu2000} and W4F~\cite{Sahuguet1999}, 
 which are HTML-aware tools that infer meaningful patterns from the HTML structure.
-
-\item RAPIER \cite{Califf1999}, SRV \cite{Freitag1998}, WHISK \cite{Soderland1999}, which 
+\item RAPIER~\cite{Califf1999}, SRV~\cite{Freitag1998}, WHISK~\cite{Soderland1999}, which 
 are NLP-based tools.
-
-\item WIEN \cite{Kushmerick2000}, Soft Mealy \cite{Hsu1998} and STALKER \cite{Muslea1999} which 
+\item WIEN~\cite{Kushmerick2000}, Soft Mealy~\cite{Hsu1998} and STALKER~\cite{Muslea1999} which 
 are wrapper induction methods.
-
-\item NoDoSE \cite{Adelberg1998} and Debye \cite{Laender2002a}, which are semi supervised modeling
-based tools that require some interaction with the user by means of a graphical
+\item NoDoSE~\cite{Adelberg1998} and Debye~\cite{Laender2002a}, which are semi-supervised
+tools that require some interaction with the user by means of a graphical
 user interface.
 \end{itemize}
-
-In 2006, Chang et al. \cite{Chang2006} complemented the previous surveys with semisupervised 
-technologies such as Thresher \cite{Hogue2005}, IEPAD \cite{Chang2001} and 
-OLERA \cite{Chang2004}. They differed from supervised 
+%
+% Text Runner.
+% https://www.aaai.org/Papers/IJCAI/2007/IJCAI07-429.pdf
+\cite{Chang2006} complemented the previous surveys with semi-supervised 
+technologies such as Thresher~\cite{Hogue2005}, IEPAD~\cite{Chang2001} and 
+OLERA~\cite{Chang2004}. They differed from supervised 
 and unsupervised methods because they either needed only a rough description of
 data from users for extraction rule generation or some level of post processing
-that needed user attention. The survey also mentioned newer unsupervised methods
-such as DeLa \cite{Wang2003}, Exalg \cite{Arasu2003} and Depta \cite{Zhai2005}.
-
-Most of the early information extraction systems were rule-based with either 
+that needed user attention. 
+%The survey also mentioned newer unsupervised methods
+% such as DeLa~\cite{Wang2003}, Exalg~\cite{Arasu2003} and Depta~\cite{Zhai2005}.
+
+Most of the early \gls{wde} systems were rule-based with either 
 manual rule description or automatic rule learning from examples, thus they
@@
 Huge progress in the field of statistical learning led to the development of
-statistical models that tried to solve this problem.
-
-In 2008, Sarawagi \cite{Sarawagi2008} produced a survey that classified wrappers into
+models that tried to solve this problem.
+
+\cite{Sarawagi2008} introduced a classification that segmented wrappers in
 rule-based methods, statistical methods and hybrid models, bringing together 
-the fields of named entity recognition, relationship extraction and information extraction. 
-The rule based methods encompass most of the 
-previous models. The statistical methods convert the extraction task into a token labeling 
-task, identifying the target entities through the assignment of labels as in a typical 
-Named Entity Recognition task. Traditionally, Hidden Markov Models \cite{Leek1997,Freitag1999}, 
-Linear Chain Conditional Random Fields \cite{Lafferty2001}, and Maximum Entropy Taggers 
-\cite{McCallum2000} have been the usual choice for linear sequence tagging models.
-More recently, with the advancement of Natural Language Processing and Deep Learning, 
-neural models outperformed previous NER methods for plain text. Huang et. al. \cite{Huang2015} introduced the 
-bidirectional Long Short-Term Memory (LSTM) model with a Conditional Random Field (CRF) output layer
-for NER. Ma and Hovy \cite{Ma2016} incorporated Convolutional Neural Network based character representations 
-on top of the architecture. And Lample et. al. \cite{Lample2016} introduced
-LSTM based character representations.
-
-Surveys by Ferrara et al. \cite{Ferrara2014}, Schulz et al. \cite{Schulz2016} and 
-Varlamov et al. \cite{Varlamov2016} updated the previous surveys on information 
-extraction methods with some interesting innovations. 
-Some examples are: the Visual Box Model \cite{Krupl2005}, a data extraction system that produces 
-a visualization of the web page to exploit visual cues to identify data presented in a tabular form;
-automatic wrapper adaptation \cite{Ferrara2011}, a technique that tries to reduce the cost of 
+the fields of \gls{ner}, Relationship Extraction and \gls{wde}. 
+The rule based methods encompass most of the previous models. While the statistical methods 
+convert the extraction task into a token labeling task, solved with \gls{ner} 
+and Relationship Extractions methods. Traditionally, these subtasks were solved with 
+generative models based on \gls{hmm}s or discriminative models based on the 
+Maximum Entropy principle, but recently these have been largely superseded by Deep Neural 
+Networks. Different from automatic wrapper generators, statistical methods are suitable for
+a large variety of tasks, especially when we want the system to handle cross website information 
+extraction and plain text information extraction. That is why this class of methods is of 
+special interest to our application. The progress of statistical models will be 
+discussed in Section~\ref{sec:ner}.
+
+Surveys by~\cite{Ferrara2014}, \cite{Schulz2016} and \cite{Varlamov2016} updated the 
+previous surveys on Information Extraction methods with some interesting innovations. 
+Some examples are: the Visual Box Model~\cite{Krupl2005}, a data extraction system that produces 
+a visualization of the webpage to exploit visual cues to identify records presented in a tabular form;
+automatic wrapper adaptation~\cite{Ferrara2011}, a technique that tries to reduce the cost of 
 wrapper maintenance by measuring the similarity of HTML trees and adapting
-wrappers to the new page structure; AutoRM \cite{Shi2015}, a method to mine
-records from a single web page by identifying similar data regions through DOM
-tree analysis; Knowledge Vault \cite{Dong2014}, a method that combines different 
+wrappers to the new page structure; AutoRM~\cite{Shi2015}, a method to mine
+records from a single webpage by identifying similar data regions through DOM
+tree analysis; and Knowledge Vault~\cite{Dong2014}, a method that combines different 
 extraction approaches to feed a probabilistic knowledge base.
@@
 and are therefore unsuited for cross website extraction tasks. Even unsupervised
-approaches that are domain independent, such as RoadRunner \cite{Crescenzi2001} 
-and EXALG \cite{Arasu2003} only work well for extracting data from pages generated 
-from a same template.
+approaches that are application domain independent, such as RoadRunner and EXALG, 
+only work well when extracting data from pages generated from a same template.
 
 A statistical approach to unsupervised domain 
-independent web data extraction was described by Zhu et al \cite{Zhu2005}. The 2D CRF 
-model takes a web page segmented into data blocks and employs a two dimensional conditional 
-random field model to perform attribute labelling. The model was further improved
-\cite{Zhu2006} to model record segmentation and attribute labelling as a joint task.
+independent \gls{wde} was described by~\cite{Zhu2005}. The 2D CRF 
+model takes a webpage segmented into data blocks and employs a two dimensional \gls{crf}
+model to perform attribute labeling. The model was further improved 
+in~\cite{Zhu2006} to model record segmentation and attribute labeling as a joint task.
 Some of the limitations of early unsupervised methods 
-were also tackled by ObjectRunner \cite{Abdessalem2010} and AMBER \cite{Furche2012}. 
+were also addressed by ObjectRunner~\cite{Abdessalem2010} and DIADEM~\cite{Furche2012}. 
 These methods work by annotating webpages automatically with regular expressions, gazetteers and 
@@
 
-Web data extraction methods have undoubtedly improved extraordinarily, but
-as pointed by Schulz et al. \cite{Schulz2016}, it is difficult to compare the results 
-achieved by competing tools, and many seem to rely excessively on heuristic methods.
-In that regard, the recent advancements in sequence taggers may provide more robust and
-flexible extraction tools.
+\gls{wde} methods have undoubtedly improved extraordinarily, but
+as pointed by \cite{Schulz2016}, it is difficult to compare the results 
+achieved by competing tools. Also, many tools seem to rely excessively on heuristic methods.
+The recent advancements in sequence taggers may provide more robust and flexible techniques
+to address this problem.
+
+\subsection{Named Entity Recognition}
+\label{sec:ner}
+
+\gls{ner} is an important subtask in \gls{ie}.
+The \gls{ner} task was defined in the Third Message 
+Understanding Conference (MUC-3)~\cite{Sundheim1991}, where researchers were asked to extract
+entities from a news corpus about terrorist incidents. However, it was the 
+language-independent \gls{ner} shared task at the Conference 
+on Computational Natural Language Learning in 2003 ({CoNLL-2003})~\cite{KimSang2003},
+that established an enduring labeled dataset constructed with news texts from Reuters.
+Despite its reduced size and the limited variability of its documents, the {CoNLL-2003}
+dataset is still used to compare the performance of NER systems in English and 
+German.
+
+Sequence labeling for \gls{ner} and \gls{pos} tagging (labeling nouns, verbs, pronouns, etc.) 
+is very similar, so, many times, research articles that propose new methods for \gls{ner}
+also report results for the \gls{pos} Tagging task. And frequently, the best methods for 
+\gls{pos} Tagging are also the best methods for \gls{ner}.
+
+Traditionally, the \gls{ner} task was solved with generative models based on 
+\gls{hmm}s. The first appearance of \gls{hmm}s in the
+field of \gls{nlp} occurred in the mid-seventies and was
+primarily focused on the problem of Speech Recognition. 
+But in the late nineties, \gls{hmm}s also found important applications in \gls{ie}
+and \gls{ner} as in the works by~\cite{Bikel1999}, 
+\cite{Freitag1999}, and \cite{Freitag2000}.
+
+The problem with \gls{hmm}s is that they model the joint probability between 
+sequences of observations and labels $ P(X, Y) $, a harder problem than modelling the corresponding 
+conditional probability $ P(Y|X) $. They assume conditional independence for the observations $ X $, and
+therefore, they cannot handle overlapping features. This lack of flexibility led to the 
+development of discriminative approaches to sequence labeling based on the Maximum Entropy principle.
+
+Some early examples are Maximum Entropy Taggers for NER~\cite{Borthwick1998} and
+\gls{pos} Tagging~\cite{Ratnaparkhi1998}. The Maximum Entropy Markov Model~\cite{McCallum2000} 
+was developed just a while later, building up on the intuition of \gls{hmm}s combined with
+the flexibility of discriminative approaches. However, because of the label bias problem,
+this model was superseded by \gls{crf}s~\cite{Lafferty2001, McCallum2003}. 
+At this time, the best performing systems almost always resorted to external gazetteers 
+and hand-chosen features, as is the case for the {CoNLL-2003} winning model~\cite{Florian2003}.
+
+With the advancement of Machine Learning in recent years, we saw the rise
+of Neural Networks applied to sequence labeling. In 2011, \cite{Collobert2011} 
+introduced Neural Networks free of feature engineering to sequence labeling tasks,
+using \gls{cnn} over word embeddings with a CRF output layer to tackle 
+the problems of \gls{pos} tagging, Chunking, Semantic Role Labeling, and NER. A similar architecture 
+proposed in 2015 by~\cite{Huang2015}, the Bi-LSTM-CRF, replaced the \gls{cnn} in \cite{Collobert2011} 
+with a bidirectional LSTM, achieving better results.
+
+In 2016, further advancement to the NER models was achieved by incorporating character 
+representations at the bottom of the Bi-LSTM-CRF architecture to extract morphological 
+features from words automatically. The model by~\cite{Lample2016} uses a 
+bidirectional \gls{lstm} over character embeddings and the model by~\cite{Ma2016} uses a
+one dimensional \gls{cnn} with max pooling over character embeddings. Both models also 
+made use of pre-trained GloVe word embeddings, created by~\cite{Pennington2014}.
+
+Small improvements to NER systems have been made since then, primarily due to the 
+introduction of new word embeddings on variations of the Bi-LSTM-CRF architecture. From
+this group, we can mention ELMo~\cite{Peters2018}, BERT~\cite{Devlin2018}, and
+Flair~\cite{Akbik2018}. 
+All of them were introduced in 2018 and they differ primarily 
+in how to construct contextual embeddings from the internal states of a language 
+modelling neural network.
+
+To our knowledge, the best NER system up to this date (considering the performance in the
+{CoNLL-2003} dataset) is the bidirectional transformer model proposed by~\cite{Baevski2019} that uses
+a stack of self-attention modules and ELMo embeddings. Table~\ref{tab:ner_model_comparison}
+shows a comparison of the history of reported F1 scores in the English test set of the {CoNLL-2003} dataset
+for the NER systems that were mentioned in this section. Each of the mentioned systems held the 
+record for the task at a given time.
+
+\begin{table}[h]
+  \small
+  \begin{center}
+    \begin{tabular}{ lc }
+      \toprule
+      Model & Test F1 \\
+      \midrule
+       \cite{Florian2003} ({CoNLL-2003} Winner)    & 88.76 \\
+       \cite{Collobert2011}                        & 89.59 \\
+       \cite{Huang2015}                            & 90.10 \\
+       \cite{Lample2016}                           & 90.94 \\
+       \cite{Ma2016}                               & 91.21 \\
+       \cite{Peters2018}                           & 92.22 \\
+       \cite{Devlin2018}                           & 92.80 \\
+       \cite{Akbik2018}                            & 93.09 \\
+       \cite{Baevski2019}                          & 93.50 \\
+      \bottomrule
+    \end{tabular}
+  \end{center}
+  \caption{Model performances in the {CoNLL-2003} English test set.}
+  \label{tab:ner_model_comparison}
+\end{table}
 
@@
 
-Many web data extraction systems rely on hand crafted rules or gazetteers to perform
+Many \gls{wde} systems rely on hand crafted rules or gazetteers to perform
 attribute annotation. Machine learning approaches to NER can improve annotations of 
@@
 engineering. We explored many methods of Named Entity Recognition
-in the context of a web data extraction task. First, we discuss two traditional 
+in the context of a \gls{wde} task. First, we discuss two traditional 
 approaches: Hidden Markov Models, and Linear Chain Conditional Random Fields. Then,
@@
 
-HMM based taggers have been succesfully applied in many NLP and WDE tasks 
-\cite{Rabiner1990,Leek1997,Freitag2000}. They are incredibly fast to train and also they are very 
+HMM based taggers have been successfully applied in many NLP and WDE tasks 
+\cite{Rabiner1990,Freitag2000}. They are incredibly fast to train and also they are very 
 interpretable, making them a good choice for a first approximation. However, these models 
@@
 
-\subsubsection{Self training} \label{sssec:self_training}
-
-In the task of NER on HTML, there are useful features related to the HTML
-structure that can help in identifying named entities. On a given website, named
-entities tend to occur inside the same HTML tags. The HTML tag feature or other
-HTML features could easily be incorporated in the HMM. However, these 
-features are only useful inside a single website and they cannot be generalized, 
-because different websites use distinct HTML templates. 
-Therefore, we propose a self training strategy to obtain probabilities for
-these HTML features. It is implemented like this:
-
+\subsubsection{Self-Training for Hidden Markov Models} 
+\label{sssec:self_training}
+
+As described in Section~\ref{sec:hmm}. An \gls{hmm} for the sequence labeling task 
+has the form:
+\begin{equation}
+P(Y|X) \propto \prod_{i=1}^n P(x_i|y_i) P(y_i, y_{i-1})
+\end{equation}
+where $ X $ is a sequence of words and $ Y $ is a sequence of labels, both with size $ n $,
+and the initial probabilities $ P(y_1|y_0) $ follow a uniform distribution across all label 
+assignments.
+To construct this model from the data, we need to estimate the following probabilities:
+%
+\begin{itemize}
+  \item $ P(x_i|y_i) $: the emission probability of word $ x_i $ given label $ y_i $.
+  \item $ P(y_i|y_{i-1}) $: the transition probability of going from label $ y_{i-1} $ to label $ y_i $.
+\end{itemize}
+%
+We may consider $ x_i $ to be a binary feature vector $ x_i = \{ f_{i,1}, f_{i,2}, ..., f_{i,k} \} $
+as long as all the feature distributions are independent, conditioned on $ y_i $. That is:
+\begin{equation}
+P(x_i|y_i) = P(f_{i,1}, f_{i,2}, ..., f_{i,k}|y_i) = \prod_{j=1}^k P(f_{i,j}|y_i)
+\end{equation}
+%
+Also, due to the time invariance assumption, the $ P(f_{i,j}|y_i) $ probabilities 
+are independent of the timestep $ i $. Therefore, for each binary feature $ f_j $ we
+need only estimate the parameters $ \hat{P}(f_{j}|y) $, relative to each possible
+assignment of $ y $.
+The maximum likelihood estimators for these feature parameters can be obtained
+from their relative frequencies, just as we did in Section~\ref{sec:hmm} for single words 
+(Equation~\ref{eq:mle_words}). Then, for binary features:
+%
+\begin{equation}
+\hat{P}(f_{j}=1|y=l) = \frac{\text{Count}(f_{j}=1, y=l)}
+{\text{Count}(f_{j}=0, y=l) + \text{Count}(f_{j}=1, y=l)}
+\label{eq:feature_mle}
+\end{equation}
+%
+Where $ \text{Count}(f_{j}=1, y=l) $ is the number of times in the training set that
+feature $ f_j $ was equal to one when the actual label was $ l $ (the other counts follow the same logic).
+This approach yields good experimental results for textual features such as the capitalization
+of a word, but if we try to use HTML structural features such as the HTML tags, we will find that
+they are not very useful, contradicting our intuition.
+The problem is that there is not much similarity between the HTML structure in different web pages.
+For example, only because a named entity label occurs more often inside <div> tags
+in a page, that does not mean this is the case for most web pages. Consider for example a faculty web page 
+that shows researcher names in a table (<td> tags) in contrast to a web page that organizes researcher
+names in a list (<li> tags). If there are many cases like the former page in our training set, and we use the 
+HTML tag feature in a model that assigns labels to the latter page in our test set, we will probably get many 
+wrong predictions.
+Nonetheless, the HTML features are not useless. Inside a single web page, the HTML tag is a good predictor
+of the correct labels. Words with a similar HTML context tend to have similar labels. For example, words
+that happen together in a list have very similar HTML contexts and are very likely to belong to
+the same category. The question is how to obtain better parameter estimators for HTML features.
+
+Consider a set $ F^T $ of $ m $ textual features unrelated to the HTML structure:
+%
+\begin{equation*}
+F^T = \{ f^T_1, f^T_2, ..., f^T_m \}
+\end{equation*}
+%
+And a set $ F^H $ of $ k $ HTML features that are related to the HTML structure:
+%
+\begin{equation*}
+F^H = \{ f^H_1, f^H_2, ..., f^H_k \}
+\end{equation*}
+%
+Given a \gls{hmm} trained with only the first set of features $ F^T $,
+we can use this model to predict the labels for an unlabeled document, and then by simply replacing
+the actual labels in Equation~\ref{eq:feature_mle} with the predicted labels, we get:
+%
+\begin{equation}
+\hat{P}(f_{j}=1|y=l) = \frac{\text{Count}(f_{j}=1, \tilde{y}=l)}
+{\text{Count}(f_{j}=0, \tilde{y}=l) + \text{Count}(f_{j}=1, \tilde{y}=l)}
+\end{equation}
+%
+\begin{equation}
+\hat{P}(\text{Tag}=\text{<li>}|y=\text{I-PER}) = \frac{4}{4 + 0} = 1
+\end{equation}
+%
+Where $ \tilde{y} $ is the label predicted by the \gls{hmm} trained with only the textual features.
+We use this formulation to calculate feature probabilities for the HTML features only.
+And next, we incorporate the estimators for the HTML feature probabilities in the original \gls{hmm} 
+and predict the final labels with the whole set of features $ F^T \cup F^H $. 
+This process could be repeated multiple times. If the predictions are becoming more accurate with
+each iteration, then the estimates for the HTML feature probabilities are also likely to improve.
+
+In a simpler explanation, the self-training strategy can be divided into the following steps:
+%
 \begin{itemize}
@@
 \end{itemize}
-
-In theory, this strategy could be used with any sequence tagger, however
-retraining a classifier with new features can become prohibitively expensive.
-This strategy is only possible because the computation of HTML feature
-frequencies can be performed very quickly. This adds very little overhead 
-to the original HMM and improves precision and recall by a considerable 
-margin.
+%
+To understand why this strategy could help labeling named entities on the web, consider the 
+example shown in Figure~\ref{fig:self_training}. This example shows a snippet from a webpage 
+and how a naive \gls{hmm} would probably attribute 
+labels to each word. Despite being rather uncommon, North West is an actual person name,
+what becomes obvious in this case once we know the HTML context where it happens 
+(inside a list with other person names), but this is not so obvious if we consider the
+sentence in isolation. The naive \gls{hmm} could be improved if we calculated
+feature probabilities for the parent tags using proxies for the correct labels. We would find
+that four times in a total of six occurrences, the correct label for a word that happened inside
+a \textit{<li>} tag was \mbox{\textit{I-PER}}. By incorporating this knowledge in the model 
+using the self-training strategy, we would improve the probability that words North and West 
+were labeled correctly as a person name in this case.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.5\textwidth]{pics/self_training_example}
+  \caption{Example of a webpage snippet with labels attributed by a HMM.}
+  \label{fig:self_training}
+\end{figure}
+
+This strategy could possibly be incorporated in the Baum-Welch algorithm to provide a more 
+statistically solid argument for its effectiveness, but this heuristic
+already yields a consistent improvement to sequence labeling on the web. In theory, this 
+strategy could be used with any sequence tagger, however retraining a classifier with new features can 
+become prohibitively expensive in the case of CRFs or Neural Networks. 
+In HMMs, retraining the features
+is fast, because we assume feature independence and the maximum likelihood estimator can be 
+obtained with a simple closed form expression.
+
+% \subsubsection{Self training} 
+% \label{sssec:self_training}
+% 
+% In the task of NER on HTML, there are useful features related to the HTML
+% structure that can help in identifying named entities. In a given website, named
+% entities tend to occur inside the same HTML tags. The HTML tag feature or other
+% HTML features could easily be incorporated in the HMM. However, these 
+% features are only useful inside a single website and they cannot be generalized, 
+% because different websites use distinct HTML templates. 
+% Therefore, we propose a self-training strategy to obtain probabilities for
+% these HTML features. It is implemented like this:
+% 
+% \begin{itemize}
+% \item Train the HMM without any HTML features.
+% \item Compute labels for a website with the trained HMM.
+% \item Use the computed labels as a proxy for the actual labels in the 
+% website and estimate HTML feature frequencies for this website alone.
+% \item Recompute the labels now using the HTML feature probabilities.
+% \end{itemize}
+% 
+% In theory, this strategy could be used with any sequence tagger, however
+% retraining a classifier with new features can become prohibitively expensive.
+% This strategy is only possible because the computation of HTML feature
+% frequencies can be performed very quickly. This adds very little overhead 
+% to the original HMM and improves precision and recall by a considerable 
+% margin.
 
@@
 
-Recurrent neural networks (RNN) have been succesfully employed on numerous NLP tasks such as
-language modelling, POS tagging, speech recognition and NER. Different from feedforward 
-neural networks, RNNs can retain information in their internal state, making them more 
-suitable for processing sequences, and consequently for solving text related tasks. 
-Figure~\ref{fig:rnn_network} describes an RNN for sequence labeling unrolled through multiple 
-timesteps. At each timestep, the neural network computes a hidden state $ h_t $ using an input 
+At each timestep, the neural network computes a hidden state $ h_t $ using an input 
 vector $ x_t $ and the previous hidden state $ h_{t-1} $, that retains information from past 
@@
 
-This architecture achieved an F1 score of 90.10 on the English data from the ConLL-2003 
-NER shared task \cite{Sang2003}, in contrast to 85.17 for a bidirectional LSTM without 
+This architecture achieved an F1 score of 90.10 on the English data from the CoNLL-2003 
+NER shared task \cite{KimSang2003}, in contrast to 85.17 for a bidirectional LSTM without 
 a CRF layer. 
@@
 
-The convolutional neural netwrok receives character embeddings as inputs. The character 
+The convolutional neural network receives character embeddings as inputs. The character 
 representations generated by the CNN are combined with word level representations 
-and fed to the BI-LSTM-CRF in section \ref{sssec:lstm_crf}.
+and fed to the BI-LSTM-CRF described in section \ref{sssec:lstm_crf}.
 This architecture can learn morphological features that are very
 useful in the NER task, since similar named entities often present morphological similarities. 
-This architecture obtained an F1 score of 91.21 in the ConLL2003 dataset. In our experiments, 
+This architecture obtained an F1 score of 91.21 in the CoNLL2003 dataset. In our experiments, 
 the LSTM-CRF architecture with CNN character representations uses a one dimensional convolutional 
@@
 
-\section{NER on HTML Dataset}
-\label{sec:ner_dataset}
-
-We built a novel dataset to evaluate the performance of NER models
-on the web data extraction task. The task consists of finding researcher
-names in faculty listings from university web pages across the world. This would be a
-necessary step when linking researcher profiles from university websites to their entries
-in public databases such as DBLP \footnote{http://dblp.uni-trier.de/}. Unlike many
-information extraction datasets, each web page in the dataset comes from a different 
-website, and therefore has a different format, what makes many information
-extraction approaches impractical. The idea is to explore systems that are general 
-enough to allow efficient entity extraction from different sources while requiring
+\section{Researcher Name Extraction Dataset}
+\label{cha:dataset}
+
+This chapter describes the dataset used to evaluate the performance of sequence labeling models
+on the \gls{wde} task of \gls{rne}. We call it the \gls{rne} dataset.
+We attested experimentally that 
+models trained in a popular \gls{ner} dataset (the {CoNLL-2003} English dataset) do not perform 
+well in the \gls{rne} task and this is likely due to the differences
+between plain text and HTML. The lack of other \gls{ner} 
+datasets built for HTML name extraction imposes the need to construct a dataset specific for \gls{rne}.
+
+The \gls{rne} task consists of finding researcher names in faculty listings from university 
+webpages across the world, mainly from Computer Science departments.
+This would be a necessary step when linking researcher profiles from university 
+websites to their entries in public databases. Unlike many
+\gls{wde} datasets, each webpage in the \gls{rne} dataset comes from a different 
+website, and therefore has a different format, what makes many \gls{wde}
+approaches impractical. The idea is to explore systems that are general 
+enough to allow accurate entity extraction from different sources while requiring
 no supervision between different websites.
 
-This task is similar to labeling authors in comments or articles collected
-from different publishing platforms. Another similar task is NER on tweets,
-because of the character limitation that is comparable to what we find in 
-HTML text.
-
-We collected 145 computer science faculty pages from 42 different countries in
-multiple languages, although the English version was prefered when it was available.
-We gathered faculty web pages randomly in proportion to
+We collected 145 Computer Science and Engineering faculty pages from 42 different countries in
+multiple languages, although the English version was preferred when it was available.
+We gathered faculty webpages in proportion to
 the number of universities in each country\footnote{A detailed list of universities can
-be found in https://univ.cc/world.php}. Each HTML page was preprocessed and converted
-to the CONLL 2003 data format. That is, one word per line with empty lines representing
+be found in https://univ.cc/world.php}. 
+The dataset size was limited to a number of pages that could be viably labeled manually and
+that could still represent many different countries. 
+Also, university pages that contained 
+corrupt HTML or JavaScript code that performed lazy loading of data records were
+not included in this dataset.
+
+This chapter is divided as follows. Section~\ref{sec:data_description} describes the 
+dataset format and how it was split in
+three data files. 
+Section~\ref{sec:evaluation} describes how the evaluation of results in this 
+dataset was carried on. 
+Section~\ref{sec:dictionary} describes how we obtained a dictionary
+of relevant named entities for this dataset, and discusses some baselines.
+Lastly,
+Section~\ref{sec:conll_comparison} compares the characteristics of the \gls{rne} dataset
+with another popular \gls{ner} dataset, the {CoNLL-2003} English \gls{ner} dataset.
+
+\subsection{Data Description} 
+\label{sec:data_description}
+
+Each of the 145 faculty pages was preprocessed and converted
+to the {CoNLL-2003} data format. That is, one word per line with empty lines representing
 sentence boundaries. Sentence boundaries were determined by line break HTML tags
-(div, p, table, li, br, etc.) in contrast to inline tags (span, em, a, td, etc.). 
+(div, p, table, li, br, etc.) in contrast to inline tags (span, em, a, td, etc.). For example,
+the HTML sentence: 
+%
+\begin{quote}
+\centering
+<p>E. <b>Smith</b> is a <a href="/link">professor</a>.</p>
+\end{quote}
+%
+\noindent
+becomes:
+%
+\begin{quote}
+\centering
+E. Smith is a professor.
+\end{quote}
+%
 Sentences that were more than fifty tokens long were also split according to the
-punctuation.
-
-A proper HTML segmenter poses many challenges by itself. We wanted to evaluate 
-models without relying on any sophisticated data record segmentation system.
+punctuation. Some algorithms have trouble handling very big sentences, so we verified
+experimentally that fifty tokens provide a large enough context 
+and allow efficient training using a GPU. A few sentences in the dataset would be 
+more than a thousand tokens long if this step was not performed, what would make batch training
+for neural networks less efficient.
+
+% The algorithm used for sentence segmentation is described in
+% Appendix~\ref{app:html_segmenter}.
+
+A robust tool for HTML segmentation poses many challenges by itself, but the simple approach 
+adopted here has proved to be sufficient to perform \gls{rne} adequately. 
+Also, it is best to evaluate \gls{ner} models without relying on any sophisticated data 
+record segmentation system.
 In many cases, entity annotation may precede the segmentation
-phase on web data extraction methods, so annotators that are able to work 
-with raw HTML data allow for more flexible systems.
-
-Finally, all tokens were tagged using the IOB scheme put forward by
-Ramshaw and Marcus \cite{Ramshaw1999}.
-
-\subsection{Data}
+phase on \gls{wde} methods. Also, depending on the task (as is the case
+for researcher name extraction), a good annotator that is able to work 
+with raw HTML provides a good solution to the problem.
+
+Finally, all tokens were tagged using the IOB scheme put forward by~\cite{Ramshaw1999}
+and used in {CoNLL-2003}, this is:
+
+\begin{quote}
+Words tagged with O are outside of named entities
+and the I-XXX tag is used for words inside a
+named entity of type XXX. Whenever two entities of
+type XXX are immediately next to each other, the
+first word of the second entity will be tagged B-XXX
+in order to show that it starts another entity~\cite{KimSang2003}.
+\end{quote}
+
+The \gls{rne} dataset only has entities of type person PER, therefore a classifier has to
+label each token with one of the labels: O, B-PER, or I-PER. This is an example 
+sentence from the dataset:
+
+\begin{table}[h]
+  \small
+  \begin{center}
+    \begin{tabular}{ ll }
+      Token & Correct Label \\
+      \midrule
+      Kasper    & I-PER \\ 
+      Rasmussen & I-PER \\
+      Associate & O     \\
+      Professor & O     \\    
+      ,         & O     \\    
+      Royal     & O     \\    
+      Society   & O     \\    
+      Research  & O     \\    
+      Fellow    & O     \\    
+    \end{tabular}     
+  \end{center}
+\end{table}
+
+The \gls{rne} dataset was divided in training, validation and test sets, which are described in 
+Table~\ref{tab:dataset}. The sizes of the data files were chosen with more or 
+less the same proportion adopted in other sequence labeling datasets such
+as {CoNLL-2003}, that is described in Table~\ref{tab:conll}. The validation set 
+was used in the early stopping 
+validation strategy to avoid overfitting classifiers, but model performance 
+was only evaluated by comparing the performance in the test set, which is
+never observed during training.
 
@@
       Validation  & 30  & 8743  & 36757  & 1788  \\
-      Test        & 30 & 10399 & 44795  & 2708 \\
+      Test        & 30  & 10399 & 44795  & 2723  \\
+      \midrule
+      Total       & 145 & 43870 & 151821 & 10333 \\
       \bottomrule
@@
   \end{center}
-  \caption{Number of HTML pages, sentences and tokens in each data file}
+  \caption{Description of the data files in the RNE dataset.}
   \label{tab:dataset}
@@
 
-The dataset was divided in a training, validation and test set. Table \ref{tab:dataset} contains
-a description of the data files. The validation set was used in the early stopping validation strategy
-for the neural networks and CRF training, while the model performance was evaluated by comparing 
-results in the test set.
+\begin{table}[h]
+  \small
+  \begin{center}
+    \begin{tabular}{ llllllll }
+      \toprule
+      Data file & Documents & Sentences & Tokens & LOC & MISC & ORG & PER \\
+      \midrule
+      Training    & 946  & 14987 & 203621 & 7140 & 3438 & 6321 & 6600 \\  
+      Validation  & 216  & 3466  & 51362 & 1837 & 922 & 1341 & 1842  \\
+      Test        & 231  & 3684  & 46435 & 1668 & 702 & 1661 & 1617  \\
+      \midrule
+      Total       & 1393 & 22137 & 301418 & 10645 & 5062 & 9323 & 10059 \\
+      \bottomrule
+    \end{tabular}
+  \end{center}
+  \caption{Description of the {CoNLL-2003} English dataset}
+  \label{tab:conll}
+\end{table}
+
+Most webpages in this dataset are faculty directories with informative
+text in small passages, however long prose is not absent. 
+Size and structure varies wildly, therefore some documents 
+may contain up to a few hundred names whereas other documents may contain 
+only a dozen names. This difference in document size and characteristics 
+may be problematic when comparing different extraction systems, because a system 
+that performs well on some types of pages may perform poorly in other types.
+To avoid this problem, we tried to keep the proportion between the number of tokens
+and the number of documents roughly the same for all data files.
+
+\subsection{Evaluation}
+\label{sec:evaluation}
+
+The performance of classifiers in the \gls{rne} dataset was evaluated according to their Precision (P), Recall (R) and F-scores
+in the test set. The Precision and Recall 
+measures are defined in terms of the number of true positives, false negatives, and false 
+positives made by the classifier when extracting named entities. That is:
+
+\begin{equation*}
+\text{Precision} = \frac{\text{TruePos}}{\text{TruePos} + \text{FalsePos}}      
+\qquad
+\text{Recall} = \frac{\text{TruePos}}{\text{TruePos} + \text{FalseNeg}}
+\end{equation*}
+
+Precision accounts for the proportion of named entities found by the model that are 
+correct relative to all predicted named entities.
+Recall is the proportion of named entities correctly predicted by the model relative to
+all named entities in the dataset. Precision measures Type I errors 
+(false positives) and Recall measures Type II errors (false negatives). Partial matches are
+not considered, so a classification only counts as a true positive if the entire named entity
+has been correctly extracted. Additionally, the F-score, proposed by~\cite{Rijsbergen1979}, 
+is a composite measure that combines Precision and Recall, defined as:
+
+\begin{equation}
+F_{\beta} = (1 + \beta^2) \cdot \frac{\text{Precision} \cdot \text{Recall}}{(\beta^2 \cdot \text{Precision}) + \text{Recall}}
+\label{eq:fscore_formula}
+\end{equation}
+
+The choice of $ \beta $ depends on the relative importance attributed to Precision over Recall.
+This formula ``measures the effectiveness of retrieval with respect to a user who attaches 
+$ \beta$ times as much importance to recall as precision''~\cite{Rijsbergen1979}. A common choice
+for the value of $ \beta $ is $ 1 $, this measure is called the $ F_1 $-score (F1). That is, we attribute 
+as much importance to Recall as to Precision.
+
+In our experiments, we considered the Precision, Recall and $ F_1 $-scores over the entire 
+data files. Considering that each webpage has a different number of named entities,
+this naturally privileges models that work well for pages with more named entities. 
+A different approach might be to consider the averaged Precision, Recall and $ F_1 $-scores 
+per webpage, privileging systems that have more regularity between different websites. However, 
+this approach would cover other deficiencies. That is, the impact of errors in pages with many 
+named entities would diminish and the impact of errors in pages with few named entities would
+increase. So, the former approach was preferred.
+
+\subsection{Dictionary}
+\label{sec:dictionary}
+
+A dictionary of named entities can be a powerful aid to sequence labeling systems,
+especially when considering traditional statistical methods. For the \gls{rne} task, we extracted 
+a list of 1,595,771 researcher names from the DBLP database and annotated tokens in the
+\gls{rne} dataset with exact and partial match tags. That is, if a sequence of tokens
+corresponded exactly to a name from the DBLP list, the entire sequence was annotated as 
+an exact match. Otherwise, if only some tokens in the sequence matched a name from the DBLP
+list partially, the matching tokens were annotated with a partial match tag. This dictionary
+was used by some of the models that will be discussed in the experiments chapter, however it 
+must be stated that one of the main advantages of Deep Neural Networks relative to other
+approaches is the fact that they can perform well even without the aid of a dictionary.
+
+\begin{table}[h]
+  \small
+  \begin{center}
+    \begin{tabular}{ lllll }
+      \toprule
+      Data file & Precision & Recall & F1 & Correct names \\
+      \midrule
+      Training   & 0.7316 & 0.2303 & 0.3504 & 1341 of 5822 \\ 
+      Validation & 0.8474 & 0.2858 & 0.4274 & 511 of 1788 \\ 
+      Test       & 0.8717 & 0.3287 & 0.4773 & 890 of 2708 \\ 
+      \bottomrule
+    \end{tabular}
+  \end{center}
+  \caption{DBLP dictionary coverage in each data file of the RNE dataset.}
+  \label{tab:gazetteer}
+\end{table}
+
+To understand how this dictionary can be useful for some models in the \gls{rne}, 
+we consider the Precision, Recall and $ F_1 $-scores for an exact dictionary matching 
+strategy in each \gls{rne} data file. The results are described in 
+Table~\ref{tab:gazetteer}. These results also provide a baseline with which to compare
+other methods of sequence labeling. 
+The reported performance was obtained by only extracting named entities that corresponded to an exact 
+match. Any useful extraction method should at least improve upon this approach.
+Recall is very low because the dictionary is incomplete and precision falls short of
+top performing extraction methods. This last result is surprising since we are only extracting 
+exact matches. The reason for the low precision is that exact dictionary matches may actually 
+only correspond to partial matches in the dataset. For example, if the dictionary has an entry
+for "Ann Smith", it may partially overlap an entry in the dataset for "Mary Ann Smith", yielding
+a false positive.
+
+\subsection{Comparison with {CoNLL-2003}}
+\label{sec:conll_comparison}
+
+The {CoNLL-2003} dataset introduced in the \gls{ner}
+shared-task in 2003 is frequently used to attest 
+the performance of state-of-the-art sequence labeling systems~\cite{Huang2015,Lample2016,Ma2016,Peters2018}. 
+The English data is composed of news stories extracted from the Reuters Corpus, and 
+provides annotations for four types of entities: people (PER), organizations (ORG), 
+locations (LOC), and miscellaneous (MISC), which includes entities that cannot be 
+classified in one of the former groups. The statistics for the {CoNLL-2003} dataset 
+were already described in Table~\ref{tab:conll}.
+
+Considering this dataset, it comes to mind why exactly do we need a \gls{ner} dataset for HTML. 
+If the {CoNLL-2003} English dataset is used to both train and evaluate 
+state-of-the-art models, it is to be expected that models trained in this dataset will
+be able to extract the same named entities in other documents with reasonable 
+effectiveness. However, this is hardly the case. By intuition, we know that tabular HTML 
+documents, such as faculty listings, are very different from plain text. But now, having a
+labeled dataset for \gls{ner} on HTML, we can understand how different they really are.
+
+We trained three classifiers to perform the task of person name extraction using
+the {CoNLL-2003} training set. The {CoNLL-2003} dataset was relabeled so that classifiers only had to extract
+person entities (PER labels), thus other entity types (LOC, ORG, and MISC) were relabeled as
+not an entity (O label). We trained the classifiers with the relabeled {CoNLL-2003} training set,
+and validated the results with the relabeled validation set. The models were tested with the relabeled {CoNLL-2003}
+test set and the \gls{rne} test set.
+In Table~\ref{tab:conll_to_ner_on_html}, we present the results for a first order \gls{hmm}, 
+a Linear Chain \gls{crf}, and a Bi-LSTM-CRF classifier with GloVe embeddings~\cite{Huang2015} in the 
+aforementioned experimental setting.
+
+\begin{table}[h]
+  \small
+  \begin{center}
+    \begin{tabular}{ lllllll }
+      \toprule
+      \multirow{2}{*}{Model} & \multicolumn{3}{c}{CoNLL-2003} & \multicolumn{3}{c}{\gls{rne}} \\
+                             & \multicolumn{1}{c}{P} & \multicolumn{1}{c}{R} & \multicolumn{1}{c}{F1}
+                             & \multicolumn{1}{c}{P} & \multicolumn{1}{c}{R} & \multicolumn{1}{c}{F1} \\
+      \midrule
+      HMM         & 0.777 & 0.452 & 0.571 & 0.189 & 0.180 & 0.184 \\
+      CRF         & 0.774 & 0.754 & 0.764 & 0.138 & 0.129 & 0.133 \\
+      Bi-LSTM-CRF & 0.969 & 0.931 & 0.950 & 0.282 & 0.258 & 0.269 \\
+      \bottomrule
+    \end{tabular}
+  \end{center}
+  \caption{
+    Performance of three classifiers trained with the {CoNLL-2003} training set and tested in
+    the CoNLL-2003 and RNE test sets.
+  }
+  \label{tab:conll_to_ner_on_html}
+\end{table}
+
+The very low $ F_1 $-score obtained by all models in the \gls{rne} test set is worse than the established
+dictionary baseline. We cannot use these results to properly compare the relative performances 
+between the models (this topic will be explored in the next chapter), but it is possible to conclude
+that machine learning models trained in plain text do not necessarily perform very well in HTML 
+extraction tasks. The Bi-LSTM-CRF model obtained a 0.269 $ F_1 $-score in the \gls{rne} test
+set, what is surprising considering that it is a very efficient approach to sequence labeling in plain 
+text. By looking at some of its mistakes we can shed some light on this result. The Bi-LSTM-CRF model
+extracted "Dean Emeritus" and "14101 INF" as names, and it missed the last names in "George E. Elliott"
+and "Carl J. Galligan". These mistakes are representative of some of the major flaws with the systems
+trained with the CoNLL-2003 training set. The names in the \gls{rne} dataset 
+are usually longer than in CoNLL-2003 and the word distributions are vastly different, what may
+account for some of the mistakes of the Bi-LSTM-CRF model.
+
+Lets consider some other differences between both datasets. 
+The number of documents in the \gls{rne} dataset is much smaller: only 145 against 
+1393. However, the number of sentences in the \gls{rne}
+dataset is higher: 43870 against 22137. Also, the number of tokens in the \gls{rne} dataset
+is roughly half the number present in the {CoNLL-2003} dataset. These numbers show that 
+the HTML documents in the \gls{rne} dataset are longer than news 
+stories and, more importantly, they are composed of much shorter sentences when compared 
+to the text from news corpora (3.46 words per sentence in the \gls{rne} dataset
+against 13.62 words per sentence in {CoNLL-2003}). Most faculty webpages have a lot of 
+boilerplate text that contributes to their size, while the news stories in {CoNLL-2003}
+are usually rather short. These numbers show that HTML provides far less context to be made 
+use by sequence models, what imposes the need to seek other sources of evidence in addition to 
+the text, such as dictionaries and the HTML structure.
+
+Another aspect that differs among the NER datasets is the word distributions. Word frequencies
+tend to vary considerably in documents with different topics. Table~\ref{tab:frequent_words}
+shows the ten most frequent words for each dataset, including punctuation signs. Punctuation
+signs are frequently present in proper names, as in: Mary B. Smith, Susan (Susie) Williams, John Al-Azzawi, etc.
+Also, punctuation signs can be useful to detect boundaries between named entities.
+The {CoNLL-2003} English dataset contains a more generic selection of terms whereas the 
+subject of the \gls{rne} dataset becomes evident with words such as "professor" and "university" 
+happening with a high frequency in the corpus. Also, punctuation signs are much more frequent in
+the \gls{rne} dataset.
+
+Lastly, in Figure~\ref{fig:word_frequency_plot}
+we plot the word frequencies for the hundred most frequent words in the {CoNLL-2003} and 
+the \gls{rne} datasets. In both plots we have a few very frequent words and a long tail of
+infrequent words. Most named entities are located in this long tail, therefore a good sequence
+labeling method needs to be able to handle the labeling of infrequent tokens effectively. 
+The probabilities attributed to unseen tokens is another aspect where models vary significantly 
+between different datasets.
+
+\begin{table}[h]
+  \small
+  \begin{center}
+    \begin{tabular}{ llll }
+      \toprule
+      \multicolumn{2}{c}{CoNLL-2003} & \multicolumn{2}{c}{\gls{rne}} \\
+      \multicolumn{1}{c}{Word} & \multicolumn{1}{c}{Frequency} &
+      \multicolumn{1}{c}{Word} & \multicolumn{1}{c}{Frequency} \\
+      \midrule
+      the & 12310 & , & 10439      \\
+      , & 10876 & - & 8140         \\
+      . & 10874 & ) & 3655         \\
+      of & 5502 & ( & 3641         \\
+      in & 5405 & : & 3484         \\
+      to & 5129 & of & 3345        \\
+      a & 4731 & and & 2499        \\
+      ( & 4226 & professor & 2456  \\
+      ) & 4225 & university & 1611 \\
+      and & 4223 & research & 1315 \\
+      \bottomrule
+    \end{tabular}
+  \end{center}
+  \caption{Ten most frequent words for the {CoNLL-2003} dataset and the RNE dataset.}
+  \label{tab:frequent_words}
+\end{table}
+
+\begin{figure}[h!]
+  \begin{center}
+    \begin{tikzpicture}
+      \begin{axis}[
+        title={Word frequencies},
+        xmin=0, xmax=100,
+        ymin=0, ymax=12000,
+        ylabel={Frequency},
+        xlabel={Words (most to least frequent)},
+        ymajorgrids=true,
+        grid style=dashed,
+        legend pos=north east,
+        % scaled y ticks=false,
+      ]
+
+      \addplot[color=blue, color=blue] coordinates {
+        (0,12310)(1,10876)(2,10874)(3,5502)(4,5405)(5,5129)(6,4731)(7,4226)(8,4225)(9,4223)(10,3239)(11,3115)(12,2694)(13,2339)(14,2109)(15,1866)(16,1845)(17,1679)(18,1593)(19,1342)(20,1267)(21,1264)(22,1232)(23,1212)(24,1166)(25,1146)(26,1113)(27,1082)(28,1057)(29,984)(30,973)(31,920)(32,867)(33,841)(34,804)(35,796)(36,786)(37,786)(38,780)(39,768)(40,754)(41,738)(42,656)(43,645)(44,643)(45,636)(46,591)(47,584)(48,579)(49,567)(50,558)(51,546)(52,545)(53,524)(54,523)(55,517)(56,512)(57,510)(58,486)(59,486)(60,474)(61,470)(62,470)(63,457)(64,448)(65,444)(66,442)(67,441)(68,419)(69,415)(70,413)(71,405)(72,402)(73,386)(74,377)(75,375)(76,369)(77,358)(78,354)(79,348)(80,346)(81,340)(82,338)(83,328)(84,327)(85,325)(86,320)(87,319)(88,310)(89,308)(90,300)(91,296)(92,293)(93,292)(94,291)(95,289)(96,278)(97,272)(98,271)(99,271)
+      };
+      \addplot[color=red, color=red] coordinates {
+        (0,10439)(1,8140)(2,3655)(3,3641)(4,3484)(5,3345)(6,2499)(7,2456)(8,1611)(9,1315)(10,1053)(11,1046)(12,1006)(13,963)(14,897)(15,863)(16,849)(17,838)(18,773)(19,749)(20,720)(21,713)(22,695)(23,668)(24,652)(25,626)(26,602)(27,593)(28,581)(29,580)(30,569)(31,553)(32,539)(33,527)(34,520)(35,499)(36,492)(37,490)(38,469)(39,454)(40,446)(41,444)(42,429)(43,429)(44,422)(45,420)(46,419)(47,403)(48,403)(49,394)(50,390)(51,379)(52,379)(53,371)(54,362)(55,356)(56,355)(57,346)(58,342)(59,337)(60,324)(61,318)(62,314)(63,311)(64,298)(65,297)(66,288)(67,282)(68,279)(69,265)(70,263)(71,259)(72,259)(73,258)(74,258)(75,254)(76,250)(77,245)(78,243)(79,236)(80,236)(81,235)(82,234)(83,232)(84,225)(85,219)(86,218)(87,215)(88,212)(89,212)(90,210)(91,209)(92,208)(93,208)(94,205)(95,198)(96,197)(97,196)(98,191)(99,191)
+      };
+      \legend{CoNLL-2003, \gls{rne}};
+
+      \end{axis}
+    \end{tikzpicture}
+    \caption{
+      Word frequencies plot for the {CoNLL-2003} dataset and the RNE dataset.
+    }
+    \label{fig:word_frequency_plot}
+  \end{center}
+\end{figure}
 
@@
 We conducted experiments to evaluate sequence labeling methods of named entity 
-recognition on HTML in the context of web data extraction using the dataset 
+recognition on HTML in the context of \gls{wde} using the dataset 
 described in Section~\ref{sec:ner_dataset}. The tested models are described in
@@
 first experiment. So, when these features are added explicitly, the differences 
-in performance become less noticeable.
-
-Finally, all results presented in this section considered a dataset with a minimum
-amount of preprocessing and no trimming strategy to delimitate named entities. In many cases, 
-a model may miss a few named entities because it includes a punctuation sign
-or an honorific at the start or end of a named entity. Some simple strategies could 
-be used to boost the F1-score modestly.
+in performance between different neural models become less noticeable.
 
@@
 
-In this paper we compared the performance of different sequence models in the task of
-NER on HTML, introducing a novel dataset that is publicly available. We showed that
-LSTM-CRF neural networks with LSTM-based character representations can be employed 
-effectively to solve this task while demanding no feature engineering (F1-score of 0.8867).
+Machine-learning-based sequence labeling models provide a flexible approach to \gls{wde}, 
+in contrast to more traditional methods. In simple cases, a neural
+named entity tagger may be sufficient to solve the entire data extraction task. In 
+other cases, the sequence tagger remains an important part of the \gls{wde} 
+system, as it performs attribute labeling on data records with accuracy and flexibility.
+
+In this article, we compared the performance of different sequence models on the task of
+named entity recognition on HTML, introducing a novel dataset that is publicly available. 
 We found that there are two components to the most successful models: neural based character 
-representations constructed with convolutional neural networks or bidirectional LSTMs and joint 
-modelling of the output labels provided by a linear chain CRF output layer. The effective recognition 
-of named entities on HTML is an essential step in most general web data extraction methods. 
-However it may also point to the possibility of constructing a truly flexible approach to
-cross domain data extraction based on neural networks.
-
-% \bibliographystyle{unsrt}
+representations that extract morphological features automatically, and the joint modelling 
+of output labels.
+
+We showed that a BI-LSTM-CRF neural network with LSTM-based character representations can 
+be employed effectively to solve a \gls{wde} task, achieving an F1-score of 
+0.8867 with no feature engineering on the faculty listings dataset.
+
+The effective recognition of named entities on HTML is an essential step in most general 
+\gls{wde} methods. The accuracy achieved by deep neural architectures even
+on webpages that are very different from the plain text for which these architectures 
+were initially designed shows the potential for a truly flexible approach to cross domain 
+\gls{wde}.
+
+% \bibliographystyle{named}
 % \bibliography{bibfile}
 
+% \begin{thebibliography}{}
+%   \bibitem[\protect\citename{Akmajian and Lehrer }1976]{akm76}
+%   Akmajian, A. and Lehrer, A. (1976) NP-like quantifiers and the
+%   problem of determining the head of an NP. {\it Linguistic
+%   Analysis\/} {\bf 2}: 295--313.
+%   \bibitem[\protect\citename{Huddleston }1984]{hud84}
+%   Huddleston, Rodney. (1984) {\it Introduction to the Grammar of
+%   English}. Cambridge: Cambridge University Press.
+%   \bibitem[\protect\citename{McCord }1990]{mcc90}
+%   McCord, Michael C. (1990) Slot grammar: a system for simpler
+%   construction of practical natural language grammars. In R.
+%   Studer (ed.), {\it Natural Language and Logic: International
+%   Scientific Symposium}, pp.~118--45. Lecture Notes in Computer
+%   Science. Berlin: Springer-Verlag.
+%   \bibitem[\protect\citename{Salton {\it et al.}\ }1990]{sal90}
+%   Salton, Gerald, Zhao, Zhongnan and Buckley, Chris. (1990)
+%   A simple syntactic approach for the generation of indexing
+%   phrases. Technical Report 90--1137, Department of Computer
+%   Science, Cornell University.
+% \end{thebibliography}
+
+\bibliographystyle{apa}
+
+% \cite{Zhu2005,Zhu2006,Abdessalem2010,Furche2012,Furche2012a}. Usually,
+
 \begin{thebibliography}{}
-  \bibitem[\protect\citename{Akmajian and Lehrer }1976]{Crescenzi2001}
-   Akmajian, A. and Lehrer, A. (1976) NP-like quantifiers and the
-   problem of determining the head of an NP. {\it Linguistic
-   Analysis\/} {\bf 2}: 295--313.
-  \bibitem[\protect\citename{Akmajian and Lehrer }1976]{Arasu2003}
-   Akmajian, A. and Lehrer, A. (1976) NP-like quantifiers and the
-   problem of determining the head of an NP. {\it Linguistic
-   Analysis\/} {\bf 2}: 295--313.
+
+\bibitem[\protect\citename{Kushmerick }2000]{Kushmerick2000}
+Kushmerick, N. (2000) 
+Wrapper induction: efficiency and expressiveness.
+{\it Artificial Intelligence\/} 
+{\bf 118(1-2)}: 15--68.
+
+\bibitem[\protect\citename{Muslea, Minton and Knoblock }1999]{Muslea1999}
+Muslea I., Minton S., and Knoblock C. (1999) 
+A Hierarchical Approach to Wrapper Induction.
+In {\it Proceedings of the Third Annual Conference on Autonomous Agents}, 
+pp.~190--197, New York: ACM.
+
+\bibitem[\protect\citename{Hsu and Dung }{1998}]{Hsu1998}
+Hsu, Chun-Nan and Dung Ming-Tzung. (1998) 
+Generating finite-state transducers for semi-structured data extraction from the Web.
+{\it Information Systems \/}, 
+{\bf 23(8)}: 521--538.
+
+\bibitem[\protect\citename{Crescenzi, Mecca, and Merialdo }2001]{Crescenzi2001}
+Crescenzi V., Mecca G., and Merialdo P. (2001)
+Roadrunner: Towards automatic data extraction from large web sites.
+In {\it Proceedings of the 27th International Conference on Very Large Data Bases}, 
+pp. 109--118.
+
+\bibitem[\protect\citename{Zhu, Nie, Wen, Zhang, and Ma }2005]{Zhu2005}
+Zhu J., Nie Z., Wen J., Zhang B., and Ma W. (2005)
+2D Conditional Random Fields for Web Information Extraction.
+In {\it Proceedings of the 22Nd International Conference on Machine Learning (ICML '05)}, 
+pp.~1044--1051, New York: ACM.
+
+\bibitem[\protect\citename{Zhu, Nie, Wen, Zhang, and Ma }2006]{Zhu2006}
+Zhu J., Nie Z., Wen J., Zhang B., and Ma W. (2006)
+Simultaneous Record Detection and Attribute Labeling in Web Data Extraction.
+In {\it Proceedings of the 12th ACM SIGKDD International Conference on Knowledge Discovery and Data Mining (KDD '06)}, 
+pp.~494--503, New York: ACM.
+
+\bibitem[\protect\citename{Abdessalem T., Cautis B., and Derouiche N. }{2010}]{Abdessalem2010}
+Abdessalem T., Cautis B., and Derouiche N. (2010)
+ObjectRunner: Lightweight, targeted extraction and querying of structured web data.
+In {\it Proceedings of the VLDB Endowment}
+{\bf 3(1-2)}: 1585--1588.
+
+\bibitem[\protect\citename{Furche {\it et al.}\ }{2012}]{Furche2012}
+Furche, T., Gottlob, G., Grasso, G., Gunes, O., Guo, X., Kravchenko, A., Orsi, G., Schallhart, C., Sellers, A., and Wang, C. (2012)
+Diadem: Domain-centric, intelligent, automated data extraction methodology.
+In {\it Proceedings of the 21st International Conference on World Wide Web (WWW '12 Companion)}, 
+pp. 267--270, New York, ACM.
+
+\bibitem[\protect\citename{Collobert, Weston, Bottou, Karlen, Kavukcuoglu, and Kuksa }2011]{Collobert2011}
+Collobert, R., Weston, J., Bottou, L., Karlen, M., Kavukcuoglu, K. and Kuksa P. (2011)
+Natural language processing (almost) from scratch.
+{\it Journal of Machine Learning Research}
+{\bf 12}: 2493--2537.
+
+\bibitem[\protect\citename{Ribas, Ribeiro-Neto, de Souza e Silva, Ueda, and Ziviani }2015]{Ribas2015}
+Ribas, S., Ribeiro-Neto, B., de Souza e Silva, E., Ueda, A., and Ziviani, N. (2015)
+In {\it Proceedings of the 24th International Conference on World Wide Web (WWW '15 Companion)}, 
+pp. 603--608, New York, ACM.
+
+\bibitem[\protect\citename{Adelberg }1998]{Adelberg1998}
+Adelberg B. (1998)
+NoDoSE---a tool for semi-automatically extracting structured and semistructured data from text documents.
+{\it ACM SIGMOD Record} 
+{\bf 27(2)}: 283--294.
+
+\bibitem[\protect\citename{Laender, Ribeiro-Neto, da Silva }2002a]{Laender2002a}
+Laender, A., Ribeiro-Neto, B. and da Silva, A. (2002)
+DEByE - Date extraction by example.
+{\it Data Knowledge Engineering}
+{\bf 40(2)}: 121--154.
+
+\bibitem[\protect\citename{Califf and Mooney }1999]{Califf1999}
+Califf, M. and Mooney, R. (1999)
+Relational learning of pattern-match rules for information extraction.
+{\it Computational Linguistics}
+{\bf 4}: 9--15.
+
+\bibitem[\protect\citename{Laender, Ribeiro-Neto, da Silva and Teixeira }2002b]{Laender2002b}
+Laender, A., Ribeiro-Neto, B., da Silva, A., and Teixeira, J. (2002)
+A brief survey of web data extraction tools.
+{\it SIGMOD Record}
+{\bf 31(2)}: 84--93.
+
+\bibitem[\protect\citename{Hammer, McHugh and Garcia-Molin }1997]{Hammer1997}
+Hammer, J., McHugh, J. and Garcia-Molin, H. (1997)
+Semistructured Data: The TSIMMIS Experience.
+In {\it Proceedings of the First East-European Conference on Advances in Databases and Information Systems (ADBIS'97)}
+pp 22--22, Swindon, UK, BCS Learning \& Development Ltd.
+
+\bibitem[\protect\citename{Arocena and Mendelzon}{1998}]{Arocena1999}
+Gustavo~O. Arocena and Alberto~O. Mendelzon.
+\newblock {WebOQL}: Restructuring documents, databases, and webs.
+\newblock In {\em Proceedings of the Fourteenth International Conference on
+  Data Engineering}, ICDE '98, pages 24--33, Washington, DC, USA, 1998. IEEE
+  Computer Society.
+
+\bibitem[\protect\citename{Akbik \bgroup \em et al.\egroup
+  }{2018}]{Akbik2018}
+Alan Akbik, Duncan Blythe, and Roland Vollgraf.
+\newblock Contextual string embeddings for sequence labeling.
+\newblock In {\em Proceedings of the 27th International Conference on
+  Computational Linguistics}, pages 1638--1649, Santa Fe, New Mexico, USA,
+  August 2018. Association for Computational Linguistics.
+
+\bibitem[\protect\citename{Baevski \bgroup \em et al.\egroup
+  }{2019}]{Baevski2019}
+Alexei Baevski, Sergey Edunov, Yinhan Liu, Luke Zettlemoyer, and Michael Auli.
+\newblock Cloze-driven pretraining of self-attention networks.
+\newblock {\em Preprint arXiv:1903.07785}, 2019.
+
+\bibitem[\protect\citename{Bikel \bgroup \em et al.\egroup
+  }{1999}]{Bikel1999}
+Daniel~M. Bikel, Richard Schwartz, and Ralph~M. Weischedel.
+\newblock An algorithm that learns what's in a name.
+\newblock {\em Machine Learning}, 34(1):211--231, Feb 1999.
+
+\bibitem[\protect\citename{Borthwick \bgroup \em et al.\egroup
+  }{1998}]{Borthwick1998}
+Andrew Borthwick, John Sterling, Eugene Agichtein, and Ralph Grishman.
+\newblock Exploiting diverse knowledge sources via maximum entropy in named
+  entity recognition.
+\newblock In {\em Proceedings of the Sixth Workshop on Very Large Corpora},
+  pages 152--160. Association for Computational Linguistics, 1998.
+
+\bibitem[\protect\citename{Caruana \bgroup \em et al.\egroup
+  }{2000}]{Caruana2000}
+Rich Caruana, Steve Lawrence, and Lee Giles.
+\newblock Overfitting in neural nets: Backpropagation, conjugate gradient, and
+  early stopping.
+\newblock In {\em Proceedings of the 13th International Conference on Neural
+  Information Processing Systems}, NIPS'00, pages 381--387, Cambridge, MA, USA,
+  2000. MIT Press.
+
+\bibitem[\protect\citename{Chang and Kuo}{2004}]{Chang2004}
+Chia~Hui Chang and Shih~Chien Kuo.
+\newblock {OLERA: Semisupervised Web-data extraction with visual support}.
+\newblock {\em IEEE Intelligent Systems}, 19(6):56--64, 2004.
+
+\bibitem[\protect\citename{Chang \bgroup \em et al.\egroup
+  }{2001}]{Chang2001}
+C.H. Chang, C.H. Chang, S.C. Lui, and S.C. Lui.
+\newblock {IEPAD: information extraction based on pattern discovery}.
+\newblock {\em Proceedings of the 10th international conference on World Wide
+  Web}, pages 681--688, 2001.
+
+\bibitem[\protect\citename{Chang \bgroup \em et al.\egroup
+  }{2006}]{Chang2006}
+Chia-Hui Chang, Mohammed Kayed, Moheb~Ramzy Girgis, and Khaled~F Shaalan.
+\newblock {A Survey of Web Information Extraction Systems}.
+\newblock {\em IEEE Transactions on Knowledge and Data Engineering},
+  18(10):1411--1428, 2006.
+
+\bibitem[\protect\citename{Devlin \bgroup \em et al.\egroup
+  }{2018}]{Devlin2018}
+Jacob Devlin, Ming-Wei Chang, Kenton Lee, and Kristina Toutanova.
+\newblock {BERT}: Pre-training of deep bidirectional transformers for language
+  understanding.
+\newblock {\em Preprint arXiv:1810.04805}, 2018.
+
+\bibitem[\protect\citename{Dong \bgroup \em et al.\egroup
+  }{2014}]{Dong2014}
+Xin Dong, Evgeniy Gabrilovich, Geremy Heitz, Wilko Horn, Ni~Lao, Kevin Murphy,
+  Thomas Strohmann, Shaohua Sun, and Wei Zhang.
+\newblock {Knowledge Vault: a web-scale approach to probabilistic knowledge
+  fusion}.
+\newblock {\em Proceedings of the 20th ACM SIGKDD international conference on
+  Knowledge discovery and data mining - KDD '14}, pages 601--610, 2014.
+
+\bibitem[\protect\citename{Ferrara and Baumgartner}{2011}]{Ferrara2011}
+Emilio Ferrara and Robert Baumgartner.
+\newblock {Automatic wrapper adaptation by tree edit distance matching}.
+\newblock {\em Smart Innovation, Systems and Technologies}, 8:41--54, 2011.
+
+\bibitem[\protect\citename{Ferrara \bgroup \em et al.\egroup
+  }{2014}]{Ferrara2014}
+Emilio Ferrara, Pasquale {De Meo}, Giacomo Fiumara, and Robert Baumgartner.
+\newblock {Web data extraction, applications and techniques: A survey}.
+\newblock {\em Knowledge-Based Systems}, 70:301--323, 2014.
+
+\bibitem[\protect\citename{Florian \bgroup \em et al.\egroup
+  }{2003}]{Florian2003}
+Radu Florian, Abe Ittycheriah, Hongyan Jing, and Tong Zhang.
+\newblock Named entity recognition through classifier combination.
+\newblock In {\em Proceedings of the Seventh Conference on Natural Language
+  Learning at HLT-NAACL 2003}, pages 168--171, 2003.
+
+\bibitem[\protect\citename{Freitag and Mccallum}{1999}]{Freitag1999}
+Dayne Freitag and Andrew~Kachites Mccallum.
+\newblock {Information Extraction with HMMs and Shrinkage}.
+\newblock In {\em Proceedings of the AAAI-99 Workshop on Machine Learning for
+  Information Extraction}, pages 31--36. AAAI Press, 2 1999.
+
+\bibitem[\protect\citename{Freitag and McCallum}{2000}]{Freitag2000}
+Dayne Freitag and Andrew McCallum.
+\newblock {Information Extraction with HMM Structures Learned by Stochastic
+  Optimization}.
+\newblock In {\em Proceedings of the Seventeenth National Conference on
+  Artificial Intelligence and Twelfth Conference on Innovative Applications of
+  Artificial Intelligence}, pages 584--589. AAAI Press, 2000.
+
+\bibitem[\protect\citename{Freitag}{1998}]{Freitag1998}
+Dayne Freitag.
+\newblock {Information Extraction from HTML: Application of a General Machine
+  Learning Approach}.
+\newblock In {\em Proceedings of the Fifteenth National/Tenth Conference on
+  Artificial Intelligence/Innovative Applications of Artificial Intelligence},
+  AAAI '98/IAAI '98, pages 517--523, Menlo Park, CA, USA, 1998. American
+  Association for Artificial Intelligence.
+
+\bibitem[\protect\citename{Hochreiter and
+  Schmidhuber}{1997}]{Hochreiter1997}
+Sepp Hochreiter and J\"{u}rgen Schmidhuber.
+\newblock Long short-term memory.
+\newblock {\em Neural Computation}, 9(8):1735--1780, November 1997.
+
+\bibitem[\protect\citename{Hogue and Karger}{2005}]{Hogue2005}
+Andrew Hogue and David Karger.
+\newblock {Thresher: Automating the Unwrapping of Semantic Content from the
+  World Wide Web}.
+\newblock In {\em Proceedings of the 14th International Conference on World
+  Wide Web}, WWW '05, pages 86--95, New York, NY, USA, 2005. ACM.
+
+\bibitem[\protect\citename{Huang \bgroup \em et al.\egroup
+  }{2015}]{Huang2015}
+Zhiheng Huang, Wei Xu, and Kai Yu.
+\newblock Bidirectional {LSTM-CRF} models for sequence tagging.
+\newblock {\em CoRR}, abs/1508.01991, 2015.
+
+\bibitem[\protect\citename{Kr{\"{u}}pl \bgroup \em et al.\egroup
+  }{2005}]{Krupl2005}
+Bernhard Kr{\"{u}}pl, Marcus Herzog, and Wolfgang Gatterbauer.
+\newblock {Using visual cues for extraction of tabular data from arbitrary HTML
+  documents}.
+\newblock {\em Special interest tracks and posters of the 14th international
+  conference on World Wide Web - WWW '05}, pages 1000----1001, 2005.
+
+\bibitem[\protect\citename{Lafferty \bgroup \em et al.\egroup
+  }{2001}]{Lafferty2001}
+John~D. Lafferty, Andrew McCallum, and Fernando C.~N. Pereira.
+\newblock Conditional random fields: Probabilistic models for segmenting and
+  labeling sequence data.
+\newblock In {\em Proceedings of the Eighteenth International Conference on
+  Machine Learning}, ICML '01, pages 282--289, San Francisco, CA, USA, 2001.
+  Morgan Kaufmann Publishers Inc.
+
+\bibitem[\protect\citename{Lample \bgroup \em et al.\egroup
+  }{2016}]{Lample2016}
+Guillaume Lample, Miguel Ballesteros, Sandeep Subramanian, Kazuya Kawakami, and
+  Chris Dyer.
+\newblock Neural architectures for named entity recognition.
+\newblock {\em CoRR}, abs/1603.01360, 2016.
+
+\bibitem[\protect\citename{Li and Gray}{2000}]{Li2000}
+Jia Li and Robert~M. Gray.
+\newblock {\em Image Segmentation and Compression Using Hidden Markov Models}.
+\newblock Kluwer Academic Publishers, Norwell, MA, USA, 2000.
+
+\bibitem[\protect\citename{Liu and Nocedal}{1989}]{Liu1989}
+Dong~C. Liu and Jorge Nocedal.
+\newblock On the limited memory bfgs method for large scale optimization.
+\newblock {\em Mathematical Programming}, 45(1):503--528, Aug 1989.
+
+\bibitem[\protect\citename{Liu \bgroup \em et al.\egroup
+  }{2000}]{Liu2000}
+L.~Liu, C.~Pu, and W.~Han.
+\newblock {XWRAP: an XML-enabled wrapper construction system for Web
+  information sources}.
+\newblock {\em Proceedings of 16th International Conference on Data
+  Engineering}, pages 611--621, 2000.
+
+\bibitem[\protect\citename{Ma and Hovy}{2016}]{Ma2016}
+Xuezhe Ma and Eduard Hovy.
+\newblock End-to-end sequence labeling via bi-directional {LSTM}-{CNN}s-{CRF}.
+\newblock In {\em Proceedings of the 54th Annual Meeting of the Association for
+  Computational Linguistics (Volume 1: Long Papers)}, pages 1064--1074, Berlin,
+  Germany, August 2016. Association for Computational Linguistics.
+
+\bibitem[\protect\citename{McCallum and Li}{2003}]{McCallum2003}
+Andrew McCallum and Wei Li.
+\newblock Early results for named entity recognition with conditional random
+  fields, feature induction and web-enhanced lexicons.
+\newblock In {\em Proceedings of the Seventh Conference on Natural Language
+  Learning at HLT-NAACL 2003 - Volume 4}, CONLL '03, pages 188--191,
+  Stroudsburg, PA, USA, 2003. Association for Computational Linguistics.
+
+\bibitem[\protect\citename{McCallum \bgroup \em et al.\egroup
+  }{2000}]{McCallum2000}
+Andrew McCallum, Dayne Freitag, and Fernando C.~N. Pereira.
+\newblock Maximum entropy markov models for information extraction and
+  segmentation.
+\newblock In {\em Proceedings of the Seventeenth International Conference on
+  Machine Learning}, ICML '00, pages 591--598, San Francisco, CA, USA, 2000.
+  Morgan Kaufmann Publishers Inc.
+
+\bibitem[\protect\citename{Pennington \bgroup \em et al.\egroup
+  }{2014}]{Pennington2014}
+Jeffrey Pennington, Richard Socher, and Christopher~D. Manning.
+\newblock Glove: Global vectors for word representation.
+\newblock In {\em Empirical Methods in Natural Language Processing (EMNLP)},
+  pages 1532--1543, 2014.
+
+\bibitem[\protect\citename{Peters \bgroup \em et al.\egroup
+  }{2018}]{Peters2018}
+Matthew Peters, Mark Neumann, Mohit Iyyer, Matt Gardner, Christopher Clark,
+  Kenton Lee, and Luke Zettlemoyer.
+\newblock Deep contextualized word representations.
+\newblock In {\em Proceedings of the 2018 Conference of the North {A}merican
+  Chapter of the Association for Computational Linguistics: Human Language
+  Technologies, Volume 1 (Long Papers)}, pages 2227--2237, New Orleans,
+  Louisiana, June 2018. Association for Computational Linguistics.
+
+\bibitem[\protect\citename{Rabiner}{1990}]{Rabiner1990}
+Lawrence~R. Rabiner.
+\newblock {\em {Readings in Speech Recognition. Chapter: A Tutorial on Hidden
+  Markov Models and Selected Applications in Speech Recognition}}.
+\newblock Morgan Kaufmann Publishers Inc., San Francisco, CA, USA, 1990.
+
+\bibitem[\protect\citename{Ramshaw and Marcus}{1999}]{Ramshaw1999}
+L.~A. Ramshaw and M.~P. Marcus.
+\newblock {\em Text Chunking Using Transformation-Based Learning}, pages
+  157--176.
+\newblock Springer Netherlands, Dordrecht, 1999.
+
+\bibitem[\protect\citename{Ratnaparkhi}{1998}]{Ratnaparkhi1998}
+Adwait Ratnaparkhi.
+\newblock {\em Maximum Entropy Models for Natural Language Ambiguity
+  Resolution}.
+\newblock PhD thesis, Philadelphia, PA, USA, 1998.
+\newblock AAI9840230.
+
+\bibitem[\protect\citename{Rijsbergen}{1979}]{Rijsbergen1979}
+C.~J.~Van Rijsbergen.
+\newblock {\em Information Retrieval}.
+\newblock Butterworth-Heinemann, Newton, MA, USA, 2nd edition, 1979.
+
+\bibitem[\protect\citename{Sahuguet and Azavant}{1999}]{Sahuguet1999}
+Arnaud Sahuguet and Fabien Azavant.
+\newblock {Building Light-Weight Wrappers for Legacy Web Data-Sources Using
+  W4F}.
+\newblock In {\em Proceedings of the 25th International Conference on Very
+  Large Data Bases}, VLDB '99, pages 738--741, San Francisco, CA, USA, 1999.
+  Morgan Kaufmann Publishers Inc.
+
+\bibitem[\protect\citename{Sarawagi}{2008}]{Sarawagi2008}
+Sunita Sarawagi.
+\newblock {Information extraction}.
+\newblock {\em Foundations and Trends in Databases}, 1(3):261--377, 2008.
+
+\bibitem[\protect\citename{Schulz \bgroup \em et al.\egroup
+  }{2016}]{Schulz2016}
+Andreas Schulz, J{\"{o}}rg L{\"{a}}ssig, and Martin Gaedke.
+\newblock {Practical web data extraction: Are we there yet? --- A short
+  survey}.
+\newblock {\em IEEE/WIC/ACM International Conference on Web Intelligence (WI),
+  2016}, pages 562----567, 2016.
+
+\bibitem[\protect\citename{Shi \bgroup \em et al.\egroup
+  }{2015}]{Shi2015}
+Shengsheng Shi, Chengfei Liu, Yi~Shen, Chunfeng Yuan, and Yihua Huang.
+\newblock {AutoRM: An effective approach for automatic Web data record mining}.
+\newblock {\em Knowledge-Based Systems}, 89:314--331, 2015.
+
+\bibitem[\protect\citename{Soderland}{1999}]{Soderland1999}
+Stephen Soderland.
+\newblock {Learning Information Extraction Rules for Semi-Structured and Free
+  Text}.
+\newblock {\em Machine Learning}, 34(1):233--272, 1999.
+
+\bibitem[\protect\citename{Sundheim}{1991}]{Sundheim1991}
+Beth~M. Sundheim.
+\newblock Overview of the third message understanding evaluation and
+  conference.
+\newblock In {\em Proceedings of the 3rd Conference on Message Understanding},
+  MUC3 '91, pages 3--16, Stroudsburg, PA, USA, 1991. Association for
+  Computational Linguistics.
+
+\bibitem[\protect\citename{Tjong Kim~Sang and
+  De~Meulder}{2003}]{KimSang2003}
+Erik~F. Tjong Kim~Sang and Fien De~Meulder.
+\newblock {Introduction to the CoNLL-2003 Shared Task: Language-independent
+  Named Entity Recognition}.
+\newblock In {\em Proceedings of the Seventh Conference on Natural Language
+  Learning at HLT-NAACL 2003 - Volume 4}, CONLL '03, pages 142--147,
+  Stroudsburg, PA, USA, 2003. Association for Computational Linguistics.
+
+\bibitem[\protect\citename{Varlamov and Turdakov}{2016}]{Varlamov2016}
+M.~I. Varlamov and D.~Yu. Turdakov.
+\newblock {A survey of methods for the extraction of information from Web
+  resources}.
+\newblock {\em Programming and Computer Software}, 42(5):279--291, 2016.
+
 \end{thebibliography}
-
 \end{document}

### 2019-05-20 tex/article.tex
Artigo NLE.

@@
 
-% \author[João Mateus de Freitas Veneroso and Berthier Ribeiro-Neto]
-%        {João Mateus de Freitas Veneroso$^A$ \and
-%         Berthier Ribeiro-Neto$^B$\\
-% 	Universidade Federal de Minas Gerais$^{A,B}$ \\
-% 	Google Engineering$^A$, Belo Horizonte - MG, Brazil}
+\author[João Mateus de Freitas Veneroso and Berthier Ribeiro-Neto]
+       {João Mateus de Freitas Veneroso$^A$ \and
+        Berthier Ribeiro-Neto$^B$\\
+	Universidade Federal de Minas Gerais$^{A,B}$ \\
+	Google Engineering$^A$, Belo Horizonte - MG, Brazil}
 
@@
 the flexibility of discriminative approaches. However, because of the label bias problem,
-this model was superseded by \gls{crf}s~\cite{Lafferty2001, McCallum2003}. 
+this model was superseded by \gls{crf}s~\cite{Lafferty2001}. % McCallum2003
 At this time, the best performing systems almost always resorted to external gazetteers 
@@
 more complex entities and even perform entity detection without any feature
-engineering. We explored many methods of Named Entity Recognition
+engineering. We explored three methods of Named Entity Recognition
 in the context of a \gls{wde} task. First, we discuss two traditional 
@@
 states. For example in NER, the words are observed, however the Named Entity labels
-associated with these words are not. Formally, we want to compute the most probable
+associated with these words are not. We want to compute the most probable
 sequence of labels $ Y = \{y_1, y_2, ..., y_n\} $ for a sequence of observed tokens
 $ X = \{x_1, x_2, ..., x_n\} $.
-
+%
 \begin{equation}
@@
 \end{equation}
-
+%
 With Bayes theorem, we can write $ P(Y|X) $ as:
-
+%
 \begin{equation}
@@
 \end{equation}
-
+%
 Since $ P(X) $ is the same for all label sequences $ Y $, we can simply maximize
@@
 only on a fixed number of previous states. That is:
-
+%
 \begin{equation}
@@
 \end{equation}
-
+%
 In fact, we can get much better results on the NER task by looking at trigrams
@@
 Second, the probability of a word depends only on its assigned label. That is:
-
+%
 \begin{equation}
@@
 \end{equation}
-
+%
 With these assumptions, 
-the probability $ P(Y|X) $ can be approximated by the expression:
-
+the probability $ P(Y|X) $ can be calculated with the expression:
+%
 \begin{equation}
@@
 \end{equation}
-
-All relevant probabilities can be estimated through maximum likelihood estimation from the relative
-frequencies of labels and features in the corpus. The best sequence of labels can be computed 
+%
+In a HMM, we need to estimate the following probabilities:
+%
+\begin{itemize}
+  \item $ \hat{P}(x_i|y_i) $: the probability of word $ x_i $ given label $ y_i $.
+  \item $ \hat{P}(y_i|y_{i-1}) $: the probability of going from label $ y_{i-1} $ to label $ y_i $.
+\end{itemize}
+%
+These parameters can obtained with maximum likelihood estimation from the relative
+frequencies of labels and words in the corpus. The best sequence of labels can be computed 
 with a variable state Viterbi approach \cite{Li2000}. However, as we increase $ k $, this computation 
@@
 
-\subsubsection{Self-Training for Hidden Markov Models} 
+\subsubsection{Self-Training Hidden Markov Models} 
 \label{sssec:self_training}
 
-As described in Section~\ref{sec:hmm}. An \gls{hmm} for the sequence labeling task 
-has the form:
-\begin{equation}
-P(Y|X) \propto \prod_{i=1}^n P(x_i|y_i) P(y_i, y_{i-1})
-\end{equation}
-where $ X $ is a sequence of words and $ Y $ is a sequence of labels, both with size $ n $,
-and the initial probabilities $ P(y_1|y_0) $ follow a uniform distribution across all label 
-assignments.
-To construct this model from the data, we need to estimate the following probabilities:
-%
-\begin{itemize}
-  \item $ P(x_i|y_i) $: the emission probability of word $ x_i $ given label $ y_i $.
-  \item $ P(y_i|y_{i-1}) $: the transition probability of going from label $ y_{i-1} $ to label $ y_i $.
-\end{itemize}
-%
-We may consider $ x_i $ to be a binary feature vector $ x_i = \{ f_{i,1}, f_{i,2}, ..., f_{i,k} \} $
-as long as all the feature distributions are independent, conditioned on $ y_i $. That is:
+We propose the Self-Training strategy for \gls{hmm}s to incorporate knowledge about the HTML structure
+and boost the quality of the model in sequence labeling tasks for the web.
+Some \gls{wde} tasks, such as researcher name extraction, need extraction systems
+that can handle different webpage structures without needing to resort to human supervision
+between webpages. 
+The problem is that there is not a lot of similarity between the HTML structure in different web pages.
+For example, only because a named entity label occurs more often inside lists in a page, we cannot
+assume that this will be the case on other web pages. 
+Nonetheless, the HTML structure is not useless. Inside a single web page, the HTML tag is a good predictor
+of the correct labels, because words with a similar HTML context tend to have similar labels. For example, words
+that happen together inside a list are very likely to belong to the same category. 
+Yet, this pattern cannot be generalized to other pages, because we cannot expect that every list will
+be listing the same types of entities.
+
+The Self-Training strategy for HMMs consists of using the predicted labels as a proxy for the
+correct labels and estimating HTML feature probabilities for each webpage separately.
+Consider $ x_i $ to be a binary feature vector $ x_i = \{ f_{i,1}, f_{i,2}, ..., f_{i,k} \} $
+where all the feature are assumed to be independent, conditioned on $ y_i $. That is:
 \begin{equation}
@@
 %
-Also, due to the time invariance assumption, the $ P(f_{i,j}|y_i) $ probabilities 
-are independent of the timestep $ i $. Therefore, for each binary feature $ f_j $ we
-need only estimate the parameters $ \hat{P}(f_{j}|y) $, relative to each possible
-assignment of $ y $.
+Assuming time invariance, we need to estimate parameters $ \hat{P}(f_{j}|y) $, 
+relative to each possible assignment of $ y $.
 The maximum likelihood estimators for these feature parameters can be obtained
-from their relative frequencies, just as we did in Section~\ref{sec:hmm} for single words 
-(Equation~\ref{eq:mle_words}). Then, for binary features:
+from their relative frequencies in the corpus. That is:
 %
@@
 %
-Where $ \text{Count}(f_{j}=1, y=l) $ is the number of times in the training set that
-feature $ f_j $ was equal to one when the actual label was $ l $ (the other counts follow the same logic).
-This approach yields good experimental results for textual features such as the capitalization
-of a word, but if we try to use HTML structural features such as the HTML tags, we will find that
-they are not very useful, contradicting our intuition.
-The problem is that there is not much similarity between the HTML structure in different web pages.
-For example, only because a named entity label occurs more often inside <div> tags
-in a page, that does not mean this is the case for most web pages. Consider for example a faculty web page 
-that shows researcher names in a table (<td> tags) in contrast to a web page that organizes researcher
-names in a list (<li> tags). If there are many cases like the former page in our training set, and we use the 
-HTML tag feature in a model that assigns labels to the latter page in our test set, we will probably get many 
-wrong predictions.
-Nonetheless, the HTML features are not useless. Inside a single web page, the HTML tag is a good predictor
-of the correct labels. Words with a similar HTML context tend to have similar labels. For example, words
-that happen together in a list have very similar HTML contexts and are very likely to belong to
-the same category. The question is how to obtain better parameter estimators for HTML features.
-
-Consider a set $ F^T $ of $ m $ textual features unrelated to the HTML structure:
-%
-\begin{equation*}
-F^T = \{ f^T_1, f^T_2, ..., f^T_m \}
-\end{equation*}
-%
-And a set $ F^H $ of $ k $ HTML features that are related to the HTML structure:
-%
-\begin{equation*}
-F^H = \{ f^H_1, f^H_2, ..., f^H_k \}
-\end{equation*}
-%
-Given a \gls{hmm} trained with only the first set of features $ F^T $,
-we can use this model to predict the labels for an unlabeled document, and then by simply replacing
-the actual labels in Equation~\ref{eq:feature_mle} with the predicted labels, we get:
-%
-\begin{equation}
-\hat{P}(f_{j}=1|y=l) = \frac{\text{Count}(f_{j}=1, \tilde{y}=l)}
-{\text{Count}(f_{j}=0, \tilde{y}=l) + \text{Count}(f_{j}=1, \tilde{y}=l)}
-\end{equation}
-%
-\begin{equation}
-\hat{P}(\text{Tag}=\text{<li>}|y=\text{I-PER}) = \frac{4}{4 + 0} = 1
-\end{equation}
-%
-Where $ \tilde{y} $ is the label predicted by the \gls{hmm} trained with only the textual features.
-We use this formulation to calculate feature probabilities for the HTML features only.
-And next, we incorporate the estimators for the HTML feature probabilities in the original \gls{hmm} 
-and predict the final labels with the whole set of features $ F^T \cup F^H $. 
-This process could be repeated multiple times. If the predictions are becoming more accurate with
+These estimators yield good experimental results for textual features such as the 
+capitalization of a word, but for the reasons already discussed, it does not work
+well with HTML features, such as the current HTML tag. To make better use of the
+HTML features, consider a set $ F_T $ textual features unrelated to the HTML structure
+and a set $ F_H $ of HTML features related to the HTML structure.
+We can use a \gls{hmm} trained exclusively with the first set of features $ F_T $
+to predict the labels of an unlabeled webpage. With the predicted labels $ \tilde{y} $, we calculate
+the HTML feature probabilities $ \hat{P}(f_{j}=1|\tilde{y}=l) $ using the feature counts from
+that webpage alone. Next, we incorporate the estimators for the HTML feature probabilities 
+in the original \gls{hmm} and predict the final labels with the whole set of features 
+{$ F_T~\cup~F_H $}. This needs to be done separately for every webpage and
+the process can be repeated multiple times. If the predictions are becoming more accurate with
 each iteration, then the estimates for the HTML feature probabilities are also likely to improve. 
-
-In a simpler explanation, the self-training strategy can be divided into the following steps:
+This self-training strategy showed good experimental results in the \gls{rne} task. Stated
+simply, it can be divided into the following steps:
 %
@@
 %
-To understand why this strategy could help labeling named entities on the web, consider the 
-example shown in Figure~\ref{fig:self_training}. This example shows a snippet from a webpage 
-and how a naive \gls{hmm} would probably attribute 
-labels to each word. Despite being rather uncommon, North West is an actual person name,
-what becomes obvious in this case once we know the HTML context where it happens 
-(inside a list with other person names), but this is not so obvious if we consider the
-sentence in isolation. The naive \gls{hmm} could be improved if we calculated
-feature probabilities for the parent tags using proxies for the correct labels. We would find
-that four times in a total of six occurrences, the correct label for a word that happened inside
-a \textit{<li>} tag was \mbox{\textit{I-PER}}. By incorporating this knowledge in the model 
-using the self-training strategy, we would improve the probability that words North and West 
-were labeled correctly as a person name in this case.
-
-\begin{figure}
-  \centering
-  \includegraphics[width=0.5\textwidth]{pics/self_training_example}
-  \caption{Example of a webpage snippet with labels attributed by a HMM.}
-  \label{fig:self_training}
-\end{figure}
-
-This strategy could possibly be incorporated in the Baum-Welch algorithm to provide a more 
-statistically solid argument for its effectiveness, but this heuristic
-already yields a consistent improvement to sequence labeling on the web. In theory, this 
-strategy could be used with any sequence tagger, however retraining a classifier with new features can 
-become prohibitively expensive in the case of CRFs or Neural Networks. 
-In HMMs, retraining the features
-is fast, because we assume feature independence and the maximum likelihood estimator can be 
-obtained with a simple closed form expression.
-
-% \subsubsection{Self training} 
-% \label{sssec:self_training}
-% 
-% In the task of NER on HTML, there are useful features related to the HTML
-% structure that can help in identifying named entities. In a given website, named
-% entities tend to occur inside the same HTML tags. The HTML tag feature or other
-% HTML features could easily be incorporated in the HMM. However, these 
-% features are only useful inside a single website and they cannot be generalized, 
-% because different websites use distinct HTML templates. 
-% Therefore, we propose a self-training strategy to obtain probabilities for
-% these HTML features. It is implemented like this:
-% 
-% \begin{itemize}
-% \item Train the HMM without any HTML features.
-% \item Compute labels for a website with the trained HMM.
-% \item Use the computed labels as a proxy for the actual labels in the 
-% website and estimate HTML feature frequencies for this website alone.
-% \item Recompute the labels now using the HTML feature probabilities.
-% \end{itemize}
-% 
-% In theory, this strategy could be used with any sequence tagger, however
-% retraining a classifier with new features can become prohibitively expensive.
-% This strategy is only possible because the computation of HTML feature
-% frequencies can be performed very quickly. This adds very little overhead 
-% to the original HMM and improves precision and recall by a considerable 
-% margin.
+This strategy could be used with any sequence tagger, however retraining a classifier 
+with new features in every webpage can become prohibitively expensive in the case of 
+CRFs or Neural Networks. Contrastingly, in \gls{hmm}s, retraining the HTML features is fast, 
+because we assume feature independence and the maximum likelihood estimator can be obtained 
+with a simple closed form expression.
 
@@
 A Linear Chain Conditional Random Field (CRF) is the discriminative analog to the HMM,
-it was first introduced by Lafferty \cite{Lafferty2001}. It is a distribution $ P(Y|X) $ that takes the form:
-
+it was first introduced by Lafferty \cite{Lafferty2001}. The model can be described by a 
+distribution $ P(Y|X) $ that takes the form:
+%
 \begin{equation}
@@
 \end{equation}
-\\
-
+%
 where $ \theta $ is the parameter vector that we are going to learn, $ f_k(y_{t-1}, y_{t}, X) $ 
@@
 and the observation vector $ X $. And the partition function $ Z(x) $, takes the form:
-
+%
 \begin{equation}
@@
 \end{equation}
-\\
-
+%
 which is a sum over all possible label assignments $ Y $. The partition function can be efficiently
@@
 maximum entropy models such as L-BFGS \cite{Liu1989}. The most likely label sequences can be decoded 
-with the Viterbi algorithm, as was the case for HMMs.
+with the Viterbi algorithm.
 
@@
 timesteps. 
-
+%
 \begin{figure}[h]
   \centering
-  \includegraphics[width=0.75\textwidth]{pics/rnn_network}
+  \includegraphics[width=0.5\textwidth]{pics/rnn_network}
   \caption{RNN for NER}
@@
 \end{figure}
-
+%
 At each timestep, the neural network computes a hidden state $ h_t $ using an input 
@@
 timestep. A common definition for an RNN cell is given by the equations:
-
-\begin{flalign*}
+%
+\begin{align*}
 h_t &= tanh(W_x x_t + W_h h_{t-1}) &\\
 y_t &= softmax(W_y h_t) &
-\end{flalign*}
-
+\end{align*}
+%
 Where $ W_x $, $ W_h $ and $ W_y $ are weight matrices that can be trained with the 
@@
   \centering
-  \includegraphics[width=0.75\textwidth]{pics/lstm_cell}
+  \includegraphics[width=0.5\textwidth]{pics/lstm_cell}
   \caption{LSTM Cell}
@@
 The equations for the LSTM cell are:
-
-\begin{flalign*}
+%
+\begin{align*}
 \Gamma_{i} &= \sigma(W_i \cdot [x_t,h_{t-1}] + b_i) &\\
@@
 h_t        &= \Gamma_{o} \ast tanh(c_t) &
-\end{flalign*}
-
+\end{align*}
+%
 Where $ \sigma $ is the logistic sigmoid function. $ \Gamma_i $, $ \Gamma_f $, and $ \Gamma_o $ are the input,
@@
 
-On named entity recognition tasks, both past and future words are important 
+On \gls{ner} tasks, both past and future words are important 
 to attribute a label at time $ t $, however a regular LSTM network only takes 
@@
   \centering
-  \includegraphics[width=0.75\textwidth]{pics/bi_lstm_crf}
+  \includegraphics[width=0.5\textwidth]{pics/bi_lstm_crf}
   \caption{Bidirectional LSTM-CRF}
@@
   \centering
-	  \includegraphics[width=0.75\textwidth]{pics/cnn}
+  \includegraphics[width=0.5\textwidth]{pics/cnn}
   \caption{CNN based character representations}
@@
   \centering
-  \includegraphics[width=0.75\textwidth]{pics/lstm_char_representations}
+  \includegraphics[width=0.5\textwidth]{pics/lstm_char_representations}
   \caption{LSTM based character representations}
@@
 
-All neural models were trained using mini batch Stochastic Gradient Descent over 50 epochs with batch size 10,
+In the experiments, all neural models were trained using mini batch Stochastic Gradient Descent over 50 epochs with batch size 10,
 learning rate 0.01, momentum 0.9 and decay rate 0.05. We used early stopping \cite{Caruana2000} to select the best 
 parameters, considering the F1 measure in the validation set. All neural models used 
-GloVe 100-dimensional word embeddings \cite{Pennington2014} that were fine tuned during training.
-In the case of NER on HTML, word embeddings work similarly to a gazetteer. Named entities 
-with the same type have similar embeddings, so good word embeddings can achieve exceptional 
-performance with little training and without a gazetteer.
+GloVe 300-dimensional word embeddings \cite{Pennington2014} that were fine tuned during training.
 
@@
 
-This chapter describes the dataset used to evaluate the performance of sequence labeling models
+This section describes the dataset used to evaluate the performance of sequence labeling models
 on the \gls{wde} task of \gls{rne}. We call it the \gls{rne} dataset.
@@
 
-This chapter is divided as follows. Section~\ref{sec:data_description} describes the 
-dataset format and how it was split in
-three data files. 
-Section~\ref{sec:evaluation} describes how the evaluation of results in this 
-dataset was carried on. 
-Section~\ref{sec:dictionary} describes how we obtained a dictionary
-of relevant named entities for this dataset, and discusses some baselines.
-Lastly,
-Section~\ref{sec:conll_comparison} compares the characteristics of the \gls{rne} dataset
-with another popular \gls{ner} dataset, the {CoNLL-2003} English \gls{ner} dataset.
-
 \subsection{Data Description} 
@@
 sentence boundaries. Sentence boundaries were determined by line break HTML tags
-(div, p, table, li, br, etc.) in contrast to inline tags (span, em, a, td, etc.). For example,
-the HTML sentence: 
-%
-\begin{quote}
-\centering
-<p>E. <b>Smith</b> is a <a href="/link">professor</a>.</p>
-\end{quote}
-%
-\noindent
-becomes:
-%
-\begin{quote}
-\centering
-E. Smith is a professor.
-\end{quote}
-%
+(div, p, table, li, br, etc.) in contrast to inline tags (span, em, a, td, etc.). 
 Sentences that were more than fifty tokens long were also split according to the
@@
 experimentally that fifty tokens provide a large enough context 
-and allow efficient training using a GPU. A few sentences in the dataset would be 
-more than a thousand tokens long if this step was not performed, what would make batch training
-for neural networks less efficient.
+and allow efficient training.
 
@@
 
-The \gls{rne} dataset only has entities of type person PER, therefore a classifier has to
-label each token with one of the labels: O, B-PER, or I-PER. This is an example 
-sentence from the dataset:
-
-\begin{table}[h]
-  \small
-  \begin{center}
-    \begin{tabular}{ ll }
-      Token & Correct Label \\
-      \midrule
-      Kasper    & I-PER \\ 
-      Rasmussen & I-PER \\
-      Associate & O     \\
-      Professor & O     \\    
-      ,         & O     \\    
-      Royal     & O     \\    
-      Society   & O     \\    
-      Research  & O     \\    
-      Fellow    & O     \\    
-    \end{tabular}     
-  \end{center}
-\end{table}
-
+The \gls{rne} dataset only has entities of type person (PER), therefore a classifier has to
+label each token with one of the labels: O, B-PER, or I-PER. 
+% This is an example 
+% sentence from the dataset:
+% 
+% \begin{table}[h]
+%   \small
+%   \begin{center}
+%     \begin{tabular}{ ll }
+%       Token & Correct Label \\
+%       \midrule
+%       Kasper    & I-PER \\ 
+%       Rasmussen & I-PER \\
+%       Associate & O     \\
+%       Professor & O     \\    
+%       ,         & O     \\    
+%       Royal     & O     \\    
+%       Society   & O     \\    
+%       Research  & O     \\    
+%       Fellow    & O     \\    
+%     \end{tabular}     
+%   \end{center}
+% \end{table}
+% 
 The \gls{rne} dataset was divided in training, validation and test sets, which are described in 
@@
 dictionary baseline. We cannot use these results to properly compare the relative performances 
-between the models (this topic will be explored in the next chapter), but it is possible to conclude
+between the models (this topic will be explored in the next section), but it is possible to conclude
 that machine learning models trained in plain text do not necessarily perform very well in HTML 
@@
 the \gls{rne} datasets. In both plots we have a few very frequent words and a long tail of
-infrequent words. Most named entities are located in this long tail, therefore a good sequence
-labeling method needs to be able to handle the labeling of infrequent tokens effectively. 
-The probabilities attributed to unseen tokens is another aspect where models vary significantly 
-between different datasets.
+infrequent words. In the \gls{rne} dataset, most named entities are located in this long tail, 
+therefore a good sequence labeling method needs to be able to handle the labeling of infrequent 
+tokens effectively. 
+Table~\ref{tab:unknown_tokens} shows the number of unknown tokens~\footnote{
+Unknown tokens are tokens that occur at least once in the validation or test sets 
+but do not occur in the training set.
+}
+in the validation and test
+sets of the \gls{rne} dataset, and the number of named entities that contain at least one 
+unknown token.
 
@@
 
+\begin{table}[h]
+  \small
+  \begin{center}
+    \begin{tabular}{ lllll }
+      \toprule
+      Tokens / Named Entities (NE) & Valid & \% & Test & \%\\
+      \midrule
+      Unknown Tokens & 12076 & 26.96\% & 8324  & 22.65\% \\
+      Known Tokens   & 32719 & 73.04\% & 28433 & 77.35\% \\
+      Total          & 44795 & 100.00\%   & 36757 & 100.00\%   \\
+      \midrule
+      NEs with Unknown Tokens    & 1446 & 80.87\% & 2205 & 80.98\% \\
+      NEs without Unknown Tokens & 342  & 19.13\% & 518  & 19.02\% \\
+      Total                      & 1693 & 100.00\%   & 2638 & 100.00\%   \\
+      \bottomrule
+    \end{tabular}
+  \end{center}
+  \caption{Unknown tokens in the RNE dataset.}
+  \label{tab:unknown_tokens}
+\end{table}
+
 \begin{figure}[h!]
@@
 
-\subsection{Features}
-
-Thirteen categorical features were associated with each token in the dataset. They 
-are presented in Table \ref{tab:features}.
-
-\begin{table}[h]
-  \small
-  \begin{center}
-    \begin{tabular}{ ll }
-      \toprule
-      Feature & Description \\
-      \midrule
-      1  & Unaccented lowercase token \\
-      2  & Exact gazetteer match \\
-      3  & Partial gazetteer match \\
-      4  & Log name gazetteer count\\
-      5  & Log word gazetteer count\\
-      6  & Email \\
-      7  & Number \\
-      8  & Honorific (Mr., Mrs., Dr., etc.)\\
-      9  & URL \\
-      10 & Is capitalized \\
-      11 & Is a punctuation sign \\
-      12 & HTML tag + parent \\
-      13 & CSS class \\
-      \bottomrule
-    \end{tabular}
-  \end{center}
-  \caption{Features used in the NER on HTML dataset}
-  \label{tab:features}
-\end{table}
-
-\begin{table}[h]
-  \small
-  \begin{center}
-    \begin{tabular}{ lllll }
-      \toprule
-      Data file & Precision & Recall & F1 & Correct names \\
-      \midrule
-      Training   & 0.7316 & 0.2303 & 0.3504 & 1341 of 5822 \\ 
-      Validation & 0.8474 & 0.2858 & 0.4274 & 511 of 1788 \\ 
-      Test       & 0.8717 & 0.3287 & 0.4773 & 890 of 2708 \\ 
-      \bottomrule
-    \end{tabular}
-  \end{center}
-  \caption{Gazetteer coverage in each data file}
-  \label{tab:gazetteer}
-\end{table}
-
-The unaccented lowercase token was used as the key for the GloVe-100 embedding lookup.
-A gazetteer was constructed from a researcher list extracted from DBLP with 1,595,771
-names. Table \ref{tab:gazetteer} shows the precision, recall and F1 score obtained with an
-exact gazetteer matching strategy in each data file as a baseline.
-Feature 2 represents an exact match of a sequence of tokens to any of the 1,595,771 
-names, and feature 3 represents a partial match. Feature 4 is the rounded logarithm of 
-the frequency of a token in the gazetteer, and feature 5 is the rounded logarithm of the frequency
-of a token in a word corpus obtained through a random crawl on university websites.
-Features 6 to 11 represent a simple regular expression match to an email, number, 
-honorific, URL, capitalization or punctuation sign.
-
-Feature 12 represents the HTML enclosing tag and its parent concatenated. Feature 13
-represents all CSS classes concatenated. These features are not very useful in a general
-sense, because every HTML document has a different format, so only because a named entity
-occurs inside a given HTML tag in a document we cannot say it is more likely to be the case 
-in other documents. However, these features can be useful for the HMM self-training strategy 
-described in section \ref{sssec:self_training}.
-
 \section{Experiments}
 
-We conducted experiments to evaluate sequence labeling methods of named entity 
-recognition on HTML in the context of \gls{wde} using the dataset 
-described in Section~\ref{sec:ner_dataset}. The tested models are described in
-Table~\ref{tab:models}.
-
-\begin{table}[h]
-  \small
-  \begin{center}
-    \begin{tabular}{ ll }
-      \toprule
-      Model & Description \\
-      \midrule
-      hmm-1            & Regular HMM \\
-      hmm-2            & HMM with $ k=2 $ \\
-      hmm-3            & HMM with $ k=3 $ \\
-      crf              & Linear chain conditional random fields \\
-      bi-lstm-crf      & BI-LSTM-CRF model \\
-      bi-lstm-crf-cnn  & BI-LSTM-CRF with CNN character representations \\
-      bi-lstm-crf-lstm & BI-LSTM-CRF with LSTM character representations \\
-      \bottomrule
-    \end{tabular}
-  \end{center}
-  \caption{Model descriptions}
-  \label{tab:models}
-\end{table}
-
-The evaluation of model performance was done through the precision, recall and 
-F1 scores \cite{Rijsbergen1979}. Precision is the percentage of named entities found by 
-the model that are correct. Recall is the percentage of named entities that are present
-in the corpus and were found by the model. The F1 score is a composite measure that combines
-precision and recall with the formula:
-
-\begin{equation}
-F1 = \frac{2 * precision * recall}{precision + recall}
-\end{equation}
-
-Named entities were only considered to be correct if they were a complete match of the 
-corresponding entity in the dataset.
+We conducted two groups of experiments to evaluate machine learning models of 
+\gls{ner} at the researcher name extraction task and answer the following 
+research questions:
+%
+\begin{enumerate}
+\item Which are the best featureless machine learning models for NER on the web?
+\item Which are the best machine learning models for NER on the web with a dictionary and a good selection of features?
+\end{enumerate}
+%
+A model that works well despite the absence of a good feature selection is arguably more valuable than
+a method that requires a lot of feature engineering or a big dictionary of named entities, as long as 
+its accuracy is sufficiently high for the intended purpose. This is where Deep Neural Networks are most
+useful. However, the improved accuracy of neural architectures comes at the expense of more complexity
+and a longer training time, what must also be taken into account.
 
@@
       \midrule
-      hmm-1	       & 0.6965 & 0.5749 & 0.6299 & 0.6263 & 0.4431 & 0.5190 \\
-      hmm-2	       & 0.7047 & 0.6286 & 0.6645 & 0.6480 & 0.5222 & 0.5783 \\
-      hmm-3	       & 0.6127 & 0.6141 & 0.6134 & 0.5471 & 0.4634 & 0.5018 \\
-      crf	       & 0.7173 & 0.6683 & 0.6920 & 0.6671 & 0.5868 & 0.6244 \\
-      bi-lstm-crf      & 0.8484 & 0.9044 & 0.8755 & 0.8358 & 0.8497 & 0.8427 \\
-      bi-lstm-crf-cnn  & 0.9058 & 0.9575 & 0.9309 & 0.8779 & 0.8737 & 0.8758 \\
-      bi-lstm-crf-lstm & 0.9134 & 0.9435 & 0.9282 & \textbf{0.8920} & \textbf{0.8815} & \textbf{0.8867} \\
+      HMM-1                 & 0.693 & 0.581 & 0.632 & 0.637 & 0.458 & 0.533 \\
+      HMM-2                 & 0.703 & 0.630 & 0.665 & 0.653 & 0.527 & 0.583 \\
+      HMM-3                 & 0.616 & 0.618 & 0.617 & 0.551 & 0.468 & 0.506 \\
+      CRF                   & 0.806 & 0.805 & 0.806 & 0.795 & 0.710 & 0.750 \\
+      Bi-LSTM-CRF           & 0.906 & 0.938 & 0.922 & 0.909 & 0.865 & 0.886 \\
+      +CNNc                 & 0.929 & 0.946 & 0.938 & 0.921 & 0.881 & 0.901 \\
+      +LSTMc                & 0.928 & 0.950 & 0.939 & 0.920 & 0.886 & 0.902 \\
       \bottomrule
@@
 
+Eleven discrete features were extracted from the dataset. 
+These were selected from a larger pool of features, 
+considering their aid to the performance of the extraction systems. Deep learning 
+architectures can work incredibly well without any of these features, however they
+are of critical importance to traditional approaches such as HMMs and CRFs. 
+The selected features are presented in Table~\ref{tab:features}.
+
+\begin{table}[h]
+  \small
+  \begin{center}
+    \begin{tabular}{ lll }
+      \toprule
+      Feature & Description & Type \\
+      \midrule
+      1  & Unaccented lowercase token & Categorical \\
+      2  & Exact dictionary match & Binary \\
+      3  & Partial dictionary match & Binary \\
+      4  & Email & Binary \\
+      5  & Number & Binary \\
+      6  & Honorific (Mr., Mrs., Dr., etc.) & Binary \\
+      7  & Matches a URL & Binary \\
+      8  & Is capitalized & Binary \\
+      9  & Is a punctuation sign & Binary \\
+      10 & HTML tag + parent & Categorical \\
+      11 & CSS class & Categorical \\
+      \bottomrule
+    \end{tabular}
+  \end{center}
+  \caption{Features used in the RNE dataset.}
+  \label{tab:features}
+\end{table}
+
+The only features that demand further explanation are features 10 and 11.
+Feature 10 is the token's enclosing HTML tag and its parent tag concatenated.
+Feature 11 is the CSS class for the token's HTML tag.
+Both of these features are only useful in the self-training strategy for HMMs and the
+attention architectures for Bi-LSTM-CRFs. In other models, we only use features 1 to 9.
 Experiment 2 aimed to evaluate the performance of sequence model with all
@@
       \midrule
-      hmm-1	         & 0.6061 & 0.7282 & 0.6616 & 0.7106 & 0.7633 & 0.7360 \\
-      hmm-2	         & 0.6279 & 0.7550 & 0.6856 & 0.7521 & 0.7810 & 0.7663 \\
-      hmm-3	         & 0.6573 & 0.7819 & 0.7142 & 0.7523 & 0.7795 & 0.7657 \\
-      hmm-1+ST           & 0.7032 & 0.9077 & 0.7925 & 0.7522 & 0.8663 & 0.8052 \\
-      hmm-2+ST           & 0.7321 & 0.9172 & 0.8143 & 0.7737 & 0.8789 & 0.8230 \\
-      hmm-3+ST           & 0.7551 & 0.9172 & 0.8283 & 0.7961 & 0.8534 & 0.8237 \\
-      crf	         & 0.9024 & 0.9049 & 0.9037 & 0.8751 & 0.8227 & 0.8481 \\
-      bi-lstm-crf        & 0.9430 & 0.9530 & 0.9480 & 0.8998 & 0.8527 & 0.8756 \\
-      bi-lstm-crf-cnn    & 0.9244 & 0.9715 & 0.9474 & 0.9017 & \textbf{0.8973} & \textbf{0.8995} \\
-      bi-lstm-crf-lstm   & 0.9465 & 0.9692 & 0.9577 & \textbf{0.9108} & 0.8715 & 0.8907 \\
+      HMM-1                           & 0.730 & 0.714 & 0.722 & 0.826 & 0.684 & 0.748 \\
+      HMM-2                           & 0.720 & 0.710 & 0.715 & 0.820 & 0.724 & 0.769 \\
+      HMM-3                           & 0.721 & 0.702 & 0.711 & 0.791 & 0.667 & 0.724 \\
+      HMM-1 + Self-Training           & 0.747 & 0.906 & 0.819 & 0.866 & 0.867 & 0.866 \\
+      HMM-2 + Self-Training           & 0.771 & 0.912 & 0.835 & 0.885 & 0.869 & 0.877 \\
+      HMM-3 + Self-Training           & 0.788 & 0.917 & 0.847 & 0.826 & 0.803 & 0.814 \\
+      CRF (Group B)                   & 0.881 & 0.903 & 0.892 & 0.870 & 0.786 & 0.826 \\
+      Bi-LSTM-CRF (Group B)           & 0.914 & 0.947 & 0.930 & 0.921 & 0.883 & 0.901 \\
+      +CNN chars                      & 0.939 & 0.947 & 0.943 & 0.922 & 0.868 & 0.894 \\
+      +LSTM chars                     & 0.932 & 0.942 & 0.937 & 0.913 & 0.855 & 0.883 \\
       \bottomrule
@@
 
-\bibitem[\protect\citename{Furche {\it et al.}\ }{2012}]{Furche2012}
+\bibitem[\protect\citename{Furche, Gottlob, Grasso, Gunes, Guo, Kravchenko, Orsi, Schallhart, Sellers, and Wang }{2012}]{Furche2012}
 Furche, T., Gottlob, G., Grasso, G., Gunes, O., Guo, X., Kravchenko, A., Orsi, G., Schallhart, C., Sellers, A., and Wang, C. (2012)
@@
 In {\it Proceedings of the First East-European Conference on Advances in Databases and Information Systems (ADBIS'97)}
-pp 22--22, Swindon, UK, BCS Learning \& Development Ltd.
-
-\bibitem[\protect\citename{Arocena and Mendelzon}{1998}]{Arocena1999}
-Gustavo~O. Arocena and Alberto~O. Mendelzon.
-\newblock {WebOQL}: Restructuring documents, databases, and webs.
-\newblock In {\em Proceedings of the Fourteenth International Conference on
-  Data Engineering}, ICDE '98, pages 24--33, Washington, DC, USA, 1998. IEEE
-  Computer Society.
-
-\bibitem[\protect\citename{Akbik \bgroup \em et al.\egroup
-  }{2018}]{Akbik2018}
-Alan Akbik, Duncan Blythe, and Roland Vollgraf.
-\newblock Contextual string embeddings for sequence labeling.
-\newblock In {\em Proceedings of the 27th International Conference on
-  Computational Linguistics}, pages 1638--1649, Santa Fe, New Mexico, USA,
-  August 2018. Association for Computational Linguistics.
-
-\bibitem[\protect\citename{Baevski \bgroup \em et al.\egroup
-  }{2019}]{Baevski2019}
-Alexei Baevski, Sergey Edunov, Yinhan Liu, Luke Zettlemoyer, and Michael Auli.
-\newblock Cloze-driven pretraining of self-attention networks.
-\newblock {\em Preprint arXiv:1903.07785}, 2019.
-
-\bibitem[\protect\citename{Bikel \bgroup \em et al.\egroup
-  }{1999}]{Bikel1999}
-Daniel~M. Bikel, Richard Schwartz, and Ralph~M. Weischedel.
-\newblock An algorithm that learns what's in a name.
-\newblock {\em Machine Learning}, 34(1):211--231, Feb 1999.
-
-\bibitem[\protect\citename{Borthwick \bgroup \em et al.\egroup
-  }{1998}]{Borthwick1998}
-Andrew Borthwick, John Sterling, Eugene Agichtein, and Ralph Grishman.
-\newblock Exploiting diverse knowledge sources via maximum entropy in named
-  entity recognition.
-\newblock In {\em Proceedings of the Sixth Workshop on Very Large Corpora},
-  pages 152--160. Association for Computational Linguistics, 1998.
-
-\bibitem[\protect\citename{Caruana \bgroup \em et al.\egroup
-  }{2000}]{Caruana2000}
-Rich Caruana, Steve Lawrence, and Lee Giles.
-\newblock Overfitting in neural nets: Backpropagation, conjugate gradient, and
-  early stopping.
-\newblock In {\em Proceedings of the 13th International Conference on Neural
-  Information Processing Systems}, NIPS'00, pages 381--387, Cambridge, MA, USA,
-  2000. MIT Press.
-
-\bibitem[\protect\citename{Chang and Kuo}{2004}]{Chang2004}
-Chia~Hui Chang and Shih~Chien Kuo.
-\newblock {OLERA: Semisupervised Web-data extraction with visual support}.
-\newblock {\em IEEE Intelligent Systems}, 19(6):56--64, 2004.
-
-\bibitem[\protect\citename{Chang \bgroup \em et al.\egroup
-  }{2001}]{Chang2001}
-C.H. Chang, C.H. Chang, S.C. Lui, and S.C. Lui.
-\newblock {IEPAD: information extraction based on pattern discovery}.
-\newblock {\em Proceedings of the 10th international conference on World Wide
-  Web}, pages 681--688, 2001.
-
-\bibitem[\protect\citename{Chang \bgroup \em et al.\egroup
-  }{2006}]{Chang2006}
-Chia-Hui Chang, Mohammed Kayed, Moheb~Ramzy Girgis, and Khaled~F Shaalan.
-\newblock {A Survey of Web Information Extraction Systems}.
-\newblock {\em IEEE Transactions on Knowledge and Data Engineering},
-  18(10):1411--1428, 2006.
-
-\bibitem[\protect\citename{Devlin \bgroup \em et al.\egroup
-  }{2018}]{Devlin2018}
-Jacob Devlin, Ming-Wei Chang, Kenton Lee, and Kristina Toutanova.
-\newblock {BERT}: Pre-training of deep bidirectional transformers for language
-  understanding.
-\newblock {\em Preprint arXiv:1810.04805}, 2018.
-
-\bibitem[\protect\citename{Dong \bgroup \em et al.\egroup
-  }{2014}]{Dong2014}
-Xin Dong, Evgeniy Gabrilovich, Geremy Heitz, Wilko Horn, Ni~Lao, Kevin Murphy,
-  Thomas Strohmann, Shaohua Sun, and Wei Zhang.
-\newblock {Knowledge Vault: a web-scale approach to probabilistic knowledge
-  fusion}.
-\newblock {\em Proceedings of the 20th ACM SIGKDD international conference on
-  Knowledge discovery and data mining - KDD '14}, pages 601--610, 2014.
-
-\bibitem[\protect\citename{Ferrara and Baumgartner}{2011}]{Ferrara2011}
-Emilio Ferrara and Robert Baumgartner.
-\newblock {Automatic wrapper adaptation by tree edit distance matching}.
-\newblock {\em Smart Innovation, Systems and Technologies}, 8:41--54, 2011.
-
-\bibitem[\protect\citename{Ferrara \bgroup \em et al.\egroup
-  }{2014}]{Ferrara2014}
-Emilio Ferrara, Pasquale {De Meo}, Giacomo Fiumara, and Robert Baumgartner.
-\newblock {Web data extraction, applications and techniques: A survey}.
-\newblock {\em Knowledge-Based Systems}, 70:301--323, 2014.
-
-\bibitem[\protect\citename{Florian \bgroup \em et al.\egroup
-  }{2003}]{Florian2003}
-Radu Florian, Abe Ittycheriah, Hongyan Jing, and Tong Zhang.
-\newblock Named entity recognition through classifier combination.
-\newblock In {\em Proceedings of the Seventh Conference on Natural Language
-  Learning at HLT-NAACL 2003}, pages 168--171, 2003.
-
-\bibitem[\protect\citename{Freitag and Mccallum}{1999}]{Freitag1999}
-Dayne Freitag and Andrew~Kachites Mccallum.
-\newblock {Information Extraction with HMMs and Shrinkage}.
-\newblock In {\em Proceedings of the AAAI-99 Workshop on Machine Learning for
-  Information Extraction}, pages 31--36. AAAI Press, 2 1999.
-
-\bibitem[\protect\citename{Freitag and McCallum}{2000}]{Freitag2000}
-Dayne Freitag and Andrew McCallum.
-\newblock {Information Extraction with HMM Structures Learned by Stochastic
-  Optimization}.
-\newblock In {\em Proceedings of the Seventeenth National Conference on
-  Artificial Intelligence and Twelfth Conference on Innovative Applications of
-  Artificial Intelligence}, pages 584--589. AAAI Press, 2000.
-
-\bibitem[\protect\citename{Freitag}{1998}]{Freitag1998}
-Dayne Freitag.
-\newblock {Information Extraction from HTML: Application of a General Machine
-  Learning Approach}.
-\newblock In {\em Proceedings of the Fifteenth National/Tenth Conference on
-  Artificial Intelligence/Innovative Applications of Artificial Intelligence},
-  AAAI '98/IAAI '98, pages 517--523, Menlo Park, CA, USA, 1998. American
-  Association for Artificial Intelligence.
-
-\bibitem[\protect\citename{Hochreiter and
-  Schmidhuber}{1997}]{Hochreiter1997}
-Sepp Hochreiter and J\"{u}rgen Schmidhuber.
-\newblock Long short-term memory.
-\newblock {\em Neural Computation}, 9(8):1735--1780, November 1997.
-
-\bibitem[\protect\citename{Hogue and Karger}{2005}]{Hogue2005}
-Andrew Hogue and David Karger.
-\newblock {Thresher: Automating the Unwrapping of Semantic Content from the
-  World Wide Web}.
-\newblock In {\em Proceedings of the 14th International Conference on World
-  Wide Web}, WWW '05, pages 86--95, New York, NY, USA, 2005. ACM.
-
-\bibitem[\protect\citename{Huang \bgroup \em et al.\egroup
-  }{2015}]{Huang2015}
-Zhiheng Huang, Wei Xu, and Kai Yu.
-\newblock Bidirectional {LSTM-CRF} models for sequence tagging.
-\newblock {\em CoRR}, abs/1508.01991, 2015.
-
-\bibitem[\protect\citename{Kr{\"{u}}pl \bgroup \em et al.\egroup
-  }{2005}]{Krupl2005}
-Bernhard Kr{\"{u}}pl, Marcus Herzog, and Wolfgang Gatterbauer.
-\newblock {Using visual cues for extraction of tabular data from arbitrary HTML
-  documents}.
-\newblock {\em Special interest tracks and posters of the 14th international
-  conference on World Wide Web - WWW '05}, pages 1000----1001, 2005.
-
-\bibitem[\protect\citename{Lafferty \bgroup \em et al.\egroup
-  }{2001}]{Lafferty2001}
-John~D. Lafferty, Andrew McCallum, and Fernando C.~N. Pereira.
-\newblock Conditional random fields: Probabilistic models for segmenting and
-  labeling sequence data.
-\newblock In {\em Proceedings of the Eighteenth International Conference on
-  Machine Learning}, ICML '01, pages 282--289, San Francisco, CA, USA, 2001.
-  Morgan Kaufmann Publishers Inc.
-
-\bibitem[\protect\citename{Lample \bgroup \em et al.\egroup
-  }{2016}]{Lample2016}
-Guillaume Lample, Miguel Ballesteros, Sandeep Subramanian, Kazuya Kawakami, and
-  Chris Dyer.
-\newblock Neural architectures for named entity recognition.
-\newblock {\em CoRR}, abs/1603.01360, 2016.
-
-\bibitem[\protect\citename{Li and Gray}{2000}]{Li2000}
-Jia Li and Robert~M. Gray.
-\newblock {\em Image Segmentation and Compression Using Hidden Markov Models}.
-\newblock Kluwer Academic Publishers, Norwell, MA, USA, 2000.
-
-\bibitem[\protect\citename{Liu and Nocedal}{1989}]{Liu1989}
-Dong~C. Liu and Jorge Nocedal.
-\newblock On the limited memory bfgs method for large scale optimization.
-\newblock {\em Mathematical Programming}, 45(1):503--528, Aug 1989.
-
-\bibitem[\protect\citename{Liu \bgroup \em et al.\egroup
-  }{2000}]{Liu2000}
-L.~Liu, C.~Pu, and W.~Han.
-\newblock {XWRAP: an XML-enabled wrapper construction system for Web
-  information sources}.
-\newblock {\em Proceedings of 16th International Conference on Data
-  Engineering}, pages 611--621, 2000.
-
-\bibitem[\protect\citename{Ma and Hovy}{2016}]{Ma2016}
-Xuezhe Ma and Eduard Hovy.
-\newblock End-to-end sequence labeling via bi-directional {LSTM}-{CNN}s-{CRF}.
-\newblock In {\em Proceedings of the 54th Annual Meeting of the Association for
-  Computational Linguistics (Volume 1: Long Papers)}, pages 1064--1074, Berlin,
-  Germany, August 2016. Association for Computational Linguistics.
-
-\bibitem[\protect\citename{McCallum and Li}{2003}]{McCallum2003}
-Andrew McCallum and Wei Li.
-\newblock Early results for named entity recognition with conditional random
-  fields, feature induction and web-enhanced lexicons.
-\newblock In {\em Proceedings of the Seventh Conference on Natural Language
-  Learning at HLT-NAACL 2003 - Volume 4}, CONLL '03, pages 188--191,
-  Stroudsburg, PA, USA, 2003. Association for Computational Linguistics.
-
-\bibitem[\protect\citename{McCallum \bgroup \em et al.\egroup
-  }{2000}]{McCallum2000}
-Andrew McCallum, Dayne Freitag, and Fernando C.~N. Pereira.
-\newblock Maximum entropy markov models for information extraction and
-  segmentation.
-\newblock In {\em Proceedings of the Seventeenth International Conference on
-  Machine Learning}, ICML '00, pages 591--598, San Francisco, CA, USA, 2000.
-  Morgan Kaufmann Publishers Inc.
-
-\bibitem[\protect\citename{Pennington \bgroup \em et al.\egroup
-  }{2014}]{Pennington2014}
-Jeffrey Pennington, Richard Socher, and Christopher~D. Manning.
-\newblock Glove: Global vectors for word representation.
-\newblock In {\em Empirical Methods in Natural Language Processing (EMNLP)},
-  pages 1532--1543, 2014.
-
-\bibitem[\protect\citename{Peters \bgroup \em et al.\egroup
-  }{2018}]{Peters2018}
-Matthew Peters, Mark Neumann, Mohit Iyyer, Matt Gardner, Christopher Clark,
-  Kenton Lee, and Luke Zettlemoyer.
-\newblock Deep contextualized word representations.
-\newblock In {\em Proceedings of the 2018 Conference of the North {A}merican
-  Chapter of the Association for Computational Linguistics: Human Language
-  Technologies, Volume 1 (Long Papers)}, pages 2227--2237, New Orleans,
-  Louisiana, June 2018. Association for Computational Linguistics.
-
-\bibitem[\protect\citename{Rabiner}{1990}]{Rabiner1990}
-Lawrence~R. Rabiner.
-\newblock {\em {Readings in Speech Recognition. Chapter: A Tutorial on Hidden
-  Markov Models and Selected Applications in Speech Recognition}}.
-\newblock Morgan Kaufmann Publishers Inc., San Francisco, CA, USA, 1990.
-
-\bibitem[\protect\citename{Ramshaw and Marcus}{1999}]{Ramshaw1999}
-L.~A. Ramshaw and M.~P. Marcus.
-\newblock {\em Text Chunking Using Transformation-Based Learning}, pages
-  157--176.
-\newblock Springer Netherlands, Dordrecht, 1999.
-
-\bibitem[\protect\citename{Ratnaparkhi}{1998}]{Ratnaparkhi1998}
-Adwait Ratnaparkhi.
-\newblock {\em Maximum Entropy Models for Natural Language Ambiguity
-  Resolution}.
-\newblock PhD thesis, Philadelphia, PA, USA, 1998.
-\newblock AAI9840230.
-
-\bibitem[\protect\citename{Rijsbergen}{1979}]{Rijsbergen1979}
-C.~J.~Van Rijsbergen.
-\newblock {\em Information Retrieval}.
-\newblock Butterworth-Heinemann, Newton, MA, USA, 2nd edition, 1979.
-
-\bibitem[\protect\citename{Sahuguet and Azavant}{1999}]{Sahuguet1999}
-Arnaud Sahuguet and Fabien Azavant.
-\newblock {Building Light-Weight Wrappers for Legacy Web Data-Sources Using
-  W4F}.
-\newblock In {\em Proceedings of the 25th International Conference on Very
-  Large Data Bases}, VLDB '99, pages 738--741, San Francisco, CA, USA, 1999.
-  Morgan Kaufmann Publishers Inc.
-
-\bibitem[\protect\citename{Sarawagi}{2008}]{Sarawagi2008}
-Sunita Sarawagi.
-\newblock {Information extraction}.
-\newblock {\em Foundations and Trends in Databases}, 1(3):261--377, 2008.
-
-\bibitem[\protect\citename{Schulz \bgroup \em et al.\egroup
-  }{2016}]{Schulz2016}
-Andreas Schulz, J{\"{o}}rg L{\"{a}}ssig, and Martin Gaedke.
-\newblock {Practical web data extraction: Are we there yet? --- A short
-  survey}.
-\newblock {\em IEEE/WIC/ACM International Conference on Web Intelligence (WI),
-  2016}, pages 562----567, 2016.
-
-\bibitem[\protect\citename{Shi \bgroup \em et al.\egroup
-  }{2015}]{Shi2015}
-Shengsheng Shi, Chengfei Liu, Yi~Shen, Chunfeng Yuan, and Yihua Huang.
-\newblock {AutoRM: An effective approach for automatic Web data record mining}.
-\newblock {\em Knowledge-Based Systems}, 89:314--331, 2015.
-
-\bibitem[\protect\citename{Soderland}{1999}]{Soderland1999}
-Stephen Soderland.
-\newblock {Learning Information Extraction Rules for Semi-Structured and Free
-  Text}.
-\newblock {\em Machine Learning}, 34(1):233--272, 1999.
-
-\bibitem[\protect\citename{Sundheim}{1991}]{Sundheim1991}
-Beth~M. Sundheim.
-\newblock Overview of the third message understanding evaluation and
-  conference.
-\newblock In {\em Proceedings of the 3rd Conference on Message Understanding},
-  MUC3 '91, pages 3--16, Stroudsburg, PA, USA, 1991. Association for
-  Computational Linguistics.
-
-\bibitem[\protect\citename{Tjong Kim~Sang and
-  De~Meulder}{2003}]{KimSang2003}
-Erik~F. Tjong Kim~Sang and Fien De~Meulder.
-\newblock {Introduction to the CoNLL-2003 Shared Task: Language-independent
-  Named Entity Recognition}.
-\newblock In {\em Proceedings of the Seventh Conference on Natural Language
-  Learning at HLT-NAACL 2003 - Volume 4}, CONLL '03, pages 142--147,
-  Stroudsburg, PA, USA, 2003. Association for Computational Linguistics.
-
-\bibitem[\protect\citename{Varlamov and Turdakov}{2016}]{Varlamov2016}
-M.~I. Varlamov and D.~Yu. Turdakov.
-\newblock {A survey of methods for the extraction of information from Web
-  resources}.
-\newblock {\em Programming and Computer Software}, 42(5):279--291, 2016.
+pp. 22--22, Swindon, UK, BCS Learning \& Development Ltd.
+
+\bibitem[\protect\citename{Arocena and Mendelzon }1998]{Arocena1999}
+Arocena, G. and Mendelzon, A. (1998)
+WebOQL: Restructuring documents, databases, and webs.
+In {\it Proceedings of the Fourteenth International Conference on Data Engineering (ICDE '98)}
+pp. 24--33, Washington, DC, USA, IEEE Computer Society.
+
+\bibitem[\protect\citename{Liu, Pu and Han }2000]{Liu2000}
+Liu, L., Pu, C. and Han, W. (2000)
+XWRAP: an XML-enabled wrapper construction system for Web information sources.
+In {\it Proceedings of 16th International Conference on Data Engineering}
+pp. 611--621.
+
+\bibitem[\protect\citename{Sahuguet and Azavant }1999]{Sahuguet1999}
+Sahuguet, A. and Azavant F. (1999)
+Building Light-Weight Wrappers for Legacy Web Data-Sources Using W4F.
+In {\it Proceedings of the 25th International Conference on Very Large Data Bases (VLDB '99)}
+pp. 738--741, San Francisco, CA, USA, Morgan Kaufmann Publishers Inc.
+
+\bibitem[\protect\citename{Freitag }1998]{Freitag1998}
+Freitag, D. (1998)
+Information Extraction from HTML: Application of a General Machine Learning Approach.
+In {\it Proceedings of the Fifteenth National/Tenth Conference on Artificial Intelligence/Innovative Applications of Artificial Intelligence (AAAI '98/IAAI '98)}
+pp. 517--523, Menlo Park, CA, USA, American Association for Artificial Intelligence.
+
+\bibitem[\protect\citename{Soderland }1999]{Soderland1999}
+Soderland, S. (1999)
+Learning Information Extraction Rules for Semi-Structured and Free Text.
+{\it Machine Learning} 
+{\bf 34(1)}: 233--272.
+
+\bibitem[\protect\citename{Chang, Kayed, Girgis and Shaalan }2006]{Chang2006}
+Chang, C., Kayed, M., Girgis, M. and Shaalan, K. (2006)
+A Survey of Web Information Extraction Systems.
+{\it IEEE Transactions on Knowledge and Data Engineering}
+{\bf 18(10)}: 1411--1428.
+
+\bibitem[\protect\citename{Hogue and Karger }2005]{Hogue2005}
+Hogue, A. and Karger, D. (2005)
+Thresher: Automating the Unwrapping of Semantic Content from the World Wide Web.
+In {\it Proceedings of the 14th International Conference on World Wide Web (WWW '05)}
+pp. 86--95, New York, NY, USA, ACM.
+
+\bibitem[\protect\citename{Chang and Lui }2001]{Chang2001}
+Chang, C. and Lui, S. (2001)
+IEPAD: information extraction based on pattern discovery.
+In {\it Proceedings of the 10th international conference on World Wide Web}
+pp. 681--688.
+
+\bibitem[\protect\citename{Chang and Kuo }2004]{Chang2004}
+Chang, C. and Kuo, S. (2004)
+OLERA: Semisupervised Web-data extraction with visual support.
+{\it IEEE Intelligent Systems}
+{\bf 19(6)}: 56--64.
+
+\bibitem[\protect\citename{Sarawagi }2008]{Sarawagi2008}
+Sarawagi, S. (2008)
+Information extraction.
+{\it Foundations and Trends in Databases}
+{\bf 1(3)}: 261--377.
+
+\bibitem[\protect\citename{Ferrara and Baumgartner }2011]{Ferrara2011}
+Ferrara, E. and Baumgartner, R. (2011)
+Automatic wrapper adaptation by tree edit distance matching.
+{\it Smart Innovation, Systems and Technologies}
+{\bf 8}: 41--54.
+
+\bibitem[\protect\citename{Ferrara, De Meo, Fiumara and Baumgartner }2014]{Ferrara2014}
+Ferrara, E., De Meo, P., Fiumara, G. and Baumgartner, R. (2014)
+Web data extraction, applications and techniques: A survey.
+{\it Knowledge-Based Systems}
+{\bf 70}: 301--323.
+
+\bibitem[\protect\citename{Schulz, Lassig and Gaedke }2016]{Schulz2016}
+Schulz, A. Lassig, J. and Gaedke, M. (2016)
+Practical web data extraction: Are we there yet? --- A short survey.
+{\it IEEE/WIC/ACM International Conference on Web Intelligence (WI), 2016}, 
+pp. 562--567.
+
+\bibitem[\protect\citename{Varlamov and Turdakov }2016]{Varlamov2016}
+Varlamov, M. and Turdakov, D. (2016)
+A survey of methods for the extraction of information from Web resources.
+{\it Programming and Computer Software}
+{\bf 42(5)}: 279--291.
+
+\bibitem[\protect\citename{Krupl, Herzog and Gatterbauer }2005]{Krupl2005}
+Krupl, B. Herzog, M. and Gatterbauer, W. (2005)
+Using visual cues for extraction of tabular data from arbitrary HTML documents.
+{\it Special interest tracks and posters of the 14th international conference on World Wide Web - WWW '05} 
+pp. 1000--1001.
+
+\bibitem[\protect\citename{Shi, Liu, Shen, Yuan and Huang }{2015}]{Shi2015}
+Shi, S., Liu, C., Shen, Y., Yuan, C. and Huang, Y. (2015)
+AutoRM: An effective approach for automatic Web data record mining.
+{\it Knowledge-Based Systems}
+{\bf 89}: 314--331.
+
+\bibitem[\protect\citename{Dong, Gabrilovich, Heitz, Horn, Lao, Murphy, Strohmann, Sun, and Zhang }{2014}]{Dong2014}
+Dong, X., Gabrilovich, E., Heitz, G., Horn, W., Lao, N., Murphy, K., Strohmann, T., Sun, S. and Zhang, W. (2014)
+Knowledge Vault: a web-scale approach to probabilistic knowledge fusion.
+In {\it Proceedings of the 20th ACM SIGKDD international conference on Knowledge discovery and data mining (KDD '14)}
+pp. 601--610.
+
+\bibitem[\protect\citename{Sundheim }1991]{Sundheim1991}
+Sundheim. B. (1991)
+Overview of the third message understanding evaluation and conference.
+In {\it Proceedings of the 3rd Conference on Message Understanding (MUC3 '91)}
+pp. 3--16, Stroudsburg, PA, USA, ACL.
+
+\bibitem[\protect\citename{Kim~Sang and De-Meulder }2003]{KimSang2003}
+Kim-Sang, T. and De~Meulder, F. (2003)
+Introduction to the CoNLL-2003 Shared Task: Language-independent Named Entity Recognition.
+In {\it Proceedings of the Seventh Conference on Natural Language Learning at HLT-NAACL 2003 - Volume 4 (CONLL '03)}
+pp. 142--147, Stroudsburg, PA, USA, ACL.
+
+\bibitem[\protect\citename{Bikel, Schwartz and Weischedel }1999]{Bikel1999}
+Bikel, D., Schwartz, R. and Weischedel, R. (1999)
+An algorithm that learns what's in a name.
+{\it Machine Learning}
+{\bf 34(1)}: 211--231.
+
+\bibitem[\protect\citename{Freitag and Mccallum }1999]{Freitag1999}
+Freitag, D. and Mccallum, A. (1999)
+Information Extraction with HMMs and Shrinkage.
+In {\it Proceedings of the AAAI-99 Workshop on Machine Learning for Information Extraction}
+pp. 31--36. AAAI Press.
+
+\bibitem[\protect\citename{Freitag and McCallum }2000]{Freitag2000}
+Freitag, D. and McCallum, A. (2000)
+Information Extraction with HMM Structures Learned by Stochastic Optimization.
+In {\it Proceedings of the Seventeenth National Conference on Artificial Intelligence and Twelfth Conference on Innovative Applications of Artificial Intelligence}
+pp. 584--589. AAAI Press.
+
+\bibitem[\protect\citename{Borthwick, Sterling, Agichtein and Grishman }1998]{Borthwick1998}
+Borthwick, A., Sterling, J., Agichtein, E. and Grishman, R. (1998)
+Exploiting diverse knowledge sources via maximum entropy in named entity recognition.
+In {\it Proceedings of the Sixth Workshop on Very Large Corpora}
+pp. 152--160. ACL.
+
+\bibitem[\protect\citename{Ratnaparkhi }1998]{Ratnaparkhi1998}
+Ratnaparkhi, A. (1998)
+Maximum Entropy Models for Natural Language Ambiguity Resolution.
+{\it PhD thesis}, Philadelphia, PA, USA.
+
+\bibitem[\protect\citename{McCallum, Freitag and Pereira }2000]{McCallum2000}
+McCallum, A., Freitag, D. and Pereira, F. (2000)
+Maximum entropy markov models for information extraction and segmentation.
+In {\it Proceedings of the Seventeenth International Conference on Machine Learning (ICML '00)}
+pp. 591--598, San Francisco, CA, USA, Morgan Kaufmann Publishers Inc.
+
+\bibitem[\protect\citename{Lafferty, McCallum and Pereira }2001]{Lafferty2001}
+Lafferty, J., McCallum, A. and Pereira, F. (2001)
+Conditional random fields: Probabilistic models for segmenting and labeling sequence data.
+In {\it Proceedings of the Eighteenth International Conference on Machine Learning (ICML '01)}, 
+pp. 282--289, San Francisco, CA, USA, Morgan Kaufmann Publishers Inc.
+
+\bibitem[\protect\citename{McCallum and Li }2003]{McCallum2003}
+McCallum, A. and Li, W. (2003)
+Early results for named entity recognition with conditional random fields, feature induction and web-enhanced lexicons.
+In {\it Proceedings of the Seventh Conference on Natural Language Learning at HLT-NAACL 2003 - Volume 4 (CONLL '03)}
+pp. 188--191, Stroudsburg, PA, USA, ACL.
+
+\bibitem[\protect\citename{Florian, Ittycheriah, Jing and Zhang }2003]{Florian2003}
+Florian, R. Ittycheriah, A. Jing, H. and Zhang, T. (2003)
+Named entity recognition through classifier combination.
+In {\it Proceedings of the Seventh Conference on Natural Language Learning at HLT-NAACL 2003}
+pp. 168--171.
+
+\bibitem[\protect\citename{Huang, Xu and Yu }2015]{Huang2015}
+Huang, Z., Xu, W. and Yu, K. (2015)
+Bidirectional {LSTM-CRF} models for sequence tagging.
+{\it CoRR}, abs/1508.01991.
+
+\bibitem[\protect\citename{Lample, Ballesteros, Subramanian, Kawakami and Dyer }2016]{Lample2016}
+Lample, G., Ballesteros, M., Subramanian, S., Kawakami, K. and Dyer, C. (2016)
+Neural architectures for named entity recognition.
+{\it CoRR}, abs/1603.01360.
+
+\bibitem[\protect\citename{Ma and Hovy }2016]{Ma2016}
+Ma, X. and Hovy, E. (2016)
+End-to-end sequence labeling via bi-directional {LSTM}-{CNN}s-{CRF}.
+In {\it Proceedings of the 54th Annual Meeting of the Association for Computational Linguistics (Volume 1: Long Papers)}
+pp. 1064--1074, Berlin, Germany, ACL.
+
+\bibitem[\protect\citename{Pennington, Socher and Manning }2014]{Pennington2014}
+Pennington, J., Socher, R. and Manning, C. (2014)
+Glove: Global vectors for word representation.
+In {\it Empirical Methods in Natural Language Processing (EMNLP)}
+pp. 1532--1543.
+
+\bibitem[\protect\citename{Peters, Neumann, Iyyer, Gardner, Clark, Lee and Zettlemoyer }2018]{Peters2018}
+Peters, M., Neumann, M., Iyyer, M., Gardner, M., Clark, C., Lee, K. and Zettlemoyer, L. (2018)
+Deep contextualized word representations.
+In {\it Proceedings of the 2018 Conference of the North American Chapter of the Association for Computational Linguistics: Human Language Technologies, Volume 1 (Long Papers)}
+pp. 2227--2237, New Orleans, Louisiana, ACL.
+
+\bibitem[\protect\citename{Devlin, Chang, Lee, and Toutanova }2018]{Devlin2018}
+Devlin, J., Chang, M., Lee, K. and Toutanova, K. (2018)
+{BERT}: Pre-training of deep bidirectional transformers for language understanding.
+{\it Preprint arXiv:1810.04805}.
+
+\bibitem[\protect\citename{Akbik, Blythe and Vollgraf }2018]{Akbik2018}
+Akbik, A., Blythe, D. and Vollgraf, R. (2018)
+Contextual string embeddings for sequence labeling.
+In {\it Proceedings of the 27th International Conference on Computational Linguistics}
+pp. 1638--1649, Santa Fe, New Mexico, ACL.
+
+\bibitem[\protect\citename{Baevski, Edunov, Liu, Zettlemoyer and Auli }2019]{Baevski2019}
+Baevski, A., Edunov, S., Liu, Y., Zettlemoyer, L. and Auli, M. (2019)
+Cloze-driven pretraining of self-attention networks.
+{\it Preprint arXiv:1903.07785}.
+
+\bibitem[\protect\citename{Caruana, Lawrence and Giles }2000]{Caruana2000}
+Caruana, R., Lawrence, S. and Giles, L. (2000)
+Overfitting in neural nets: Backpropagation, conjugate gradient, and early stopping.
+In {\it Proceedings of the 13th International Conference on Neural Information Processing Systems (NIPS'00)}
+pp. 381--387, Cambridge, MA, USA, MIT Press.
+
+\bibitem[\protect\citename{Hochreiter and Schmidhuber }1997]{Hochreiter1997}
+Hochreiter, S. and Schmidhuber, J. (1997)
+Long short-term memory.
+{\it Neural Computation}
+{\bf 9(8)}: 1735--1780.
+
+\bibitem[\protect\citename{Li and Gray }2000]{Li2000}
+Li, J. and Gray, R. (2000)
+Image Segmentation and Compression Using Hidden Markov Models.
+Kluwer Academic Publishers, Norwell, MA, USA.
+
+\bibitem[\protect\citename{Liu and Nocedal }1989]{Liu1989}
+Liu, D. and Nocedal, J. (1989)
+On the limited memory bfgs method for large scale optimization.
+{\it Mathematical Programming}
+{\bf 45(1)}: 503--528.
+
+\bibitem[\protect\citename{Rabiner }1990]{Rabiner1990}
+Rabiner, L. (1990)
+Readings in Speech Recognition. Chapter: A Tutorial on Hidden Markov Models and Selected Applications in Speech Recognition.
+Morgan Kaufmann Publishers Inc., San Francisco, CA, USA.
+
+\bibitem[\protect\citename{Ramshaw and Marcus }1999]{Ramshaw1999}
+Ramshaw, L. and Marcus, M. (1999)
+Text Chunking Using Transformation-Based Learning, 
+pp. 157--176. Springer Netherlands, Dordrecht, 1999.
+
+\bibitem[\protect\citename{Rijsbergen }1979]{Rijsbergen1979}
+Rijsbergen, C. (1979)
+Information Retrieval.
+Butterworth-Heinemann, Newton, MA, USA, 2nd edition.
 

### 2019-06-16 tex/article.tex
General refactoring.

@@
 	Universidade Federal de Minas Gerais$^{A,B}$ \\
-	Google Engineering$^A$, Belo Horizonte - MG, Brazil}
+	Google Engineering$^B$, Belo Horizonte - MG, Brazil}
 
@@
 \gls{rne} task. With this purpose in mind, we introduce a novel \gls{ner} dataset 
-with labeled entities, consisting of faculty directories from universities across the world. 
+with labeled entities, consisting of faculty directories from universities across the world,
+the RNE dataset~\footnote{
+The dataset is available in https://github.com/jmfveneroso/ner-on-html.
+}.
 We compare the models in terms of their Precision, Recall, F-scores and their 
@@
 we proposed to solve with the application of machine learning methods of \gls{ner}.
-This chapter presents the related research in the fields of \gls{wde} 
+This section presents the related research in the fields of \gls{wde} 
 in Section~\ref{sec:wde} and \gls{ner} in Section~\ref{sec:ner}.
@@
 
-\cite{Sarawagi2008} introduced a classification that segmented wrappers in
+Sarawagi~\shortcite{Sarawagi2008} introduced a classification that segmented wrappers in
 rule-based methods, statistical methods and hybrid models, bringing together 
@@
 
-Surveys by~\cite{Ferrara2014}, \cite{Schulz2016} and \cite{Varlamov2016} updated the 
-previous surveys on Information Extraction methods with some interesting innovations. 
+Recent surveys by Ferrara, De Meo, Fiumara and Baumgartner~\shortcite{Ferrara2014}, 
+Schulz, Lassig and Gaedke~\shortcite{Schulz2016} and
+Varlamov and Turdakov~\shortcite{Varlamov2016}
+updated the previous surveys on Information Extraction methods with some interesting innovations. 
 Some examples are: the Visual Box Model~\cite{Krupl2005}, a data extraction system that produces 
@@
 A statistical approach to unsupervised domain 
-independent \gls{wde} was described by~\cite{Zhu2005}. The 2D CRF 
+independent \gls{wde} was described by Zhu, Nie, Wen, Zhang, and Ma~\shortcite{Zhu2005}. The 2D CRF 
 model takes a webpage segmented into data blocks and employs a two dimensional \gls{crf}
-model to perform attribute labeling. The model was further improved 
-in~\cite{Zhu2006} to model record segmentation and attribute labeling as a joint task.
+model to perform attribute labeling. The model was further improved~\cite{Zhu2006} to model 
+record segmentation and attribute labeling as a joint task.
 Some of the limitations of early unsupervised methods 
@@
 \gls{wde} methods have undoubtedly improved extraordinarily, but
-as pointed by \cite{Schulz2016}, it is difficult to compare the results 
+as pointed by Schulz, Lassig and Gaedke~\shortcite{Schulz2016}, it is difficult to compare the results 
 achieved by competing tools. Also, many tools seem to rely excessively on heuristic methods.
@@
 But in the late nineties, \gls{hmm}s also found important applications in \gls{ie}
-and \gls{ner} as in the works by~\cite{Bikel1999}, 
-\cite{Freitag1999}, and \cite{Freitag2000}.
+and \gls{ner} as in the works by Bikel, Schwartz and Weischedel~\shortcite{Bikel1999}, 
+Freitag and Mccallum~\shortcite{Freitag1999}, 
+and Freitag and Mccallum~\shortcite{Freitag2000}.
 
@@
 To our knowledge, the best NER system up to this date (considering the performance in the
-{CoNLL-2003} dataset) is the bidirectional transformer model proposed by~\cite{Baevski2019} that uses
+{CoNLL-2003} dataset) is the bidirectional transformer model proposed by Baevski, Edunov, Liu, Zettlemoyer and Auli~\shortcite{Baevski2019} that uses
 a stack of self-attention modules and ELMo embeddings. Table~\ref{tab:ner_model_comparison}
@@
       \midrule
-       \cite{Florian2003} ({CoNLL-2003} Winner)    & 88.76 \\
-       \cite{Collobert2011}                        & 89.59 \\
-       \cite{Huang2015}                            & 90.10 \\
-       \cite{Lample2016}                           & 90.94 \\
-       \cite{Ma2016}                               & 91.21 \\
-       \cite{Peters2018}                           & 92.22 \\
-       \cite{Devlin2018}                           & 92.80 \\
-       \cite{Akbik2018}                            & 93.09 \\
-       \cite{Baevski2019}                          & 93.50 \\
+      Florian, Ittycheriah, Jing and Zhang 2003 (CoNLL-2003 Winner)            & 88.76 \\
+      Collobert, Weston, Bottou, Karlen, Kavukcuoglu, and Kuksa 2011           & 89.59 \\
+      Huang, Xu and Yu 2015                                                    & 90.10 \\
+      Lample, Ballesteros, Subramanian, Kawakami and Dyer 2016                 & 90.94 \\
+      Ma and Hovy 2016                                                         & 91.21 \\
+      Peters, Neumann, Iyyer, Gardner, Clark, Lee and Zettlemoyer 2018         & 92.22 \\
+      Devlin, Chang, Lee, and Toutanova 2018                                   & 92.80 \\
+      Akbik, Blythe and Vollgraf 2018                                          & 93.09 \\
+      Baevski, Edunov, Liu, Zettlemoyer and Auli 2019                          & 93.50 \\
       \bottomrule
@@
 %
-These parameters can obtained with maximum likelihood estimation from the relative
-frequencies of labels and words in the corpus. The best sequence of labels can be computed 
+These parameters can be obtained with maximum likelihood estimation from the relative
+frequencies of labels and words in the corpus. However, tokens that do not happen in the
+training set will have null probability, what is problematic because named entities often
+contain unknown tokens. To counter this problem, we used additive smoothing in the 
+emission probability estimates.
+The best sequence of labels can be computed 
 with a variable state Viterbi approach \cite{Li2000}. However, as we increase $ k $, this computation 
@@
 For example, only because a named entity label occurs more often inside lists in a page, we cannot
-assume that this will be the case on other web pages. 
+assume that this will be the case in other web pages. 
 Nonetheless, the HTML structure is not useless. Inside a single web page, the HTML tag is a good predictor
@@
 that happen together inside a list are very likely to belong to the same category.
-Yet, this pattern cannot be generalized to other pages, because we cannot expect that every list will
-be listing the same types of entities.
 
@@
 Assuming time invariance, we need to estimate parameters $ \hat{P}(f_{j}|y) $, 
-relative to each possible assignment of $ y $.
+relative to each feature and assignment of $ y $.
 The maximum likelihood estimators for these feature parameters can be obtained
@@
 These estimators yield good experimental results for textual features such as the 
-capitalization of a word, but for the reasons already discussed, it does not work
+capitalization of a word, but for the reasons already discussed, they do not work
 well with HTML features, such as the current HTML tag. To make better use of the
-HTML features, consider a set $ F_T $ textual features unrelated to the HTML structure
-and a set $ F_H $ of HTML features related to the HTML structure.
+HTML features, consider a set $ F_T $ features unrelated to the HTML structure
+and a set $ F_H $ of features related to the HTML structure.
 We can use a \gls{hmm} trained exclusively with the first set of features $ F_T $
@@
 where $ \theta $ is the parameter vector that we are going to learn, $ f_k(y_{t-1}, y_{t}, X) $ 
-are feature functions over the current timestep $ t_y $, the previous timestep $ y_{t-1}$, 
+are the feature functions over the current timestep $ t_y $, the previous timestep $ y_{t-1}$, 
 and the observation vector $ X $. And the partition function $ Z(x) $, takes the form:
@@
 suitable for processing sequences, and consequently for solving text related tasks. 
-Figure~\ref{fig:rnn_network} describes an RNN for sequence labeling unrolled through multiple 
+Figure~\ref{fig:rnn_network} describes a RNN for sequence labeling unrolled through multiple 
 timesteps. 
@@
 At each timestep, the neural network computes a hidden state $ h_t $ using an input 
-vector $ x_t $ and the previous hidden state $ h_{t-1} $, that retains information from past 
+vector $ x_t $ and the previous hidden state $ h_{t-1} $ that retains information from past 
 iterations. Finally, the RNN produces an output vector $ y_t $ representing the label for that 
-timestep. A common definition for an RNN cell is given by the equations:
+timestep. A common definition for a RNN cell is given by the equations:
 %
@@
 in the neural sequence model is that the labels are jointly decoded for a whole sentence 
-instead of being predicted individually. Another possibility would be to use a beam search
-decoder to find an optimal sequence of labels. Predicted tags should be highly correlated 
+instead of being predicted individually. 
+Predicted tags should be highly correlated 
 in a named entity recognition task, so it is desirable to predict sequences conjointly.
@@
 
-This architecture achieved an F1 score of 90.10 on the English data from the CoNLL-2003 
+This architecture achieved a F1 score of 90.10 on the English data from the CoNLL-2003 
 NER shared task \cite{KimSang2003}, in contrast to 85.17 for a bidirectional LSTM without 
@@
 
-The convolutional neural network receives character embeddings as inputs. The character 
+The \gls{cnn} receives character embeddings as inputs and extracts
+morphological features by sliding one dimensional filters over the sequence of characters 
+and collapsing the filter outputs with a global max pooling layer, producing character
+representations with a size determined by the number of filters. 
+This means, that when a filter gets a good match at any position in the sequence, the 
+max pooling layer output relative to that filter will be triggered, therefore this type of 
+character representation detects position invariant morphological features. For example,
+the word "finger" would trigger a filter for "ing" the same way the word "writing" would
+trigger this filter. The character 
 representations generated by the CNN are combined with word level representations 
@@
 useful in the NER task, since similar named entities often present morphological similarities. 
-This architecture obtained an F1 score of 91.21 in the CoNLL2003 dataset. In our experiments, 
+This architecture obtained a F1 score of 91.21 in the CoNLL-2003 dataset. In our experiments, 
 the LSTM-CRF architecture with CNN character representations uses a one dimensional convolutional 
-neural network with 30 filters and a window size of three characters on top of the LSTM-CRF 
-architecture. The character embeddings fed to the CNN have 30 dimensions that are randomly 
+neural network with 50 filters and a window size of three characters on top of the LSTM-CRF 
+architecture. The character embeddings fed to the CNN have 50 dimensions that are randomly 
 initialized.
@@
 LSTM with 25 hidden states, producing character representations of 
-size 50. The character embeddings have 30 dimensions that are randomly initialized.
+size 50. The character embeddings have 50 dimensions that are randomly initialized.
 
@@
 
-In the experiments, all neural models were trained using mini batch Stochastic Gradient Descent over 50 epochs with batch size 10,
-learning rate 0.01, momentum 0.9 and decay rate 0.05. We used early stopping \cite{Caruana2000} to select the best 
+In the experiments, all neural models were trained using mini batch Stochastic Gradient Descent over 20 epochs with batch size 10,
+learning rate 0.001, momentum 0.9 and decay rate 0.05. We used early stopping \cite{Caruana2000} to select the best 
 parameters, considering the F1 measure in the validation set. All neural models used 
-GloVe 300-dimensional word embeddings \cite{Pennington2014} that were fine tuned during training.
+GloVe 300-dimensional word embeddings \cite{Pennington2014} that were not fine tuned during training.
 
@@
 be found in https://univ.cc/world.php}. 
-The dataset size was limited to a number of pages that could be viably labeled manually and
-that could still represent many different countries. 
-Also, university pages that contained 
+University pages that contained 
 corrupt HTML or JavaScript code that performed lazy loading of data records were
@@
 may contain up to a few hundred names whereas other documents may contain 
-only a dozen names. This difference in document size and characteristics 
-may be problematic when comparing different extraction systems, because a system 
-that performs well on some types of pages may perform poorly in other types.
-To avoid this problem, we tried to keep the proportion between the number of tokens
-and the number of documents roughly the same for all data files.
+only a dozen names.
 
@@
 list partially, the matching tokens were annotated with a partial match tag. This dictionary
-was used by some of the models that will be discussed in the experiments chapter, however it 
+was used by some of the models that will be discussed in the experiments section, however it 
 must be stated that one of the main advantages of Deep Neural Networks relative to other
@@
       Validation & 0.8474 & 0.2858 & 0.4274 & 511 of 1788 \\ 
-      Test       & 0.8717 & 0.3287 & 0.4773 & 890 of 2708 \\ 
+      Test       & 0.8717 & 0.3268 & 0.4754 & 890 of 2723 \\ 
       \bottomrule
@@
 match. Any useful extraction method should at least improve upon this approach.
-Recall is very low because the dictionary is incomplete and precision falls short of
+Recall is very low because the dictionary is incomplete and Precision falls short of
 top performing extraction methods. This last result is surprising since we are only extracting 
-exact matches. The reason for the low precision is that exact dictionary matches may actually 
+exact matches. The reason for the low Precision is that exact dictionary matches may actually 
 only correspond to partial matches in the dataset. For example, if the dictionary has an entry
@@
 effectiveness. However, this is hardly the case. By intuition, we know that tabular HTML 
-documents, such as faculty listings, are very different from plain text. But now, having a
-labeled dataset for \gls{ner} on HTML, we can understand how different they really are.
+documents, such as faculty listings, are very different from plain text. But with the
+RNE dataset for \gls{ner} on HTML, we can understand how different they really are.
 
@@
 sets of the \gls{rne} dataset, and the number of named entities that contain at least one 
-unknown token.
+unknown token. Roughly four in every five named entities contain at least one unknown
+token.
 
@@
       NEs without Unknown Tokens & 342  & 19.13\% & 518  & 19.02\% \\
-      Total                      & 1693 & 100.00\%   & 2638 & 100.00\%   \\
+      Total                      & 1788 & 100.00\% & 2723 & 100.00\%   \\
       \bottomrule
@@
 
-We conducted two groups of experiments to evaluate machine learning models of 
-\gls{ner} at the researcher name extraction task and answer the following 
-research questions:
-%
-\begin{enumerate}
-\item Which are the best featureless machine learning models for NER on the web?
-\item Which are the best machine learning models for NER on the web with a dictionary and a good selection of features?
-\end{enumerate}
-%
+The main objective of this article is to compare the best methods for \gls{ner} on the 
+web considering the \gls{rne} task. The value of a specific method is determined
+not only by its accuracy, but also by the amount of feature engineering required, the training
+time required, and the overall complexity of the model when we consider its gains relative to
+simpler alternatives. All models were trained on Amazon G3.4xlarge instances, which are equipped with 
+NVIDIA Tesla M60 GPUs with 8GB internal memory, however all the HMM operations were done in the CPU.
+The implementations were done entirely in Python using Google's Tensorflow deep learning 
+library~\footnote{https://www.tensorflow.org/.}. 
+Subsection~\ref{ssec:exp_1} discusses the results of featureless models and Subsection~\ref{ssec:exp_2} 
+discusses models that incorporated features and a dictionary.
+
+\subsection{Featureless models}
+\label{ssec:exp_1}
+
+The first experiment aimed to evaluate the performance of sequence models that used 
+only words as features in the \gls{rne} task.
 A model that works well despite the absence of a good feature selection is arguably more valuable than
-a method that requires a lot of feature engineering or a big dictionary of named entities, as long as 
+a method that requires feature engineering or a big dictionary of named entities, as long as 
 its accuracy is sufficiently high for the intended purpose. This is where Deep Neural Networks are most
@@
 and a longer training time, what must also be taken into account. 
-
-\subsection{Experiment 1: No features}
-
-Experiment 1 aimed to evaluate the performance of sequence model with no features
-besides GloVe-100 embeddings. In the case of HMMs, only the lowercase
-unaccented token was used as a feature. Table \ref{tab:experiment1} 
-shows the Precision (P), Recall (R), and F1-scores (F1) for this
-experiment.
+The tested HMMs and CRFs used only the unaccented lowercase version of the current token as a feature
+to predict labels at each timestep. The neural networks used GloVe-300 word embeddings using the 
+unaltered token as a lookup index. Due to the rugged shape of the loss function, the neural networks 
+do not necessarily converge to an optimal set of parameters, so the reported results are the averages
+over five runs of each model.
+
+Table \ref{tab:experiment1} shows the Precision (P), Recall (R), F1-scores (F1) and the time to 
+train the models and run predictions (Time) for HMMs up to third order, CRFs, and Bi-LSTM-CRFs with
+CNN-based character representations (CNNc) and LSTM-based character representations (LSTMc).
 
@@
   \begin{center}
-    \begin{tabular}{ lllllll }
+    \begin{tabular}{ llllllll }
       \toprule
-      \multirow{2}{*}{Model} & \multicolumn{3}{c}{Validation} & \multicolumn{3}{c}{Test} \\
+      \multirow{2}{*}{Model} & \multicolumn{3}{c}{Validation} & \multicolumn{3}{c}{Test} & \multirow{2}{*}{Time} \\
                              & \multicolumn{1}{c}{P} & \multicolumn{1}{c}{R} & \multicolumn{1}{c}{F1}
-                             & \multicolumn{1}{c}{P} & \multicolumn{1}{c}{R} & \multicolumn{1}{c}{F1} \\
+                             & \multicolumn{1}{c}{P} & \multicolumn{1}{c}{R} & \multicolumn{1}{c}{F1} & \\
       \midrule
-      HMM-1                 & 0.693 & 0.581 & 0.632 & 0.637 & 0.458 & 0.533 \\
-      HMM-2                 & 0.703 & 0.630 & 0.665 & 0.653 & 0.527 & 0.583 \\
-      HMM-3                 & 0.616 & 0.618 & 0.617 & 0.551 & 0.468 & 0.506 \\
-      CRF                   & 0.806 & 0.805 & 0.806 & 0.795 & 0.710 & 0.750 \\
-      Bi-LSTM-CRF           & 0.906 & 0.938 & 0.922 & 0.909 & 0.865 & 0.886 \\
-      +CNNc                 & 0.929 & 0.946 & 0.938 & 0.921 & 0.881 & 0.901 \\
-      +LSTMc                & 0.928 & 0.950 & 0.939 & 0.920 & 0.886 & 0.902 \\
+      HMM-1                 & 0.693 & 0.581 & 63.2 & 0.637 & 0.458 & 53.3 & 15.72   \\
+      HMM-2                 & 0.703 & 0.630 & 66.5 & 0.653 & 0.527 & 58.3 & 31.32   \\
+      HMM-3                 & 0.616 & 0.618 & 61.7 & 0.551 & 0.468 & 50.6 & 80.69   \\
+      CRF                   & 0.806 & 0.805 & 80.6 & 0.795 & 0.710 & 75.0 & 918.25  \\
+      Bi-LSTM-CRF           & 0.906 & 0.938 & 92.2 & 0.909 & 0.865 & 88.6 & 2580.30 \\
+      Bi-LSTM-CRF+CNNc      & 0.929 & 0.946 & 93.8 & \textbf{0.921} & 0.881 & 90.1 & 3379.33 \\
+      Bi-LSTM-CRF+LSTMc     & 0.928 & 0.950 & 93.9 & 0.920 & \textbf{0.886} & \textbf{90.2} & 4412.41 \\
       \bottomrule
@@
   \end{center}
-  \caption{Precision, recall and F1 in the NER on HTML dataset for models that incorporate no features}
+  \caption{Precision, recall and F1 in the RNE dataset for models that incorporate no features}
   \label{tab:experiment1}
@@
 
-Without carefully designed features or gazetteers, HMMs and CRFs have a very 
-poor performance, achieving an F1-score of only 0.5783 for HMM-2 and 0.6244 for CRF
-at the test set. This is expected, since these models rely on good feature selections.
-
-The neural models achieved high F1-scores in the test
-set even with the absence of features. The plain BI-LSTM-CRF architecture improved performance 
-significantly in comparison with the conventional CRF (0.8427 against 0.6244). 
-Also, neural character representations boosted performance by a significant margin
-reaching an F1-score of 0.8758 for CNN-based representations and 0.8867 for LSTM-based
-representations. LSTM based representations were superior in modelling
-morphological features, perhaps because they are able to differentiate suffixes 
-and prefixes, while CNN filters are position invariant.
-
-The results in Experiment 1 also show that pretrained word embeddings can work 
-as a kind of universal gazetteer. Words with similar embeddings are likely to 
-belong to the same class. This knowledge combined with the ability to learn 
-morphological features can make up for the scarcity of textual data on some 
-webpages.
-
-\subsection{Experiment 2: All features}
+Without resorting to features besides the current word or a dictionary of named entities, HMMs and CRFs have a
+poor performance. Increasing the number of previous timesteps considered by the HMM helps
+up to a point, but its effectiveness is limited. The second order HMM (HMM-2) achieves a 58.3 F1
+while the third order HMM (HMM-3) suffers a drop in performance with a 50.6 F1. The CRF is the
+best classical model, achieving a 75.0 F1 in the test set.
+
+All neural models achieved a considerably better performance in the RNE task. The plain Bi-LSTM-CRF
+achieved a 88.6 F1. Character representations improved the performance by a little amount,
+to 90.1 F1 for the CNN-based representations and to 90.2 F1 for the LSTM-based
+representations. In CoNLL-2003, the reported results were 91.2 F1 for the CNN-based
+representations~\cite{Ma2016} and 90.9 F1 for the LSTM-based representations~\cite{Lample2016}, improving
+upon the plain Bi-LSTM-CRF model~\cite{Huang2015}, which achieved a 90.1 F1. These results seem to be in
+accord with our own experiments for the \gls{rne} dataset, with the primary difference that the
+LSTM-based character representations were more effective in our experimental setting,
+contrasting with the CoNLL-2003 results.
+Nevertheless, the difference between the two types of character representations 
+is not substantial enough to allow a solid conclusion about the quality of
+one model over the other. However, the benefit of adding character representations 
+to plain recurrent neural networks is clearly supported by the evidence.
+
+\subsection{All features}
+\label{ssec:exp_2}
 
@@
       3  & Partial dictionary match & Binary \\
-      4  & Email & Binary \\
-      5  & Number & Binary \\
-      6  & Honorific (Mr., Mrs., Dr., etc.) & Binary \\
-      7  & Matches a URL & Binary \\
+      4  & Is an Email & Binary \\
+      5  & Contains a Number & Binary \\
+      6  & Is an Honorific (Mr., Mrs., Dr., etc.) & Binary \\
+      7  & Is a URL & Binary \\
       8  & Is capitalized & Binary \\
@@
 
-The only features that demand further explanation are features 10 and 11.
+Features 2 and 3 relate to the dictionary extracted from DBLP described in Section~\ref{cha:dataset}.
 Feature 10 is the token's enclosing HTML tag and its parent tag concatenated.
 Feature 11 is the CSS class for the token's HTML tag.
-Both of these features are only useful in the self-training strategy for HMMs and the
-attention architectures for Bi-LSTM-CRFs. In other models, we only use features 1 to 9.
-Experiment 2 aimed to evaluate the performance of sequence model with all
-the features described in Table~\ref{tab:features}. In this experiment, we
-also evaluate the self-training strategy for HMMs described in Section 
-\ref{sssec:self_training}. The self trained HMMs are described with the 
-suffix "+ST". Table \ref{tab:experiment2} shows the results for Experiment 2.
+Features 10 and 11 are only useful in the self-training strategy for HMMs, because
+the patterns represented by these features are webpage specific. In other models, we only used
+features 1 to 9.
+
+Table \ref{tab:experiment2} shows the results for the models that incorporated features. 
+The self trained HMMs are described with the suffix +ST.
 
@@
   \begin{center}
-    \begin{tabular}{ lllllll }
+    \begin{tabular}{ llllllll }
       \toprule
-      \multirow{2}{*}{Model} & \multicolumn{3}{c}{Validation} & \multicolumn{3}{c}{Test} \\
+      \multirow{2}{*}{Model} & \multicolumn{3}{c}{Validation} & \multicolumn{3}{c}{Test}                       & \multirow{2}{*}{Time} \\
                              & \multicolumn{1}{c}{P}          & \multicolumn{1}{c}{R} & \multicolumn{1}{c}{F1}
-                             & \multicolumn{1}{c}{P} & \multicolumn{1}{c}{R} & \multicolumn{1}{c}{F1} \\
+                             & \multicolumn{1}{c}{P}          & \multicolumn{1}{c}{R} & \multicolumn{1}{c}{F1} & \\
       \midrule
-      HMM-1                           & 0.730 & 0.714 & 0.722 & 0.826 & 0.684 & 0.748 \\
-      HMM-2                           & 0.720 & 0.710 & 0.715 & 0.820 & 0.724 & 0.769 \\
-      HMM-3                           & 0.721 & 0.702 & 0.711 & 0.791 & 0.667 & 0.724 \\
-      HMM-1 + Self-Training           & 0.747 & 0.906 & 0.819 & 0.866 & 0.867 & 0.866 \\
-      HMM-2 + Self-Training           & 0.771 & 0.912 & 0.835 & 0.885 & 0.869 & 0.877 \\
-      HMM-3 + Self-Training           & 0.788 & 0.917 & 0.847 & 0.826 & 0.803 & 0.814 \\
-      CRF (Group B)                   & 0.881 & 0.903 & 0.892 & 0.870 & 0.786 & 0.826 \\
-      Bi-LSTM-CRF (Group B)           & 0.914 & 0.947 & 0.930 & 0.921 & 0.883 & 0.901 \\
-      +CNN chars                      & 0.939 & 0.947 & 0.943 & 0.922 & 0.868 & 0.894 \\
-      +LSTM chars                     & 0.932 & 0.942 & 0.937 & 0.913 & 0.855 & 0.883 \\
+      HMM-1                & 0.730 & 0.714 & 72.2 & 0.826 & 0.684 & 74.8 & 15.22 \\
+      HMM-2                & 0.720 & 0.710 & 71.5 & 0.820 & 0.724 & 76.9 & 30.10 \\
+      HMM-3                & 0.721 & 0.702 & 71.1 & 0.791 & 0.667 & 72.4 & 81.14 \\
+      HMM-1+ST             & 0.747 & 0.906 & 81.9 & 0.866 & 0.867 & 86.6 & 28.54 \\
+      HMM-2+ST             & 0.771 & 0.912 & 83.5 & 0.885 & 0.869 & 87.7 & 57.52 \\
+      HMM-3+ST             & 0.788 & 0.917 & 84.7 & 0.826 & 0.803 & 81.4 & 154.67 \\
+      CRF                  & 0.881 & 0.903 & 89.2 & 0.870 & 0.786 & 82.6 & 965.59 \\
+      Bi-LSTM-CRF          & 0.918 & 0.947 & 93.2 & 0.926 & 0.878 & 90.1 & 2261.79 \\
+      Bi-LSTM-CRF+CNNc     & 0.918 & 0.956 & 93.7 & \textbf{0.933} & \textbf{0.902} & \textbf{91.7} & 3255.93 \\
+      Bi-LSTM-CRF+LSTMc    & 0.904 & 0.958 & 93.0 & 0.912 & 0.875 & 89.3 & 4249.21 \\
       \bottomrule
@@
   \end{center}
-  \caption{Precision, recall and F1 in the NER on HTML dataset for models that incorporate all features}
+  \caption{Precision, recall and F1 in the RNE dataset for models that incorporate all features}
   \label{tab:experiment2}
@@
 
-Conventional models like HMMs, and CRFs can become competitive with
-the right selection of features and a good gazetteer, however they still lose
-to the best neural model without features, demonstrating their inherent limitations.
-HMMs that employed trigrams or quadrigrams (hmm-2, hmm-3) performed better than
-regular HMMs. Also, we can see that the self-training strategy for HMMs improved 
-the quality of the models significantly in all cases, boosting both precision and recall. 
-This hints at the possibility to adapt this strategy to neural networks and boost
-the performance of neural models on the NER on HTML task.
-
-The neural models also improved a little with the addition of features. The plain BI-LSTM-CRF
-model gets a closer performance to the models that employed neural character 
-representations. It suggests that the LSTM and CNN character representations 
-were able to learn at least part of the morphological features automatically in the
-first experiment. So, when these features are added explicitly, the differences 
-in performance between different neural models become less noticeable.
+Conventional models like HMMs, and CRFs can become quite competitive with
+the right selection of features and a good gazetteer, however they still have worse F1 scores
+than the neural models without features, demonstrating their inherent limitations.
+Second-order HMMs (HMM-2) performed consistently better than
+the other HMM variants. The self-training strategy was effective in improving the 
+performance of all HMMs considerably. The best model (HMM-2) went from a 76.9 F1 to
+87.7 F1, with a substantial improvement in Recall (0.724 to 0.869). As with the 
+featureless models, the CRF is superior to the HMMs that did not incorporate the self-training
+strategy, achieving 82.6 F1.
+
+The inclusion of features in the neural models had no decisive positive effect. The plain 
+Bi-LSTM-CRF and the model with CNN-based character representations had an increase in 
+F1, 90.1 and 91.7 respectively, but the Bi-LSTM-CRF with LSTM-based character representations 
+actually suffered a slight decrease in performance relative to the featureless model. 
+Overall, the power of deep neural networks for sequence labeling lies 
+in their remarkable capacity to perform well without resorting to features besides the raw text. 
+The small difference in performance between featureless neural networks and neural networks 
+with features demonstrates that the CNN or LSTM character representations seem to be effective 
+in extracting morphological features automatically and the pre-trained GloVe word embeddings 
+can outweigh the absence of a gazetteer, since named entities that belong to the same category
+tend to have similar embeddings.
+
+Despite the superior performance of Neural Networks in this task, there remains an important 
+consideration to be made. As we increase the complexity and the training time required by the models, there 
+is only a scant gain in terms of F1. For example, the 
+Bi-LSTM-CRF with LSTM character representations achieved a 90.2 F1, while 
+the HMM-2 using a Self-Training strategy achieved a 87.9 F1. It is a small difference
+in performance, considering the disparity of model complexity. This reality
+is not limited to the RNE dataset. For example, 
+the winning NER model in the CoNLL-2003 competition~\cite{Florian2003} used a combination of simple
+statistical models and feature engineering to achieve 88.76 F1 in the English test set, 
+while the Bi-LSTM-CRF with LSTM characters achieved 90.94 F1~\cite{Lample2016} and the Bi-LSTM-CRF with 
+CNN characters achieved 91.21 F1~\cite{Ma2016}. That is,
+the improvement is below three points in the F1 score.
+
+The Neural Network approach to NER does not demand any feature engineering or self-training, 
+contrasting with the HMM approach, which is highly reliant on
+the right selection of features and the self-training strategy. However, the absence of
+human intervention in Deep Neural Networks is questionable to some degree since there is the
+need to define many hyper parameters and
+details about the neural architecture, such as the number of \textit{LSTM} layers and
+hidden weights, where to add dropout layers, which pre-trained word embeddings to use, etc. In summary, 
+there are many choices to be made, none of which have definitive theoretical justification, 
+so the model variations need to be tested empirically. This requires many iterations between setting
+parameters, obtaining results, and tuning parameters once again. Considering that each of 
+these iterations can take at least a couple of hours to finish, it is not clear if
+selecting features is necessarily a more arduous struggle.
+
+To the best of our abilities, the Tensorflow implementation of the Bi-LSTM-CRF + LSTMc
+model running on a AWS GPU instance took approximately 4412 seconds to train 
+and run predictions. While, the HMM-2 did the same in approximately
+58 seconds, running in a conventional CPU with unoptimized code. This is almost 80 times 
+faster, what is relevant if we are trying to improve the models over many iterations.
+Finally, if we consider the intellectual cost of understanding and implementing both 
+models and the code maintainability of both implementations, the difference becomes even 
+more profound.
 
@@
 
-Machine-learning-based sequence labeling models provide a flexible approach to \gls{wde}, 
-in contrast to more traditional methods. In simple cases, a neural
-named entity tagger may be sufficient to solve the entire data extraction task. In 
-other cases, the sequence tagger remains an important part of the \gls{wde} 
-system, as it performs attribute labeling on data records with accuracy and flexibility.
-
-In this article, we compared the performance of different sequence models on the task of
-named entity recognition on HTML, introducing a novel dataset that is publicly available. 
-We found that there are two components to the most successful models: neural based character 
-representations that extract morphological features automatically, and the joint modelling 
-of output labels.
-
-We showed that a BI-LSTM-CRF neural network with LSTM-based character representations can 
-be employed effectively to solve a \gls{wde} task, achieving an F1-score of 
-0.8867 with no feature engineering on the faculty listings dataset.
+Machine-learning-based sequence labeling models are an effective approach for NER 
+both on plain text and on web data extraction tasks. 
+In this article, we compared the performance of HMMs, CRFs and Neural Networks on the task of
+researcher name extraction, introducing a novel dataset that is publicly available,
+the RNE dataset.
+Models trained in plain text are not effective to perform NER on the web, because 
+HTML pages contain a substantial amount of boilerplate text and the sentences are shorter 
+than typical plain text, what confounds the classifiers. The results for the RNE dataset
+confirm many results reported in the natural language processing literature, but it also 
+demonstrates that different web extraction tasks will most likely demand specific labeled 
+datasets.
+
+Constructing labeled datasets for sequence labeling is awfully expensive, especially if we
+are interested in extracting more than a couple of entity types. This leads to the
+conclusion that unsupervised or at least semi-supervised extraction methods are a more 
+prosperous line of research. Unfortunately, the performance of unsupervised systems is still
+not comparable to what can be achieved with supervised systems.
+
+The neural architectures for sequence labeling performed better than other models in the 
+researcher name extraction task. Among them, the Bi-LSTM-CRF with LSTM-based character 
+representations achieved a 90.2 F1 in the task using only GloVe-300 word embeddings. By adding
+textual features and a gazetteer, the Bi-LSTM-CRF with CNN-based character representations
+achieved a 91.7 F1 in the test set of the RNE dataset. However, these neural architectures are
+quite complex, demanding sophisticated decisions such as the choice of hyper parameters for the 
+optimization method, the number of LSTM layers, where to add dropout layers, and the choice of 
+word embeddings. All of these decisions
+must be tested empirically since there is seldom theoretical justification for one choice over
+the other.
+
+In contrast to deep neural networks, the Hidden Markov Model is a very simple approach to 
+sequence labeling that can provide a satisfactory solution to NER on the web. In the researcher
+name extraction task, the second-order HMM using a good selection of features and the self-training
+strategy achieved a 87.7 F1, taking only 57 seconds to train and run predictions, while neural 
+network models took between 40 and 80 times longer to do the same with more expensive hardware.
+Depending on the end goal, this should be taken in consideration. However, neural models are
+undeniably more accurate and more flexible.
 
 The effective recognition of named entities on HTML is an essential step in most general 
-\gls{wde} methods. The accuracy achieved by deep neural architectures even
-on webpages that are very different from the plain text for which these architectures 
-were initially designed shows the potential for a truly flexible approach to cross domain 
-\gls{wde}.
+\gls{wde} methods. The accuracy achieved by deep neural architectures
+shows the potential for a truly flexible approach to cross domain extraction.
+Also, the self-training strategy showed a remarkable effectiveness in boosting the performance 
+of all HMM variants. It did so by using knowledge about the HTML context to make predictions,
+inspired on classical \gls{wde} systems. Future work could incorporate this 
+knowledge on neural models or CRFs to boost their performance in web extraction
+tasks.
 
@@
 
-% \cite{Zhu2005,Zhu2006,Abdessalem2010,Furche2012,Furche2012a}. Usually,
-
 \begin{thebibliography}{}
+
+\bibitem[\protect\citename{Abdessalem T., Cautis B., and Derouiche N. }{2010}]{Abdessalem2010}
+Abdessalem T., Cautis B., and Derouiche N. (2010)
+ObjectRunner: Lightweight, targeted extraction and querying of structured web data.
+In {\it Proceedings of the VLDB Endowment}
+{\bf 3(1-2)}: 1585--1588.
+
+\bibitem[\protect\citename{Adelberg }1998]{Adelberg1998}
+Adelberg B. (1998)
+NoDoSE---a tool for semi-automatically extracting structured and semistructured data from text documents.
+{\it ACM SIGMOD Record} 
+{\bf 27(2)}: 283--294.
+
+\bibitem[\protect\citename{Akbik, Blythe and Vollgraf }2018]{Akbik2018}
+Akbik, A., Blythe, D. and Vollgraf, R. (2018)
+Contextual string embeddings for sequence labeling.
+In {\it Proceedings of the 27th International Conference on Computational Linguistics}
+pp. 1638--1649, Santa Fe, New Mexico, ACL.
+
+\bibitem[\protect\citename{Arocena and Mendelzon }1998]{Arocena1999}
+Arocena, G. and Mendelzon, A. (1998)
+WebOQL: Restructuring documents, databases, and webs.
+In {\it Proceedings of the Fourteenth International Conference on Data Engineering (ICDE '98)}
+pp. 24--33, Washington, DC, USA, IEEE Computer Society.
+
+\bibitem[\protect\citename{Baevski, Edunov, Liu, Zettlemoyer and Auli }2019]{Baevski2019}
+Baevski, A., Edunov, S., Liu, Y., Zettlemoyer, L. and Auli, M. (2019)
+Cloze-driven pretraining of self-attention networks.
+{\it Preprint arXiv:1903.07785}.
+
+\bibitem[\protect\citename{Bikel, Schwartz and Weischedel }1999]{Bikel1999}
+Bikel, D., Schwartz, R. and Weischedel, R. (1999)
+An algorithm that learns what's in a name.
+{\it Machine Learning}
+{\bf 34(1)}: 211--231.
+
+\bibitem[\protect\citename{Borthwick, Sterling, Agichtein and Grishman }1998]{Borthwick1998}
+Borthwick, A., Sterling, J., Agichtein, E. and Grishman, R. (1998)
+Exploiting diverse knowledge sources via maximum entropy in named entity recognition.
+In {\it Proceedings of the Sixth Workshop on Very Large Corpora}
+pp. 152--160. ACL.
+
+\bibitem[\protect\citename{Califf and Mooney }1999]{Califf1999}
+Califf, M. and Mooney, R. (1999)
+Relational learning of pattern-match rules for information extraction.
+{\it Computational Linguistics}
+{\bf 4}: 9--15.
+
+\bibitem[\protect\citename{Caruana, Lawrence and Giles }2000]{Caruana2000}
+Caruana, R., Lawrence, S. and Giles, L. (2000)
+Overfitting in neural nets: Backpropagation, conjugate gradient, and early stopping.
+In {\it Proceedings of the 13th International Conference on Neural Information Processing Systems (NIPS'00)}
+pp. 381--387, Cambridge, MA, USA, MIT Press.
+
+\bibitem[\protect\citename{Chang and Lui }2001]{Chang2001}
+Chang, C. and Lui, S. (2001)
+IEPAD: information extraction based on pattern discovery.
+In {\it Proceedings of the 10th international conference on World Wide Web}
+pp. 681--688.
+
+\bibitem[\protect\citename{Chang and Kuo }2004]{Chang2004}
+Chang, C. and Kuo, S. (2004)
+OLERA: Semisupervised Web-data extraction with visual support.
+{\it IEEE Intelligent Systems}
+{\bf 19(6)}: 56--64.
+
+\bibitem[\protect\citename{Chang, Kayed, Girgis and Shaalan }2006]{Chang2006}
+Chang, C., Kayed, M., Girgis, M. and Shaalan, K. (2006)
+A Survey of Web Information Extraction Systems.
+{\it IEEE Transactions on Knowledge and Data Engineering}
+{\bf 18(10)}: 1411--1428.
+
+\bibitem[\protect\citename{Collobert, Weston, Bottou, Karlen, Kavukcuoglu, and Kuksa }2011]{Collobert2011}
+Collobert, R., Weston, J., Bottou, L., Karlen, M., Kavukcuoglu, K. and Kuksa P. (2011)
+Natural language processing (almost) from scratch.
+{\it Journal of Machine Learning Research}
+{\bf 12}: 2493--2537.
+
+\bibitem[\protect\citename{Crescenzi, Mecca, and Merialdo }2001]{Crescenzi2001}
+Crescenzi V., Mecca G., and Merialdo P. (2001)
+Roadrunner: Towards automatic data extraction from large web sites.
+In {\it Proceedings of the 27th International Conference on Very Large Data Bases}, 
+pp. 109--118.
+
+\bibitem[\protect\citename{Devlin, Chang, Lee, and Toutanova }2018]{Devlin2018}
+Devlin, J., Chang, M., Lee, K. and Toutanova, K. (2018)
+{BERT}: Pre-training of deep bidirectional transformers for language understanding.
+{\it Preprint arXiv:1810.04805}.
+
+\bibitem[\protect\citename{Dong, Gabrilovich, Heitz, Horn, Lao, Murphy, Strohmann, Sun, and Zhang }{2014}]{Dong2014}
+Dong, X., Gabrilovich, E., Heitz, G., Horn, W., Lao, N., Murphy, K., Strohmann, T., Sun, S. and Zhang, W. (2014)
+Knowledge Vault: a web-scale approach to probabilistic knowledge fusion.
+In {\it Proceedings of the 20th ACM SIGKDD international conference on Knowledge discovery and data mining (KDD '14)}
+pp. 601--610.
+
+\bibitem[\protect\citename{Ferrara and Baumgartner }2011]{Ferrara2011}
+Ferrara, E. and Baumgartner, R. (2011)
+Automatic wrapper adaptation by tree edit distance matching.
+{\it Smart Innovation, Systems and Technologies}
+{\bf 8}: 41--54.
+
+\bibitem[\protect\citename{Ferrara, De Meo, Fiumara and Baumgartner }2014]{Ferrara2014}
+Ferrara, E., De Meo, P., Fiumara, G. and Baumgartner, R. (2014)
+Web data extraction, applications and techniques: A survey.
+{\it Knowledge-Based Systems}
+{\bf 70}: 301--323.
+
+\bibitem[\protect\citename{Florian, Ittycheriah, Jing and Zhang }2003]{Florian2003}
+Florian, R. Ittycheriah, A. Jing, H. and Zhang, T. (2003)
+Named entity recognition through classifier combination.
+In {\it Proceedings of the Seventh Conference on Natural Language Learning at HLT-NAACL 2003}
+pp. 168--171.
+
+\bibitem[\protect\citename{Freitag }1998]{Freitag1998}
+Freitag, D. (1998)
+Information Extraction from HTML: Application of a General Machine Learning Approach.
+In {\it Proceedings of the Fifteenth National/Tenth Conference on Artificial Intelligence/Innovative Applications of Artificial Intelligence (AAAI '98/IAAI '98)}
+pp. 517--523, Menlo Park, CA, USA, American Association for Artificial Intelligence.
+
+\bibitem[\protect\citename{Freitag and Mccallum }1999]{Freitag1999}
+Freitag, D. and Mccallum, A. (1999)
+Information Extraction with HMMs and Shrinkage.
+In {\it Proceedings of the AAAI-99 Workshop on Machine Learning for Information Extraction}
+pp. 31--36. AAAI Press.
+
+\bibitem[\protect\citename{Freitag and McCallum }2000]{Freitag2000}
+Freitag, D. and McCallum, A. (2000)
+Information Extraction with HMM Structures Learned by Stochastic Optimization.
+In {\it Proceedings of the Seventeenth National Conference on Artificial Intelligence and Twelfth Conference on Innovative Applications of Artificial Intelligence}
+pp. 584--589. AAAI Press.
+
+\bibitem[\protect\citename{Furche, Gottlob, Grasso, Gunes, Guo, Kravchenko, Orsi, Schallhart, Sellers, and Wang }{2012}]{Furche2012}
+Furche, T., Gottlob, G., Grasso, G., Gunes, O., Guo, X., Kravchenko, A., Orsi, G., Schallhart, C., Sellers, A., and Wang, C. (2012)
+Diadem: Domain-centric, intelligent, automated data extraction methodology.
+In {\it Proceedings of the 21st International Conference on World Wide Web (WWW '12 Companion)}, 
+pp. 267--270, New York, ACM.
+
+\bibitem[\protect\citename{Hammer, McHugh and Garcia-Molin }1997]{Hammer1997}
+Hammer, J., McHugh, J. and Garcia-Molin, H. (1997)
+Semistructured Data: The TSIMMIS Experience.
+In {\it Proceedings of the First East-European Conference on Advances in Databases and Information Systems (ADBIS'97)}
+pp. 22--22, Swindon, UK, BCS Learning \& Development Ltd.
+
+\bibitem[\protect\citename{Hsu and Dung }{1998}]{Hsu1998}
+Hsu, Chun-Nan and Dung Ming-Tzung. (1998) 
+Generating finite-state transducers for semi-structured data extraction from the Web.
+{\it Information Systems \/}, 
+{\bf 23(8)}: 521--538.
+
+\bibitem[\protect\citename{Laender, Ribeiro-Neto, da Silva }2002a]{Laender2002a}
+Laender, A., Ribeiro-Neto, B. and da Silva, A. (2002)
+DEByE - Date extraction by example.
+{\it Data Knowledge Engineering}
+{\bf 40(2)}: 121--154.
+
+\bibitem[\protect\citename{Laender, Ribeiro-Neto, da Silva and Teixeira }2002b]{Laender2002b}
+Laender, A., Ribeiro-Neto, B., da Silva, A., and Teixeira, J. (2002)
+A brief survey of web data extraction tools.
+{\it SIGMOD Record}
+{\bf 31(2)}: 84--93.
+
+\bibitem[\protect\citename{Liu, Pu and Han }2000]{Liu2000}
+Liu, L., Pu, C. and Han, W. (2000)
+XWRAP: an XML-enabled wrapper construction system for Web information sources.
+In {\it Proceedings of 16th International Conference on Data Engineering}
+pp. 611--621.
+
+\bibitem[\protect\citename{Hochreiter and Schmidhuber }1997]{Hochreiter1997}
+Hochreiter, S. and Schmidhuber, J. (1997)
+Long short-term memory.
+{\it Neural Computation}
+{\bf 9(8)}: 1735--1780.
+
+\bibitem[\protect\citename{Hogue and Karger }2005]{Hogue2005}
+Hogue, A. and Karger, D. (2005)
+Thresher: Automating the Unwrapping of Semantic Content from the World Wide Web.
+In {\it Proceedings of the 14th International Conference on World Wide Web (WWW '05)}
+pp. 86--95, New York, NY, USA, ACM.
+
+\bibitem[\protect\citename{Huang, Xu and Yu }2015]{Huang2015}
+Huang, Z., Xu, W. and Yu, K. (2015)
+Bidirectional {LSTM-CRF} models for sequence tagging.
+{\it CoRR}, abs/1508.01991.
+
+\bibitem[\protect\citename{Kim~Sang and De-Meulder }2003]{KimSang2003}
+Kim-Sang, T. and De~Meulder, F. (2003)
+Introduction to the CoNLL-2003 Shared Task: Language-independent Named Entity Recognition.
+In {\it Proceedings of the Seventh Conference on Natural Language Learning at HLT-NAACL 2003 - Volume 4 (CONLL '03)}
+pp. 142--147, Stroudsburg, PA, USA, ACL.
+
+\bibitem[\protect\citename{Krupl, Herzog and Gatterbauer }2005]{Krupl2005}
+Krupl, B. Herzog, M. and Gatterbauer, W. (2005)
+Using visual cues for extraction of tabular data from arbitrary HTML documents.
+{\it Special interest tracks and posters of the 14th international conference on World Wide Web - WWW '05} 
+pp. 1000--1001.
 
@@
 
+\bibitem[\protect\citename{Lafferty, McCallum and Pereira }2001]{Lafferty2001}
+Lafferty, J., McCallum, A. and Pereira, F. (2001)
+Conditional random fields: Probabilistic models for segmenting and labeling sequence data.
+In {\it Proceedings of the Eighteenth International Conference on Machine Learning (ICML '01)}, 
+pp. 282--289, San Francisco, CA, USA, Morgan Kaufmann Publishers Inc.
+
+\bibitem[\protect\citename{Lample, Ballesteros, Subramanian, Kawakami and Dyer }2016]{Lample2016}
+Lample, G., Ballesteros, M., Subramanian, S., Kawakami, K. and Dyer, C. (2016)
+Neural architectures for named entity recognition.
+{\it CoRR}, abs/1603.01360.
+
+\bibitem[\protect\citename{Li and Gray }2000]{Li2000}
+Li, J. and Gray, R. (2000)
+Image Segmentation and Compression Using Hidden Markov Models.
+Kluwer Academic Publishers, Norwell, MA, USA.
+
+\bibitem[\protect\citename{Liu and Nocedal }1989]{Liu1989}
+Liu, D. and Nocedal, J. (1989)
+On the limited memory bfgs method for large scale optimization.
+{\it Mathematical Programming}
+{\bf 45(1)}: 503--528.
+
+\bibitem[\protect\citename{Ma and Hovy }2016]{Ma2016}
+Ma, X. and Hovy, E. (2016)
+End-to-end sequence labeling via bi-directional {LSTM}-{CNN}s-{CRF}.
+In {\it Proceedings of the 54th Annual Meeting of the Association for Computational Linguistics (Volume 1: Long Papers)}
+pp. 1064--1074, Berlin, Germany, ACL.
+
+\bibitem[\protect\citename{McCallum, Freitag and Pereira }2000]{McCallum2000}
+McCallum, A., Freitag, D. and Pereira, F. (2000)
+Maximum entropy markov models for information extraction and segmentation.
+In {\it Proceedings of the Seventeenth International Conference on Machine Learning (ICML '00)}
+pp. 591--598, San Francisco, CA, USA, Morgan Kaufmann Publishers Inc.
+
+\bibitem[\protect\citename{McCallum and Li }2003]{McCallum2003}
+McCallum, A. and Li, W. (2003)
+Early results for named entity recognition with conditional random fields, feature induction and web-enhanced lexicons.
+In {\it Proceedings of the Seventh Conference on Natural Language Learning at HLT-NAACL 2003 - Volume 4 (CONLL '03)}
+pp. 188--191, Stroudsburg, PA, USA, ACL.
+
 \bibitem[\protect\citename{Muslea, Minton and Knoblock }1999]{Muslea1999}
@@
 
-\bibitem[\protect\citename{Hsu and Dung }{1998}]{Hsu1998}
-Hsu, Chun-Nan and Dung Ming-Tzung. (1998) 
-Generating finite-state transducers for semi-structured data extraction from the Web.
-{\it Information Systems \/}, 
-{\bf 23(8)}: 521--538.
-
-\bibitem[\protect\citename{Crescenzi, Mecca, and Merialdo }2001]{Crescenzi2001}
-Crescenzi V., Mecca G., and Merialdo P. (2001)
-Roadrunner: Towards automatic data extraction from large web sites.
-In {\it Proceedings of the 27th International Conference on Very Large Data Bases}, 
-pp. 109--118.
+\bibitem[\protect\citename{Pennington, Socher and Manning }2014]{Pennington2014}
+Pennington, J., Socher, R. and Manning, C. (2014)
+Glove: Global vectors for word representation.
+In {\it Empirical Methods in Natural Language Processing (EMNLP)}
+pp. 1532--1543.
+
+\bibitem[\protect\citename{Peters, Neumann, Iyyer, Gardner, Clark, Lee and Zettlemoyer }2018]{Peters2018}
+Peters, M., Neumann, M., Iyyer, M., Gardner, M., Clark, C., Lee, K. and Zettlemoyer, L. (2018)
+Deep contextualized word representations.
+In {\it Proceedings of the 2018 Conference of the North American Chapter of the Association for Computational Linguistics: Human Language Technologies, Volume 1 (Long Papers)}
+pp. 2227--2237, New Orleans, Louisiana, ACL.
+
+\bibitem[\protect\citename{Rabiner }1990]{Rabiner1990}
+Rabiner, L. (1990)
+Readings in Speech Recognition. Chapter: A Tutorial on Hidden Markov Models and Selected Applications in Speech Recognition.
+Morgan Kaufmann Publishers Inc., San Francisco, CA, USA.
+
+\bibitem[\protect\citename{Ramshaw and Marcus }1999]{Ramshaw1999}
+Ramshaw, L. and Marcus, M. (1999)
+Text Chunking Using Transformation-Based Learning, 
+pp. 157--176. Springer Netherlands, Dordrecht, 1999.
+
+\bibitem[\protect\citename{Ratnaparkhi }1998]{Ratnaparkhi1998}
+Ratnaparkhi, A. (1998)
+Maximum Entropy Models for Natural Language Ambiguity Resolution.
+{\it PhD thesis}, Philadelphia, PA, USA.
+
+\bibitem[\protect\citename{Ribas, Ribeiro-Neto, de Souza e Silva, Ueda, and Ziviani }2015]{Ribas2015}
+Ribas, S., Ribeiro-Neto, B., de Souza e Silva, E., Ueda, A., and Ziviani, N. (2015)
+In {\it Proceedings of the 24th International Conference on World Wide Web (WWW '15 Companion)}, 
+pp. 603--608, New York, ACM.
+
+\bibitem[\protect\citename{Rijsbergen }1979]{Rijsbergen1979}
+Rijsbergen, C. (1979)
+Information Retrieval.
+Butterworth-Heinemann, Newton, MA, USA, 2nd edition.
+
+\bibitem[\protect\citename{Sahuguet and Azavant }1999]{Sahuguet1999}
+Sahuguet, A. and Azavant F. (1999)
+Building Light-Weight Wrappers for Legacy Web Data-Sources Using W4F.
+In {\it Proceedings of the 25th International Conference on Very Large Data Bases (VLDB '99)}
+pp. 738--741, San Francisco, CA, USA, Morgan Kaufmann Publishers Inc.
+
+\bibitem[\protect\citename{Sarawagi }2008]{Sarawagi2008}
+Sarawagi, S. (2008)
+Information extraction.
+{\it Foundations and Trends in Databases}
+{\bf 1(3)}: 261--377.
+
+\bibitem[\protect\citename{Schulz, Lassig and Gaedke }2016]{Schulz2016}
+Schulz, A. Lassig, J. and Gaedke, M. (2016)
+Practical web data extraction: Are we there yet? --- A short survey.
+{\it IEEE/WIC/ACM International Conference on Web Intelligence (WI), 2016}, 
+pp. 562--567.
+
+\bibitem[\protect\citename{Shi, Liu, Shen, Yuan and Huang }{2015}]{Shi2015}
+Shi, S., Liu, C., Shen, Y., Yuan, C. and Huang, Y. (2015)
+AutoRM: An effective approach for automatic Web data record mining.
+{\it Knowledge-Based Systems}
+{\bf 89}: 314--331.
+
+\bibitem[\protect\citename{Soderland }1999]{Soderland1999}
+Soderland, S. (1999)
+Learning Information Extraction Rules for Semi-Structured and Free Text.
+{\it Machine Learning} 
+{\bf 34(1)}: 233--272.
+
+\bibitem[\protect\citename{Sundheim }1991]{Sundheim1991}
+Sundheim. B. (1991)
+Overview of the third message understanding evaluation and conference.
+In {\it Proceedings of the 3rd Conference on Message Understanding (MUC3 '91)}
+pp. 3--16, Stroudsburg, PA, USA, ACL.
+
+\bibitem[\protect\citename{Varlamov and Turdakov }2016]{Varlamov2016}
+Varlamov, M. and Turdakov, D. (2016)
+A survey of methods for the extraction of information from Web resources.
+{\it Programming and Computer Software}
+{\bf 42(5)}: 279--291.
 
@@
 
-\bibitem[\protect\citename{Abdessalem T., Cautis B., and Derouiche N. }{2010}]{Abdessalem2010}
-Abdessalem T., Cautis B., and Derouiche N. (2010)
-ObjectRunner: Lightweight, targeted extraction and querying of structured web data.
-In {\it Proceedings of the VLDB Endowment}
-{\bf 3(1-2)}: 1585--1588.
-
-\bibitem[\protect\citename{Furche, Gottlob, Grasso, Gunes, Guo, Kravchenko, Orsi, Schallhart, Sellers, and Wang }{2012}]{Furche2012}
-Furche, T., Gottlob, G., Grasso, G., Gunes, O., Guo, X., Kravchenko, A., Orsi, G., Schallhart, C., Sellers, A., and Wang, C. (2012)
-Diadem: Domain-centric, intelligent, automated data extraction methodology.
-In {\it Proceedings of the 21st International Conference on World Wide Web (WWW '12 Companion)}, 
-pp. 267--270, New York, ACM.
-
-\bibitem[\protect\citename{Collobert, Weston, Bottou, Karlen, Kavukcuoglu, and Kuksa }2011]{Collobert2011}
-Collobert, R., Weston, J., Bottou, L., Karlen, M., Kavukcuoglu, K. and Kuksa P. (2011)
-Natural language processing (almost) from scratch.
-{\it Journal of Machine Learning Research}
-{\bf 12}: 2493--2537.
-
-\bibitem[\protect\citename{Ribas, Ribeiro-Neto, de Souza e Silva, Ueda, and Ziviani }2015]{Ribas2015}
-Ribas, S., Ribeiro-Neto, B., de Souza e Silva, E., Ueda, A., and Ziviani, N. (2015)
-In {\it Proceedings of the 24th International Conference on World Wide Web (WWW '15 Companion)}, 
-pp. 603--608, New York, ACM.
-
-\bibitem[\protect\citename{Adelberg }1998]{Adelberg1998}
-Adelberg B. (1998)
-NoDoSE---a tool for semi-automatically extracting structured and semistructured data from text documents.
-{\it ACM SIGMOD Record} 
-{\bf 27(2)}: 283--294.
-
-\bibitem[\protect\citename{Laender, Ribeiro-Neto, da Silva }2002a]{Laender2002a}
-Laender, A., Ribeiro-Neto, B. and da Silva, A. (2002)
-DEByE - Date extraction by example.
-{\it Data Knowledge Engineering}
-{\bf 40(2)}: 121--154.
-
-\bibitem[\protect\citename{Califf and Mooney }1999]{Califf1999}
-Califf, M. and Mooney, R. (1999)
-Relational learning of pattern-match rules for information extraction.
-{\it Computational Linguistics}
-{\bf 4}: 9--15.
-
-\bibitem[\protect\citename{Laender, Ribeiro-Neto, da Silva and Teixeira }2002b]{Laender2002b}
-Laender, A., Ribeiro-Neto, B., da Silva, A., and Teixeira, J. (2002)
-A brief survey of web data extraction tools.
-{\it SIGMOD Record}
-{\bf 31(2)}: 84--93.
-
-\bibitem[\protect\citename{Hammer, McHugh and Garcia-Molin }1997]{Hammer1997}
-Hammer, J., McHugh, J. and Garcia-Molin, H. (1997)
-Semistructured Data: The TSIMMIS Experience.
-In {\it Proceedings of the First East-European Conference on Advances in Databases and Information Systems (ADBIS'97)}
-pp. 22--22, Swindon, UK, BCS Learning \& Development Ltd.
-
-\bibitem[\protect\citename{Arocena and Mendelzon }1998]{Arocena1999}
-Arocena, G. and Mendelzon, A. (1998)
-WebOQL: Restructuring documents, databases, and webs.
-In {\it Proceedings of the Fourteenth International Conference on Data Engineering (ICDE '98)}
-pp. 24--33, Washington, DC, USA, IEEE Computer Society.
-
-\bibitem[\protect\citename{Liu, Pu and Han }2000]{Liu2000}
-Liu, L., Pu, C. and Han, W. (2000)
-XWRAP: an XML-enabled wrapper construction system for Web information sources.
-In {\it Proceedings of 16th International Conference on Data Engineering}
-pp. 611--621.
-
-\bibitem[\protect\citename{Sahuguet and Azavant }1999]{Sahuguet1999}
-Sahuguet, A. and Azavant F. (1999)
-Building Light-Weight Wrappers for Legacy Web Data-Sources Using W4F.
-In {\it Proceedings of the 25th International Conference on Very Large Data Bases (VLDB '99)}
-pp. 738--741, San Francisco, CA, USA, Morgan Kaufmann Publishers Inc.
-
-\bibitem[\protect\citename{Freitag }1998]{Freitag1998}
-Freitag, D. (1998)
-Information Extraction from HTML: Application of a General Machine Learning Approach.
-In {\it Proceedings of the Fifteenth National/Tenth Conference on Artificial Intelligence/Innovative Applications of Artificial Intelligence (AAAI '98/IAAI '98)}
-pp. 517--523, Menlo Park, CA, USA, American Association for Artificial Intelligence.
-
-\bibitem[\protect\citename{Soderland }1999]{Soderland1999}
-Soderland, S. (1999)
-Learning Information Extraction Rules for Semi-Structured and Free Text.
-{\it Machine Learning} 
-{\bf 34(1)}: 233--272.
-
-\bibitem[\protect\citename{Chang, Kayed, Girgis and Shaalan }2006]{Chang2006}
-Chang, C., Kayed, M., Girgis, M. and Shaalan, K. (2006)
-A Survey of Web Information Extraction Systems.
-{\it IEEE Transactions on Knowledge and Data Engineering}
-{\bf 18(10)}: 1411--1428.
-
-\bibitem[\protect\citename{Hogue and Karger }2005]{Hogue2005}
-Hogue, A. and Karger, D. (2005)
-Thresher: Automating the Unwrapping of Semantic Content from the World Wide Web.
-In {\it Proceedings of the 14th International Conference on World Wide Web (WWW '05)}
-pp. 86--95, New York, NY, USA, ACM.
-
-\bibitem[\protect\citename{Chang and Lui }2001]{Chang2001}
-Chang, C. and Lui, S. (2001)
-IEPAD: information extraction based on pattern discovery.
-In {\it Proceedings of the 10th international conference on World Wide Web}
-pp. 681--688.
-
-\bibitem[\protect\citename{Chang and Kuo }2004]{Chang2004}
-Chang, C. and Kuo, S. (2004)
-OLERA: Semisupervised Web-data extraction with visual support.
-{\it IEEE Intelligent Systems}
-{\bf 19(6)}: 56--64.
-
-\bibitem[\protect\citename{Sarawagi }2008]{Sarawagi2008}
-Sarawagi, S. (2008)
-Information extraction.
-{\it Foundations and Trends in Databases}
-{\bf 1(3)}: 261--377.
-
-\bibitem[\protect\citename{Ferrara and Baumgartner }2011]{Ferrara2011}
-Ferrara, E. and Baumgartner, R. (2011)
-Automatic wrapper adaptation by tree edit distance matching.
-{\it Smart Innovation, Systems and Technologies}
-{\bf 8}: 41--54.
-
-\bibitem[\protect\citename{Ferrara, De Meo, Fiumara and Baumgartner }2014]{Ferrara2014}
-Ferrara, E., De Meo, P., Fiumara, G. and Baumgartner, R. (2014)
-Web data extraction, applications and techniques: A survey.
-{\it Knowledge-Based Systems}
-{\bf 70}: 301--323.
-
-\bibitem[\protect\citename{Schulz, Lassig and Gaedke }2016]{Schulz2016}
-Schulz, A. Lassig, J. and Gaedke, M. (2016)
-Practical web data extraction: Are we there yet? --- A short survey.
-{\it IEEE/WIC/ACM International Conference on Web Intelligence (WI), 2016}, 
-pp. 562--567.
-
-\bibitem[\protect\citename{Varlamov and Turdakov }2016]{Varlamov2016}
-Varlamov, M. and Turdakov, D. (2016)
-A survey of methods for the extraction of information from Web resources.
-{\it Programming and Computer Software}
-{\bf 42(5)}: 279--291.
-
-\bibitem[\protect\citename{Krupl, Herzog and Gatterbauer }2005]{Krupl2005}
-Krupl, B. Herzog, M. and Gatterbauer, W. (2005)
-Using visual cues for extraction of tabular data from arbitrary HTML documents.
-{\it Special interest tracks and posters of the 14th international conference on World Wide Web - WWW '05} 
-pp. 1000--1001.
-
-\bibitem[\protect\citename{Shi, Liu, Shen, Yuan and Huang }{2015}]{Shi2015}
-Shi, S., Liu, C., Shen, Y., Yuan, C. and Huang, Y. (2015)
-AutoRM: An effective approach for automatic Web data record mining.
-{\it Knowledge-Based Systems}
-{\bf 89}: 314--331.
-
-\bibitem[\protect\citename{Dong, Gabrilovich, Heitz, Horn, Lao, Murphy, Strohmann, Sun, and Zhang }{2014}]{Dong2014}
-Dong, X., Gabrilovich, E., Heitz, G., Horn, W., Lao, N., Murphy, K., Strohmann, T., Sun, S. and Zhang, W. (2014)
-Knowledge Vault: a web-scale approach to probabilistic knowledge fusion.
-In {\it Proceedings of the 20th ACM SIGKDD international conference on Knowledge discovery and data mining (KDD '14)}
-pp. 601--610.
-
-\bibitem[\protect\citename{Sundheim }1991]{Sundheim1991}
-Sundheim. B. (1991)
-Overview of the third message understanding evaluation and conference.
-In {\it Proceedings of the 3rd Conference on Message Understanding (MUC3 '91)}
-pp. 3--16, Stroudsburg, PA, USA, ACL.
-
-\bibitem[\protect\citename{Kim~Sang and De-Meulder }2003]{KimSang2003}
-Kim-Sang, T. and De~Meulder, F. (2003)
-Introduction to the CoNLL-2003 Shared Task: Language-independent Named Entity Recognition.
-In {\it Proceedings of the Seventh Conference on Natural Language Learning at HLT-NAACL 2003 - Volume 4 (CONLL '03)}
-pp. 142--147, Stroudsburg, PA, USA, ACL.
-
-\bibitem[\protect\citename{Bikel, Schwartz and Weischedel }1999]{Bikel1999}
-Bikel, D., Schwartz, R. and Weischedel, R. (1999)
-An algorithm that learns what's in a name.
-{\it Machine Learning}
-{\bf 34(1)}: 211--231.
-
-\bibitem[\protect\citename{Freitag and Mccallum }1999]{Freitag1999}
-Freitag, D. and Mccallum, A. (1999)
-Information Extraction with HMMs and Shrinkage.
-In {\it Proceedings of the AAAI-99 Workshop on Machine Learning for Information Extraction}
-pp. 31--36. AAAI Press.
-
-\bibitem[\protect\citename{Freitag and McCallum }2000]{Freitag2000}
-Freitag, D. and McCallum, A. (2000)
-Information Extraction with HMM Structures Learned by Stochastic Optimization.
-In {\it Proceedings of the Seventeenth National Conference on Artificial Intelligence and Twelfth Conference on Innovative Applications of Artificial Intelligence}
-pp. 584--589. AAAI Press.
-
-\bibitem[\protect\citename{Borthwick, Sterling, Agichtein and Grishman }1998]{Borthwick1998}
-Borthwick, A., Sterling, J., Agichtein, E. and Grishman, R. (1998)
-Exploiting diverse knowledge sources via maximum entropy in named entity recognition.
-In {\it Proceedings of the Sixth Workshop on Very Large Corpora}
-pp. 152--160. ACL.
-
-\bibitem[\protect\citename{Ratnaparkhi }1998]{Ratnaparkhi1998}
-Ratnaparkhi, A. (1998)
-Maximum Entropy Models for Natural Language Ambiguity Resolution.
-{\it PhD thesis}, Philadelphia, PA, USA.
-
-\bibitem[\protect\citename{McCallum, Freitag and Pereira }2000]{McCallum2000}
-McCallum, A., Freitag, D. and Pereira, F. (2000)
-Maximum entropy markov models for information extraction and segmentation.
-In {\it Proceedings of the Seventeenth International Conference on Machine Learning (ICML '00)}
-pp. 591--598, San Francisco, CA, USA, Morgan Kaufmann Publishers Inc.
-
-\bibitem[\protect\citename{Lafferty, McCallum and Pereira }2001]{Lafferty2001}
-Lafferty, J., McCallum, A. and Pereira, F. (2001)
-Conditional random fields: Probabilistic models for segmenting and labeling sequence data.
-In {\it Proceedings of the Eighteenth International Conference on Machine Learning (ICML '01)}, 
-pp. 282--289, San Francisco, CA, USA, Morgan Kaufmann Publishers Inc.
-
-\bibitem[\protect\citename{McCallum and Li }2003]{McCallum2003}
-McCallum, A. and Li, W. (2003)
-Early results for named entity recognition with conditional random fields, feature induction and web-enhanced lexicons.
-In {\it Proceedings of the Seventh Conference on Natural Language Learning at HLT-NAACL 2003 - Volume 4 (CONLL '03)}
-pp. 188--191, Stroudsburg, PA, USA, ACL.
-
-\bibitem[\protect\citename{Florian, Ittycheriah, Jing and Zhang }2003]{Florian2003}
-Florian, R. Ittycheriah, A. Jing, H. and Zhang, T. (2003)
-Named entity recognition through classifier combination.
-In {\it Proceedings of the Seventh Conference on Natural Language Learning at HLT-NAACL 2003}
-pp. 168--171.
-
-\bibitem[\protect\citename{Huang, Xu and Yu }2015]{Huang2015}
-Huang, Z., Xu, W. and Yu, K. (2015)
-Bidirectional {LSTM-CRF} models for sequence tagging.
-{\it CoRR}, abs/1508.01991.
-
-\bibitem[\protect\citename{Lample, Ballesteros, Subramanian, Kawakami and Dyer }2016]{Lample2016}
-Lample, G., Ballesteros, M., Subramanian, S., Kawakami, K. and Dyer, C. (2016)
-Neural architectures for named entity recognition.
-{\it CoRR}, abs/1603.01360.
-
-\bibitem[\protect\citename{Ma and Hovy }2016]{Ma2016}
-Ma, X. and Hovy, E. (2016)
-End-to-end sequence labeling via bi-directional {LSTM}-{CNN}s-{CRF}.
-In {\it Proceedings of the 54th Annual Meeting of the Association for Computational Linguistics (Volume 1: Long Papers)}
-pp. 1064--1074, Berlin, Germany, ACL.
-
-\bibitem[\protect\citename{Pennington, Socher and Manning }2014]{Pennington2014}
-Pennington, J., Socher, R. and Manning, C. (2014)
-Glove: Global vectors for word representation.
-In {\it Empirical Methods in Natural Language Processing (EMNLP)}
-pp. 1532--1543.
-
-\bibitem[\protect\citename{Peters, Neumann, Iyyer, Gardner, Clark, Lee and Zettlemoyer }2018]{Peters2018}
-Peters, M., Neumann, M., Iyyer, M., Gardner, M., Clark, C., Lee, K. and Zettlemoyer, L. (2018)
-Deep contextualized word representations.
-In {\it Proceedings of the 2018 Conference of the North American Chapter of the Association for Computational Linguistics: Human Language Technologies, Volume 1 (Long Papers)}
-pp. 2227--2237, New Orleans, Louisiana, ACL.
-
-\bibitem[\protect\citename{Devlin, Chang, Lee, and Toutanova }2018]{Devlin2018}
-Devlin, J., Chang, M., Lee, K. and Toutanova, K. (2018)
-{BERT}: Pre-training of deep bidirectional transformers for language understanding.
-{\it Preprint arXiv:1810.04805}.
-
-\bibitem[\protect\citename{Akbik, Blythe and Vollgraf }2018]{Akbik2018}
-Akbik, A., Blythe, D. and Vollgraf, R. (2018)
-Contextual string embeddings for sequence labeling.
-In {\it Proceedings of the 27th International Conference on Computational Linguistics}
-pp. 1638--1649, Santa Fe, New Mexico, ACL.
-
-\bibitem[\protect\citename{Baevski, Edunov, Liu, Zettlemoyer and Auli }2019]{Baevski2019}
-Baevski, A., Edunov, S., Liu, Y., Zettlemoyer, L. and Auli, M. (2019)
-Cloze-driven pretraining of self-attention networks.
-{\it Preprint arXiv:1903.07785}.
-
-\bibitem[\protect\citename{Caruana, Lawrence and Giles }2000]{Caruana2000}
-Caruana, R., Lawrence, S. and Giles, L. (2000)
-Overfitting in neural nets: Backpropagation, conjugate gradient, and early stopping.
-In {\it Proceedings of the 13th International Conference on Neural Information Processing Systems (NIPS'00)}
-pp. 381--387, Cambridge, MA, USA, MIT Press.
-
-\bibitem[\protect\citename{Hochreiter and Schmidhuber }1997]{Hochreiter1997}
-Hochreiter, S. and Schmidhuber, J. (1997)
-Long short-term memory.
-{\it Neural Computation}
-{\bf 9(8)}: 1735--1780.
-
-\bibitem[\protect\citename{Li and Gray }2000]{Li2000}
-Li, J. and Gray, R. (2000)
-Image Segmentation and Compression Using Hidden Markov Models.
-Kluwer Academic Publishers, Norwell, MA, USA.
-
-\bibitem[\protect\citename{Liu and Nocedal }1989]{Liu1989}
-Liu, D. and Nocedal, J. (1989)
-On the limited memory bfgs method for large scale optimization.
-{\it Mathematical Programming}
-{\bf 45(1)}: 503--528.
-
-\bibitem[\protect\citename{Rabiner }1990]{Rabiner1990}
-Rabiner, L. (1990)
-Readings in Speech Recognition. Chapter: A Tutorial on Hidden Markov Models and Selected Applications in Speech Recognition.
-Morgan Kaufmann Publishers Inc., San Francisco, CA, USA.
-
-\bibitem[\protect\citename{Ramshaw and Marcus }1999]{Ramshaw1999}
-Ramshaw, L. and Marcus, M. (1999)
-Text Chunking Using Transformation-Based Learning, 
-pp. 157--176. Springer Netherlands, Dordrecht, 1999.
-
-\bibitem[\protect\citename{Rijsbergen }1979]{Rijsbergen1979}
-Rijsbergen, C. (1979)
-Information Retrieval.
-Butterworth-Heinemann, Newton, MA, USA, 2nd edition.
-
 \end{thebibliography}

### 2019-06-16 collect_results.sh

@@ -1,37 +1,0 @@
-arr=(
-  nb
-  hmm-1
-  hmm-2
-  hmm-3
-  maxent
-  crf
-  lstm-crf
-  lstm-crf-cnn
-  lstm-crf-lstm
-)
-
-arr2=(
-  nb
-  hmm-1
-  hmm-2
-  hmm-3
-)
-
-# # Gazetteer matching.
-# python train_model.py partial_match
-# python train_model.py exact_match
-
-for i in "${arr[@]}"
-do
-  python train_model.py $i -d $1
-done
-
-for i in "${arr[@]}"
-do
-  python train_model.py $i -f -d $1
-done
-
-for i in "${arr2[@]}"
-do
-  python train_model.py $i -f -s -d $1
-done

### 2019-06-16 convert_dataset.py

@@ -1,26 +1,0 @@
-import sys
-
-with open(sys.argv[1]) as f:
-  prev, pprev = '', ''
-  for line in f:
-    tkns = line.strip().split(' ')
-    if len(tkns) < 2:
-      print(line.strip())
-    elif line.startswith('-DOCSTART-'):
-      print(line.strip())
-    else:
-      current = tkns[1]
-      if current == 'I-PER':
-        if prev == 'PUNCT' and pprev == 'I-PER':
-          pass
-        elif prev == 'I-PER':
-          pass
-        else:
-          tkns[1] = 'B-PER'
-
-      if len(tkns) < 14:
-        tkns += ['none'] * (14 - len(tkns))
-      print(' '.join(tkns))
-
-      pprev = prev
-      prev = current

### 2019-06-16 models/attention.py

@@ -1,0 +1,289 @@
+import tensorflow as tf
+import numpy as np
+import math
+
+def rbf_kernel(Q, K, gamma=0.5):
+  Q = tf.transpose(Q, [1, 0, 2]) # Time major.
+  K = tf.transpose(K, [1, 0, 2])
+  return tf.transpose(tf.map_fn(
+    lambda k: tf.exp(-gamma * tf.reduce_sum(tf.square(Q - k), axis=-1)),
+    K
+  ), [2, 1, 0])
+
+def bahdanau(Q, K):
+  Q = tf.transpose(Q, [1, 0, 2]) # Time major.
+  K = tf.transpose(K, [1, 0, 2])
+  attention = tf.map_fn(
+    lambda k: tf.layers.dense(tf.tanh(Q + k), 1), 
+    K
+  )
+  return tf.transpose(tf.squeeze(attention, axis=-1), [2, 1, 0]) 
+
+def exact_match(Q, K):
+  Q = tf.transpose(Q, [1, 0, 2]) # Time major.
+  K = tf.transpose(K, [1, 0, 2])
+
+  attention = tf.map_fn(
+    lambda k: tf.cast(tf.reduce_all(tf.equal(Q, k), axis=-1), tf.int64),
+    K
+  )
+
+  return tf.cast(tf.transpose(attention, [2, 1, 0]), tf.float32)
+
+def dot_product(Q, K, scaled=False, cosine=False):
+  attention = tf.matmul(Q, K, transpose_b=True)
+
+  if scaled:
+    attention = tf.divide(attention, math.sqrt(Q.shape[-1].value))
+
+  if cosine:
+    norm_q = tf.sqrt(tf.reduce_sum(tf.square(Q), axis=-1, keepdims=True))
+    norm_k = tf.sqrt(tf.reduce_sum(tf.square(K), axis=-1, keepdims=True))
+    norm = tf.matmul(norm_q, norm_k, transpose_b=True)
+    attention = tf.abs(tf.divide(attention, norm))
+
+  return attention
+
+def normalize(inputs, epsilon = 1e-8):
+  inputs_shape = inputs.get_shape()
+  params_shape = inputs_shape[-1:]
+  
+  mean, variance = tf.nn.moments(inputs, [-1], keep_dims=True)
+  beta= tf.Variable(tf.zeros(params_shape))
+  gamma = tf.Variable(tf.ones(params_shape))
[…]

### 2019-06-16 models/char_representations.py

@@ -1,0 +1,83 @@
+import tensorflow as tf
+from pathlib import Path
+from six.moves import reduce
+
+def cnn_char_representations(t, weights, filters, kernel_size):
+  shape = tf.shape(t)
+  ndims = t.shape.ndims
+  dim1 = reduce(lambda x, y: x*y, [shape[i] for i in range(ndims - 2)])
+  dim2 = shape[-2]
+  dim3 = t.shape[-1]
+
+  # Reshape weights
+  weights = tf.reshape(weights, shape=[dim1, dim2, 1])
+  weights = tf.to_float(weights)
+
+  # Reshape input and apply weights
+  flat_shape = [dim1, dim2, dim3]
+  t = tf.reshape(t, shape=flat_shape)
+  t *= weights
+
+  # Apply convolution
+  t_conv = tf.layers.conv1d(t, filters, kernel_size, padding='same')
+  t_conv *= weights
+
+  # Reduce max -- set to zero if all padded
+  t_conv += (1. - weights) * tf.reduce_min(t_conv, axis=-2, keepdims=True)
+  t_max = tf.reduce_max(t_conv, axis=-2)
+
+  # Reshape the output
+  final_shape = [shape[i] for i in range(ndims-2)] + [filters]
+  t_max = tf.reshape(t_max, shape=final_shape)
+  return t_max
+
+def lstm_char_representations(char_embeddings, nchars, lstm_size, char_embedding_size, scope='lstm_chars'):
+  with tf.variable_scope(scope):
+    dim_words = tf.shape(char_embeddings)[1]
+    dim_chars = tf.shape(char_embeddings)[2]
+
+    t = tf.reshape(char_embeddings, [-1, dim_chars, char_embedding_size])
+
+    lstm_cell_fw_c = tf.nn.rnn_cell.LSTMCell(lstm_size)
+    lstm_cell_bw_c = tf.nn.rnn_cell.LSTMCell(lstm_size)
+    
+    (_, _), (output_fw, output_bw) = tf.nn.bidirectional_dynamic_rnn(
+      lstm_cell_fw_c, lstm_cell_bw_c, t,
+      dtype=tf.float32,
+      sequence_length=tf.reshape(nchars, [-1]),
+    )
+
+    # output_fw[0] is the cell state and output_fw[1] is the hidden state.
+    output = tf.concat([output_fw[1], output_bw[1]], axis=-1)
+    return tf.reshape(output, [-1, dim_words, 2 * lstm_size])
+
[…]

### 2019-06-16 models/cnn.py

@@ -1,0 +1,50 @@
+import tensorflow as tf
+import numpy as np 
+from six.moves import reduce
+
+def masked_conv1d_and_max(t, weights, filters, kernel_size):
+  """Applies 1d convolution and a masked max-pooling
+  Parameters
+  ----------
+  t : tf.Tensor
+    A tensor with at least 3 dimensions [d1, d2, ..., dn-1, dn]
+  weights : tf.Tensor of tf.bool
+    A Tensor of shape [d1, d2, dn-1]
+  filters : int
+    number of filters
+  kernel_size : int
+    kernel size for the temporal convolution
+  Returns
+  -------
+  tf.Tensor
+    A tensor of shape [d1, d2, dn-1, filters]
+  """
+  # Get shape and parameters
+  shape = tf.shape(t)
+  ndims = t.shape.ndims
+  dim1 = reduce(lambda x, y: x*y, [shape[i] for i in range(ndims - 2)])
+  dim2 = shape[-2]
+  dim3 = t.shape[-1]
+
+  # Reshape weights
+  weights = tf.reshape(weights, shape=[dim1, dim2, 1])
+  weights = tf.to_float(weights)
+
+  # Reshape input and apply weights
+  flat_shape = [dim1, dim2, dim3]
+  t = tf.reshape(t, shape=flat_shape)
+  t *= weights
+
+  # Apply convolution
+  t_conv = tf.layers.conv1d(t, filters, kernel_size, padding='same')
+  t_conv *= weights
+
+  # Reduce max -- set to zero if all padded
+  t_conv += (1. - weights) * tf.reduce_min(t_conv, axis=-2, keepdims=True)
+  t_max = tf.reduce_max(t_conv, axis=-2)
+
+  # Reshape the output
+  final_shape = [shape[i] for i in range(ndims-2)] + [filters]
+  t_max = tf.reshape(t_max, shape=final_shape)
+
+  return t_max

### 2019-06-16 models/data_loader.py

@@ -1,0 +1,505 @@
+import re
+import functools
+import json
+import math
+import random
+import tensorflow as tf
+from pathlib import Path
+
+def get_sentences(f): 
+  filename = f.parts[-1] 
+  with f.open('r', encoding="utf-8") as f:
+    sentences = f.read().strip().split('\n\n')
+    sentences = [[t.split() for t in s.split('\n')] for s in sentences if len(s) > 0] 
+    return sentences
+
+def split_array(arr, separator_fn):
+  arrays = [[]]
+  for i, el in enumerate(arr):
+    if separator_fn(el):
+      arrays.append([])
+    else:
+      arrays[-1].append(el)
+  return [a for a in arrays if len(a) > 0]
+
+def join_arrays(arr, separator):
+  res = []
+  for i, el in enumerate(arr):
+    res += el + [separator]
+  return res
+
+def pad_array(arr, padding, max_len):
+  return arr + [padding] * (max_len - len(arr))
+
+def prepare_dataset(sentences, mode='sentences', label_col=3, feature_cols=[], training=False):
+  sentences = [
+    [
+      [ t[0], t[label_col], [ t[f] for f in feature_cols if len(t) > f ] ]
+      for t in s
+    ]
+    for s in sentences
+  ] 
+
+  if mode == 'sentences':
+    sentences = [s for s in sentences if s[0][0] != '-DOCSTART-']
+    return sentences
+
+  else:
+    separator_fn = lambda el : el[0][0] == '-DOCSTART-'
+    documents = split_array(sentences, separator_fn)
+
+    # Shuffle sentences inside document.
+    if training:
+      for i, d in enumerate(documents):
+        random.shuffle(documents[i])
+ 
+    eos = ['EOS', 'O', ['0'] * len(feature_cols)]
+    documents = [join_arrays(d, eos) for d in documents]
+
+    if mode == 'documents':
+      return documents
+
+    elif mode == 'batch':
+      n = 10
+      sentences = []
+      for d in documents:
+        cur_sentence = []
+        eos_count = 0 
+        for t in d:
+          if t[0] == 'EOS':
+            eos_count += 1
+
+          if eos_count > n:
+            eos_count = 0
+            sentences.append(cur_sentence)
+            cur_sentence = []
+          else:
+            cur_sentence.append(t)
+
+        if len(cur_sentence) > 0:
+          sentences.append(cur_sentence)
+      return sentences
+
+    else: 
+      raise Exception('Invalid mode.') 
+
+class DL:
[…]

### 2019-06-16 models/estimator.py

@@ -1,0 +1,211 @@
+import numpy as np
+import re
+import json 
+import functools
+from pathlib import Path
+import tensorflow as tf
+from model.cnn import masked_conv1d_and_max
+import numpy as np
+from IPython.display import clear_output, display
+import time
+from model.data_loader import DL, NerOnHtml, Conll2003, Conll2003Person
+from model.metrics import evaluate
+from model.model import SequenceModel
+
+params = None
+
+class Estimator:
+  def __init__(self):
+    self.params = {
+      'epochs': 5,
+      'current_epoch': 0,
+      'best_f1': 0,
+    }
+    self.learning_rate = 0.001
+    self.dataset = None
+
+  def set_dataset_params(self, new_params):
+    self.params.update(new_params)
+
+  def load_params_from_file(self, json_file):
+    with Path(json_file).open('r') as f:
+      data = json.load(f)
+      self.params.update(data)
+  
+    print('===Model parameters===')
+    print(json.dumps(self.params, indent=4, sort_keys=True))
+    print('\t'.join([str(p) for p in self.params]))
+    print('\t'.join([str(self.params[p]) for p in self.params]))
+
+  def restore(self, sess, restore_params=False):
+    model_base = './checkpoints/model.ckpt'
+    saver = tf.train.import_meta_graph(model_base + '.meta')
+    sess.run([tf.tables_initializer()])
+    saver.restore(sess, model_base)
+
+    if restore_params:
+      with Path(model_base + '.params.json').open('r') as f:
+        self.params = json.load(f)
+      print('Restoring best model from epoch %s' % (self.params['current_epoch']))
+    print('Restoring model...')
+
+    return saver
+  
+  def save_model(self, sess, saver):
+    model_base = './checkpoints/model.ckpt'
+    save_path = saver.save(sess, model_base)
+
+    with Path(model_base + '.params.json').open('w') as f:
+      json.dump(self.params, f, indent=4, sort_keys=True)
+
+    print("Model saved in path: %s" % save_path) 
+
+  def get_dict(self, features, labels, train):
+    ((words, nwords), (chars, nchars)), (f_vector, html, (css_chars, css_lengths)) = features
+    # ((words, nwords), (chars, nchars)) = features
+    return {
+      'inputs/words:0': words,
+      'inputs/nwords:0': nwords,
[…]

### 2019-06-16 models/gazetteer_matcher.py

@@ -1,31 +1,0 @@
-#!/usr/bin/python
-# coding=UTF-8
-
-import np
-import re
-
-def is_punctuation(text):
-  return re.match("^[\,\;\:\-\"\(\)“”]$", text)
-
-def gazetteer_predict(X, T, mode='partial'):
-  Y = np.zeros((X.shape[0], X.shape[1], 3))
-
-  for i in range(X.shape[0]):
-    for j in range(X.shape[1]):
-      if T[i,j] is None:
-        continue
-
-      Y[i,j] = np.array([1, 0, 0])
-      # if is_punctuation(T[i,j]):
-      #   Y[i,j] = np.array([0, 0, 1])
-
-      # Exact.
-      if mode == 'exact':
-        if X[i,j,0] == 1:
-          Y[i,j] = np.array([0, 0, 1])
-
-      # Partial .
-      else:
-        if X[i,j,1] == 1:
-          Y[i,j] = np.array([0, 1, 0])
-  return Y      

### 2019-06-16 models/hmm.py

@@ -1,6 +1,31 @@
-import np
+import numpy as np
 import re
-from models.util import load_raw_dataset
+
+num_labels = 3
+
+def load_raw_dataset(f):
+  with open(f, 'r') as f:
+    data = f.read().strip()
+
+    sentences = data.split('\n\n')
+    sentences = [s for s in sentences if not s.startswith('-DOCSTART-')]
+    X = [[t.split(' ') for t in s.split('\n') if len(s) > 0] for s in sentences]
+    Y = []
+    T = []
+    for i, s in enumerate(X):
+      tkns, labels = [], []
+      for j, t in enumerate(s):
+        l = ['O', 'B-PER', 'I-PER'].index(t[1])
+        # l = ['O', 'B-PER', 'I-PER'].index(t[3])
+        labels.append(l)
+        tkns.append(t[0])
+        X[i][j] = [X[i][j][0]] + X[i][j][2:]
+        # X[i][j] = [X[i][j][0], str(X[i][j][0]).lower()]
+
+      Y.append(labels)
+      T.append(tkns)
+
+    return X, Y, T
 
 def is_punctuation(text):
   return re.match("^[\,\;\:\-\"\(\)“”；]$", text)
@@ -15,8 +40,8 @@ class HiddenMarkov:
 
     self.num_labels   = 3
     self.num_features = 11
+    # self.num_features = 1
     self.num_secondary_features = 2
-    # self.num_secondary_features = 5
     self.num_all_features = self.num_features + self.num_secondary_features
     self.num_states = self.num_labels ** self.time_steps
     self.transition_mat = np.ones((self.num_states, self.num_labels))
@@ -56,15 +81,11 @@ class HiddenMarkov:
 
     label_count = np.ones((self.num_labels))
     for i in range(len(Y)):
-      for j in range(50):
-        if np.sum(Y[i,j]) == 0:
-          break
-  
-        label_count += Y[i,j]
-        y = np.where(Y[i,j] == 1)[0][0]
+      for j in range(len(Y[i])):
+        label_count += Y[i][j]
+        y = Y[i][j]
   
         f = X[i][j][1:1+self.num_all_features]
-        # f = X[i][j][2:1+self.num_all_features]
         for k in range(self.num_all_features):
           if which_features[k] == 0:
             continue
@@ -106,25 +127,26 @@ class HiddenMarkov:
   def train_transitions(self, X, Y):
     for i in range(len(Y)):
[…]

### 2019-06-16 models/html_embeddings.py

@@ -1,0 +1,72 @@
+import tensorflow as tf
+from pathlib import Path
+from model.char_representations import get_char_embeddings, lstm_char_representations
+
+def get_html_embeddings(html, html_vocab_file):
+  with Path(html_vocab_file).open() as f:
+    num_html_tags = sum(1 for _ in f) + 1
+  
+  vocab_html = tf.contrib.lookup.index_table_from_file(
+    html_vocab_file, num_oov_buckets=1
+  )
+
+  html_tags = tf.slice(html, [0, 0, 0], [-1, -1, 2])
+  html_tag_ids = vocab_html.lookup(html_tags)
+  return html_tag_ids 
+
+  html_embedding_size = 50
+  v = tf.get_variable('html_embeddings', [num_html_tags + 1, html_embedding_size], tf.float32)
+  html_embeddings = tf.nn.embedding_lookup(v, html_tag_ids)
+  # timesteps = tf.shape(html_tags)[1]
+  # html_embeddings = tf.reshape(html_embeddings, [-1, timesteps, html_embedding_size*2])
+  html_embeddings = tf.reduce_sum(html_embeddings, axis=-2)
+  return html_embeddings
+
+def get_css_embeddings(html, css_chars, css_lengths, char_vocab_file, training=False):
+  with Path('data/ner_on_html/vocab.css.txt').open() as f:
+    num_css_classes = sum(1 for _ in f) + 1
+  
+  vocab_css = tf.contrib.lookup.index_table_from_file(
+    'data/ner_on_html/vocab.css.txt', num_oov_buckets=1
+  )
+
+  css_class = tf.slice(html, [0, 0, 2], [-1, -1, 1])
+  css_class_ids = vocab_css.lookup(css_class)
+  return css_class_ids
+
+def get_html_representations(html, html_vocab_file, css_chars, css_lengths, char_vocab_file, training=False):
+  html_embs = get_html_embeddings(html, html_vocab_file)
+  css_embs = get_css_embeddings(
+    html, css_chars, css_lengths,
+    char_vocab_file, training=training
+  )
+
+  html_embs = tf.concat([html_embs, css_embs], axis=-1)
+  return html_embs
+
+def get_soft_html_representations(html, html_vocab_file, css_chars, css_lengths, char_vocab_file, training=False):
+  with Path(html_vocab_file).open() as f:
+    num_html_tags = sum(1 for _ in f) + 1
+  
[…]

### 2019-06-16 models/lstm_crf.py

@@ -1,152 +1,0 @@
-import keras
-import np
-import re
-from models.util import Dataset, WordEmbeddings, evaluate, get_names, one_hot_to_labels
-from keras.models import Model
-from keras.layers import Input, Dense, Dropout, Flatten, TimeDistributed, Bidirectional, LSTM, Embedding, concatenate, Conv1D, GlobalMaxPooling1D
-from models.ChainCRF import ChainCRF, create_custom_objects
-from keras.utils import np_utils
-from keras import optimizers
-  
-class LstmCrf():
-  def __init__(
-    self, 
-    name,
-    lstm_cells=100, 
-    use_gazetteer=True, 
-    use_features=True, 
-    char_embedding_size=30,
-    num_cnn_filters=30,
-    char_lstm_size=25,
-    model_type=['lstm-crf', 'lstm-crf-cnn', 'lstm-crf-lstm', 'crf', 'maxent'][0],
-    dev_dataset=None,
-    validate_dataset=None,
-    test_dataset=None,
-  ):
-    self.name = name
-    self.lstm_cells = lstm_cells
-    self.num_cnn_filters = num_cnn_filters
-    self.char_lstm_size = char_lstm_size
-    self.model_type = model_type
-    self.dev_dataset = dev_dataset
-    self.validate_dataset = validate_dataset
-    self.test_dataset = test_dataset
-    self.use_gazetteer = use_gazetteer
-    self.use_features = use_features
-    self.num_labels = self.dev_dataset.Y.shape[2]
-
-  def create(self, word_embedding_matrix):
-    x1_shape = self.dev_dataset.X1.shape
-    x2_shape = self.dev_dataset.X2.shape
-    x3_shape = self.dev_dataset.X3.shape
-    x4_shape = self.dev_dataset.X4.shape
-
-    char_embedding_matrix = np.random.randn(128, 30)
-
-    x = Input(shape=(x1_shape[1], x1_shape[2]), dtype='int32')
-    inputs = [x]
-    
-    # Word embeddings.
-    word_emb = Embedding(
-      input_dim=word_embedding_matrix.shape[0], 
-      output_dim=word_embedding_matrix.shape[1], 
-      weights=[word_embedding_matrix], 
-      trainable=False
-    )(Flatten()(x))
-
-    # Feature embeddings.
-    shared_layer = [word_emb]
-
-    if self.use_gazetteer:
-      x2 = Input(shape=(x2_shape[1], x2_shape[2]), dtype='float32')
[…]

### 2019-06-16 models/lstm_crf_cnn.py

@@ -1,0 +1,103 @@
+import numpy as np 
+
+from six.moves import reduce
+import tensorflow as tf
+
+def model_fn(features, labels, mode, params):
+  # For serving features are a bit different
+  if isinstance(features, dict):
+    features = ((features['words'], features['nwords']),
+          (features['chars'], features['nchars']))  
+    
+  # Read vocabs and inputs
+  dropout = params['dropout']
+  (words, nwords), (chars, nchars) = features
+  training = (mode == tf.estimator.ModeKeys.TRAIN)
+  vocab_words = tf.contrib.lookup.index_table_from_file(
+    params['words'], num_oov_buckets=params['num_oov_buckets'])
+  vocab_chars = tf.contrib.lookup.index_table_from_file(
+    params['chars'], num_oov_buckets=params['num_oov_buckets'])
+  with Path(params['tags']).open() as f:
+    indices = [idx for idx, tag in enumerate(f) if tag.strip() != 'O']
+    num_tags = len(indices) + 1
+  with Path(params['chars']).open() as f:
+    num_chars = sum(1 for _ in f) + params['num_oov_buckets']
+
+  # Char Embeddings
+  char_ids = vocab_chars.lookup(chars)
+  variable = tf.get_variable(
+    'chars_embeddings', [num_chars + 1, params['dim_chars']], tf.float32)
+  char_embeddings = tf.nn.embedding_lookup(variable, char_ids)
+  char_embeddings = tf.layers.dropout(char_embeddings, rate=dropout,
+                    training=training)
+
+  # Char 1d convolution
+  weights = tf.sequence_mask(nchars)
+  char_embeddings = masked_conv1d_and_max(
+    char_embeddings, weights, params['filters'], params['kernel_size'])
+
+  # Word Embeddings
+  word_ids = vocab_words.lookup(words)
+  glove = np.load(params['glove'])['embeddings']  # np.array
+  variable = np.vstack([glove, [[0.] * params['dim']]])
+  variable = tf.Variable(variable, dtype=tf.float32, trainable=False)
+  word_embeddings = tf.nn.embedding_lookup(variable, word_ids)
+
+  # Concatenate Word and Char Embeddings
+  embeddings = tf.concat([word_embeddings, char_embeddings], axis=-1)
[…]

### 2019-06-16 models/metrics.py

@@ -1,0 +1,98 @@
+from tensorflow.python.ops.metrics_impl import _streaming_confusion_matrix
+import tensorflow as tf
+import numpy as np 
+
+def get_named_entities(tags):
+  try:
+    tags = [t.decode("utf-8") for t in tags]
+  except AttributeError:
+    pass
+
+  r = []
+  i = 0
+  while i < len(tags):
+    if tags[i] == 'O':
+      i += 1
+    else:
+      tag_type = tags[i][2:]
+      expected_tag = 'I-' + tag_type
+      start, end = i, i
+      i += 1
+      while i < len(tags):
+        if tags[i] == expected_tag:
+          end = i
+        else:
+          break
+        i += 1
+      r.append((start, end, tag_type))
+  return r
+
+def evaluate(val_predict, val_target, tokens, verbose=False):
+  correct_count, total = 0, 0
+  num_correct, num_predicted, num_expected = 0, 0, 0
+  for i in range(len(val_predict)):
+    correct_count += sum(p == t for p, t in zip(val_predict[i], val_target[i]))
+    total += len(val_target[i])
+    p_ne = get_named_entities(val_predict[i])
+    t_ne = get_named_entities(val_target[i])
+
+    num_correct   += len(set(p_ne) & set(t_ne))
+    num_predicted += len(p_ne)
+    num_expected  += len(t_ne)
+
+  precision, recall, f1, accuracy = 0, 0, 0, 0
+
+  if num_predicted > 0:
+    precision = num_correct / float(num_predicted)
+
+  if num_expected > 0:
+    recall = num_correct / float(num_expected)
+
+  if precision + recall > 0:
+    f1 = 2 * precision * recall / (precision + recall)
+
+  if total > 0:
+    accuracy = correct_count / float(total)
+
+  correct = num_correct
+  incorrect = num_predicted - num_correct
+  missed = num_expected - num_correct
+  # print('num_correct: %d' % (num_correct))
+  # print('num_expected: %d' % (num_expected))
+  # print('num_expected: %d' % (num_expected))
+
+  return {
+    'accuracy': accuracy,
+    'precision': precision,
+    'recall': recall,
+    'f1': f1,
+    'correct': correct,
+    'incorrect': incorrect,
+    'missed': missed
[…]

### 2019-06-16 models/model.py

@@ -1,0 +1,317 @@
+import math
+import numpy as np 
+import tensorflow as tf
+from pathlib import Path
+from model.char_representations import get_char_representations, get_char_embeddings
+from model.attention import attention, exact_attention, pos_embeddings, normalize, multihead_attention
+from model.word_embeddings import glove, elmo, word2vec, one_hot_embs
+from model.html_embeddings import get_html_representations, get_soft_html_representations
+
+class SequenceModel:
+  def __init__(self, params=None):
+    self.params = {
+      # Static configurations.
+      'datadir': 'data/conll2003',
+      # General configurations.
+      'lstm_size': 200,
+      'decoder': 'crf', # crf, logits.
+      'char_representation': 'cnn',
+      'word_embeddings': 'glove', # glove, elmo. TODO: bert.
+      'model': 'lstm_crf', # lstm_crf, html_attention, self_attention, transformer, crf
+      'use_features': False, 
+      'f_score_alpha': 0.5,
+    }
+    params = params if params is not None else {}
+    self.params.update(params)
+
+    self.params['words']     = str(Path(self.params['datadir'], 'vocab.words.txt'))
+    self.params['chars']     = str(Path(self.params['datadir'], 'vocab.chars.txt'))
+    self.params['tags' ]     = str(Path(self.params['datadir'], 'vocab.tags.txt'))
+    self.params['html_tags'] = str(Path(self.params['datadir'], 'vocab.htmls.txt'))
+    self.params['glove']     = str(Path(self.params['datadir'], 'glove.npz'))
+    self.params['word2vec']  = str(Path(self.params['datadir'], 'word2vec.npz'))
+
+    with Path(self.params['tags']).open() as f:
+      indices = [idx for idx, tag in enumerate(f) if tag.strip() != 'O']
+      self.num_tags = len(indices) + 1
+  
+  def dropout(self, x):
+    return tf.layers.dropout(x, rate=0.5, training=self.training)
+
+  def create_placeholders(self):
+    with tf.name_scope('inputs'):
+      self.words         = tf.placeholder(tf.string,  shape=(None, None),       name='words'       )
+      self.nwords        = tf.placeholder(tf.int32,   shape=(None,),            name='nwords'      )
+      self.chars         = tf.placeholder(tf.string,  shape=(None, None, None), name='chars'       )
[…]

### 2019-06-16 models/train_model.py

@@ -1,0 +1,191 @@
+import sys
+import time
+import np
+from optparse import OptionParser
+from keras.callbacks import Callback
+from models.util import load_raw_dataset, Dataset, WordEmbeddings, evaluate
+from models.lstm_crf import LstmCrf
+from models.gazetteer_matcher import gazetteer_predict
+from models.hmm import HiddenMarkov
+
+class Metrics(Callback):
+  def __init__(self, the_model):
+    self.max_f_measure = 0
+    self.the_model = the_model
+
+  def on_epoch_end(self, epoch, logs={}):
+    val_predict, val_targ, T = self.the_model.validate()
+    a, p, r, f1, c, i, m = evaluate(val_predict, val_targ, T)
+    
+    improved = False
+    if f1 > self.max_f_measure:
+      self.max_f_measure = f1
+      self.the_model.save()
+      improved = True
+
+    print('Epoch: %d, Loss: %f, F1: %f %s' % (epoch, logs['loss'], f1, '- IMPROVED' if improved else ''))
+ 
+start = time.time()
+
+parser = OptionParser()
+parser.add_option("-f", "--features", dest="use_features", action="store_true")
+parser.add_option("-s", "--self-train", dest="self_train", action="store_true")
+parser.add_option("-v", "--verbose", dest="verbose", action="store_true")
+parser.add_option("-d", "--dataset", dest="dataset")
+verbose = False
+
+if len(sys.argv) < 2:
+  print('Wrong number of arguments')
+
+model = sys.argv[1]
+
+def print_results(dataset, val_predict, val_targ, T):
+  a, p, r, f1, c, i, m = evaluate(val_predict, val_targ, T, verbose=verbose)
+
+  print('----------------')
+  print(dataset)
+  print('----------------')
+  print('Accuracy:', a)
+  print('Precision:', p)
+  print('Recall:', r)
+  print('F1:', f1)
+  print('Correct:', c)
+  print('Incorrect:', i)
+  print('Missed:', m)
+  print('')
+
+if not model in [
+  'partial_match',
+  'exact_match',
+  'nb',
+  'hmm-1',
+  'hmm-2',
+  'hmm-3',
+  'hmm-4',
+  'maxent',
+  'crf',
+  'lstm-crf',
+  'lstm-crf-cnn',
+  'lstm-crf-lstm',
+]:
+  print('Wrong model')
+  quit()
+
[…]

### 2019-06-16 models/util.py

@@ -1,419 +1,0 @@
-import np
-import re
-from keras.utils import np_utils
-# np.set_printoptions(suppress=True)
-
-num_labels = 3
-
-def is_punctuation(text):
-  return re.match("^[\,\;\:\-\"\(\)“”；]$", text)
-
-class WordEmbeddings():
-  def __init__(self, emb_type):
-    self.words  = []
-    self.word2Idx  = {}
-    self.matrix = None
-    self.load_embeddings(emb_type)
-
-  def load_glove(self, dimensions):
-    self.matrix = np.zeros((400002, dimensions), dtype=float)
-    with open('embeddings/glove.6B.' + str(dimensions) + 'd.txt') as f:
-      counter = 2
-      for vector in f:
-        features = vector.strip().split(' ')
-        w = features[0]
-        self.words.append(w)
-        self.word2Idx[w] = counter
-        self.matrix[counter,:] = np.array(features[1:], dtype=float)
-        counter += 1
-
-  def load_embeddings(self, emb_type):
-    if emb_type == 'glove-50':
-      self.load_glove(50)
-    elif emb_type == 'glove-100':
-      self.load_glove(100)
-    elif emb_type == 'glove-200':
-      self.load_glove(200)
-    elif emb_type == 'glove-300':
-      self.load_glove(300)
-
-def load_raw_dataset(f, max_sentence_len=50):
-  with open(f, 'r') as f:
-    data = f.read().strip()
-
-    # sentences = re.compile("-DOCSTART-.+\n\n").split(data)
-    # sentences = [s for s in sentences if len(s) > 0]
-    # X = [[t.split(' ') for t in re.compile("\n+").split(s) if not re.match("^\s+$", s)] for s in sentences]
-
-    sentences = data.split('\n\n')
-    sentences = [s for s in sentences if not s.startswith('-DOCSTART-')]
-    X = [[t.split(' ') for t in s.split('\n') if len(s) > 0] for s in sentences]
-    Y = np.zeros((len(X), max_sentence_len, num_labels))
-    T = np.ndarray(shape=(len(X), max_sentence_len), dtype=object)
-    for i, s in enumerate(X):
-      tkns, labels = [], []
-      if len(X[i]) > max_sentence_len-1:
-        X[i] = X[i][:max_sentence_len-1]
-
-      for j, t in enumerate(s[:max_sentence_len-1]):
[…]

### 2019-06-16 models/word_embeddings.py

@@ -1,0 +1,78 @@
+import tensorflow as tf
+import tensorflow_hub as hub
+import numpy as np
+from pathlib import Path
+
+# def trainable_embs(words, words_vocab_file):
+#   vocab_size = 0
+#   with Path(words_vocab_file).open() as f:
+#     indices = [idx for idx, tag in enumerate(f)]
+#     vocab_size = len(indices) + 1
+# 
+#   vocab_words = tf.contrib.lookup.index_table_from_file(
+#     words_vocab_file, num_oov_buckets=1
+#   )
+# 
+#   word_ids = vocab_words.lookup(words)
+#   variable = np.vstack([glove, [[0.] * 300]])
+#   variable = tf.Variable(variable, dtype=tf.float32, trainable=True)
+#   word_embeddings = tf.nn.embedding_lookup(variable, word_ids)
+# 
+#   return word_embeddings
+#   
+# 
+#   return tf.one_hot(word_ids, vocab_size)
+
+def one_hot_embs(words, words_vocab_file):
+  vocab_size = 0
+  with Path(words_vocab_file).open() as f:
+    indices = [idx for idx, tag in enumerate(f)]
+    vocab_size = len(indices) + 1
+
+  vocab_words = tf.contrib.lookup.index_table_from_file(
+    words_vocab_file, num_oov_buckets=1
+  )
+
+  word_ids = vocab_words.lookup(words)
+  return tf.one_hot(word_ids, vocab_size)
+
+def glove(words, words_vocab_file, glove_file):
+  vocab_words = tf.contrib.lookup.index_table_from_file(
+    words_vocab_file, num_oov_buckets=1
+  )
+
+  word_ids = vocab_words.lookup(words)
+  glove = np.load(glove_file)['embeddings']
+  print(glove.shape)
+  variable = np.vstack([glove, [[0.] * 300]])
+  variable = tf.Variable(variable, dtype=tf.float32, trainable=False)
+  word_embeddings = tf.nn.embedding_lookup(variable, word_ids)
+
+  return word_embeddings
+
+def word2vec(words, words_vocab_file, w2v_file):
+  vocab_words = tf.contrib.lookup.index_table_from_file(
+    words_vocab_file, num_oov_buckets=1
+  )
+
+  word_ids = vocab_words.lookup(words)
+  w2v = np.load(w2v_file)['embeddings']
+  variable = np.vstack([w2v, [[0.] * 300]])
[…]

### 2019-06-16 process_log.py

@@ -1,43 +1,0 @@
-import sys
-import re
-
-def print_model(attrs):
-  if len(attrs) == 0:
-    return
-
-  f  = '+F' if attrs['V-Use features'] == 'True' else ''
-  st = '+ST' if attrs['V-Self train'] == 'True' else ''
-
-  s = attrs['Model'] + f + st + '\t'
-  s += attrs['V-Precision'] + '\t'
-  s += attrs['V-Recall'] + '\t'
-  s += attrs['V-F1'] + '\t'
-  s += attrs['V-Accuracy'] + '\t'
-  s += attrs['T-Precision'] + '\t'
-  s += attrs['T-Recall'] + '\t'
-  s += attrs['T-F1'] + '\t'
-  s += attrs['T-Accuracy'] + '\t'
-  s += attrs['Time']
-  print(s)
-
-with open(sys.argv[1], 'r') as f:
-  is_validate = True
-  attrs = {}
-  lines = [l.strip() for l in f if not re.match(r'^[A-Z]', l) is None]
-  for l in lines:
-    if l.startswith('Model'):
-      print_model(attrs)
-      attrs = {'Model': l.split(': ')[1]}
-      is_validate = True
-    elif l.startswith('Validate'):
-      pass
-    elif l.startswith('Test'):
-      is_validate = False
-    elif l.startswith('Time elapsed'):
-      x = l.split(' ')
-      attrs['Time'] = x[2]
-    else:
-      x = l.split(': ')
-      mark = 'V-' if is_validate else 'T-'
-      attrs[mark + x[0]] = x[1]
-  print_model(attrs)

### 2019-06-16 run.py

@@ -1,0 +1,63 @@
+import matplotlib
+matplotlib.use('Agg')
+from model.estimator import Estimator
+import numpy as np
+import matplotlib.pyplot as plt
+import time
+import sys
+import os
+import tensorflow as tf
+from optparse import OptionParser
+from PIL import Image
+from models.hmm import HiddenMarkov, load_raw_dataset
+from pathlib import Path
+
+os.environ['TF_CPP_MIN_LOG_LEVEL'] = '3' # Disable debug logs Tensorflow.
+tf.logging.set_verbosity(tf.logging.ERROR)
+
+# parser = OptionParser()
+# parser.add_option("-j", "--json", dest="json_file")
+# parser.add_option("-s", "--small", dest="small", action="store_true")
+# (options, args) = parser.parse_args()
+# options = vars(options)
+
+if __name__ == '__main__':
+  estimator = Estimator('data')
+  estimator.train()
+  estimator.test()
+
+# if sys.argv[1] == 'hmm':
+#   start_time = time.time()
+#   timesteps = int(sys.argv[2])
+#   naive_bayes = timesteps == 0
+#   if naive_bayes:
+#     timesteps = 1
+#   
+#   print('Fitting...')
+#   # X, Y, _ = load_raw_dataset('data/conll2003_person/train')
+#   X, Y, _ = load_raw_dataset('data/ner_on_html/train')
+#   hmm = HiddenMarkov(
+#     timesteps, 
+#     naive_bayes=naive_bayes,
+#     use_gazetteer=True,
+#     use_features=True,
+#     self_train=True
+#   )
+#   hmm.fit(X, Y)
+# 
+#   for name in ['train', 'valid', 'test']:
+#     print('Predicting ' + name)
+#     # x, t, w = load_raw_dataset('data/conll2003_person/' + name)
+#     x, t, w = load_raw_dataset('data/ner_on_html/' + name)
+#     p = hmm.predict(x)
+# 
+#     t = [[['O', 'B-PER', 'I-PER'][t__] for t__ in t_] for t_ in t]
+#     p = [[['O', 'B-PER', 'I-PER'][p__] for p__ in p_] for p_ in p]
+# 
+#     with Path('results/score/{}.preds.txt'.format(name)).open('wb') as f:
+#       for words, preds, tags in zip(w, p, t):
+#         f.write(b'\n')
+#         for word, pred, tag in zip(words, preds, tags):
[…]

### 2019-06-17 models/data_loader.py
General refactoring.

@@ -83,236 +83,11 @@ def prepare_dataset(sentences, mode='sentences', label_col=3, feature_cols=[], t
     else: 
       raise Exception('Invalid mode.') 
 
-class DL:
-  __instance = None
-  def __new__(cls, *args, **kwargs):
-    if not DL.__instance:
-      DL.__instance = DL.__DataLoader(*args, **kwargs)
-    return DL.__instance 
-
-  def __getattr__(self, name):
-    return getattr(self.instance, name)
-
-  class __DataLoader:
-    def __init__(self):
-      self.params = {
-        'label_col': 3,
-        'batch_size': 1,
-        'buffer': 15000,
-        'datadir': 'data/conll2003',
-        'fulldoc': True,
-        'splitsentence': False,
-      }
-
-    def __str__(self):
-      return repr(self)
-
-    def save_params(self):
-      with Path(self.params['datadir'], 'params.json').open('w') as f:
-        json.dump(self.params, f, indent=2, sort_keys=True)
-
-    def parse_sentence(self, sentence):
-      # Encode in Bytes for Tensorflow.
-      words = [s[0] for s in sentence]
-      tags = [s[1].encode() for s in sentence]
- 
-      # Chars.
-      chars = [[c.encode() for c in w] for w in words]
-      lengths = [len(c) for c in chars]
-      chars = [pad_array(c, b'<pad>', max(lengths)) for c in chars]
-      
-      # HTML features.
-      html_features = [[f.encode() for f in s[2]] for s in sentence]
-      html_features = [pad_array(f, b'<pad>', 3) for f in html_features]
-
-      # CSS Chars.
-      css_chars = [[c.encode() for c in f[2].decode()] for f in html_features]
-      css_lengths = [len(c) for c in css_chars]
-      css_chars = [pad_array(c, b'<pad>', max(css_lengths)) for c in css_chars]
-      
-      words = [s[0].encode() for s in sentence]    
-      return ((words, len(words)), (chars, lengths), html_features, (css_chars, css_lengths)), tags
-      
-    def generator_fn(self, filename, training=False):
-      sentences = get_sentences(Path(self.params['datadir'], filename))
-
-      mode = 'sentences'
-      label_col = 3
-      feature_cols = []
-      if self.params['datadir'] == 'data/ner_on_html':
-        label_col = 1
-        feature_cols = [13, 14, 15]
-        for i, s in enumerate(sentences):
-          for j, t in enumerate(s):
[…]

### 2019-06-17 models/estimator.py

@@ -2,15 +2,15 @@ import numpy as np
 import re
 import json 
 import functools
+import time
 from pathlib import Path
 import tensorflow as tf
-from model.cnn import masked_conv1d_and_max
 import numpy as np
 from IPython.display import clear_output, display
-import time
-from model.data_loader import DL, NerOnHtml, Conll2003, Conll2003Person
-from model.metrics import evaluate
-from model.model import SequenceModel
+from models.cnn import masked_conv1d_and_max
+from models.data_loader import NerOnHtml
+from models.metrics import evaluate
+from models.model import SequenceModel
 
 params = None
 
@@ -62,7 +62,6 @@ class Estimator:
 
   def get_dict(self, features, labels, train):
     ((words, nwords), (chars, nchars)), (f_vector, html, (css_chars, css_lengths)) = features
-    # ((words, nwords), (chars, nchars)) = features
     return {
       'inputs/words:0': words,
       'inputs/nwords:0': nwords,
@@ -94,38 +93,19 @@ class Estimator:
           'output/loss:0', 
           'output/accuracy:0', 
           'output/index_to_string_Lookup:0',
-          # 'output/m_pos_tilde:0',
-          # 'output/n_pos:0',
-          # 'output/a_tilde:0',
-          # 'output/a_tilde_prev:0',
-          # 'output/masked_a:0',
-          # 'output/mask:0',
         ]
         if train:
           target.append('output/Adam')
-          # target.append('output/GradientDescent')
 
         feed_dict = self.get_dict(features, labels, train)
         r = sess.run(target, feed_dict=feed_dict)
-        # print('=============')
-        # print('loss:', r[0])
-        # print('mpos_tilde:', r[3])
-        # print('n_pos:', r[4])
-        # print('a_tilde:', r[5])
-        # print('a_tilde_prev:', r[6])
-        # print('masked_a:', r[7])
-        # print('mask:', r[8])
-        # print(words_)
- 
-        # for w, m, p in zip(words_[0], r[8][0], r[2][0]):
-        #   print(w, m, p)
   
         seqlens = nwords_.tolist()
         words += [w[:seqlens[i]] for i, w in enumerate(words_.tolist())]
         tags  += [l[:seqlens[i]] for i, l in enumerate(labels.tolist())]
         preds += [p[:seqlens[i]] for i, p in enumerate(r[2].tolist())]
 
[…]

### 2019-06-17 models/hmm.py

@@ -4,7 +4,7 @@ import re
 num_labels = 3
 
 def load_raw_dataset(f):
-  with open(f, 'r') as f:
+  with open(f, 'r', encoding="utf-8") as f:
     data = f.read().strip()
 
     sentences = data.split('\n\n')
@@ -135,18 +135,15 @@ class HiddenMarkov:
         states.pop(0) 
         states.append(y) 
   
-    print(self.transition_mat)
     # self.transition_mat /= np.expand_dims(np.sum(self.transition_mat, axis=1), axis=1)
     # self.transition_mat = np.nan_to_num(self.transition_mat)
 
     if self.naive_bayes:
       self.transition_mat = np.sum(self.transition_mat, axis=0)
       self.transition_mat /= np.sum(self.transition_mat)
-      print(self.transition_mat)
     else:
       self.transition_mat /= np.expand_dims(np.sum(self.transition_mat, axis=1), axis=1)
       self.transition_mat = np.nan_to_num(self.transition_mat)
-      print(self.transition_mat)
 
   def fit(self, X, Y):
     which_features = [0] * self.num_all_features 

### 2019-06-17 models/html_embeddings.py

@@ -1,6 +1,6 @@
 import tensorflow as tf
 from pathlib import Path
-from model.char_representations import get_char_embeddings, lstm_char_representations
+from models.char_representations import get_char_embeddings, lstm_char_representations
 
 def get_html_embeddings(html, html_vocab_file):
   with Path(html_vocab_file).open() as f:

### 2019-06-17 models/lstm_crf_cnn.py

@@ -1,103 +1,0 @@
-import numpy as np 
-
-from six.moves import reduce
-import tensorflow as tf
-
-def model_fn(features, labels, mode, params):
-  # For serving features are a bit different
-  if isinstance(features, dict):
-    features = ((features['words'], features['nwords']),
-          (features['chars'], features['nchars']))  
-    
-  # Read vocabs and inputs
-  dropout = params['dropout']
-  (words, nwords), (chars, nchars) = features
-  training = (mode == tf.estimator.ModeKeys.TRAIN)
-  vocab_words = tf.contrib.lookup.index_table_from_file(
-    params['words'], num_oov_buckets=params['num_oov_buckets'])
-  vocab_chars = tf.contrib.lookup.index_table_from_file(
-    params['chars'], num_oov_buckets=params['num_oov_buckets'])
-  with Path(params['tags']).open() as f:
-    indices = [idx for idx, tag in enumerate(f) if tag.strip() != 'O']
-    num_tags = len(indices) + 1
-  with Path(params['chars']).open() as f:
-    num_chars = sum(1 for _ in f) + params['num_oov_buckets']
-
-  # Char Embeddings
-  char_ids = vocab_chars.lookup(chars)
-  variable = tf.get_variable(
-    'chars_embeddings', [num_chars + 1, params['dim_chars']], tf.float32)
-  char_embeddings = tf.nn.embedding_lookup(variable, char_ids)
-  char_embeddings = tf.layers.dropout(char_embeddings, rate=dropout,
-                    training=training)
-
-  # Char 1d convolution
-  weights = tf.sequence_mask(nchars)
-  char_embeddings = masked_conv1d_and_max(
-    char_embeddings, weights, params['filters'], params['kernel_size'])
-
-  # Word Embeddings
-  word_ids = vocab_words.lookup(words)
-  glove = np.load(params['glove'])['embeddings']  # np.array
-  variable = np.vstack([glove, [[0.] * params['dim']]])
-  variable = tf.Variable(variable, dtype=tf.float32, trainable=False)
-  word_embeddings = tf.nn.embedding_lookup(variable, word_ids)
-
-  # Concatenate Word and Char Embeddings
-  embeddings = tf.concat([word_embeddings, char_embeddings], axis=-1)
[…]

### 2019-06-17 models/model.py

@@ -2,16 +2,16 @@ import math
 import numpy as np 
 import tensorflow as tf
 from pathlib import Path
-from model.char_representations import get_char_representations, get_char_embeddings
-from model.attention import attention, exact_attention, pos_embeddings, normalize, multihead_attention
-from model.word_embeddings import glove, elmo, word2vec, one_hot_embs
-from model.html_embeddings import get_html_representations, get_soft_html_representations
+from models.char_representations import get_char_representations, get_char_embeddings
+from models.attention import attention, exact_attention, pos_embeddings, normalize, multihead_attention
+from models.word_embeddings import glove, elmo, word2vec, one_hot_embs
+from models.html_embeddings import get_html_representations, get_soft_html_representations
 
 class SequenceModel:
   def __init__(self, params=None):
     self.params = {
       # Static configurations.
-      'datadir': 'data/conll2003',
+      'datadir': 'data',
       # General configurations.
       'lstm_size': 200,
       'decoder': 'crf', # crf, logits.

### 2019-06-17 models/train_model.py

@@ -1,191 +1,0 @@
-import sys
-import time
-import np
-from optparse import OptionParser
-from keras.callbacks import Callback
-from models.util import load_raw_dataset, Dataset, WordEmbeddings, evaluate
-from models.lstm_crf import LstmCrf
-from models.gazetteer_matcher import gazetteer_predict
-from models.hmm import HiddenMarkov
-
-class Metrics(Callback):
-  def __init__(self, the_model):
-    self.max_f_measure = 0
-    self.the_model = the_model
-
-  def on_epoch_end(self, epoch, logs={}):
-    val_predict, val_targ, T = self.the_model.validate()
-    a, p, r, f1, c, i, m = evaluate(val_predict, val_targ, T)
-    
-    improved = False
-    if f1 > self.max_f_measure:
-      self.max_f_measure = f1
-      self.the_model.save()
-      improved = True
-
-    print('Epoch: %d, Loss: %f, F1: %f %s' % (epoch, logs['loss'], f1, '- IMPROVED' if improved else ''))
- 
-start = time.time()
-
-parser = OptionParser()
-parser.add_option("-f", "--features", dest="use_features", action="store_true")
-parser.add_option("-s", "--self-train", dest="self_train", action="store_true")
-parser.add_option("-v", "--verbose", dest="verbose", action="store_true")
-parser.add_option("-d", "--dataset", dest="dataset")
-verbose = False
-
-if len(sys.argv) < 2:
-  print('Wrong number of arguments')
-
-model = sys.argv[1]
-
-def print_results(dataset, val_predict, val_targ, T):
-  a, p, r, f1, c, i, m = evaluate(val_predict, val_targ, T, verbose=verbose)
-
-  print('----------------')
-  print(dataset)
-  print('----------------')
-  print('Accuracy:', a)
-  print('Precision:', p)
-  print('Recall:', r)
-  print('F1:', f1)
-  print('Correct:', c)
-  print('Incorrect:', i)
-  print('Missed:', m)
-  print('')
-
-if not model in [
-  'partial_match',
-  'exact_match',
-  'nb',
-  'hmm-1',
-  'hmm-2',
-  'hmm-3',
-  'hmm-4',
-  'maxent',
-  'crf',
-  'lstm-crf',
-  'lstm-crf-cnn',
-  'lstm-crf-lstm',
-]:
-  print('Wrong model')
-  quit()
-
[…]

### 2019-06-17 models/word_embeddings.py

@@ -1,5 +1,4 @@
 import tensorflow as tf
-import tensorflow_hub as hub
 import numpy as np
 from pathlib import Path
 

### 2019-06-17 models/data_loader.py
General refactoring.

@@ -107,7 +107,6 @@ class NerOnHtml:
     chars = [pad_array(c, b'<pad>', max(lengths)) for c in chars]
     
     # Feature vector. 
-    # features = [[float(f) for f in s[2][:2] + s[2][4:10]] for s in sentence]
     features = [[float(f) for f in s[2][:2] + s[2][4:9]] for s in sentence]
 
     # HTML features.

### 2019-06-17 models/estimator.py

@@ -7,10 +7,9 @@ from pathlib import Path
 import tensorflow as tf
 import numpy as np
 from IPython.display import clear_output, display
-from models.cnn import masked_conv1d_and_max
 from models.data_loader import NerOnHtml
-from models.metrics import evaluate
 from models.model import SequenceModel
+from models.metrics import evaluate
 
 params = None
 
@@ -24,7 +23,7 @@ class Estimator:
     self.learning_rate = 0.001
     self.dataset = None
 
-  def set_dataset_params(self, new_params):
+  def set_params(self, new_params):
     self.params.update(new_params)
 
   def load_params_from_file(self, json_file):
@@ -149,8 +148,8 @@ class Estimator:
       for name in ['train', 'valid', 'test']:
         _, (p, t, w) = self.run_epoch(sess, name)
   
-        Path('results/score').mkdir(parents=True, exist_ok=True)
-        with Path('results/score/{}.preds.txt'.format(name)).open('wb') as f:
+        Path('results').mkdir(parents=True, exist_ok=True)
+        with Path('results/{}.preds.txt'.format(name)).open('wb') as f:
           for words, preds, tags in zip(w, p, t):
             f.write(b'\n\n')
             for word, pred, tag in zip(words, preds, tags):

### 2019-06-17 models/hmm.py

@@ -31,12 +31,11 @@ def is_punctuation(text):
   return re.match("^[\,\;\:\-\"\(\)“”；]$", text)
 
 class HiddenMarkov:
-  def __init__(self, timesteps, naive_bayes=False, use_gazetteer=True, use_features=True, self_train=False):
-    self.time_steps   = timesteps
-    self.use_gazetteer = use_gazetteer
+  def __init__(self, timesteps, use_features=True, self_train=False):
+    self.naive_bayes = timesteps == 0
+    self.time_steps = 1 if (timesteps == 0) else timesteps
     self.use_features = use_features
     self.do_self_train = self_train
-    self.naive_bayes = naive_bayes
 
     self.num_labels   = 3
     self.num_features = 11

### 2019-06-17 models/metrics.py

@@ -57,9 +57,6 @@ def evaluate(val_predict, val_target, tokens, verbose=False):
   correct = num_correct
   incorrect = num_predicted - num_correct
   missed = num_expected - num_correct
-  # print('num_correct: %d' % (num_correct))
-  # print('num_expected: %d' % (num_expected))
-  # print('num_expected: %d' % (num_expected))
 
   return {
     'accuracy': accuracy,
@@ -70,29 +67,3 @@ def evaluate(val_predict, val_target, tokens, verbose=False):
     'incorrect': incorrect,
     'missed': missed
   }
-
-# MAX_TOKEN_LENGTH = 10
-# MINIBATCH_SIZE = 10
-# DATADIR = 'data/conll2003'
-# LABEL_COL = 3
-# 
-# # Params
-# params = {
-#   'dim_chars': 100,
-#   'dim': 300,
-#   'dropout': 0.5,
-#   'num_oov_buckets': 1,
-#   'epochs': 25,
-#   'batch_size': 20,
-#   'buffer': 15000,
-#   'filters': 50,
-#   'kernel_size': 3,
-#   'lstm_size': 100,
-#   'words': str(Path(DATADIR, 'vocab.words.txt')),
-#   'chars': str(Path(DATADIR, 'vocab.chars.txt')),
-#   'tags': str(Path(DATADIR, 'vocab.tags.txt')),
-#   'glove': str(Path(DATADIR, 'glove.npz')),
-#   'fulldoc': False
-# }
-# 
-# DL().set_params(params)

### 2019-06-17 models/model.py

@@ -17,7 +17,7 @@ class SequenceModel:
       'decoder': 'crf', # crf, logits.
       'char_representation': 'cnn',
       'word_embeddings': 'glove', # glove, elmo. TODO: bert.
-      'model': 'lstm_crf', # lstm_crf, html_attention, self_attention, transformer, crf
+      'model': 'bi_lstm_crf', # bi_lstm_crf, html_attention, self_attention, transformer, crf
       'use_features': False, 
       'f_score_alpha': 0.5,
     }
@@ -44,7 +44,6 @@ class SequenceModel:
       self.nwords        = tf.placeholder(tf.int32,   shape=(None,),            name='nwords'      )
       self.chars         = tf.placeholder(tf.string,  shape=(None, None, None), name='chars'       )
       self.nchars        = tf.placeholder(tf.int32,   shape=(None, None),       name='nchars'      )
-      # self.features      = tf.placeholder(tf.float32, shape=(None, None, 4),    name='features'    )
       self.features      = tf.placeholder(tf.float32, shape=(None, None, 7),    name='features'    )
       self.html          = tf.placeholder(tf.string,  shape=(None, None, None), name='html'        )
       self.css_chars     = tf.placeholder(tf.string,  shape=(None, None, None), name='css_chars'   )
@@ -114,23 +113,11 @@ class SequenceModel:
       correct = tf.equal(tf.to_int64(pred_ids), tags)
       accuracy = tf.reduce_mean(tf.cast(correct, tf.float32), name='accuracy')
       train_step = tf.train.AdamOptimizer(learning_rate=self.learning_rate).minimize(loss)
-      # train_step = tf.train.GradientDescentOptimizer(learning_rate=self.learning_rate).minimize(loss)
 
       reverse_vocab_tags = tf.contrib.lookup.index_to_string_table_from_file(
         self.params['tags']
       )
       pred_strings = reverse_vocab_tags.lookup(tf.to_int64(pred_ids))  
-
-  def maxent(self, use_features=False):
-    word_embs = one_hot_embs(self.words, self.params['words'])
-
-    # embs = [word_embs]
-
-    # if use_features: 
-    #   embs.append(self.features)
-    # embs = tf.concat(embs, axis=-1)
-
-    return tf.layers.dense(word_embs, 100)
 
   def crf(self, word_embs='glove', char_embs='cnn', use_features=False):
     if word_embs == 'elmo':
@@ -145,13 +132,6 @@ class SequenceModel:
[…]

### 2019-06-17 models/tokenizer.py

@@ -1,0 +1,366 @@
+#!/usr/bin/python
+# coding=UTF-8
+
+import sys
+import re
+from math import log
+from bs4 import BeautifulSoup, Tag
+from bs4.element import NavigableString
+
+def remove_accents(tkn):
+  text = tkn.strip().lower()
+
+  special_chars = "ÀÁÂÃÄÅÆÇÈÉÊËÌÍİÎÏÐÑÒÓÔÕÖĞ×ØÙÚÛÜÝÞßàáâãäåæçèéêëìíîïðñòóôõö÷øùúûüýþÿšŽčžŠšČłńężśćŞ"
+  chars         = "aaaaaaeceeeeiiiiidnooooogxouuuuypsaaaaaaeceeeeiiiionooooooouuuuypyszczssclnezscs"
+
+  new_text = ""
+  for c in text:
+    index = special_chars.find(c)
+    if index != -1:
+      new_text += chars[index]
+    else:
+      new_text += c
+
+  return new_text 
+
+def is_punctuation(text):
+  return re.match("^[\,\;\:\-\"\(\)“”；]$", text)
+
+def tokenize_text(text):
+  tkns = re.compile("(\s+|[\,\;\:\-\"\(\)“”；])").split(text)
+  return [t for t in tkns if re.compile("\s+").match(t) is None and len(t) > 0] 
+
+class HtmlToken():
+  def __init__(self, tkn, element):
+    self.tkn = tkn
+    self.element = element
+    self.features = []
+    self.bio_tag = 'O'
+    self.set_features()
+
+  def is_punctuation(self):
+    return 1 if re.match("^[\,\;\:\-\"\(\)“”；]$", self.tkn) else 0
+
+  def is_email(self):
+    return 1 if re.match('\S+@\S+(\.\S+)+', self.tkn) else 0
+
+  def is_url(self):
+    regex = 'http[s]?://(?:[a-zA-Z]|[0-9]|[$-_@.&+]|[!*\(\),]|(?:%[0-9a-fA-F][0-9a-fA-F]))+'
+    return 1 if re.match(regex, self.tkn) else 0
+
+  def is_number(self):
+    return 1 if any(c.isdigit() for c in self.tkn) else 0
+
+  def is_capitalized(self):
+    if len(self.tkn) > 0:
+      return 1 if self.tkn[0].isupper() else 0
+    return 0
+
[…]

### 2019-06-17 models/word_embeddings.py

@@ -2,26 +2,6 @@ import tensorflow as tf
 import numpy as np
 from pathlib import Path
 
-# def trainable_embs(words, words_vocab_file):
-#   vocab_size = 0
-#   with Path(words_vocab_file).open() as f:
-#     indices = [idx for idx, tag in enumerate(f)]
-#     vocab_size = len(indices) + 1
-# 
-#   vocab_words = tf.contrib.lookup.index_table_from_file(
-#     words_vocab_file, num_oov_buckets=1
-#   )
-# 
-#   word_ids = vocab_words.lookup(words)
-#   variable = np.vstack([glove, [[0.] * 300]])
-#   variable = tf.Variable(variable, dtype=tf.float32, trainable=True)
-#   word_embeddings = tf.nn.embedding_lookup(variable, word_ids)
-# 
-#   return word_embeddings
-#   
-# 
-#   return tf.one_hot(word_ids, vocab_size)
-
 def one_hot_embs(words, words_vocab_file):
   vocab_size = 0
   with Path(words_vocab_file).open() as f:
@@ -42,36 +22,8 @@ def glove(words, words_vocab_file, glove_file):
 
   word_ids = vocab_words.lookup(words)
   glove = np.load(glove_file)['embeddings']
-  print(glove.shape)
   variable = np.vstack([glove, [[0.] * 300]])
   variable = tf.Variable(variable, dtype=tf.float32, trainable=False)
   word_embeddings = tf.nn.embedding_lookup(variable, word_ids)
-
-  return word_embeddings
-
-def word2vec(words, words_vocab_file, w2v_file):
-  vocab_words = tf.contrib.lookup.index_table_from_file(
-    words_vocab_file, num_oov_buckets=1
-  )
-
-  word_ids = vocab_words.lookup(words)
-  w2v = np.load(w2v_file)['embeddings']
-  variable = np.vstack([w2v, [[0.] * 300]])
-  variable = tf.Variable(variable, dtype=tf.float32, trainable=False)
-  word_embeddings = tf.nn.embedding_lookup(variable, word_ids)
-
-  return word_embeddings
-
-def elmo(words, nwords):
-  elmo = hub.Module("https://tfhub.dev/google/elmo/2", trainable=False)
-  
-  word_embeddings = elmo(
-    inputs={
-      "tokens": words,
-      "sequence_len": nwords
-    },
-    signature="tokens",
-    as_dict=True
-  )["elmo"]
 
   return word_embeddings

### 2019-06-17 run.py

@@ -1,63 +1,0 @@
-import matplotlib
-matplotlib.use('Agg')
-from model.estimator import Estimator
-import numpy as np
-import matplotlib.pyplot as plt
-import time
-import sys
-import os
-import tensorflow as tf
-from optparse import OptionParser
-from PIL import Image
-from models.hmm import HiddenMarkov, load_raw_dataset
-from pathlib import Path
-
-os.environ['TF_CPP_MIN_LOG_LEVEL'] = '3' # Disable debug logs Tensorflow.
-tf.logging.set_verbosity(tf.logging.ERROR)
-
-# parser = OptionParser()
-# parser.add_option("-j", "--json", dest="json_file")
-# parser.add_option("-s", "--small", dest="small", action="store_true")
-# (options, args) = parser.parse_args()
-# options = vars(options)
-
-if __name__ == '__main__':
-  estimator = Estimator('data')
-  estimator.train()
-  estimator.test()
-
-# if sys.argv[1] == 'hmm':
-#   start_time = time.time()
-#   timesteps = int(sys.argv[2])
-#   naive_bayes = timesteps == 0
-#   if naive_bayes:
-#     timesteps = 1
-#   
-#   print('Fitting...')
-#   # X, Y, _ = load_raw_dataset('data/conll2003_person/train')
-#   X, Y, _ = load_raw_dataset('data/ner_on_html/train')
-#   hmm = HiddenMarkov(
-#     timesteps, 
-#     naive_bayes=naive_bayes,
-#     use_gazetteer=True,
-#     use_features=True,
-#     self_train=True
-#   )
-#   hmm.fit(X, Y)
-# 
-#   for name in ['train', 'valid', 'test']:
-#     print('Predicting ' + name)
-#     # x, t, w = load_raw_dataset('data/conll2003_person/' + name)
-#     x, t, w = load_raw_dataset('data/ner_on_html/' + name)
-#     p = hmm.predict(x)
-# 
-#     t = [[['O', 'B-PER', 'I-PER'][t__] for t__ in t_] for t_ in t]
-#     p = [[['O', 'B-PER', 'I-PER'][p__] for p__ in p_] for p_ in p]
-# 
-#     with Path('results/score/{}.preds.txt'.format(name)).open('wb') as f:
-#       for words, preds, tags in zip(w, p, t):
-#         f.write(b'\n')
-#         for word, pred, tag in zip(words, preds, tags):
[…]

### 2019-06-17 util/html_segmenter.py

@@ -1,0 +1,355 @@
+#!/usr/bin/python
+# coding=UTF-8
+
+import sys
+import re
+from math import log
+from bs4 import BeautifulSoup, Tag
+from bs4.element import NavigableString
+
+def remove_accents(tkn):
+  text = tkn.strip().lower()
+
+  special_chars = "ÀÁÂÃÄÅÆÇÈÉÊËÌÍİÎÏÐÑÒÓÔÕÖĞ×ØÙÚÛÜÝÞßàáâãäåæçèéêëìíîïðñòóôõö÷øùúûüýþÿšŽčžŠšČłńężśćŞ"
+  chars         = "aaaaaaeceeeeiiiiidnooooogxouuuuypsaaaaaaeceeeeiiiionooooooouuuuypyszczssclnezscs"
+
+  new_text = ""
+  for c in text:
+    index = special_chars.find(c)
+    if index != -1:
+      new_text += chars[index]
+    else:
+      new_text += c
+
+  return new_text 
+
+def is_punctuation(text):
+  return re.match("^[\,\;\:\-\"\(\)“”；]$", text)
+
+def tokenize_text(text):
+  tkns = re.compile("(\s+|[\,\;\:\-\"\(\)“”；])").split(text)
+  return [t for t in tkns if re.compile("\s+").match(t) is None and len(t) > 0] 
+
+class HtmlToken():
+  def __init__(self, tkn, element):
+    self.tkn = tkn
+    self.element = element
+    self.features = []
+    self.bio_tag = 'O'
+    self.set_features()
+
+  def is_punctuation(self):
+    return 1 if re.match("^[\,\;\:\-\"\(\)“”；]$", self.tkn) else 0
+
+  def is_email(self):
+    return 1 if re.match('\S+@\S+(\.\S+)+', self.tkn) else 0
+
+  def is_url(self):
+    regex = 'http[s]?://(?:[a-zA-Z]|[0-9]|[$-_@.&+]|[!*\(\),]|(?:%[0-9a-fA-F][0-9a-fA-F]))+'
+    return 1 if re.match(regex, self.tkn) else 0
+
+  def is_number(self):
+    return 1 if any(c.isdigit() for c in self.tkn) else 0
+
+  def is_capitalized(self):
+    if len(self.tkn) > 0:
+      return 1 if self.tkn[0].isupper() else 0
+    return 0
+
[…]
